### 2024-07-31 manuscript/main.tex
local manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% This is a (brief) model paper using the achemso class
%% The document class accepts keyval options, which should include
%% the target journal and optionally the manuscript type. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal=jacsat,manuscript=article]{achemso}
\usepackage{multicol}
\usepackage{graphicx}% Include figure files
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{pgffor}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{listings}
\lstset{language=Python}
\usepackage{rotating} % Rotating table
\usepackage{caption}
\usepackage{subcaption}

\usepackage{color}
\usepackage{dcolumn} % decimal align in tables
\usepackage{bm} % bold math
\usepackage{graphicx}
\usepackage{multirow} % for table cells to span rows
\usepackage{pifont} % for checkmarks
\usepackage{epsfig}
\usepackage{amsmath} % matrix
% \usepackage{subfigure}
\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{natbib}
\usepackage{gensymb}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11.0in}
\usepackage{rotating}
\usepackage{threeparttable}
\usepackage{comment}
%for corrections
\usepackage[normalem]{ulem}
% \usepackage{xr-hyper}
\usepackage[hidelinks]{hyperref} % allows hyperlinking for references
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later. Do NOT use any
%% packages which require e-TeX (for example etoolbox): the e-TeX
%% extensions are not currently available on the ACS conversion
%% servers.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\usepackage{xcolor}
% \usepackage{xr-hyper}
\usepackage{xr-hyper}
\usepackage{xr}

\usepackage[hidelinks]{hyperref} % allows hyperlinking for references

% \usepackage{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools,physics}

\usepackage{subcaption}
\usepackage{caption}
% \usepackage{titling}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If issues arise when submitting your manuscript, you may want to
%% un-comment the next line.  This provides information on the
%% version of every file you have used.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\listfiles

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional macros here.  Please use \newcommand* where
%% possible, and avoid layout-changing macros (which are not used
%% when typesetting).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
% \newtheorem{example}[theorem]{Example}
\newtheorem{example}{Example}[section]
\newtheorem{remark}{Remark}

% Add line numbers, as requested by Nature
\usepackage{lineno}
% \linenumbers

\newcommand*\mycommand[1]{\texttt{\emph{#1}}}
\newcommand{\noteg}[1]{\textcolor{red}{({Grier: #1})}}
\newcommand{\notek}[1]{\textcolor{darkspringgreen}{({Kostas: #1})}}

%%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
% (from an answer by cyberSingularity at http://tex.stackexchange.com/a/69832/226)
%%%

\usepackage{xcite}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----Helper code for dealing with external references----
% (by cyberSingularity at http://tex.stackexchange.com/a/69832/226)

\usepackage{xr}
\makeatletter

\newcommand*{\addFileDependency}[1]{% argument=file name and extension
\typeout{(#1)}% latexmk will find this if $recorder=0
% however, in that case, it will ignore #1 if it is a .aux or 
% .pdf file etc and it exists! If it doesn't exist, it will appear 
% in the list of dependents regardless)
%
% Write the following if you want it to appear in \listfiles 
% --- although not really necessary and latexmk doesn't use this
%
\@addtofilelist{#1}
%
% latexmk will find this message if #1 doesn't exist (yet)
\IfFileExists{#1}{}{\typeout{No file #1.}}
}\makeatother

\newcommand*{\myexternaldocument}[1]{%
\externaldocument{#1}%
\addFileDependency{#1.tex}%
\addFileDependency{#1.aux}%
}
%------------End of helper code--------------

% put all the external documents here!
\myexternaldocument{SI}
\newcommand{\siref}[1]{\ref{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Grier M. Jones}
\affiliation[UTSG ECE]{
The Edward S. Rogers Sr. Department of Electrical and Computer Engineering, 
University of Toronto, 
10 Kings College Road, Toronto, Ontario, 
Canada M5S 3G4}
\alsoaffiliation[UTM CHEM]{
Department of Chemical and Physical Sciences, 
University of Toronto Mississauga, 
3359 Mississauga Road, Mississauga, Ontario, 
Canada L5L 1C6}

\author{Nick Taylor}
\affiliation[UTSG ECE]{
The Edward S. Rogers Sr. Department of Electrical and Computer Engineering, 
University of Toronto, 
10 Kings College Road, Toronto, Ontario, 
Canada M5S 3G4}

\author{Viki Kumar Prasad}
\affiliation[UTSG ECE]{
The Edward S. Rogers Sr. Department of Electrical and Computer Engineering, 
University of Toronto, 
10 Kings College Road, Toronto, Ontario, 
Canada M5S 3G4}
\alsoaffiliation[UTM CHEM]{
Department of Chemical and Physical Sciences, 
University of Toronto Mississauga, 
3359 Mississauga Road, Mississauga, Ontario, 
Canada L5L 1C6}

\author{Ulrich Fekl}
\affiliation[UTM CHEM]{
Department of Chemical and Physical Sciences, 
University of Toronto Mississauga, 
3359 Mississauga Road, Mississauga, Ontario, 
Canada L5L 1C6}
\email{ulrich.fekl@utoronto.ca}

\author{Hans-Arno Jacobsen}
\affiliation[UTSG ECE]{
The Edward S. Rogers Sr. Department of Electrical and Computer Engineering, 
University of Toronto, 
10 Kings College Road, Toronto, Ontario, 
Canada M5S 3G4}
\email{jacobsen@eecg.toronto.edu}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{}
\keywords{American Chemical Society, \LaTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The manuscript does not need to include \maketitle, which is
%% executed automatically.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\R}{\mathbb{R}}

\begin{document}

\section{Abstract}
The rapid growth of quantum computing has seen a rise in the development of applicable near-term quantum algorithms. A promising candidate to run on current noisy intermediate-scale quantum (NISQ) hardware is quantum machine learning (QML). Parameterized quantum circuits can be learned as models in a hybrid classical-quantum approach. It has been shown that QML models may need less training data to generalize compared to classical methods. Although QML has been explored largely within classification tasks, regression tasks have received much less attention. Existing studies have only utilized few qubits and lack relevant practical applications. We will discuss our work on the development and comparisons of QML models for highly desired prediction of chemical properties such as bond dissociation energies and barrier height energies. Our work investigates the trainability, expressibility, and generalization capability of various quantum models for the purpose of regression of molecular properties. Our work also provides a benchmark against classical machine learning models and implications of using error mitigation techniques for QML. \par

\newpage
\section{Introduction}
\cite{prasad_applications_2024}
\cite{suzuki_predicting_2020}
\cite{mitarai_quantum_2018}
\cite{sim_expressibility_2019}
\cite{hatakeyama-sato_quantum_2023}
\cite{krenn_artificial_2023}
\cite{benedetti_parameterized_2019}
\cite{biamonte_quantum_2017}

As current quantum hardware grows, much attention is brought to find applicable uses for the potentially powerful new technology while it continues to grow. Current research in the areas of developing quantum algorithms for use with current noisy intermediate-scale quantum (NISQ) hardware lays the foundation for understanding and applying quantum computing. These near-term algorithms have seen a wide deployment across many areas of science and technology as the field grows. Computational chemistry is a natural such candidate for quantum computing applications due to the quantum nature of many problems in the field. An especially important problem is that of calculating the bond separation energies of (molecules?). Efficient and accurate predictions of these values can aid research in material science and drug discovery.\par

One of the most promising near-term applications of quantum computing within any field has been quantum machine learning (QML). The advantages of QML comes largely from its ability to be readily deployed on quantum computers with few qubits, and its potential to speedup problems with minimal loss of accuracy. The number of qubits needed for a QML model is determined primarily by the number of features in the dataset. As there exist data science techniques developed in the realm of classical machine learning to reduce feature spaces, they can be adopted over to reduce problems to a suitable number of qubits. Further, since QML only needs to train once, it has potential to perform faster when compared to other current NISQ algorithms such as the variational quantum eigensolver, which needs to be trained separately for each problem. \par

Quantum machine learning has been widely applied to classification tasks with much success. However, little research has been done to understand its capabilities for regression. Previous works have set important groundwork to the understanding of QML for regression by theoretically formulating upper bounds for the generalization error. Most notably, this research suggests that with an efficiently implemented QML model can achieve good generalizability with modest training data sizes.  This highlights a potential for QML models to outperform and out-generalize classical models. Further understanding and verification of this, however, requires numerical validation and demonstration, and while some experimental work has been done, it remains limited to few qubits with little practical application.\par

Our work expands on the current knowledge base by providing a comprehensive exploration of QML for regression. Specfically, we will by applying QML to the problem of calculating bond dissociation enthalpies of various molecules. This demonstrates 
a practical application of regression in QML with many applications. The efficient and accurate prediction of these chemical properties can aid research in material science and drug discovery with far reaching implications. Our work serves to benchmark QML and test its capabilities within this context. \par

\section{Methods}
Quantum machine learning is a hybrid classical-quantum approach utilizing parameterized quantum circuits. Typical hybrid algorithms consist of shallow circuit depth of one qubit rotations and two qubit entangling gates. In the context of machine learning, we can subdivide our circuit into three components: the encoder, the variational circuit, and the act of measuring to estimate predictions. The encoder takes our $n$-dimensional data $\bm x \in \R^n$ and encodes it into a unitary feature map $U(\bm x)$ in our working Hilbert Space. This unitary acts on our initialized state $\ket{0}^{\otimes n'}$ to produce the state $U(\bm x) \ket{0}^{\otimes n'}$. It is usual to take $n' = n$ and for each feature $x_i$ to correspond to a qubit. With $n < n'$, features can be repeated across the qubits present in the system. Further elaboration will be discussed with specific encoding circuits. After the encoder produces the state $U(\bm x)\ket{0}^{\otimes n}$, we then tune the state with a parameterized unitary $U(\bm \theta)$ to transform the state into a meaningful prediction. Finally, some configuration of qubits are measured to produce expectation values $\hat y_k$ for our data labels $y_i$ which we then use to minimize a loss function. An obstacle in creating quantum models is there is no way to determine the best encoding or variational circuit for the problem. As such, this paper explores many different encoding and variational circuits. \par

\subsection{Encoder Circuit}
Representation of the data in any machine learning context is a crucial factor in its success. In a classical sense, this can be thought of as generating features and selecting the appropriate features to input into your model. In the quantum context, however, there is the additional question of how to translate the data into the Hilbert space. Different proposed  methods include angle encoding, and amplitude encoding. Following the work done by Suzuki and Katouda, we explore three base encoders composed together with entangling operations. Additionally, we explore the  IQP encoding as given in PennyLane. \par

We composed circuits out of primary rotation blocks and entangling blocks. These rotation blocks include the one proposed by Mitrai et al.\cite{mitarai_quantum_2018}, a single angle rotation, and a double rotation encoder:
\begin{align}
    U_{A1} &= \prod_{i=1}^n R^Y_i(x_i) \\
    U_{A2} &= \prod_{i=1}^n R^Y_i(x_i) R^Z_i(x_i) \\
    U_{M}  &= \prod_{i=1}^n R^Z_i(\arccos x_i^2) R^Y_i(\arcsin x_i^2)
\end{align}
Where $R^j_i$ is a rotation about the $j$ axis on qubit $i$. It's clear to see that this method of encoding imposes a restriction on the number of features to the number of qubits. With this encoding method, it is possible to use more features than qubits and to re-encode the features along the remaining qubits. Then, to compose these encoders together we use entangling circuits that entangle adjacent qubits using either CNOT or CZ entangling operations. These encoding circuits can be seen presented in Figure \ref{fig: idk circuits or something}.

\subsection{Variational Circuit}
After encoding the data, we have a quantum circuit in a state $U_{\text{enc}}(\bm x)\ket{0}^{\otimes n}$. We need to act on this state with a unitary that has parameters which can be tuned in our machine learning model. Choosing this circuit ansatz can greatly dictate the performance of a given model. Model performance can be greatly influenced by the variational circuit chosen as well as the depth of the circuit as we will later show. It is not obvious which circuit we should pick for our given problem, especially given that our algorithm is not physically motivated like other popular parameterized quantum circuit algorithms. We have gathered a list of 12 variational circuit blocks from previous works and libraries which we will then benchmark for our particular problem. These circuits each can be decomposed into individual rotation gates and two-qubit entangling gates. \par
After our variational circuit acts on our state we have the state:
\begin{align}
    \ket\psi &= U_{\text{var}}(\bm\theta)U_{\text{enc}}(\bm x)\ket{0}^{\otimes n} \label{eq: psi}
\end{align}
where $\bm \theta$ is our parameter vector to be tuned in learning. We can further modify this state; by repeating variational circuit blocks we create a more rich and complex model with a better ability to explore the Hilbert space. This would give us the state:
\begin{align}
    \ket\psi &= U_{\text{var}}(\bm\phi)U_{\text{var}}(\bm\theta)U_{\text{enc}}(\bm x)\ket{0}^{\otimes n} \label{eq: layers}
\end{align}
However, as we are interested in NISQ applications, it should be noted that increasing layer depths creates decoherence in quantum devices. Additionally, we can use the idea of data re-uploading to create redundancies in the encoding of the model to explore a richer feature space. 
\begin{align}
    \ket\psi &= U_{\text{var}}(\bm\phi)U_{\text{enc}}(\bm x)U_{\text{var}}(\bm\theta)U_{\text{enc}}(\bm x)\ket{0}^{\otimes n} \label{eq: re-up}
\end{align}
This paper uses and compares both the data re-uploading and increased depth approaches of creating more complicated models.

\subsection{Measurement}
After our system is in state $\ket\psi$ as given by either \eqref{eq: psi}, \eqref{eq: layers} or \eqref{eq: re-up} we can measure our system to generate a predicted value $\hat y_i$. At this point in the algorithm, any loss function can be used. In our simplest system, we measured the first qubit so that,
\begin{align}
    \hat y_i &= \langle Z_0 \rangle _\psi 
\end{align}
for a $\psi$ generated by the $k$th data point. Then, we have the loss function we are trying to minimize as,
\begin{align}
    \mathcal{L}(\bm{\hat y}) &= \sum_i^N \frac{(y_i - \hat y_i)^2}{N}
\end{align}

\subsection{Implementation}
Our work was implemented in Python using PennyLane for constructing the quantum circuits, and Qulacs as a primary backend for simulating the circuits. The optimization was implemented using the scipy.optimize module from the SciPy library. Classical models were implemented using scikit-learn while processing of the data was handled with Pandas, NumPy, and SciPy libraries.

Simulated using FakeCairo backend

\subsection{Dataset}
We trained our models using three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis (cite Jacob); and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.

For the function fitting dataset, there is only one feature per target value.
For the DDCC dataset, there are initially X features, reduced down to 5 and 16 features, respectively, using SHapley Additive exPlanation (SHAP) values.

*LIST THE INITIAL AND REDUCED FEATURES IN THE SI FOR DDCC*

For the BSE dataset, various molecular representations are explored, and we settled on using Morgan fingerprints with X parameters. 
For the feature reduction, we use PCA, as explained in Section \ref{subsubsection:BSE}.

% Make distribution plot
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=\linewidth]{images/BSE.png}
%	\caption{BSE}
%	\label{fig:BSE}
%\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/linear_train_vs_test.png}
		\caption{}
		\label{fig:linear_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/quadratic_train_vs_test.png}
		\caption{}
		\label{fig:quadratic_train_vs_test}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/sine_train_vs_test.png}
		\caption{}
		\label{fig:sine_train_vs_test}
	\end{subfigure}
	\caption{}
	\label{fig:train_vs_test}
\end{figure}

\section{Results}

\subsection{Classical Testing}

\subsubsection{Function Fitting}
We found that on average the best models for the linear function is KNN (Fig. \siref{fig:linear}),  KRR for quadratic (Fig. \siref{fig:quadratic}), and KNN for sine (Fig. \siref{fig:sine}).

\subsubsection{DDCC}

$t_{ij}^{ab}$

Dimensions reduced using SHapley Additive Explanation (SHAP) values
\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/DDCC_feature_set.png}
	\caption{DDCC feature set}
	\label{fig:DDCC_feature_set}
\end{figure}

\subsubsection{BSE}\label{subsubsection:BSE}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/Feat_redR2.png}
	\caption{Feat redR2}
	\label{fig:Feat_redR2}
\end{figure}
% Key: 
% 'ridge': Ridge(),
% 'lasso': Lasso(),
% 'elastic': ElasticNet(),
% 'knn': KNeighborsRegressor(),
% 'rfr': RandomForestRegressor(),
% 'grad': GradientBoostingRegressor(),
% 'svr': SVR(),
% 'krr': KernelRidge(),
% 'gpr': GaussianProcessRegressor()
% \begin{table}[H]
%     \begin{tabular}{||c | c c c||}
%      \hline
%      Training Set Size & Linear & Quadratic  & Sine \\ [0.5ex] 
%      \hline\hline
%      0.1 & SVR & KNN & GPR \\ 
%      \hline
%      0.3 & GPR & KRR & KRR \\
%      \hline
%      0.5 & SVR & KNN & RFR \\
%      \hline
%      0.7& GPR& Grad & RFR \\
%      \hline
%      0.8 & GPR & KRR & SVR \\ [1ex] 
%      \hline
%     \end{tabular}
%     \caption{Function testing}
%     \label{table:function_testing}
% \end{table}

\subsection{5 qubit function fitting}

Fig. \siref{fig:lin5qubits_metric}
Fig. \siref{fig:quad5qubits_metric}
Fig. \siref{fig:sine5qubits_metric}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/5qubit_function_fitting_best.png}
	\caption{REMAKE}
	\label{fig:5qubit_function_fitting_best}
\end{figure}

\subsection{16 qubit function fitting}

Fig. \siref{fig:lin16qubits_metric}
Fig. \siref{fig:quad16qubits_metric}
Fig. \siref{fig:sine16qubits_metric}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/16qubit_Linear_RUD_AL.png}
	\caption{REMAKE}
	\label{fig:16qubit_Linear_RUD_AL}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/16qubit_Quadratic_RUD_AL.png}
	\caption{REMAKE}
	\label{fig:16qubit_Quadratic_RUD_AL}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/16qubit_Sine_RUD_AL.png}
	\caption{REMAKE}
	\label{fig:16qubit_Sine_RUD_AL}
\end{figure}

The best is IQP\textunderscore Full-Pauli-CRX with 5AL and 5 RUD

Missing 0.8 quadratic

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Linear_learning_curve.png}
		\caption{}
		\label{fig:Linear_learning_curve}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Quadratic_learning_curve.png}
		\caption{}
		\label{fig:Quadratic_learning_curve}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/Sine_learning_curve.png}
		\caption{}
		\label{fig:Sine_learning_curve}
	\end{subfigure}
	\caption{Baseline denotes IQP\textunderscore Full-Pauli-CRX with 1AL and 1RUD}
	\label{fig:learning_curve}
\end{figure}

\subsection{5 qubit BSE}
Done
\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/5qubit_BSE_RUD_AL.png}
	\caption{5qubit BSE RUD AL}
	\label{fig:5qubit_BSE_RUD_AL}
\end{figure}

\subsection{16 qubit BSE}

Missing data
\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/16qubit_BSE_RUD_AL.png}
	\caption{16qubit BSE RUD AL}
	\label{fig:16qubit_BSE_RUD_AL}
\end{figure}

\subsection{Error Correction}
TREX/MITIQ ZNE LINEAR/ MITIQ ZNE Richardson

\subsubsection{Function Fitting}
Running
\subsubsection{DDCC}
Not ran yet
\subsubsection{BSE}
Not ran yet

\subsection{IBM Device}

\bibliography{achemso-demo}

\end{document}

### 2024-07-31 function-calc-test/5RUD_5AL/quadratic/0.8/quantum/Quantum.py

@@ -222,7 +222,7 @@ class QuantumRegressor:
         self.fit_count += 1
         self._save_partial_state(xk)
 
-    def _save_partial_state(self, param_vector, force=False):
+    def _save_partial_state(self, param_vector, force=True):
         # saves every call to a bin file able to be loaded later by calling fit with load_state set to filename
         interval = self.callback_interval
         if interval is None:

### 2024-08-01 manuscript/main.tex
Thu Aug  1 09:47:31 AM EDT 2024

@@
 \subsection{Dataset}
-We trained our models using three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis (cite Jacob); and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
+We trained our models using three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
 
 For the function fitting dataset, there is only one feature per target value.
-For the DDCC dataset, there are initially X features, reduced down to 5 and 16 features, respectively, using SHapley Additive exPlanation (SHAP) values.
+For the DDCC dataset, there are initially X features, reduced down to 5 and 16 features, respectively, using SHapley Additive exPlanation (SHAP) values.\cite{lundberg_unified_2017}
 
-*LIST THE INITIAL AND REDUCED FEATURES IN THE SI FOR DDCC*
+\begin{equation}
+	t^{ab}_{ij(\text{MP2})} = \frac{\mel{ij}{}{ab}}{\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}}
+	\label{eq:MP2_t2}
+\end{equation}
+
+For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$), binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
 

### 2024-09-24 manuscript/main.tex
kill list + 5BSE
Clean up + New plan

@@
 \par
+
+\newpage
+\textcolor{red}{Reorganize}
+\begin{itemize}
+	\item Abstract
+	\item Introduction
+	\item Methods
+	\item Datasets
+	\item Results
+	\begin{itemize}
+		\item Function fitting 
+		\begin{itemize}
+			\item Classical testing
+			\item All (5 + 16 qubit)
+			\item RUD + AL (5 + 16 qubit)
+			\item Error mitigation
+			\item Real device
+		\end{itemize}
+		\item BSE
+		\begin{itemize}
+			\item Classical testing
+			\item All 5 qubit
+			\item Truncated 16 qubit set (cost analysis 5 qubit)
+			\item RUD + AL (5 + 16 qubit)
+			\item Error mitigation
+			\item Real device
+		\end{itemize}		
+		\item DDCC
+		\begin{itemize}
+			\item Classical testing
+			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
+			\item Truncated 16 qubit set (based on BSE 5 qubit cost analysis)
+			\item RUD + AL (5 + 16 qubit)
+			\item Error mitigation
+			\item Real device
+		\end{itemize}		
+	\end{itemize}
+	\item Discussion and Conclusion
+\end{itemize}
 
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{images/AllBSE5_circuitdepth_MAE_vs_iterationtime.png}
+	\caption{\textcolor{red}{ADD KILL LIST}}
+	\label{fig:AllBSE5_circuitdepth_MAE_vs_iterationtime}
+\end{figure}
+
 \subsection{16 qubit BSE}

### 2024-09-24 BSE-calc-test/16qubit/done.sh

@@ -1,21 +1,0 @@
-mv -f ./M-A1-CZ_ESU2 finished
-mv -f ./M-M-CNOT_Efficient-CRZ finished
-mv -f ./M-A2-CNOT_Efficient-CRZ finished
-mv -f ./M-M-CNOT_ESU2 finished
-mv -f ./M-A2-CZ_Efficient-CRZ finished
-mv -f ./A1_Efficient-CRX finished
-mv -f ./M_Efficient-CRX finished
-mv -f ./M-M-CZ_ESU2 finished
-mv -f ./M-A1-CNOT_Full-CRZ finished
-mv -f ./A1-A1-CZ_Full-CRX finished
-mv -f ./A1-A1-CNOT_Full-CRZ finished
-mv -f ./A1-A1-CZ_Efficient-CRX finished
-mv -f ./A2-A2-CNOT_Efficient-CRX finished
-mv -f ./M-A1-CZ_Efficient-CRZ finished
-mv -f ./M_Full-CRX finished
-mv -f ./A1_Full-CRX finished
-mv -f ./A2_Full-CRZ finished
-mv -f ./A1-A1-CNOT_Efficient-CRX finished
-mv -f ./A2-A2-CZ_Efficient-CRX finished
-mv -f ./IQP_ESU2 finished
-mv -f ./IQP_Full-CRZ finished

### 2024-09-26 manuscript/main.tex
Reorganize

@@
 
-Simulated using FakeCairo backend
+Simulated using FakeQuebecbackend
 
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/linear_train_vs_test.png}
+		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/linear_train_vs_test.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/quadratic_train_vs_test.png}
+		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/sine_train_vs_test.png}
+		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/sine_train_vs_test.png}
 		\caption{}
@@
 \section{Results}
+\subsection{Model Calibration Using Function fitting} 
+We used the function fitting to determine if our models were implemented correctly.
 
-\subsection{Classical Testing}
-
-\subsubsection{Function Fitting}
-We found that on average the best models for the linear function is KNN (Fig. \siref{fig:linear}),  KRR for quadratic (Fig. \siref{fig:quadratic}), and KNN for sine (Fig. \siref{fig:sine}).
-
-\subsubsection{DDCC}
-
-$t_{ij}^{ab}$
-
-Dimensions reduced using SHapley Additive Explanation (SHAP) values
+\subsubsection{All (5 + 16 qubit)}
+Figure \ref{fig:5qubit_Func_funcfit_R2} shows every encoder and ansatz pair explored for the function fitting datasest with 5 qubits.
 \begin{figure}[H]
 	\centering
-	\includegraphics[width=\linewidth]{images/DDCC_feature_set.png}
-	\caption{DDCC feature set}
-	\label{fig:DDCC_feature_set}
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Linear_funcfit_R2.png}
+		\caption{}
+		\label{fig:5qubit_Linear_funcfit_R2}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Quadratic_funcfit_R2.png}
+		\caption{}
+		\label{fig:5qubit_Quadratic_funcfit_R2}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Sine_funcfit_R2.png}
+		\caption{}
+		\label{fig:5qubit_Sine_funcfit_R2}
+	\end{subfigure}
+	\caption{}
+	\label{fig:5qubit_Func_funcfit_R2}
 \end{figure}
 
-\subsubsection{BSE}\label{subsubsection:BSE}
+Figure \ref{fig:16qubit_Func_funcfit_R2} shows every encoder and ansatz pair explored for the function fitting datasest with 16 qubits.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{images/Feat_redR2.png}
-	\caption{Feat redR2}
-	\label{fig:Feat_redR2}
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Linear_funcfit_R2.png}
+		\caption{}
+		\label{fig:16qubit_Linear_funcfit_R2}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Quadratic_funcfit_R2.png}
+		\caption{}
+		\label{fig:16qubit_Quadratic_funcfit_R2}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Sine_funcfit_R2.png}
+		\caption{}
+		\label{fig:16qubit_Sine_funcfit_R2}
+	\end{subfigure}
+	\caption{}
+	\label{fig:16qubit_Func_funcfit_R2}
 \end{figure}
-% Key: 
-% 'ridge': Ridge(),
-% 'lasso': Lasso(),
-% 'elastic': ElasticNet(),
-% 'knn': KNeighborsRegressor(),
-% 'rfr': RandomForestRegressor(),
-% 'grad': GradientBoostingRegressor(),
-% 'svr': SVR(),
-% 'krr': KernelRidge(),
-% 'gpr': GaussianProcessRegressor()
-% \begin{table}[H]
-%     \begin{tabular}{||c | c c c||}
-%      \hline
-%      Training Set Size & Linear & Quadratic  & Sine \\ [0.5ex] 
-%      \hline\hline
-%      0.1 & SVR & KNN & GPR \\ 
-%      \hline
-%      0.3 & GPR & KRR & KRR \\
-%      \hline
-%      0.5 & SVR & KNN & RFR \\
-%      \hline
-%      0.7& GPR& Grad & RFR \\
-%      \hline
-%      0.8 & GPR & KRR & SVR \\ [1ex] 
-%      \hline
-%     \end{tabular}
-%     \caption{Function testing}
-%     \label{table:function_testing}
-% \end{table}
 
-\subsection{5 qubit function fitting}
-
-Fig. \siref{fig:lin5qubits_metric}
-Fig. \siref{fig:quad5qubits_metric}
-Fig. \siref{fig:sine5qubits_metric}
+\subsubsection{RUD + AL (5 + 16 qubit)}\label{subsection:func_depth}
+The best, median, and worst 5 were chosen from the 16 qubit data.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{images/5qubit_function_fitting_best.png}
-	\caption{REMAKE}
-	\label{fig:5qubit_function_fitting_best}
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Linear_RUD_AL.png}
+		\caption{}
+		\label{fig:16qubit_Linear_RUD_AL}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Quadratic_RUD_AL.png}
+		\caption{}
+		\label{fig:16qubit_Quadratic_RUD_AL}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Sine_RUD_AL.png}
+		\caption{}
+		\label{fig:16qubit_Sine_RUD_AL}
+	\end{subfigure}
+	\caption{}
+	\label{fig:16qubit_Func_RUD_AL}
 \end{figure}
 
-\subsection{16 qubit function fitting}
+\subsubsection{Learning curve}
+The best models from Section \ref{subsection:func_depth} were then used to compare them with classical machine learning models using learning curves, where the test set was held to 10 points, while the training data was varied from 10-80 points.
 
-Fig. \siref{fig:lin16qubits_metric}
-Fig. \siref{fig:quad16qubits_metric}
-Fig. \siref{fig:sine16qubits_metric}
+For the linear model with 16 qubits, the IQP encoding with the Full Pauli CRZ ansatz layer outperforms the classical models at 10\% of the training data, as show in  Fig.
+\ref{fig:linear_learning_curves}.
+The quantum model is less overfit and has a more accurate test score than any of the classical models. 
+As the training set size increases, the quantum model maintains an average train and test R$^{2}$ of 0.98, while the classical models maintain an average train and test R$^{2}$ of 0.99.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{images/Function_Fitting/linear_learning_curves.png}
+	\caption{Linear learning curve}
+	\label{fig:linear_learning_curves}
+\end{figure}
+
+\subsubsection{Error mitigation}
+FakeQuebec backend
+ZNE linear and Richardson
+TREX
+Without
+
+\subsubsection{Real device}
+IBM Quebec!
+
+\subsection{BSE}
+
+\subsubsection{Classical testing}
+After an extensive search of the possible moleuclar representations for the BSE dataset, we decided to use Morgan fingerprints.
+To map this set of features down to 5 and 16 qubits, we analyzed using SHapley Additive exPlanation (SHAP) values and principal component analysis.
+Based of of the analysis from Fig. \ref{fig:Feat_redR2}, we chose to use the set of features reduced using PCA due to the more accurate, albiet overfit data.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{images/BSE/Feat_redR2.png}
+	\caption{BSE Feature Reduction}
+	\label{fig:Feat_redR2}
+\end{figure}
+\subsubsection{All (5 + 16 qubit)}
+Using the aforementioned datasets, along with the 168 encoder-ansatz pairs we analyzed the cost of modeling the BSE dataset using the 5 qubit feature set first.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{images/16qubit_Linear_RUD_AL.png}
-	\caption{REMAKE}
-	\label{fig:16qubit_Linear_RUD_AL}
+	\includegraphics[width=\textwidth]{images/BSE/5qubit_BSE_MAE.png}
+	\caption{5 qubit BSE MAE (kcal/mol)}
+	\label{fig:5qubit_BSE_MAE}
 \end{figure}
 
+Using this data, we analyzed the mean time per training iteration versus the MAE and circuit depth. 
+We found that within the 168 encoder-ansatz pairs, there existed a bimodal distribution, where there were a set of 70 circuits with the mean time per iteration greater than 100 seconds and those with less.
+Going forward, we will only use the set of circuits that belong to the set with mean iteration times less than 100 seconds due to cost considerations.
 \begin{figure}[H]
 	\centering
-	\includegraphics[width=\linewidth]{images/16qubit_Quadratic_RUD_AL.png}
-	\caption{REMAKE}
-	\label{fig:16qubit_Quadratic_RUD_AL}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{images/16qubit_Sine_RUD_AL.png}
-	\caption{REMAKE}
-	\label{fig:16qubit_Sine_RUD_AL}
-\end{figure}
-
-The best is IQP\textunderscore Full-Pauli-CRX with 5AL and 5 RUD
-
-Missing 0.8 quadratic
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Linear_learning_curve.png}
-		\caption{}
-		\label{fig:Linear_learning_curve}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Quadratic_learning_curve.png}
-		\caption{}
-		\label{fig:Quadratic_learning_curve}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Sine_learning_curve.png}
-		\caption{}
-		\label{fig:Sine_learning_curve}
-	\end{subfigure}
-	\caption{Baseline denotes IQP\textunderscore Full-Pauli-CRX with 1AL and 1RUD}
-	\label{fig:learning_curve}
-\end{figure}
-
-\subsection{5 qubit BSE}
-Done
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{images/5qubit_BSE_RUD_AL.png}
-	\caption{5qubit BSE RUD AL}
-	\label{fig:5qubit_BSE_RUD_AL}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{images/AllBSE5_circuitdepth_MAE_vs_iterationtime.png}
-	\caption{\textcolor{red}{ADD KILL LIST}}
+	\includegraphics[width=\textwidth]{images/BSE/AllBSE5_circuitdepth_MAE_vs_iterationtime.png}
+	\caption{5 qubit BSE MAE (kcal/mol)}
 	\label{fig:AllBSE5_circuitdepth_MAE_vs_iterationtime}
@@
 
-\subsection{16 qubit BSE}
+For the 70 circuits that belong to those with iterations less than 100 seconds for the BSE 5 qubit set, we used these for the 16 qubit as well and found that...
 
-Missing data
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{images/16qubit_BSE_RUD_AL.png}
-	\caption{16qubit BSE RUD AL}
-	\label{fig:16qubit_BSE_RUD_AL}
-\end{figure}
+\subsubsection{RUD + AL (5 + 16 qubit)}
+Based off of the improvements shown in the function fitting dataset, we only used the best encoding ansatz pair for the real datasets
+For the 5 qubit, it is A2 HWE-CNOT
 
-\subsection{Error Correction}
-TREX/MITIQ ZNE LINEAR/ MITIQ ZNE Richardson
+\subsubsection{Error mitigation}
+\subsubsection{Real device}
 
-\subsubsection{Function Fitting}
-Running
-\subsubsection{DDCC}
-Not ran yet
-\subsubsection{BSE}
-Not ran yet
+\subsection{DDCC}
 
-\subsection{IBM Device}
+\subsubsection{Classical testing}
+\subsubsection{All (5 + 16 qubit)}
+\subsubsection{RUD + AL (5 + 16 qubit)}
+\subsubsection{Error mitigation}
+\subsubsection{Real device}
+
+\section{Conclusion}
+
+Molecular representations specifically for QML
+Distributed QC to incorporate more features
 

### 2024-09-26 function-calc-test/learning_curves/linear/0.1/helperfiles/run.sh

@@ -1,0 +1,33 @@
+#! /bin/bash
+cwd=$(pwd)
+errorname=$(basename `pwd`)
+echo $cwd
+for i in */; do
+    name=${i%/}
+    # Extracting the parent directory name
+    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
+    path="${cwd}/${name}"
+    if [ ! -f ${path}/${name}_results.json ]; then
+        echo "${name}.done not found!"
+    	cat > ${name}.sub <<EOF
+#! /bin/bash
+#SBATCH -t 0-23:59:59
+#SBATCH -J ${errorname}_linear_${name}
+#SBATCH -N 1
+#SBATCH -n 80
+#SBATCH --account=rrg-fekl-ac
+#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
+#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
+
+module load apptainer
+cd $(pwd)/$name
+
+apptainer run -C -B ${cwd} /home/j/jacobsen/gjones/deb.sif /opt/miniconda/bin/python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/linear_train.bin --test_set ${cwd}/linear_test.bin --scaler ${cwd}/linear_scaler.bin >> ${name}.out 2>&1
+
+cd ..
+touch ${name}.done
+
+EOF
+    fi
+    echo "Done ${name}.sub"
+done

### 2024-09-26 function-calc-test/learning_curves/linear/0.7/run.sh

@@ -1,0 +1,33 @@
+#! /bin/bash
+cwd=$(pwd)
+errorname=$(basename `pwd`)
+echo $cwd
+for i in */; do
+    name=${i%/}
+    # Extracting the parent directory name
+    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
+    path="${cwd}/${name}"
+    if [ ! -f ${path}/${name}_results.json ]; then
+        echo "${name}.done not found!"
+    	cat > ${name}.sub <<EOF
+#! /bin/bash
+#SBATCH -t 0-23:59:59
+#SBATCH -J ${errorname}_linear_${name}
+#SBATCH -N 1
+#SBATCH -n 80
+#SBATCH --account=rrg-fekl-ac
+#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
+#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
+
+module load apptainer
+cd $(pwd)/$name
+
+apptainer run -C -B ${cwd} /home/j/jacobsen/gjones/deb.sif /opt/miniconda/bin/python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/${errorname}_linear_train.bin --test_set ${cwd}/linear_test.bin --scaler ${cwd}/linear_scaler.bin >> ${name}.out 2>&1
+
+cd ..
+touch ${name}.done
+
+EOF
+    fi
+    echo "Done ${name}.sub"
+done

### 2024-09-26 function-calc-test/learning_curves/sine/0.7/add_params.py
linear and sine learning curves + manuscript

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[1]:
+
+
+from glob import glob
+import sys
+import os
+import shutil
+import joblib
+import json
+
+
+# In[2]:
+
+
+for p in glob('*/*.json'):
+    print(p)
+    with open(p,'r') as f:
+        olddt=json.load(f)
+    
+    
+    olddt["BATCH_SIZE"]=25
+    olddt["NUM_CORES"]=36
+    olddt['TOLERANCE']=1e-6
+    olddt['MAX_ITER']=1000
+    print(olddt)    
+
+    with open(p,'w') as g:
+        json.dump(olddt,g)
+

### 2024-09-26 function-calc-test/learning_curves/sine/0.8/run.sh

@@ -1,0 +1,33 @@
+#! /bin/bash
+cwd=$(pwd)
+errorname=$(basename `pwd`)
+echo $cwd
+for i in */; do
+    name=${i%/}
+    # Extracting the parent directory name
+    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
+    path="${cwd}/${name}"
+    if [ ! -f ${path}/${name}_results.json ]; then
+        echo "${name}.done not found!"
+    	cat > ${name}.sub <<EOF
+#! /bin/bash
+#SBATCH -t 0-23:59:59
+#SBATCH -J ${errorname}_sine_${name}
+#SBATCH -N 1
+#SBATCH -n 80
+#SBATCH --account=rrg-fekl-ac
+#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
+#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
+
+module load apptainer
+cd $(pwd)/$name
+
+apptainer run -C -B ${cwd} /home/j/jacobsen/gjones/deb.sif /opt/miniconda/bin/python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/sine_train.bin --test_set ${cwd}/sine_test.bin --scaler ${cwd}/sine_scaler.bin >> ${name}.out 2>&1
+
+cd ..
+touch ${name}.done
+
+EOF
+    fi
+    echo "Done ${name}.sub"
+done

### 2024-10-09 manuscript/main.tex
linear and sine learning curves + manuscript
manuscript

@@
 		\end{itemize}
+		\item DDCC (5 qubit only because classically it can be done with 5 features!)
+		\begin{itemize}
+			\item Classical testing
+			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
+			\item RUD + AL (5)
+			\item Error mitigation
+			\item Real device
+		\end{itemize}
 		\item BSE
@@
 			\item Truncated 16 qubit set (cost analysis 5 qubit)
-			\item RUD + AL (5 + 16 qubit)
-			\item Error mitigation
-			\item Real device
-		\end{itemize}		
-		\item DDCC
-		\begin{itemize}
-			\item Classical testing
-			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
-			\item Truncated 16 qubit set (based on BSE 5 qubit cost analysis)
 			\item RUD + AL (5 + 16 qubit)
@@
 
+A2 HWE-CZ
+Performs better than all but 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{images/Function_Fitting/sine_learning_curves.png}
+	\caption{sine learning curve}
+	\label{fig:sine_learning_curves}
+\end{figure}
+
 \subsubsection{Error mitigation}
@@
 \section{Conclusion}
-
+Depth is not always better!
 Molecular representations specifically for QML

### 2024-11-19 manuscript/main.tex

@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{images/BSE/16qubit_BSE_MAE.png}
+	\caption{16 qubit BSE MAE (kcal/mol)}
+	\label{fig:16qubit_BSE_MAE}
+\end{figure}
+
 Using this data, we analyzed the mean time per training iteration versus the MAE and circuit depth. 
@@
 Based off of the improvements shown in the function fitting dataset, we only used the best encoding ansatz pair for the real datasets
-For the 5 qubit, it is A2 HWE-CNOT
+For the 5 qubit, it is  M-M-CZ HWE-CNOT
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{images/BSE/BSE5_RUDAL.png}
+	\caption{5 qubit BSE MAE (kcal/mol) AL RUD}
+	\label{fig:	BSE5_RUDAL}
+\end{figure}
+
+For 16 qubit A2 Hadamard
 

### 2024-11-21 manuscript/main.tex
Thu 21 Nov 2024 16:22:11 EST update

@@
 \newpage
-\textcolor{red}{Reorganize}
 \begin{itemize}
@@
 	\item Datasets
-	\item Results
+	\item Results and Discussion
 	\begin{itemize}
@@
 		\begin{itemize}
-			\item Classical testing
 			\item All (5 + 16 qubit)
 			\item RUD + AL (5 + 16 qubit)
-			\item Error mitigation
-			\item Real device
+			\item Error mitigation on FakeQuebec
+		\end{itemize}
+		\item BSE
+		\begin{itemize}
+			\item All 5 qubit
+			\item Truncated 16 qubit set (cost analysis 5 qubit)
+			\item RUD + AL (5 + 16 qubit)
+			\item Real device (without error mitigation and with whatever the best is from function fitting)
 		\end{itemize}		
@@
 		\begin{itemize}
-			\item Classical testing
 			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
-			\item RUD + AL (5)
-			\item Error mitigation
-			\item Real device
-		\end{itemize}
-		\item BSE
-		\begin{itemize}
-			\item Classical testing
-			\item All 5 qubit
-			\item Truncated 16 qubit set (cost analysis 5 qubit)
-			\item RUD + AL (5 + 16 qubit)
-			\item Error mitigation
-			\item Real device
+			\item RUD + AL (5 qubit)
+			\item Real device (without error mitigation and with whatever the best is from function fitting)
 		\end{itemize}				
 	\end{itemize}
-	\item Discussion and Conclusion
+	\item Conclusion
 \end{itemize}
@@
 \cite{prasad_applications_2024}
-\cite{suzuki_predicting_2020}
-\cite{mitarai_quantum_2018}
-\cite{sim_expressibility_2019}
+
+A1, A2, M-Encoding \cite{suzuki_predicting_2020}
+M-Encoding \cite{mitarai_quantum_2018}
+
+Ansaetze \cite{sim_expressibility_2019}
+``In particular, a substantial improvement in performance of two-qubit gates in a ring or all-to-all connected arrangement, compared to thatof those on a line, is observed.''
+
+``Furthermore, improvement in both descriptors is achieved by sequences of controlled X-rotation gates compared tosequences of controlled Z-rotation gates.''
+
+``investigated howexpressibility “saturates” with increased circuit depth, finding that the rateand saturated value appear to be distinguishing features of a PQC''
+
+IQP \cite{bremner_average-case_2015}
+
 \cite{hatakeyama-sato_quantum_2023}

### 2024-11-21 qml_DDCC/RUD_AL_5/RUD_AL/RUD_AL/3RUD/helperfiles/quantum/circuits/Encoders.py

@@ -1,0 +1,98 @@
+import pennylane as qml
+import numpy as np
+
+
+def mitarai(features, wires):
+    # encoding as proposed by Mitarai et al.
+    num_features = len(features)
+    num_wires = len(wires)
+
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        if np.isnan(np.arcsin(features[feature_idx])) or np.isnan(np.arccos(features[feature_idx])):
+            print(f'Ignoring NaN found at index: {feature_idx}. With feature: {features[feature_idx]}. ')
+        else:
+            qml.RY(np.arcsin(features[feature_idx]), wires=wires[i])
+            qml.RZ(np.arccos(features[feature_idx] ** 2), wires=wires[i])
+
+
+def single_angle(features, wires):
+    #  creates a circuit that encodes features into wires via angle encoding with a single RY gate
+    #  the features are encoded 1-1 onto the qubits
+    #  if more wires are passed then features the remaining wires will be filled from the beginning of the feature list
+    if len(features) > len(wires):
+        raise ValueError("Cannot encode more features than there are wires")
+    for i in range(len(wires)):
+        feature_index = i % len(features)
+        qml.RY(features[feature_index], wires=wires[i])
+
+
+def double_angle(features, wires):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
+    #  if more wires are passed then features the remaining wires will be filled from the beginning of the feature list
+    if len(features) >> len(wires):
+        raise ValueError("Cannot encode more features than there are wires")
+    for i in range(len(wires)):
+        feature_index = i % len(features)
+        qml.RY(features[feature_index], wires=wires[i])
+        qml.RZ(features[feature_index], wires=wires[i])
+
+
+def entangle_cnot(wires):
+    #  entangles all of the wires in a circular fashion using cnot gates
+    for i in wires:
+        if i == len(wires) - 1:
+            qml.CNOT(wires=(i, 0))
+        else:
+            qml.CNOT(wires=(i, i+1))
+
+
+def entangle_cz(wires):
+    #  entangles all of the wires in a circular fashion using cz gates
+    for i in wires:
+        if i == len(wires) - 1:
+            qml.CZ(wires=(i, 0))
+        else:
+            qml.CZ(wires=(i, i+1))
+
+
+def composer(*args):
[…]

### 2024-12-02 manuscript/main.tex
Manuscript + Conversion to Qiskit progress

@@
 \section{Introduction}
-\cite{prasad_applications_2024}
+[quantum machine learning]
 
-A1, A2, M-Encoding \cite{suzuki_predicting_2020}
-M-Encoding \cite{mitarai_quantum_2018}
+[parameterized circuits for chemical applications]
 
-Ansaetze \cite{sim_expressibility_2019}
-``In particular, a substantial improvement in performance of two-qubit gates in a ring or all-to-all connected arrangement, compared to thatof those on a line, is observed.''
+[What we introduce]
 
-``Furthermore, improvement in both descriptors is achieved by sequences of controlled X-rotation gates compared tosequences of controlled Z-rotation gates.''
+Our work includes the single and double encoding layers found in the paper of Suzuki and Katouda\cite{suzuki_predicting_2020}, including the encoding of Mitarai \textit{et al.}\cite{mitarai_quantum_2018}, along with using instantanious quantum polynomial (IQP) as an encoding layer.
+\cite{bremner_average-case_2015}
+All of our variational (ansatz) layers can be found in the study of Sim \textit{et al.}\cite{sim_expressibility_2019}, where the expressiblity and entanglement capability of these circuits is analyzed.
 
-``investigated howexpressibility “saturates” with increased circuit depth, finding that the rateand saturated value appear to be distinguishing features of a PQC''
+\cite{krenn_artificial_2023}
 
-IQP \cite{bremner_average-case_2015}
+QML\cite{biamonte_quantum_2017}:
+\begin{itemize}
+	\item ``Quantum machine learning software makes use of quantum algorithms as part of a larger implementation.
+By analysing the steps that quantum algorithms prescribe, it becomes clear that they have the potential to outperform classical algorithms for specific problems (that is, reduce the number of steps required).
+This potential is known as quantum speedup.''
+	\item ``The notion of a quantum speedup depends on whether one takes a formal computer science perspective—which demands mathematical proofs—or a perspective based on what can be done with realistic, finitesize devices—which requires solid statistical evidence of a scaling advantage over some finite range of problem sizes.
+For the case of quantum machine learning, the best possible performance of classical algorithms is not always known.''
+	\item DO WE SEE THIS: ``Determination of a scaling advantage contrasting quantum and classical machine learning would rely on the existence of a quantum computer and is called a ‘benchmarking’ problem.
+Such advantages could include improved classification accuracy and sampling of classically inaccessible systems.
+Accordingly, quantum speedups in machine learning are currently characterized using idealized measures from complexity theory: query complexity and gate complexity (see Box 1 and Box 1 Table).
+Query complexity measures the number of queries to the information source for the classical or quantum algorithm.
+A quantum speedup results if the number of queries needed to solve a problem is lower for the quantum algorithm than for the classical algorithm.
+To determine the gate complexity, the number of elementary quantum operations (or gates) required to obtain the desired result are counted.''
+	\item Input problem: ``Classical data must be input before being processed on a quantum computer.
+This ‘input problem’ often has little overhead but can present a serious bottleneck for certain algorithms.
+Likewise, the ‘output problem’ is faced when reading out data after being processed on a quantum device.
+Like the input problem, the output problem often causes a noticeable operational slowdown.''
+	\item  QML challenges: ``These hardware challenges are technical in nature, and clear paths exist towards overcoming them.
+They must be overcome, however, if quantum machine learning is to become a ‘killer app’ for quantum computers.
+As noted previously, most of the quantum algorithms that have been identified face a number of caveats that limits their applicability.
+We can distill the caveats mentioned above into four fundamental problems.
+(1) The input problem.
+Although quantum algorithms can provide dramatic speedups for processing data, they seldom provide advantages in reading data.
+This means that the cost of reading in the input can in some cases dominate the cost of quantum algorithms.
+Understanding this factor is an ongoing challenge.
+(2) The output problem.
+Obtaining the full solution from some quantum algorithms as a string of bits requires learning an exponential number of bits.
+This makes some applications of quantum machine learning algorithms infeasible.
+This problem can potentially be sidestepped by learning only summary statistics for the solution state.
+(3) The costing problem.
+Closely related to the input/outputproblems, at present very little is known about the true number of gates required by quantum machine learning algorithms.
+Bounds on the complexity suggest that for sufficiently large problems they will offer huge advantages, but it is still unclear when that crossover point occurs.
+(4) The benchmarking problem.
+It is often difficult to assert that a quantum algorithm is ever better than all known classical machine algorithms in practice because this would require extensive benchmarking against modern heuristic methods.
+Establishing lower bounds for quantum machine learning would partially address this issue.''
+\end{itemize}
 
-\cite{hatakeyama-sato_quantum_2023}
-\cite{krenn_artificial_2023}
-\cite{benedetti_parameterized_2019}
-\cite{biamonte_quantum_2017}
+PQCs\cite{benedetti_parameterized_2019}:
+\begin{itemize}
+	\item ``Parameterized quantum circuits (PQCs) offer a concrete way to implement algorithms and demonstrate quantum supremacy in the NISQ era.
+PQCs are typically composed of fixed gates, e.g.
+controlled NOTs, and adjustable gates, e.g.
+qubit rotations.
+Even at low circuit depth, some classes of PQCs are capable of generating highly non-trivial outputs.
+For example, under well-believed complexity-theoretic assumptions, the class of PQCs called instantaneous quantum polynomial-time cannot be efficiently simulated by classical resources (see Lund et al [3] and Harrow and Montanaro [4] for accessible Reviews of quantum supremacy proposals).
+The demonstration of quantum supremacy is an important milestone in the development of quantum computers.
+In practice, however, it is highly desirable to demonstrate a quantum advantage on applications.
+The main approach taken by the community consists in formalizing problems of interest as variational optimization problems and use hybrid systems of quantum and classical hardware to find approximate solutions.
+The intuition is that by implementing some subroutines on classical hardware, the requirement of quantum resources is significantly reduced, particularly the number of qubits, circuit depth, and coherence time.
+Therefore, in the hybrid algorithmic approach NISQ hardware focuses entirely on the classically intractable part of the problem.''
+\end{itemize}
 
-As current quantum hardware grows, much attention is brought to find applicable uses for the potentially powerful new technology while it continues to grow.
-Current research in the areas of developing quantum algorithms for use with current noisy intermediate-scale quantum (NISQ) hardware lays the foundation for understanding and applying quantum computing.
-These near-term algorithms have seen a wide deployment across many areas of science and technology as the field grows.
-Computational chemistry is a natural such candidate for quantum computing applications due to the quantum nature of many problems in the field.
-An especially important problem is that of calculating the bond separation energies of (molecules?).
-Efficient and accurate predictions of these values can aid research in material science and drug discovery.\par
+PQCs \cite{suzuki_predicting_2020}:
+\begin{itemize}
+	\item ``More recently, quantum machine learning (QML) [26–30] is a rapidly growing research field that combines near-term quantum algorithms and machine learning techniques.
+In particular, parameterized quantum circuits (PQCs) have been considered as machine learning models with high expressive power within the hybrid quantum–classical framework [31, 32].
+PQCs are typically composed of fixed quantum gates (e.g., qubit rotations and entangling gates) in a shallow circuit layout, with variable parameters optimized in a classical feedback loop.''
+	\item ``To our knowledge, however, the application of QML to regression tasks has not been fully investigated in the literature.
+It remains unclear what kinds of quantum states should be used in order to generate the feature map with high expressibility that is suited for real-world data sets.''
+	\item ``quantitative structure–toxicity relationship (QSTR) models for predicting the toxicity of 221 phenols.
+While there are a variety of QSAR/QSTR models (e.g., 3D-QSAR [1, 4]),asafirst step we employ QSAR/QSTR models including molecular descriptors such as hydrophobicity, acidity constant, and frontier orbital energies.
+There have been quantum computations in biochemical and pharmaceutical areas, such as protein folding [43–45], molecular similarity [46], and biological data [47]; yet, there has been no study on quantum application to QSAR modeling, albeit an important part of ligand-based computer-aided drug design.''
+	\item ``PQCs have been regarded as machine learning models with high expressive power within the framework of the hybrid quantum–classical approach.
+PQCs are usually composed of one-qubit rotations and two-qubit entangling operations in a shallow circuit layout, with parameters optimized in a feedback loop.''
+	\item ``Combining near-term quantum algorithms and machine learning, QML using the framework of PQCs is sometimes referred to as quantum circuit learning (QCL)''
+	\item ``PQCs consist of three components: the encoder circuit, the variational circuit, and the measurement for the estimation of the loss function''
 
-One of the most promising near-term applications of quantum computing within any field has been quantum machine learning (QML).
-The advantages of QML comes largely from its ability to be readily deployed on quantum computers with few qubits, and its potential to speedup problems with minimal loss of accuracy.
-The number of qubits needed for a QML model is determined primarily by the number of features in the dataset.
-As there exist data science techniques developed in the realm of classical machine learning to reduce feature spaces, they can be adopted over to reduce problems to a suitable number of qubits.
-Further, since QML only needs to train once, it has potential to perform faster when compared to other current NISQ algorithms such as the variational quantum eigensolver, which needs to be trained separately for each problem.
-\par
+\end{itemize}
 
-Quantum machine learning has been widely applied to classification tasks with much success.
-However, little research has been done to understand its capabilities for regression.
-Previous works have set important groundwork to the understanding of QML for regression by theoretically formulating upper bounds for the generalization error.
-Most notably, this research suggests that with an efficiently implemented QML model can achieve good generalizability with modest training data sizes.
-This highlights a potential for QML models to outperform and out-generalize classical models.
-Further understanding and verification of this, however, requires numerical validation and demonstration, and while some experimental work has been done, it remains limited to few qubits with little practical application.\par
-
-Our work expands on the current knowledge base by providing a comprehensive exploration of QML for regression.
-Specfically, we will by applying QML to the problem of calculating bond dissociation enthalpies of various molecules.
-This demonstrates
-a practical application of regression in QML with many applications.
-The efficient and accurate prediction of these chemical properties can aid research in material science and drug discovery with far reaching implications.
-Our work serves to benchmark QML and test its capabilities within this context.
-\par
+PQCs \cite{hatakeyama-sato_quantum_2023}:
+\begin{itemize}
+	\item What they do: ``ntroduce quantum circuit learning (QCL) as an emerging regression algorithm for chemo- and materials-informatics.
+The supervised model, functioning on the rule of quantum mechanics, can process linear and smooth non-linear functions from small datasets (<100 records).
+Compared with conventional algorithms, such as random forest, support vector machine, and linear regressions, the QCL can offer better predictions with some one-dimensional functions and experimental chemical databases''
+	\item ``Here, we introduce quantum circuit learning (QCL), an emerging algorithm for supervised learning.15–18 QCL works on the rule of quantum mechanics.
+It can predict various parameters likewise to classical models.
+The current quantum systems (noisy intermediate-scale quantum computers: NISQ)19,20 face the problems of calculation noise and the limited processable number of information units (qubits).''
+	\item ``Since QCL is a frontier for machine learning, few reports have been published on authentic regression tasks.
+The success of prediction with a toxicity dataset of organic molecules was reported,17 whereas the study was still conceptual.
+The prediction processes and advantages have been unclear, especially from chemical and material viewpoints.
+Here, we conducted a more comprehensive study on QCL with standard datasets of one-dimensional functions and chemical properties.
+Both simulated and actual quantum computing was undertaken to clarify the challenges of QCL.
+Various hyperparameters were optimized for higher accuracy.
+The comparison with conventional models contrasted the benefits of the new approach: capable of learning both linear and non-linear functions even from small datasets.
+The property was also favorable for predicting the so-called extrapolating data region, which is essential for chemical and material research.''
+	\item They cite \cite{takaki_learning_2021,suzuki_predicting_2020,mitarai_quantum_2018} as examples of PQCs/quantum circuit learning for regression task
+	\item Justification for starting with 1D regression: ``Preliminary optimization of quantum circuits15,17 and our optimization revealed that the following configuration was concise and practical for regression tasks (for details, see results and explanations in Fig.
+S1''
+\end{itemize}
 
 \section{Methods}
+Use a mix of  \cite{hatakeyama-sato_quantum_2023} and \cite{suzuki_predicting_2020} for the methods.
+
+Format from \cite{suzuki_predicting_2020}:
+\begin{itemize}
+	\item Feature set $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$
+	\item Feature map (encoding) $U_{\Phi(\mathbf{x})}$ produces the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$
+	\item Variational circuit (ansatz) $U(\mathbf{\theta})$, leads to the parameterized quantum circuit $U(\mathbf{\theta})U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$
+\end{itemize}
+
 Quantum machine learning is a hybrid classical-quantum approach utilizing parameterized quantum circuits.
@@
 \section{Results}
-\subsection{Model Calibration Using Function fitting} 
-We used the function fitting to determine if our models were implemented correctly.
 
-\subsubsection{All (5 + 16 qubit)}
-Figure \ref{fig:5qubit_Func_funcfit_R2} shows every encoder and ansatz pair explored for the function fitting datasest with 5 qubits.
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Linear_funcfit_R2.png}
-		\caption{}
-		\label{fig:5qubit_Linear_funcfit_R2}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Quadratic_funcfit_R2.png}
-		\caption{}
-		\label{fig:5qubit_Quadratic_funcfit_R2}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/5qubit_Sine_funcfit_R2.png}
-		\caption{}
-		\label{fig:5qubit_Sine_funcfit_R2}
-	\end{subfigure}
-	\caption{}
-	\label{fig:5qubit_Func_funcfit_R2}
-\end{figure}
+Ansaetze analysis \cite{sim_expressibility_2019}
+``In particular, a substantial improvement in performance of two-qubit gates in a ring or all-to-all connected arrangement, compared to thatof those on a line, is observed.''
 
-Figure \ref{fig:16qubit_Func_funcfit_R2} shows every encoder and ansatz pair explored for the function fitting datasest with 16 qubits.
+``Furthermore, improvement in both descriptors is achieved by sequences of controlled X-rotation gates compared tosequences of controlled Z-rotation gates.''
 
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Linear_funcfit_R2.png}
-		\caption{}
-		\label{fig:16qubit_Linear_funcfit_R2}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Quadratic_funcfit_R2.png}
-		\caption{}
-		\label{fig:16qubit_Quadratic_funcfit_R2}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Sine_funcfit_R2.png}
-		\caption{}
-		\label{fig:16qubit_Sine_funcfit_R2}
-	\end{subfigure}
-	\caption{}
-	\label{fig:16qubit_Func_funcfit_R2}
-\end{figure}
-
-\subsubsection{RUD + AL (5 + 16 qubit)}\label{subsection:func_depth}
-The best, median, and worst 5 were chosen from the 16 qubit data.
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Linear_RUD_AL.png}
-		\caption{}
-		\label{fig:16qubit_Linear_RUD_AL}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Quadratic_RUD_AL.png}
-		\caption{}
-		\label{fig:16qubit_Quadratic_RUD_AL}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/16qubit_Sine_RUD_AL.png}
-		\caption{}
-		\label{fig:16qubit_Sine_RUD_AL}
-	\end{subfigure}
-	\caption{}
-	\label{fig:16qubit_Func_RUD_AL}
-\end{figure}
-
-\subsubsection{Learning curve}
-The best models from Section \ref{subsection:func_depth} were then used to compare them with classical machine learning models using learning curves, where the test set was held to 10 points, while the training data was varied from 10-80 points.
-
-For the linear model with 16 qubits, the IQP encoding with the Full Pauli CRZ ansatz layer outperforms the classical models at 10\% of the training data, as show in  Fig.
-\ref{fig:linear_learning_curves}.
-The quantum model is less overfit and has a more accurate test score than any of the classical models. 
-As the training set size increases, the quantum model maintains an average train and test R$^{2}$ of 0.98, while the classical models maintain an average train and test R$^{2}$ of 0.99.
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{images/Function_Fitting/linear_learning_curves.png}
-	\caption{Linear learning curve}
-	\label{fig:linear_learning_curves}
-\end{figure}
-
-A2 HWE-CZ
-Performs better than all but 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{images/Function_Fitting/sine_learning_curves.png}
-	\caption{sine learning curve}
-	\label{fig:sine_learning_curves}
-\end{figure}
-
-\subsubsection{Error mitigation}
-FakeQuebec backend
-ZNE linear and Richardson
-TREX
-Without
-
-\subsubsection{Real device}
-IBM Quebec!
-
-\subsection{BSE}
-
-\subsubsection{Classical testing}
-After an extensive search of the possible moleuclar representations for the BSE dataset, we decided to use Morgan fingerprints.
-To map this set of features down to 5 and 16 qubits, we analyzed using SHapley Additive exPlanation (SHAP) values and principal component analysis.
-Based of of the analysis from Fig. \ref{fig:Feat_redR2}, we chose to use the set of features reduced using PCA due to the more accurate, albiet overfit data.
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{images/BSE/Feat_redR2.png}
-	\caption{BSE Feature Reduction}
-	\label{fig:Feat_redR2}
-\end{figure}
-\subsubsection{All (5 + 16 qubit)}
-Using the aforementioned datasets, along with the 168 encoder-ansatz pairs we analyzed the cost of modeling the BSE dataset using the 5 qubit feature set first.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{images/BSE/5qubit_BSE_MAE.png}
-	\caption{5 qubit BSE MAE (kcal/mol)}
-	\label{fig:5qubit_BSE_MAE}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{images/BSE/16qubit_BSE_MAE.png}
-	\caption{16 qubit BSE MAE (kcal/mol)}
-	\label{fig:16qubit_BSE_MAE}
-\end{figure}
-
-Using this data, we analyzed the mean time per training iteration versus the MAE and circuit depth. 
-We found that within the 168 encoder-ansatz pairs, there existed a bimodal distribution, where there were a set of 70 circuits with the mean time per iteration greater than 100 seconds and those with less.
-Going forward, we will only use the set of circuits that belong to the set with mean iteration times less than 100 seconds due to cost considerations.
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{images/BSE/AllBSE5_circuitdepth_MAE_vs_iterationtime.png}
-	\caption{5 qubit BSE MAE (kcal/mol)}
-	\label{fig:AllBSE5_circuitdepth_MAE_vs_iterationtime}
-\end{figure}
-
-For the 70 circuits that belong to those with iterations less than 100 seconds for the BSE 5 qubit set, we used these for the 16 qubit as well and found that...
-
-\subsubsection{RUD + AL (5 + 16 qubit)}
-Based off of the improvements shown in the function fitting dataset, we only used the best encoding ansatz pair for the real datasets
-For the 5 qubit, it is  M-M-CZ HWE-CNOT
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{images/BSE/BSE5_RUDAL.png}
-	\caption{5 qubit BSE MAE (kcal/mol) AL RUD}
-	\label{fig:	BSE5_RUDAL}
-\end{figure}
-
-For 16 qubit A2 Hadamard
-
-\subsubsection{Error mitigation}
-\subsubsection{Real device}
-
-\subsection{DDCC}
-
-\subsubsection{Classical testing}
-\subsubsection{All (5 + 16 qubit)}
-\subsubsection{RUD + AL (5 + 16 qubit)}
-\subsubsection{Error mitigation}
-\subsubsection{Real device}
+``investigated howexpressibility “saturates” with increased circuit depth, finding that the rateand saturated value appear to be distinguishing features of a PQC''
 

### 2024-12-02 Pennylane_to_Qiskit/add_params.py

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[1]:
+
+
+from glob import glob
+import sys
+import os
+import shutil
+import joblib
+import json
+
+
+# In[2]:
+
+
+for p in glob('*/*.json'):
+    print(p)
+    with open(p,'r') as f:
+        olddt=json.load(f)
+    
+    
+    olddt["BATCH_SIZE"]=32
+    olddt["NUM_CORES"]=80
+    olddt['TOLERANCE']=1e-6
+    olddt['MAX_ITER']=500
+    print(olddt)    
+
+    with open(p,'w') as g:
+        json.dump(olddt,g)
+

### 2024-12-02 Pennylane_to_Qiskit/run.sh

@@ -1,0 +1,56 @@
+#! /bin/bash
+cwd=$(pwd)
+errorname=$(basename `pwd`)
+echo $cwd
+for i in */; do
+    name=${i%/}
+    # Extracting the parent directory name
+    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
+    path="${cwd}/${name}"
+    if [ ! -f ${path}/partial_state_model.bin ]; then
+        echo "${name}.done not found!"
+    	cat > ${name}.sub <<EOF
+#! /bin/bash
+#SBATCH -t 0-23:59:59
+#SBATCH -J ${errorname}_PCA5_0.8_Morgan_${name}
+#SBATCH -N 1
+#SBATCH -n 80
+#SBATCH --account=rrg-fekl-ac
+#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
+#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
+
+cd $(pwd)/$name
+
+/scinet/niagara/software/2019b/opt/base/python/3.11.5/bin/python3 ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA5_0.8_Morgan_train.bin --test_set ${cwd}/PCA5_0.8_Morgan_test.bin --scaler ${cwd}/PCA5_0.8_Morgan_scaler.bin > ${name}.out 2>&1
+
+cd ..
+touch ${name}.done
+
+EOF
+
+    else
+        echo "partial_state_model.bin found"
+    	cat > ${name}.sub <<EOF
+#! /bin/bash
+#SBATCH -t 0-23:59:59
+#SBATCH -J ${errorname}_PCA5_0.8_Morgan_${name}
+#SBATCH -N 1
+#SBATCH -n 80
+#SBATCH --account=rrg-fekl-ac
+#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
+#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
+
+cd $(pwd)/$name
+
[…]

### 2025-01-06 manuscript/main.tex
Mon  6 Jan 2025 13:15:39 EST

@@
 \section{Abstract}
-The rapid growth of quantum computing has seen a rise in the development of applicable near-term quantum algorithms.
-A promising candidate to run on current noisy intermediate-scale quantum (NISQ) hardware is quantum machine learning (QML).
-Parameterized quantum circuits can be learned as models in a hybrid classical-quantum approach.
-It has been shown that QML models may need less training data to generalize compared to classical methods.
-Although QML has been explored largely within classification tasks, regression tasks have received much less attention.
-Existing studies have only utilized few qubits and lack relevant practical applications.
-We will discuss our work on the development and comparisons of QML models for highly desired prediction of chemical properties such as bond dissociation energies and barrier height energies.
-Our work investigates the trainability, expressibility, and generalization capability of various quantum models for the purpose of regression of molecular properties.
-Our work also provides a benchmark against classical machine learning models and implications of using error mitigation techniques for QML.
+Within the quantum machine learning (QML) field, parameterized quantum circuits (PQCs), built using fixed and parameterized gates, offer a hybrid approach for complex machine learning tasks.
+While many potential use cases have been proposed, the exploration of relevant datasets for chemists is lacking.
+Our study seeks to understand the possible advantages and disadvantages of PQCs for two chemically relevant datasets: one based on the bond separation energies of 49 different classes of bonds, called the BSE49 dataset, and another consisting of water confirmations, where coupled-cluster singles and doubles (CCSD) wave functions are predicted using electronic structure theory data from lower-level methods using the data-driven coupled-cluster (DDCC) method.
+In our study, we examine a combinatorial space of 14 data encoding layers and 12 variational (ansatz) layers, for a combined total of 168 PQCs.
+To calibrate our PQCs, we utilize a dataset of noisy linear, quadratic, and sine functions to explore the effects of the circuit width and depth, the effects of the feature set size, and various error mitigation techniques.
+Following this step, we similarly examine our chemically relevant datasets.
+Our work highlights the difficulties in encoding classical molecular representations in a PQC for predicting bond separation energies and the aptitude for PQCs for predicting molecular wave functions.
 \par

### 2025-01-06 Pennylane_to_Qiskit/convert_ML.py

@@ -1,11 +1,11 @@
 #!/usr/bin/env python
 # coding: utf-8
 
-# In[1]:
+# In[ ]:
 
 
 import os
-n_jobs = 12
+n_jobs = 16
 os.environ["OMP_NUM_THREADS"] = str(n_jobs)
 import joblib
 import click
@@ -37,9 +37,10 @@ from qiskit_ibm_runtime.fake_provider import FakeQuebec
 from qiskit_ibm_runtime import Session
 
 
+from joblib import dump, load
 
 
-# In[2]:
+# In[ ]:
 
 
 def mitarai(quantumcircuit,num_wires,paramname='x'):
@@ -93,7 +94,7 @@ def HardwareEfficient(quantumcircuit,num_wires,paramname='theta'):
 
 
 
-# In[3]:
+# In[ ]:
 
 
 # def circuit(nqubits):
@@ -119,7 +120,7 @@ def circuit(nqubits,RUD=1):
     return qc
 
 
-# In[4]:
+# In[ ]:
 
 
 # with open('linear_train.bin','rb') as f:
@@ -177,10 +178,106 @@ X_test, y_test = X_ddcc_test, y_ddcc_test
 scaler = ddcc_scaler
 
 
-# In[5]:
+# In[ ]:
 
 
-def predict(params, ansatz, hamiltonian, estimator, num_qubits, X):
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+def incremental_save_minimize(fun, x0, save_path, args=(), method='cobyla', options=None):
+    """
+    Minimize a function using scipy.optimize.minimize with incremental saving of parameters and loss.
+
+    Parameters:
+        fun (callable): The objective function to be minimized.
+        x0 (ndarray): Initial guess.
+        save_path (str): Path to save progress with joblib.
+        args (tuple, optional): Extra arguments passed to the objective function.
+        method (str, optional): Optimization method (default is 'BFGS').
+        options (dict, optional): Options passed to scipy.optimize.minimize.
+
+    Returns:
+        result (OptimizeResult): The optimization result represented as a `OptimizeResult` object.
+    """
+    if os.path.exists(save_path):
+        progress = load(save_path)
+        x0 = progress['x']
+        print("Resuming optimization from saved state.")        
+    else:
+        progress = {'x': x0, 'loss': None}
+
+    def callback(x):
+        # Save current parameters and function value
+        progress['x'] = x
[…]

### 2025-01-06 manuscript/main.tex
manuscript

@@
 \section{Introduction}
-[quantum machine learning]
+Within the field of chemistry, tools such as machine learning and quantum computing have become popular due to the promise of discoverying new molecules and materials.
+Machine learning in chemistry has already become a broadly applicable tool for exploring chemical compound space\cite{ramakrishnan_quantum_2014,ramakrishnan_big_2015}, accelerating wave functions\cite{townsend_data-driven_2019,jones_chapter_2023}, and for applications, such as catalysis and drug discovery.\cite{behler_perspective_2016,goh_deep_2017,sanchez-lengeling_{i}nverse_2018,butler_machine_2018,janet_machine_2020}
+[Sentence about quantum computing]
+Another popular avenue, which combines quantum computing and machine learning, is quantum machine learning (QML).
+QML utilizes quantum algorithms during some portion of the machine learning process in an attempt to outperform classical algorithms. \cite{biamonte_quantum_2017}
+On the current era of quantum computers, parameterized quantum circuits (PQCs) offer an example of QML that is performed using a hybrid quantum-classical feedback loop, where the variational parameters are optimized classical, while the circuit is ran on quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
 
-[parameterized circuits for chemical applications]
+PQCs are often composed using two different subcircuits: the encoding layer, which is used to encode the features into the quantum circuit, and variational layers, which are composed of parameterized gates which can be optimized classical.
 
-[What we introduce]
+PQCs are composed of data-encoding and variational subcircuits, which can be repeated multiple times.
 
+While several examples exist for PQCs applied to chemical applications, they are largely relegated to drug discovery\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,ishiyama_noise-robust_2022,ranga_quantum_2024,alam_qnet_2022,avramouli_quantum_2023,avramouli_unlocking_2023,bhatia_quantum_2023} and experimental properties\cite{hatakeyama-sato_quantum_2023}.
+Herein, we explore two different chemical datasets: one consisting of bond separation energies of 49 unique bond types, called the BSE49 dataset\cite{prasad_bse49_2021}, and another which utilizes data-driven coupled cluster (DDCC)\cite{townsend_data-driven_2019} to predict the coupled-cluster singles and doubles wave function parameters using lower-level quantum chemistry methods.
+
+In this study, we create a robust Python code base for exploring a set of 14 data-encoding and 12 variational (ansatz) subcircuits for a total of 168 combined PQCs.
 Our work includes the single and double encoding layers found in the paper of Suzuki and Katouda\cite{suzuki_predicting_2020}, including the encoding of Mitarai \textit{et al.}\cite{mitarai_quantum_2018}, along with using instantanious quantum polynomial (IQP) as an encoding layer.
@@
 All of our variational (ansatz) layers can be found in the study of Sim \textit{et al.}\cite{sim_expressibility_2019}, where the expressiblity and entanglement capability of these circuits is analyzed.
+We also examine the effects of the number of re-upload and ansatz layers, the effects of feature set size, and various error mitigation techniques.
 
@@
 \section{Methods}
+For our PQCs, we follow the notation provided by Suzuki and Katouda in Ref. \citep{suzuki_predicting_2020}.
+
 Use a mix of  \cite{hatakeyama-sato_quantum_2023} and \cite{suzuki_predicting_2020} for the methods.
 
-Format from \cite{suzuki_predicting_2020}:
-\begin{itemize}
-	\item Feature set $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$
-	\item Feature map (encoding) $U_{\Phi(\mathbf{x})}$ produces the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$
-	\item Variational circuit (ansatz) $U(\mathbf{\theta})$, leads to the parameterized quantum circuit $U(\mathbf{\theta})U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$
-\end{itemize}
+A $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, can be mapped onto a quantum circuit through a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ are the number of qubits.
+For encoding layers, we utilize the three encoding layers found in Ref. \citep{suzuki_predicting_2020} and the instantaneous quantum polynomial circuit found in Ref. \citep{bremner_average-case_2016}
 
-Quantum machine learning is a hybrid classical-quantum approach utilizing parameterized quantum circuits.
-Typical hybrid algorithms consist of shallow circuit depth of one qubit rotations and two qubit entangling gates.
-In the context of machine learning, we can subdivide our circuit into three components: the encoder, the variational circuit, and the act of measuring to estimate predictions.
-The encoder takes our $n$-dimensional data $\bm x \in \R^n$ and encodes it into a unitary feature map $U(\bm x)$ in our working Hilbert Space.
-This unitary acts on our initialized state $\ket{0}^{\otimes n'}$ to produce the state $U(\bm x) \ket{0}^{\otimes n'}$.
-It is usual to take $n' = n$ and for each feature $x_i$ to correspond to a qubit.
-With $n < n'$, features can be repeated across the qubits present in the system.
-Further elaboration will be discussed with specific encoding circuits.
-After the encoder produces the state $U(\bm x)\ket{0}^{\otimes n}$, we then tune the state with a parameterized unitary $U(\bm \theta)$ to transform the state into a meaningful prediction.
-Finally, some configuration of qubits are measured to produce expectation values $\hat y_k$ for our data labels $y_i$ which we then use to minimize a loss function.
-An obstacle in creating quantum models is there is no way to determine the best encoding or variational circuit for the problem.
-As such, this paper explores many different encoding and variational circuits.
-\par
+The single-angle encoding layer is defined as 
+\begin{equation}
+	U_{\text{A1}} = \prod_{i=1}^{n} R^{Y}_{i}(x_{i}) 
+	\label{eq:A1}
+\end{equation}
 
-\subsection{Encoder Circuit}
-Representation of the data in any machine learning context is a crucial factor in its success.
-In a classical sense, this can be thought of as generating features and selecting the appropriate features to input into your model.
-In the quantum context, however, there is the additional question of how to translate the data into the Hilbert space.
-Different proposed  methods include angle encoding, and amplitude encoding.
-Following the work done by Suzuki and Katouda, we explore three base encoders composed together with entangling operations.
-Additionally, we explore the  IQP encoding as given in PennyLane.
-\par
+Double-angle encoding defined as
+\begin{equation}
+	U_{\text{A2}} = \prod_{i=1}^{n}  R^{Z}_{i}(x_{i}) R^{Y}_{i}(x_{i})
+	\label{eq:A2}
+\end{equation}
 
-We composed circuits out of primary rotation blocks and entangling blocks.
-These rotation blocks include the one proposed by Mitrai et al.\cite{mitarai_quantum_2018}, a single angle rotation, and a double rotation encoder:
-\begin{align}
-    U_{A1} &= \prod_{i=1}^n R^Y_i(x_i) \\
-    U_{A2} &= \prod_{i=1}^n R^Y_i(x_i) R^Z_i(x_i) \\
-    U_{M}  &= \prod_{i=1}^n R^Z_i(\arccos x_i^2) R^Y_i(\arcsin x_i^2)
-\end{align}
-Where $R^j_i$ is a rotation about the $j$ axis on qubit $i$.
-It's clear to see that this method of encoding imposes a restriction on the number of features to the number of qubits.
-With this encoding method, it is possible to use more features than qubits and to re-encode the features along the remaining qubits.
-Then, to compose these encoders together we use entangling circuits that entangle adjacent qubits using either CNOT or CZ entangling operations.
-These encoding circuits can be seen presented in Figure \ref{fig: idk circuits or something}.
+Mitarai encoding subcircuits found in 
+\begin{equation}
+	U_{\text{M}}  = \prod_{i=1}^{n} R^{Z}_{i}(\arccos (x_{i}^{2})) R^{Y}_{i}(\arcsin (x_{i}^{2}))
+	\label{eq:M}
+\end{equation}
+IQP [CHECK]
+\begin{equation}
+	U_{\text{IQP}}  = \prod_{i=1}^{n} R^{Z}_{i} (x_{i}) \prod_{i<j} CZ_{ij}  \prod_{i=1}^{n} R^{X}_{i} (x_{i})
+\label{eq:IQP}
+\end{equation}
 
-\subsection{Variational Circuit}
-After encoding the data, we have a quantum circuit in a state $U_{\text{enc}}(\bm x)\ket{0}^{\otimes n}$.
-We need to act on this state with a unitary that has parameters which can be tuned in our machine learning model.
-Choosing this circuit ansatz can greatly dictate the performance of a given model.
-Model performance can be greatly influenced by the variational circuit chosen as well as the depth of the circuit as we will later show.
-It is not obvious which circuit we should pick for our given problem, especially given that our algorithm is not physically motivated like other popular parameterized quantum circuit algorithms.
-We have gathered a list of 12 variational circuit blocks from previous works and libraries which we will then benchmark for our particular problem.
-These circuits each can be decomposed into individual rotation gates and two-qubit entangling gates.
-\par
-After our variational circuit acts on our state we have the state:
-\begin{align}
-    \ket\psi &= U_{\text{var}}(\bm\theta)U_{\text{enc}}(\bm x)\ket{0}^{\otimes n} \label{eq: psi}
-\end{align}
-where $\bm \theta$ is our parameter vector to be tuned in learning.
-We can further modify this state; by repeating variational circuit blocks we create a more rich and complex model with a better ability to explore the Hilbert space.
-This would give us the state:
-\begin{align}
-    \ket\psi &= U_{\text{var}}(\bm\phi)U_{\text{var}}(\bm\theta)U_{\text{enc}}(\bm x)\ket{0}^{\otimes n} \label{eq: layers}
-\end{align}
-However, as we are interested in NISQ applications, it should be noted that increasing layer depths creates decoherence in quantum devices.
-Additionally, we can use the idea of data re-uploading to create redundancies in the encoding of the model to explore a richer feature space.
-\begin{align}
-    \ket\psi &= U_{\text{var}}(\bm\phi)U_{\text{enc}}(\bm x)U_{\text{var}}(\bm\theta)U_{\text{enc}}(\bm x)\ket{0}^{\otimes n} \label{eq: re-up}
-\end{align}
-This paper uses and compares both the data re-uploading and increased depth approaches of creating more complicated models.
+OR
 
-\subsection{Measurement}
-After our system is in state $\ket\psi$ as given by either \eqref{eq: psi}, \eqref{eq: layers} or \eqref{eq: re-up} we can measure our system to generate a predicted value $\hat y_i$.
-At this point in the algorithm, any loss function can be used.
-In our simplest system, we measured the first qubit so that,
-\begin{align}
-    \hat y_i &= \langle Z_0 \rangle _\psi 
-\end{align}
-for a $\psi$ generated by the $k$th data point. Then, we have the loss function we are trying to minimize as,
-\begin{align}
-    \mathcal{L}(\bm{\hat y}) &= \sum_i^N \frac{(y_i - \hat y_i)^2}{N}
-\end{align}
+IQP [CHECK; pennylane]
+\begin{equation}
+	U_{\text{IQP}}  = \prod_{i=1}^{n} H_{i} R^{Z}_{i}(x_{i})  \prod_{i<j} ZZ_{ij}
+	\label{eq:IQP}
+\end{equation}
 

### 2025-01-07 images/encoders/quantikz/IQP.tex
manuscript

\documentclass[preview, border=1mm]{standalone}
\usepackage{tikz} %Format quantum circuits
\usetikzlibrary{quantikz2}%Format quantum circuits
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools,physics}
\def\myvdots{\ \vdots\ }

\begin{document}
\begin{quantikz} 
\lstick{$q_0$} & \gate{H} & \gate{R_{Z} (x_{0})} & \gate[2,disable auto height]{ZZ(x_{0},x_{1})} &  & \gate[3,disable auto height]{ZZ(x_{0},x_{2})} & \gate[5,disable auto height]{ZZ(x_{0},x_{n})}   & & &  \\ 
\lstick{$q_1$} & \gate{H} & \gate{R_{Z} (x_{1})} & & \gate[2,disable auto height]{ZZ(x_{1},x_{2})}  & & &  \gate[4,disable auto height]{ZZ(x_{1},x_{n})}  &  &\\ 
\lstick{$q_2$} & \gate{H} & \gate{R_{Z} (x_{2})} & & & & & & \gate[3,disable auto height]{ZZ(x_{2},x_{n})}  & \\ 
\setwiretype{n} \lstick{}  & \myvdots & \myvdots & \myvdots  & \myvdots & \myvdots & \\
\lstick{$q_n$}& \gate{H}  & \gate{R_{Z} (x_{n})} & & & & & & &\\
\end{quantikz}
\end{document}

### 2025-01-07 manuscript/main.tex
manuscript

@@
 \documentclass[journal=jacsat,manuscript=article]{achemso}
+\SectionNumbersOn
+\usepackage{tikz} %Format quantum circuits
+\usetikzlibrary{quantikz2}%Format quantum circuits
+
 \usepackage{multicol}
@@
 \usepackage[normalem]{ulem}
-% \usepackage{xr-hyper}
-\usepackage[hidelinks]{hyperref} % allows hyperlinking for references
+\usepackage{hyperref} % allows hyperlinking for references
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \usepackage{xcolor}
-% \usepackage{xr-hyper}
-\usepackage{xr-hyper}
-\usepackage{xr}
-
-\usepackage[hidelinks]{hyperref} % allows hyperlinking for references
-
-% \usepackage{hyperref}
 \usepackage{amsmath,amssymb,amsthm}
 \usepackage{mathtools,physics}
-
 \usepackage{subcaption}
-\usepackage{caption}
 % \usepackage{titling}
@@
 
+\def\myvdots{\ \vdots\ }
 %%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
@@
 
-\section{Abstract}
+\section*{Abstract}
 Within the quantum machine learning (QML) field, parameterized quantum circuits (PQCs), built using fixed and parameterized gates, offer a hybrid approach for complex machine learning tasks.
@@
 \newpage
+\setcounter{secnumdepth}{1}
 \section{Introduction}
@@
 \section{Methods}
-For our PQCs, we follow the notation provided by Suzuki and Katouda in Ref. \citep{suzuki_predicting_2020}.
+PQCs are often constructed of three parts: encoding layers that are used to encode the features onto a quantum circuit, variational layers which include parameters that are optimized classically, and measurements which provide numerical estimations of the regression target values.\citep{suzuki_predicting_2020}
+In this study, we utilize the Mitarai (M)\cite{mitarai_quantum_2018}, single- (A1) and double-angle (A2) encoding layers found in Ref.
+\citep{suzuki_predicting_2020}, along with the instantaneous quantum polynomial (IQP) circuit found in Refs.
+\citep{bremner_average-case_2016} and \citep{havlicek_supervised_2019}.
+In the following section, we follow the notations derived from  Ref. \citep{suzuki_predicting_2020}.
+Encoding layers work mapping a $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, normalized on the range $[-1,1]$, onto a quantum circuit using a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ are the number of qubits.
+The encoding layer takes the following general form,
+\begin{equation}
+	U_{\Phi(x)} =  \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})}
+	\label{eq:general_encoding}
+\end{equation}
+where, $E_{\text{ent}}^{l}$ denotes the entangling gates, which can be a CNOT, CZ, or identity ($\mathbf{I}$) gates,   $U_{\phi_{l}(\mathbf{x})}$ denotes the choice of encoding unitaries. 
+Like in  Ref. \citep{suzuki_predicting_2020}, we choose $l \in \{1, 2\}$, such that when $l=1$, $E_{\text{ent}}$ corresponds to an identity matrix and $U_{\Phi(x)} = U_{\phi_{1}(\mathbf{x})}$.
 
-Use a mix of  \cite{hatakeyama-sato_quantum_2023} and \cite{suzuki_predicting_2020} for the methods.
-
-A $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, can be mapped onto a quantum circuit through a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ are the number of qubits.
-For encoding layers, we utilize the three encoding layers found in Ref. \citep{suzuki_predicting_2020} and the instantaneous quantum polynomial circuit found in Ref. \citep{bremner_average-case_2016}
-
-The single-angle encoding layer is defined as 
+When $l=1$, $U_{\Phi(x)}$ can be one of the following four encoding layers: $U_{\text{A1}}$, $U_{\text{A2}}$, $U_{\text{M}}$, or $U_{\text{IQP}}$.
+The single-angle encoding (Fig. \ref{fig:A1}) is the simplest and takes the following form,
 \begin{equation}
-	U_{\text{A1}} = \prod_{i=1}^{n} R^{Y}_{i}(x_{i}) 
+	U_{\text{A1}} = \prod_{i=0}^{n} R^{Y}_{i}(x_{i}),
 	\label{eq:A1}
 \end{equation}
-
-Double-angle encoding defined as
+where $R^{Y}_{i}$ denotes a parameterized Y rotation gate on qubit $i$.
+Like the single-angle encoding, the double-angle encoding (Fig.
+\ref{fig:A2}) utilizes a parameterized Y rotation gate on qubit $i$, with the addition of a parameterized Z rotation gate on qubit $i$, denoted as
 \begin{equation}
-	U_{\text{A2}} = \prod_{i=1}^{n}  R^{Z}_{i}(x_{i}) R^{Y}_{i}(x_{i})
+	U_{\text{A2}} = \prod_{i=0}^{n}  R^{Z}_{i}(x_{i}) R^{Y}_{i}(x_{i}).
 	\label{eq:A2}
 \end{equation}
-
-Mitarai encoding subcircuits found in 
+The Mitarai encoding layer (Fig. \ref{fig:M}) is a double-angle encoding layer with the addition of an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
 \begin{equation}
-	U_{\text{M}}  = \prod_{i=1}^{n} R^{Z}_{i}(\arccos (x_{i}^{2})) R^{Y}_{i}(\arcsin (x_{i}^{2}))
+	U_{\text{M}}  = \prod_{i=0}^{n} R^{Z}_{i}(\arccos (x_{i}^{2})) R^{Y}_{i}(\arcsin (x_{i}^{2})).
 	\label{eq:M}
 \end{equation}
-IQP [CHECK]
+Following the formulation provided in the PennyLane\cite{bergholm_pennylane_2022} software package, the IQP encoding layer (Fig. \ref{fig:IQP}) is defined as,
 \begin{equation}
-	U_{\text{IQP}}  = \prod_{i=1}^{n} R^{Z}_{i} (x_{i}) \prod_{i<j} CZ_{ij}  \prod_{i=1}^{n} R^{X}_{i} (x_{i})
+	U_{\text{IQP}}  = \prod_{i=0}^{n} H_{i} R^{Z}_{i}(x_{i})  \prod_{i<j} ZZ_{ij},
 	\label{eq:IQP}
 \end{equation}
+where $H_{i}$ denotes a Hadamard gate on qubit $i$ and $ZZ_{ij}$ denotes a two-qubit entangline gate defined as $ZZ_{ij} = e^{-i x_{i} x_{j} \sigma_{z} \otimes \sigma_{z}}$.
 
-OR
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[width=\columnwidth]{images/encoders/quantikz/A1.png}
+		\caption{}
+		\label{fig:A1}		
+	\end{subfigure}%
+	\hfill
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[width=\columnwidth]{images/encoders/quantikz/A2.png}
+		\caption{}
+		\label{fig:A2}		
+	\end{subfigure}%
+	\hfill
+	\begin{subfigure}{0.3\textwidth}
+		\centering
+		\includegraphics[width=1\columnwidth]{images/encoders/quantikz/M.png}
+		\caption{}
+		\label{fig:M}		
+	\end{subfigure}%	  
+	\hfill
+	\begin{subfigure}{1\textwidth}
+		\centering
+		    \includegraphics[width=\columnwidth]{images/encoders/quantikz/IQP.png}
+		\caption{}
+		\label{fig:IQP}
+	\end{subfigure}%
+	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
+	\label{fig:encoders}
+\end{figure}
 
-IQP [CHECK; pennylane]
+When $l=2$, like in Ref.
+\citep{suzuki_predicting_2020} we choose entanglement gates, $E_{\text{ent}}^{1}$ and $E_{\text{ent}}^{2}$ to be equivalent, and the encoding layer takes the following form, $U_{\Phi(x)} =  E_{\text{ent}} U_{\phi_{2}(\mathbf{x})} E_{\text{ent}} U_{\phi_{1}(\mathbf{x})}$ .
+We also exclude IQP encoding when $l=2$ due to the increased circuit depth, when compared to A1, A2, and M encoding.
+Therefore, there are five unique combinations of $U_{\phi_{1}(\mathbf{x})}$ and $U_{\phi_{2}(\mathbf{x})}$ (M-M, A1-A1, A2-A2, M-A1, and M-A2) and two different entanglement layer options (CNOT and CZ) for a total of 10 encoding circuits.
+These circuits are denoted as $U_{\phi_{1}(\mathbf{x})}-U_{\phi_{2}(\mathbf{x})}-E_{\text{ent}}$, for example, two example encoding circuits are M--M--CNOT and M--A1--CNOT.
+Table \ref{tab:encoders} shows all fourteen encoding circuits examined in this study.
+
+\begin{table}[htbp]
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{Name} & $U_{\phi_{1}(\mathbf{x})}$ & $U_{\phi_{2}(\mathbf{x})}$ & $E_{\text{ent}}$  \\
+		\hline
+		\hline
+		A1 & $U_{\text{A1}}$ & --- & --- \\
+		\hline
+		A2 & $U_{\text{A2}}$ & --- & --- \\
+		\hline		
+		M & $U_{\text{M}}$ & --- & --- \\
+		\hline
+		IQP & $U_{\text{IQP}}$ & --- & --- \\
+		\hline
+		A1--A1--CNOT & $U_{\text{A1}}$ & $U_{\text{A1}}$ & $E_{\text{CNOT}}$ \\
+		\hline
+		 A2--A2--CNOT & $U_{\text{A2}}$ & $U_{\text{A2}}$ & $E_{\text{CNOT}}$ \\
+		\hline
+		M--M--CNOT & $U_{\text{M}}$ & $U_{\text{M}}$ & $E_{\text{CNOT}}$ \\
+		\hline
+		M--A1--CNOT & $U_{\text{M}}$ & $U_{\text{A1}}$ & $E_{\text{CNOT}}$ \\
+		\hline		
+		M--A2--CNOT & $U_{\text{M}}$ & $U_{\text{A2}}$ & $E_{\text{CNOT}}$ \\
+		\hline				
+		A1--A1--CZ & $U_{\text{A1}}$ & $U_{\text{A1}}$ & $E_{\text{CZ}}$ \\
+		\hline
+		A2--A2--CZ& $U_{\text{A2}}$ & $U_{\text{A2}}$ & $E_{\text{CZ}}$ \\
+		\hline
+		M--M--CZ & $U_{\text{M}}$ & $U_{\text{M}}$ & $E_{\text{CZ}}$ \\
+		\hline
+		M--A1--CZ & $U_{\text{M}}$ & $U_{\text{A1}}$ & $E_{\text{CZ}}$ \\
+		\hline		
+		M--A2--CZ & $U_{\text{M}}$ & $U_{\text{A2}}$ & $E_{\text{CZ}}$ \\
+		\hline						
+	\end{tabular}
+	\caption{Add something smart}
+	\label{tab:encoders}
+\end{table}
+
+Following the encoding layers,variational (or ansatz) layers are used to introduce trainable parameters into the quantum circuit.
+We use a mixed notation from Refs.
+\citep{suzuki_predicting_2020} and \citep{sim_expressibility_2019}, since Ref.
+\citep{sim_expressibility_2019} contains all of the variational layers used within this work.
+We relegate the discussion of the expressibility and entanglement of these layers to Section \ref{section:results_and_discussion}
+
 \begin{equation}
-	U_{\text{IQP}}  = \prod_{i=1}^{n} H_{i} R^{Z}_{i}(x_{i})  \prod_{i<j} ZZ_{ij}
-	\label{eq:IQP}
+	U(\bm{\theta}) = \prod_{v} U_{v}(\bm{\theta}_{v}) E_{\text{ent}}^{v}
+	\label{eq:general_variational}
 \end{equation}
+
+12 variational layers
+ESU2
+Efficient-CRX
+Efficient-CRZ
+Full-CRX
+Full-CRZ
+Full-Pauli-CRX
+Full-Pauli-CRZ
+HWE-CNOT
+HWE-CZ
+Hadamard
+Modified-Pauli-CRX
+Modified-Pauli-CRZ
+
+\begin{quantikz}
+	\lstick{$q_0$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{0}^{2}))} & \gate{R_{Z} (\arccos(x_{0})^{2})} & \\
+	\lstick{$q_1$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{1}^{2}))} & \gate{R_{Z} (\arccos(x_{1})^{2})} & \\
+	\lstick{$q_2$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{2}^{2}))} & \gate{R_{Z} (\arccos(x_{2})^{2})} & \\
+	\setwiretype{n} \lstick{}  & \myvdots & \myvdots & \myvdots & \\
+	\lstick{$q_n$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{n}^{2}))} & \gate{R_{Z} (\arccos(x_{n})^{2})} & \\
+\end{quantikz}
+
+\begin{equation}
+	U(\bm{\theta}) U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n} = \prod_{k}
+	\left( \prod_{v} U_{v}(\bm{\theta}_{v}) E_{\text{ent}}^{v}   \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})} \right)  \ket{0}^{\otimes n}
+\end{equation}
+
+$v \in \{1, 3, 5\}$
+$k \in \{1, 3, 5\}$
 
@@
 For the BSE dataset, various molecular representations are explored, and we settled on using Morgan fingerprints with X parameters. 
-For the feature reduction, we use PCA, as explained in Section \ref{subsubsection:BSE}.
+For the feature reduction, we use PCA, as explained in Section
 
@@
 
-\section{Results}
+\section{Results and Discussion}
+\label{section:results_and_discussion}
 

### 2025-01-07 BSE_RUD_AL_test/16qubit/3RUD/helperfiles/add_params.py

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[1]:
+
+
+from glob import glob
+import sys
+import os
+import shutil
+import joblib
+import json
+
+
+# In[2]:
+
+
+for p in glob('*/*.json'):
+    print(p)
+    with open(p,'r') as f:
+        olddt=json.load(f)
+    
+    
+    olddt["BATCH_SIZE"]=25
+    olddt["NUM_CORES"]=16
+    olddt['TOLERANCE']=1e-6
+    olddt['MAX_ITER']=1000
+    print(olddt)    
+
+    with open(p,'w') as g:
+        json.dump(olddt,g)
+

### 2025-01-07 BSE_RUD_AL_test/16qubit/3RUD/rnd1_A2_Hadamard/runlocal.sh

@@ -1,0 +1,1 @@
+python3 /home/ubuntu/5qubit/3RUD/main.py --settings /home/ubuntu/5qubit/3RUD/M-M-CZ_HWE-CNOT/M-M-CZ_HWE-CNOT.json --train_set /home/ubuntu/5qubit/3RUD/PCA5_0.8_Morgan_train.bin --test_set /home/ubuntu/5qubit/3RUD/PCA5_0.8_Morgan_test.bin --scaler /home/ubuntu/5qubit/3RUD/PCA5_0.8_Morgan_scaler.bin --save_path /home/ubuntu/5qubit/3RUD/M-M-CZ_HWE-CNOT --resume_file final_state_model.bin 

### 2025-01-07 BSE_RUD_AL_test/16qubit/3_RUD/run.sh

@@ -1,31 +1,0 @@
-#! /bin/bash
-
-for i in */; do
-    name=${i%/}
-    # Extracting the parent directory name
-    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
-    path="/home/gjones/scratch/BSE_RUD_AL_test/16qubit/3_RUD/${name}"
-    if [ ! -f ${path}/${name}_results.json ]; then
-        echo "${name}.done not found!"
-    	cat > ${name}.sub <<EOF
-#! /bin/bash
-#SBATCH -t 7-00:00:00
-#SBATCH -J 3_RUD_PCA16_Morgan_${name}
-#SBATCH -N 1
-#SBATCH -n 16
-#SBATCH --mem-per-cpu=260M
-#SBATCH --account=rrg-jacobsen-ab
-#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
-#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
-
-module load apptainer 
-cd /home/gjones/scratch/BSE_RUD_AL_test/16qubit/3_RUD/$name
-apptainer run -C -B /home/gjones/scratch/BSE_RUD_AL_test/16qubit/3_RUD ~/deb.sif /opt/miniconda/bin/python /home/gjones/scratch/BSE_RUD_AL_test/16qubit/3_RUD/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set /home/gjones/scratch/BSE_RUD_AL_test/16qubit/3_RUD/PCA16_Morgan_train.bin --test_set /home/gjones/scratch/BSE_RUD_AL_test/16qubit/3_RUD/PCA16_Morgan_test.bin --scaler /home/gjones/scratch/BSE_RUD_AL_test/16qubit/3_RUD/PCA16_Morgan_scaler.bin >> ${name}.out 2>&1 
-
-cd ..
-touch ${name}.done
-
-EOF
-    fi
-    echo "Done ${name}.sub"
-done

### 2025-01-07 BSE_RUD_AL_test/16qubit/5AL/run.sh

@@ -1,0 +1,28 @@
+#! /bin/bash
+cwd=$(pwd)
+errorname=$(basename `pwd`)
+echo $cwd
+i="A2_Hadamard/"
+name=${i%/}
+# Extracting the parent directory name
+settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
+path="${cwd}/${name}"
+cat > ${name}.sub <<EOF
+#! /bin/bash
+#SBATCH -t 0-23:59:59
+#SBATCH -J ${errorname}_${name}
+#SBATCH -N 1
+#SBATCH -n 80
+#SBATCH --account=rrg-fekl-ac
+#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
+#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
+
+
+export OMP_NUM_THREADS=80
+cd $(pwd)/$name
+/scinet/niagara/software/2019b/opt/base/python/3.11.5/bin/python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.8_Morgan_train.bin --test_set ${cwd}/PCA16_0.8_Morgan_test.bin --scaler ${cwd}/PCA16_0.8_Morgan_scaler.bin  --resume_file ${path}/partial_state_model.bin  > ${name}.out 2>&1
+
+cd ..
+touch ${name}.done
+
+EOF

### 2025-01-07 BSE_RUD_AL_test/16qubit/fix.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+for i in ./* ; do
+ if [[ $i != '5qubithelp' && -d $i ]]; then
+ echo $i
+ cd $i 
+ cp ../add_params.py ./ 
+ python3 add_params.py 
+ cd ../
+ fi
+done

### 2025-01-07 BSE_RUD_AL_test/16qubit/rename.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+dir=$(find . -name "M-M-CZ_HWE-CNOT")
+
+for i in $dir; do
+ topdir=$(dirname $i)
+ echo $topdir
+ echo $i
+ mv -f $i $topdir/A2_Hadamard
+done

### 2025-01-07 BSE_RUD_AL_test/16qubit/run.sh

@@ -1,0 +1,33 @@
+#! /bin/bash
+cwd=$(pwd)
+errorname=$(basename `pwd`)
+echo $cwd
+for i in */; do
+    name=${i%/}
+    # Extracting the parent directory name
+    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
+    path="${cwd}/${name}"
+    if [ ! -f ${path}/${name}_results.json ]; then
+        echo "${name}.done not found!"
+    	cat > ${name}.sub <<EOF
+#! /bin/bash
+#SBATCH -t 0-23:59:59
+#SBATCH -J ${errorname}_${name}
+#SBATCH -N 1
+#SBATCH -n 80
+#SBATCH --account=rrg-fekl-ac
+#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
+#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
+
+
+export OMP_NUM_THREADS=80
+cd $(pwd)/$name
+/scinet/niagara/software/2019b/opt/base/python/3.11.5/bin/python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.8_Morgan_train.bin --test_set ${cwd}/PCA16_0.8_Morgan_test.bin --scaler ${cwd}/PCA16_0.8_Morgan_scaler.bin --resume_file ${path}/partial_state_model.bin > ${name}.out 2>&1
+
+cd ..
+touch ${name}.done
+
+EOF
+    fi
+    echo "Done ${name}.sub"
+done

### 2025-01-07 BSE_RUD_AL_test/16qubit/submitall.sh

@@ -1,16 +1,17 @@
 #!/bin/bash
-dirs=$(find . -maxdepth 1 -type d)
+dirs=$(find . -maxdepth 1 -mindepth 1 -type d)
+echo $(pwd)
 for i in $dirs; do
   echo $i
-  if [ -e "$i/run.sh" ]; then
-      echo "File exists"
-      cd $i
+  cd $i
+  echo $(pwd)
+  cp ../run.sh .
+  echo "File exists $i/run.sh"
+  if [ -e "run.sh" ]; then
       rm *done *.o* *.e* *sub
       bash run.sh
-      unzip helperfiles.zip
-      cp -r helperfiles/* .
-      rm quantum.sub __pycache__.sub helperfiles.sub 
+      rm quantum.sub __pycache__.sub helperfiles.sub
       find . -name "*sub" -exec sbatch {} \;
-      cd ../
-  fi 
+  fi
+  cd ../
 done

### 2025-01-07 images/encoders/quantikz/convert.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+pdflatex A1.tex
+pdflatex A2.tex
+pdflatex M.tex
+pdflatex IQP.tex
+
+convert -density 300 A1.pdf -quality 100 A1.png
+convert -density 300 A2.pdf -quality 100 A2.png
+convert -density 300 M.pdf -quality 100 M.png
+convert -density 300 IQP.pdf -quality 100 IQP.png
+

### 2025-01-08 images/ansatz/quantikz/Full-CRX.tex
manuscript images

\documentclass[preview, border=1mm]{standalone}
\usepackage{tikz} %Format quantum circuits
\usetikzlibrary{quantikz2}%Format quantum circuits
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools,physics}
\def\myvdots{\ \vdots\ }

\begin{document}

%Full-CRX
\resizebox{\textwidth}{!}{
\begin{quantikz}
	\lstick{$q_0$}& \gate{RX} & \gate{RZ} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RX} &&&&\gate{RX}&&&&\gate{RX}& &&&\gate{RX}&&&&\\
	\lstick{$q_1$}& \gate{RX} & \gate{RZ} & \gate{RX} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&&\\
	\lstick{$q_2$}& \gate{RX} & \gate{RZ} && \gate{RX}&&&&\gate{RX}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RX}&&&&\gate{RX}&&\\
	\lstick{$q_3$}& \gate{RX} & \gate{RZ} &&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RX}&\\
	\lstick{$q_4$}& \gate{RX} & \gate{RZ} &&&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
\end{quantikz}
}

\end{document}

### 2025-01-08 images/ansatz/quantikz/Full-CRZ.tex
manuscript images

\documentclass[preview, border=1mm]{standalone}
\usepackage{tikz} %Format quantum circuits
\usetikzlibrary{quantikz2}%Format quantum circuits
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools,physics}
\def\myvdots{\ \vdots\ }

\begin{document}
%Full-CRZ
\resizebox{\textwidth}{!}{
	\begin{quantikz}
		\lstick{$q_0$}& \gate{RX} & \gate{RZ} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RZ} &&&&\gate{RZ}&&&&\gate{RZ}& &&&\gate{RZ}&&&&\\
		\lstick{$q_1$}& \gate{RX} & \gate{RZ} & \gate{RZ} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&&\\
		\lstick{$q_2$}& \gate{RX} & \gate{RZ} && \gate{RZ}&&&&\gate{RZ}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RZ}&&&&\gate{RZ}&&\\
		\lstick{$q_3$}& \gate{RX} & \gate{RZ} &&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RZ}&\\
		\lstick{$q_4$}& \gate{RX} & \gate{RZ} &&&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RX}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
	\end{quantikz}
}

\end{document}

### 2025-01-08 manuscript/main.tex
manuscript images
manuscript Wed  8 Jan 2025 16:55:43 EST

@@
 \usepackage[normalem]{ulem}
-\usepackage{hyperref} % allows hyperlinking for references
+\usepackage[hidelinks]{hyperref} % allows hyperlinking for references
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 When $l=1$, $U_{\Phi(x)}$ can be one of the following four encoding layers: $U_{\text{A1}}$, $U_{\text{A2}}$, $U_{\text{M}}$, or $U_{\text{IQP}}$.
-The single-angle encoding (Fig. \ref{fig:A1}) is the simplest and takes the following form,
+The single-angle encoding (Fig. \ref{fig:encoders} \textbf{(a)}) is the simplest and takes the following form,
 \begin{equation}
@@
 Like the single-angle encoding, the double-angle encoding (Fig.
-\ref{fig:A2}) utilizes a parameterized Y rotation gate on qubit $i$, with the addition of a parameterized Z rotation gate on qubit $i$, denoted as
+\ref{fig:encoders} \textbf{(b)}) utilizes a parameterized Y rotation gate on qubit $i$, with the addition of a parameterized Z rotation gate on qubit $i$, denoted as
 \begin{equation}
@@
 \end{equation}
-The Mitarai encoding layer (Fig. \ref{fig:M}) is a double-angle encoding layer with the addition of an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
+The Mitarai encoding layer (Fig.
+\ref{fig:encoders} \textbf{(c)}) is a double-angle encoding layer with the addition of an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
 \begin{equation}
@@
 \end{equation}
-Following the formulation provided in the PennyLane\cite{bergholm_pennylane_2022} software package, the IQP encoding layer (Fig. \ref{fig:IQP}) is defined as,
+Following the formulation provided in the PennyLane\cite{bergholm_pennylane_2022} software package, the IQP encoding layer (Fig. \ref{fig:encoders} \textbf{(d)}) is defined as,
 \begin{equation}
@@
 
+%\begin{figure}[H]
+%       \centering
+%       \begin{subfigure}{0.3\textwidth}
+	%               \centering
+	%               \includegraphics[width=\textwidth]{images/encoders/quantikz/A1.png}
+	%               \caption{}
+	%               \label{fig:A1}
+	%       \end{subfigure}%
+%       \hfill
+%       \begin{subfigure}{0.3\textwidth}
+	%               \centering
+	%               \includegraphics[width=\textwidth]{images/encoders/quantikz/A2.png}
+	%               \caption{}
+	%               \label{fig:A2}
+	%       \end{subfigure}%
+%       \hfill
+%       \begin{subfigure}{0.3\textwidth}
+	%               \centering
+	%               \includegraphics[width=1\textwidth]{images/encoders/quantikz/M.png}
+	%               \caption{}
+	%               \label{fig:M}
+	%       \end{subfigure}%
+%       \hfill
+%       \begin{subfigure}{1\textwidth}
+	%               \centering
+	%                   \includegraphics[width=\textwidth]{images/encoders/quantikz/IQP.png}
+	%               \caption{}
+	%               \label{fig:IQP}
+	%       \end{subfigure}%
+%       \caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
+%       \label{fig:encoders}
+%\end{figure}
+
 \begin{figure}[H]
 	\centering
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[width=\columnwidth]{images/encoders/quantikz/A1.png}
-		\caption{}
-		\label{fig:A1}		
-	\end{subfigure}%
-	\hfill
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[width=\columnwidth]{images/encoders/quantikz/A2.png}
-		\caption{}
-		\label{fig:A2}		
-	\end{subfigure}%
-	\hfill
-	\begin{subfigure}{0.3\textwidth}
-		\centering
-		\includegraphics[width=1\columnwidth]{images/encoders/quantikz/M.png}
-		\caption{}
-		\label{fig:M}		
-	\end{subfigure}%	  
-	\hfill
-	\begin{subfigure}{1\textwidth}
-		\centering
-		    \includegraphics[width=\columnwidth]{images/encoders/quantikz/IQP.png}
-		\caption{}
-		\label{fig:IQP}
-	\end{subfigure}%
+	\includegraphics[width=\textwidth]{images/encoders/quantikz/combined.png}
 	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
@@
 \citep{sim_expressibility_2019} contains all of the variational layers used within this work.
-We relegate the discussion of the expressibility and entanglement of these layers to Section \ref{section:results_and_discussion}
-
+We relegate the discussion of the expressibility and entanglement examined in that work to Section \ref{section:results_and_discussion}.
+A general variational layer can be denoted as,
 \begin{equation}
-	U(\bm{\theta}) = \prod_{v} U_{v}(\bm{\theta}_{v}) E_{\text{ent}}^{v}
+	U(\bm{\theta}) = \prod_{v} U_{v}(\bm{\theta}_{v}), % E_{\text{ent}}^{v}
 	\label{eq:general_variational}
 \end{equation}
+where $\bm{\theta}$ denotes the variational parameters and $v$ denotes the number of times that the layer is repeated within the circuit. 
+As $v$ increases and the number of trainable parameters ($\bm{\theta}$) increase, the theoretical assumption is that the model expressibility should also increase.
+In our study, we choose $v \in \{1, 3, 5\}$ and refer to this as the number of ansatz layers (ALs).
+We examine 12 different variational circuits, as shown in Fig.
+\ref{fig:ansatz}, which are denoted using the following labels: Modified-Pauli-CRZ (Fig.
+\ref{fig:ansatz}\textbf{(a)}) , Modified-Pauli-CRX (Fig.
+\ref{fig:ansatz}\textbf{(b)}), Efficient-CRZ (Fig.
+\ref{fig:ansatz}\textbf{(c)}), Efficient-CRX (Fig.
+\ref{fig:ansatz}\textbf{(d)}),, HWE-CNOT (Fig.
+\ref{fig:ansatz}\textbf{(e)}), HWE-CZ (Fig.
+\ref{fig:ansatz}\textbf{(f)}), ESU2 (Fig.
+\ref{fig:ansatz}\textbf{(g)}), Full-Pauli-CRZ (Fig.
+\ref{fig:ansatz}\textbf{(h)}), Full-Pauli-CRX (Fig.
+\ref{fig:ansatz}\textbf{(i)}), Hadamard (Fig.
+\ref{fig:ansatz}\textbf{(j)}), Full-CRZ (Fig.
+\ref{fig:ansatz}\textbf{(k)}), and Full-CRX (Fig.
+\ref{fig:ansatz}\textbf{(l)}),
 
-12 variational layers
-ESU2
-Efficient-CRX
-Efficient-CRZ
-Full-CRX
-Full-CRZ
-Full-Pauli-CRX
-Full-Pauli-CRZ
-HWE-CNOT
-HWE-CZ
-Hadamard
-Modified-Pauli-CRX
-Modified-Pauli-CRZ
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{images/ansatz/quantikz/combined.png}
+	\caption{(a) Modified-Pauli-CRZ, (b) Modified-Pauli-CRX, (c) Efficient-CRZ, (d) Efficient-CRX, (e) HWE-CNOT, (f) HWE-CZ,  (g) ESU2, (h) Full-Pauli-CRZ, (i) Full-Pauli-CRX, (j) Hadamard, (k) Full-CRZ, and (l)Full-CRX}
+	\label{fig:ansatz}
+\end{figure}
 
-\begin{quantikz}
-	\lstick{$q_0$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{0}^{2}))} & \gate{R_{Z} (\arccos(x_{0})^{2})} & \\
-	\lstick{$q_1$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{1}^{2}))} & \gate{R_{Z} (\arccos(x_{1})^{2})} & \\
-	\lstick{$q_2$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{2}^{2}))} & \gate{R_{Z} (\arccos(x_{2})^{2})} & \\
-	\setwiretype{n} \lstick{}  & \myvdots & \myvdots & \myvdots & \\
-	\lstick{$q_n$} & \gate{H} & \gate{R_{Y} (\arcsin(x_{n}^{2}))} & \gate{R_{Z} (\arccos(x_{n})^{2})} & \\
-\end{quantikz}
+Now that we have define the encoding (Eq. \ref{eq:general_encoding}) and variational (Eq. \ref{eq:general_variational}) circuits, we can then combine them to denote a general, complete circuit as,
+\begin{equation}
+	\ket{\Psi} = U(\bm{\theta}) U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n} = \prod_{k}
+	\left( \prod_{v} U_{v}(\bm{\theta}_{v}) \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})} \right)  \ket{0}^{\otimes n},
+\end{equation}
+where we choose $k \in \{1, 3, 5\}$, which denotes the re-upload depth (RUD) of the circuit.
+When a sufficient number of data re-uploading occur, it has been shown by P\'{e}rez-Salinas \textit{et al.} that data re-uploading is equivalent to the Universal Approximation Theorem for artificial neural networks.\cite{perez-salinas_data_2020}
 
+Lastly, to recover the predicted target values, $\hat{y}_{i}$, from our quantum circuits, measurement of the quantum state, $\ket{\Psi}$, must be performed.
+To perform this operation, we apply the Pauli Z operator on the first qubit denoted as,
 \begin{equation}
-	U(\bm{\theta}) U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n} = \prod_{k}
-	\left( \prod_{v} U_{v}(\bm{\theta}_{v}) E_{\text{ent}}^{v}   \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})} \right)  \ket{0}^{\otimes n}
+	\hat{y}_{i} = \bra{\Psi}Z_{0}\ket{\Psi}_{i}.
+	\label{eq:y_pred}
+\end{equation}
+The set of predicted target values, $\bm{\hat{y}} = (\hat{y}_{1}, \ldots, \hat{y}_{N}) \in \mathbb{R}^{N}$, where $N$ is the number of samples, is then passed to the loss function, $\mathcal{L}(\bm{y}, \bm{\hat y})$, where $y_{i}$ belongs to the set of true target values $\bm{y} = (y_{1}, \ldots, y_{N}) \in \mathbb{R}^{N}$.
+In practice, $\mathcal{L}$ can be any loss function but we choose to use the mean square error loss function denoted as,
+\begin{equation}
+	\mathcal{L}(\bm{y}, \bm{\hat y}) = \frac{1}{N} \sum_{i=1}^{N} (y_{i} - \hat{y}_{i})^{2}.
+	\label{eq:isthisloss}
 \end{equation}
 
-$v \in \{1, 3, 5\}$
-$k \in \{1, 3, 5\}$
-
 \subsection{Implementation}
-Our work was implemented in Python using PennyLane for constructing the quantum circuits, and Qulacs as a primary backend for simulating the circuits.
-The optimization was implemented using the scipy.optimize module from the SciPy library.
-Classical models were implemented using scikit-learn while processing of the data was handled with Pandas, NumPy, and SciPy libraries.
+Python
+Pennylane
+Pennylane Qiskit
+Pennylane Qulacs
+Qiskit
+SciPy
+Scikit-learn
 
 Simulated using FakeQuebecbackend
+IBM Quebec
+
+Error mitigation using
+MITIQ (delete because this is useless for the Qiskit stuff... try level 2 for ZNE...)
 
@@
 We trained our models using three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
-
-For the function fitting dataset, there is only one feature per target value.
-For the DDCC dataset, there are initially X features, reduced down to 5 and 16 features, respectively, using SHapley Additive exPlanation (SHAP) values.\cite{lundberg_unified_2017}
-
-\begin{equation}
-	t^{ab}_{ij(\text{MP2})} = \frac{\mel{ij}{}{ab}}{\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}}
-	\label{eq:MP2_t2}
-\end{equation}
-
-For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$), binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
-
-For the BSE dataset, various molecular representations are explored, and we settled on using Morgan fingerprints with X parameters. 
-For the feature reduction, we use PCA, as explained in Section
-
-% Make distribution plot
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=\linewidth]{images/BSE.png}
-%	\caption{BSE}
-%	\label{fig:BSE}
-%\end{figure}
 
@@
 
+For the function fitting dataset, there is only one feature per target value.
+
+For the BSE dataset, various molecular representations are explored, and we settled on using Morgan fingerprints with X parameters. 
+For the feature reduction, we use PCA, as explained in Section
+
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../classical_testing/BSE/BSE_16_learning_curve}
+		\caption{}
+		\label{fig:bse16learningcurve}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
+		\caption{}
+		\label{fig:classicalfuncfit}
+	\end{subfigure}
+	\caption{}
+	\label{fig:bse16classical}	
+\end{figure}
+
+For the DDCC dataset, there are initially X features, reduced down to 5 and 16 features, respectively, using SHapley Additive exPlanation (SHAP) values.\cite{lundberg_unified_2017}
+
+\begin{equation}
+	t^{ab}_{ij(\text{MP2})} = \frac{\mel{ij}{}{ab}}{\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}}
+	\label{eq:MP2_t2}
+\end{equation}
+
+For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$), binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
+
+% Make distribution plot
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=\linewidth]{images/BSE.png}
+%	\caption{BSE}
+%	\label{fig:BSE}
+%\end{figure}
+
 \section{Results and Discussion}
 \label{section:results_and_discussion}
+
+\subsection{Classical Data Analysis}
+
+ \begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/BSE/classical_features_MAE.png}
+		\caption{}
+		\label{fig:BSE_bse_classical_features_MAE}
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/BSE/classical_features_R2.png}
+		\caption{}
+		\label{fig:BSE_classical_features_R2}
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/DDCC/DDCC_feature_set.png}
+		\caption{}
+		\label{fig:DDCC_feature_set}
+	\end{subfigure}
+	\hfill	
+	\caption{}
+	\label{fig:chemical_classical_features}
+\end{figure}
+
+\subsection{Function Fitting}
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/linear_heatplots.png}
+		\caption{}
+		\label{fig:linear_heatplots}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/linear_boxplots.png}
+		\caption{}
+		\label{fig:linear_boxplots}
+	\end{subfigure}
+	\hfill	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/quadratic_heatplots.png}
+		\caption{}
+		\label{fig:quadratic_heatplots}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/quadratic_boxplots.png}
+		\caption{}
+		\label{fig:quadratic_boxplots}
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/sine_heatplots.png}
+		\caption{}
+		\label{fig:sine_heatplots}
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/sine_boxplots.png}
+		\caption{}
+		\label{fig:sine_boxplots}
+	\end{subfigure}
+	\hfill		
+	\caption{}
+	\label{fig:fivequbit_ff_heat}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/linear_heatplots.png}
+		\caption{}
+		\label{fig:sixteenlinear_heatplots}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/linear_boxplots.png}
+		\caption{}
+		\label{fig:sixteenlinear_boxplots}
+	\end{subfigure}
+	\hfill	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/quadratic_heatplots.png}
+		\caption{}
+		\label{fig:sixteenquadratic_heatplots}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/quadratic_boxplots.png}
+		\caption{}
+		\label{fig:sixteenquadratic_boxplots}
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/sine_heatplots.png}
+		\caption{}
+		\label{fig:sixteensine_heatplots}
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/sine_boxplots.png}
+		\caption{}
+		\label{fig:sixteensine_boxplots}
+	\end{subfigure}
+	\hfill		
+	\caption{}
+	\label{fig:sixteensixteenqubit_ff_heat}
+\end{figure}
+
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
+		\caption{}
+		\label{fig:16qubit_Linear_RUD_AL}
+	\end{subfigure}
+	\hfill	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/linear_circuitdepth_vs_R2}
+		\caption{}
+		\label{fig:linear_circuitdepth_vs_R2}
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Quadratic_RUD_AL}
+		\caption{}
+		\label{fig:16qubit_Quadratic_RUD_AL}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/quadratic_circuitdepth_vs_R2}
+		\caption{}
+		\label{fig:quadratic_circuitdepth_vs_R2}
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
+		\caption{}
+		\label{fig:16qubitlinearrudal}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/sine_circuitdepth_vs_R2}
+		\caption{}
+		\label{fig:sine_circuitdepth_vs_R2}
+	\end{subfigure}
+	\hfill		
+	\caption{}
+	\label{fig:16qubit_RUD_AL}	
+\end{figure}
+
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/linear_learning_curves.png}
+		\caption{}
+		\label{fig:linear_learning_curves}
+	\end{subfigure}
+	\hfill	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/quadratic_learning_curves.png}
+		\caption{}
+		\label{fig:quadratic_learning_curves}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/Function_Fitting/sine_learning_curves.png}
+		\caption{}
+		\label{fig:sine_learning_curves}
+	\end{subfigure}	
+	\caption{}
+	\label{fig:functionfitting_learning_curves}	
+\end{figure}
+
+\subsection{BSE}
+
+\subsection{DDCC}
+
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/DDCC/DDCC_heatplots}
+		\caption{}
+		\label{fig:ddccheatplots}
+	\end{subfigure}
+	\hfill	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/DDCC/DDCC_boxplots}
+		\caption{}
+		\label{fig:ddccboxplots}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
+		\caption{}
+		\label{fig:allddcc5circuitdepthr2vsiterationtime}
+	\end{subfigure}	
+	\caption{}
+	\label{fig:ddcc_all_analysis}	
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{images/DDCC/DDCC_RUDAL}
+	\caption{}
+	\label{fig:ddccrudal}
+\end{figure}
 

### 2025-01-09 manuscript/main.tex
rm symbolic link manuscript/images

@@
 	%               \centering
-	%               \includegraphics[width=\textwidth]{images/encoders/quantikz/A1.png}
+	%               \includegraphics[width=\textwidth]{../images/encoders/quantikz/A1.png}
 	%               \caption{}
@@
 	%               \centering
-	%               \includegraphics[width=\textwidth]{images/encoders/quantikz/A2.png}
+	%               \includegraphics[width=\textwidth]{../images/encoders/quantikz/A2.png}
 	%               \caption{}
@@
 	%               \centering
-	%               \includegraphics[width=1\textwidth]{images/encoders/quantikz/M.png}
+	%               \includegraphics[width=1\textwidth]{../images/encoders/quantikz/M.png}
 	%               \caption{}
@@
 	%               \centering
-	%                   \includegraphics[width=\textwidth]{images/encoders/quantikz/IQP.png}
+	%                   \includegraphics[width=\textwidth]{../images/encoders/quantikz/IQP.png}
 	%               \caption{}
@@
 	\centering
-	\includegraphics[width=\textwidth]{images/encoders/quantikz/combined.png}
+	\includegraphics[width=\textwidth]{../images/encoders/quantikz/combined.png}
 	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
@@
 	\centering
-	\includegraphics[width=\textwidth]{images/ansatz/quantikz/combined.png}
+	\includegraphics[width=\textwidth]{../images/ansatz/quantikz/combined.png}
 	\caption{(a) Modified-Pauli-CRZ, (b) Modified-Pauli-CRX, (c) Efficient-CRZ, (d) Efficient-CRX, (e) HWE-CNOT, (f) HWE-CZ,  (g) ESU2, (h) Full-Pauli-CRZ, (i) Full-Pauli-CRX, (j) Hadamard, (k) Full-CRZ, and (l)Full-CRX}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/linear_train_vs_test.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/linear_train_vs_test.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/function_dataset/sine_train_vs_test.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/sine_train_vs_test.png}
 		\caption{}
@@
 %	\centering
-%	\includegraphics[width=\linewidth]{images/BSE.png}
+%	\includegraphics[width=\linewidth]{../images/BSE.png}
 %	\caption{BSE}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/BSE/classical_features_MAE.png}
+		\includegraphics[width=\textwidth]{../images/BSE/classical_features_MAE.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/BSE/classical_features_R2.png}
+		\includegraphics[width=\textwidth]{../images/BSE/classical_features_R2.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/DDCC/DDCC_feature_set.png}
+		\includegraphics[width=\textwidth]{../images/DDCC/DDCC_feature_set.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/linear_heatplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/linear_heatplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/linear_boxplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/linear_boxplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/quadratic_heatplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/quadratic_heatplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/quadratic_boxplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/quadratic_boxplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/sine_heatplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/sine_heatplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/fivequbit/sine_boxplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/sine_boxplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/linear_heatplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/linear_heatplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/linear_boxplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/linear_boxplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/quadratic_heatplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/quadratic_heatplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/quadratic_boxplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/quadratic_boxplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/sine_heatplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/sine_heatplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\textwidth]{images/Function_Fitting/sixteenqubit/sine_boxplots.png}
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/sine_boxplots.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/Function_Fitting/linear_circuitdepth_vs_R2}
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_circuitdepth_vs_R2}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/Function_Fitting/sixteenqubit/16qubit_Quadratic_RUD_AL}
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Quadratic_RUD_AL}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/Function_Fitting/quadratic_circuitdepth_vs_R2}
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_circuitdepth_vs_R2}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/Function_Fitting/sine_circuitdepth_vs_R2}
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_circuitdepth_vs_R2}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/Function_Fitting/linear_learning_curves.png}
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_learning_curves.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/Function_Fitting/quadratic_learning_curves.png}
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_learning_curves.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/Function_Fitting/sine_learning_curves.png}
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_learning_curves.png}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/DDCC/DDCC_heatplots}
+		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_heatplots}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/DDCC/DDCC_boxplots}
+		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_boxplots}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
+		\includegraphics[width=\linewidth]{../images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
 		\caption{}
@@
 	\centering
-	\includegraphics[width=\linewidth]{images/DDCC/DDCC_RUDAL}
+	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL}
 	\caption{}

### 2025-01-09 manuscript/main.tex
Thu Jan  9 04:57:33 PM EST 2025

@@
 Python
-Pennylane
-Pennylane Qiskit
-Pennylane Qulacs
-Qiskit
-SciPy
-Scikit-learn
+Pennylane\cite{bergholm_pennylane_2022}
+Pennylane Qiskit\cite{javadi-abhari_quantum_2024}
+Pennylane Qulacs\cite{suzuki_qulacs_2021}
+Qiskit\cite{javadi-abhari_quantum_2024}
+SciPy Minimize \cite{virtanen_scipy_2020}
+Scikit-learn\cite{pedregosa_scikit-learn_2011}
+
+``All HF calculations were performed in the Psi4 \cite{parrish_psi4_2017} program.
+The MP2 and coupled-cluster calculations were performed using the Psi4Numpy \cite{smith_psi4numpy_2018} spin-factored CCSD implementation.
+\cite{stanton_direct_1991}''
 
@@
 Error mitigation using
-MITIQ (delete because this is useless for the Qiskit stuff... try level 2 for ZNE...)
+TREX \cite{van_den_berg_model-free_2022}
 
@@
 
-% Make distribution plot
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=\linewidth]{../images/BSE.png}
-%	\caption{BSE}
-%	\label{fig:BSE}
-%\end{figure}
-
-\section{Results and Discussion}
-\label{section:results_and_discussion}
-
-\subsection{Classical Data Analysis}
-
 \begin{figure}[H]
@@
 \end{figure}
+
+% Make distribution plot
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=\linewidth]{../images/BSE.png}
+%	\caption{BSE}
+%	\label{fig:BSE}
+%\end{figure}
+
+\section{Results and Discussion}
+\label{section:results_and_discussion}
 
@@
 
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_error_mitigation.png}
+		\caption{}
+		\label{fig:linear_error_mitigation}
+	\end{subfigure}
+	\hfill	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_error_mitigation.png}
+		\caption{}
+		\label{fig:linear_error_mitigation}
+	\end{subfigure}	
+	\caption{}
+	\label{fig:functionfitting_errormitigation}	
+\end{figure}
+
 \subsection{BSE}

### 2025-01-09 function-calc-test/funct_error_mitigation/quadratic/Without/IQP_Full-Pauli-CRX/runtest.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+export OMP_NUM_THREADS=64
+topdir=$(dirname "$(pwd)")
+python3 ${topdir}/main.py --settings $(pwd)/IQP_Full-Pauli-CRX.json --train_set ${topdir}/quadratic_train.bin --test_set ${topdir}/quadratic_test.bin --scaler ${topdir}/quadratic_scaler.bin --save_path $(pwd) # --resume_file $(pwd)/final_state_model.bin  

### 2025-01-09 function-calc-test/funct_error_mitigation/quadratic/Without/view_loss.py

@@ -1,0 +1,27 @@
+#!/bin/python3
+import click
+import numpy as np
+import matplotlib.pyplot as plt
+
+@click.command()
+@click.option('--path', required=True, type=click.Path(exists=True), help='Path to model_log.csv')
+
+def main(path):
+
+    with open(path,'r') as f:
+        filename=f.readlines()
+    
+    save=[]
+    for i in filename:
+        if ':' in i:
+            splitf=i.split(',')
+            save.append((splitf[1],splitf[2]))
+    
+    save=np.array(save).astype(float)
+    
+    plt.plot(save[:,0],save[:,1])
+    plt.show()
+
+
+if __name__ == '__main__':
+    main()

### 2025-01-09 function-calc-test/funct_error_mitigation/quadratic/without/IQP_Full-Pauli-CRX/runtest.sh

@@ -1,4 +1,0 @@
-#!/bin/bash
-export OMP_NUM_THREADS=64
-topdir=$(dirname "$(pwd)")
-python3 ${topdir}/main.py --settings $(pwd)/IQP_Full-Pauli-CRX.json --train_set ${topdir}/quadratic_train.bin --test_set ${topdir}/quadratic_test.bin --scaler ${topdir}/quadratic_scaler.bin --save_path $(pwd) # --resume_file $(pwd)/final_state_model.bin  

### 2025-01-09 function-calc-test/funct_error_mitigation/quadratic/without/combined_loss.py

@@ -1,44 +1,0 @@
-#!/usr/bin/env python3
-import click
-import numpy as np
-import matplotlib.pyplot as plt
-from glob import glob
-import os
-
-@click.command()
-@click.option('--path', required=True, type=click.Path(exists=True), help='Path to model_log.csv; e.g. A2_HWE-CNOT/')
-def main(path):
-    splitsort = []
-    smaller = []
-    for i in glob(os.path.join(path, '*log.csv')):
-        splitname = os.path.basename(i).split('_')
-        if len(splitname)==3:
-            splitsort.append((int(splitname[0]),i))
-        else:
-            smaller.append(i)
-
-    loss = []
-    for i in list(np.array(sorted(splitsort))[:,1])+smaller:
-        print(f"Processing file: {i}")
-        loss.append(split(i)[:, 1])  # Get only the loss values (assumed to be in the second column)
-    plt.plot(np.hstack(loss))
-    plt.xlabel("Iteration")
-    plt.ylabel("Loss")
-    plt.title("Loss Curve")
-    plt.show()
-
-def split(path):
-    """Helper function to read CSV file and extract required columns."""
-    save = []
-    with open(path, 'r') as f:
-        for line in f:
-            if ':' in line:
-                split_line = line.strip().split(',')
-                # Assuming the structure of each line is: [timestamp, loss_value, ...]
-                save.append((float(split_line[1]), float(split_line[2])))
-    return np.array(save)
-
-if __name__ == '__main__':
-    main()
-
-

### 2025-01-13 manuscript/main.tex
manuscript bse

@@
 \subsection{BSE}
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_heatplots}
+		\caption{}
+		\label{fig:5BSE_heatplots}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_boxplots}
+		\caption{}
+		\label{fig:5BSE_boxplots}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_heatplots}
+		\caption{}
+		\label{fig:16BSE_heatplots}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_boxplots}
+		\caption{}
+		\label{fig:16BSE_boxplots}
+	\end{subfigure}
+	\caption{}
+	\label{fig:BSEboxandheat}	
+\end{figure}
+
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE5_RUDAL}
+		\caption{}
+		\label{fig:bse5rudal}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE16_RUDAL}
+		\caption{}
+		\label{fig:bse16rudal}
+	\end{subfigure}
+	\caption{}
+	\label{fig:BSE_RUD_AL}	
+\end{figure}
 

### 2025-01-15 manuscript/main.tex
manuscript + Batches
manuscript Wed 15 Jan 2025 17:07:35 EST

@@
 \subsection{Implementation}
-Python
-Pennylane\cite{bergholm_pennylane_2022}
-Pennylane Qiskit\cite{javadi-abhari_quantum_2024}
-Pennylane Qulacs\cite{suzuki_qulacs_2021}
-Qiskit\cite{javadi-abhari_quantum_2024}
-SciPy Minimize \cite{virtanen_scipy_2020}
-Scikit-learn\cite{pedregosa_scikit-learn_2011}
-
-``All HF calculations were performed in the Psi4 \cite{parrish_psi4_2017} program.
-The MP2 and coupled-cluster calculations were performed using the Psi4Numpy \cite{smith_psi4numpy_2018} spin-factored CCSD implementation.
-\cite{stanton_direct_1991}''
-
-Simulated using FakeQuebecbackend
-IBM Quebec
-
-Error mitigation using
-TREX \cite{van_den_berg_model-free_2022}
+We perform all simulation calculations using PennyLane\cite{bergholm_pennylane_2022}, either using Qulacs\cite{suzuki_qulacs_2021} for state vector calcualtions, while noisy calculations were performed using \textit{qiskit-aer} with the \textit{FakeQuebec} backend as implemented in the PennyLane-Qiskit plugin.\cite{javadi-abhari_quantum_2024}
+We perform calculations in the \textit{ibm\_quebec} device using circuits implemented using Qiskit\cite{javadi-abhari_quantum_2024}, due to issues we initially faced with running experiments on the real device using the PennyLane-Qiskit plugin.
+For the experiments using PennyLane,  we utilize the Simultaneous Perturbation Stochastic Approximation method (SPSA) as implemented in PennyLane, while for the experiments run on \textit{ibm\_quebec} utilizes the Constrained Optimization By Linear Approximation (COBYLA) optimizer as implemented ing SciPy\cite{virtanen_scipy_2020}.
+Each optimizer was chosen based on the performance for the given task.
+All features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all featues and target values are $\mathbb{R}\in [ -1,1 ]$.
+For the simulations using \textit{FakeQuebec} and experiments on \textit{ibm\_quebec} we utilize Twirled Readout Error eXtinction (TREX) error mitigation.
 
 \subsection{Dataset}
-We trained our models using three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
+In this study, we explore three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
+
+The noisy function fitting dataset is generated by
+
+$f(x) = x + \varepsilon$ such that $\varepsilon \in \mathcal{N} (0, \sigma^{2} )$
 
@@
 \end{figure}
+
+``All HF calculations were performed in the Psi4 \cite{parrish_psi4_2017} program.
+The MP2 and coupled-cluster calculations were performed using the Psi4Numpy \cite{smith_psi4numpy_2018} spin-factored CCSD implementation.
+\cite{stanton_direct_1991}''
 
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\linewidth]{../images/BSE/fivequbit/BSE5_learning_curves}
+	\caption{}
+	\label{fig:bse5learningcurves}
+\end{figure}
+
 \subsection{DDCC}

### 2025-01-16 manuscript/main.tex
Thu Jan 16 03:21:02 PM EST 2025

@@
 The noisy function fitting dataset is generated by
-
-$f(x) = x + \varepsilon$ such that $\varepsilon \in \mathcal{N} (0, \sigma^{2} )$
+$f(x) = x + \varepsilon$ such that $\varepsilon \in \mathcal{N} (0, \sigma^{2} )$, where $\sigma\approx0.34$.
+The linear function is $f(x)=x$, quadratic is $f(x) = 0.3967 x^{2} - 3.2807 x + 6.7569$, and sine function is $f(x) = 0.9913 \sin(2.3838 x+0.0344)$.
+The normalized versions are shown in Fig. \ref{fig:train_vs_test}.
 
@@
 
-For the function fitting dataset, there is only one feature per target value.
+The first chemical dataset we explore is the BSE49 dataset. 
+This dataset consists of homolytic bond cleavages of X molecules and 49 unique bond types.
+One important aspect of this dataset is the choice of molecular representation, or how the molecule is represented in the machine learning models.
 
 For the BSE dataset, various molecular representations are explored, and we settled on using Morgan fingerprints with X parameters. 
+80\% train 20\%test Fig. \ref{fig:classicalfuncfit} 
+\ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE}
+
 For the feature reduction, we use PCA, as explained in Section
@@
 	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../classical_testing/BSE/BSE_16_learning_curve}
-		\caption{}
-		\label{fig:bse16learningcurve}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
 	\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
@@
 	\label{fig:classicalfuncfit}
-	\end{subfigure}
-	\caption{}
-	\label{fig:bse16classical}	
 \end{figure}

### 2025-01-18 manuscript/main.tex
Fri Jan 17 07:14:41 PM EST 2025

@@
 \usepackage{xcite}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Our work includes the single and double encoding layers found in the paper of Suzuki and Katouda\cite{suzuki_predicting_2020}, including the encoding of Mitarai \textit{et al.}\cite{mitarai_quantum_2018}, along with using instantanious quantum polynomial (IQP) as an encoding layer.
-\cite{bremner_average-case_2015}
+\cite{bremner_average-case_2016}
 All of our variational (ansatz) layers can be found in the study of Sim \textit{et al.}\cite{sim_expressibility_2019}, where the expressiblity and entanglement capability of these circuits is analyzed.
@@
 
-The first chemical dataset we explore is the BSE49 dataset. 
-This dataset consists of homolytic bond cleavages of X molecules and 49 unique bond types.
+\cite{rupp_fast_2012}
+\cite{rogers_extended-connectivity_2010}
+
+The first chemical dataset we explore is the BSE49 dataset which consists of homolytic bond cleavages, such as \ce{A-B -> A^{.} + B^{.}}, of X molecules with 49 unique bond types.
 One important aspect of this dataset is the choice of molecular representation, or how the molecule is represented in the machine learning models.
+To find the optimal molecular representation, we examined five different molecular representations including Coulomb Matrices \cite{rupp_fast_2012}, Molecular ACCess Systems fingerprint (MACCS)\cite{durant_reoptimization_2002}, persistence images (PIs) \cite{adams_persistence_2017,townsend_representation_2020,schiff_augmenting_2022}, RDKit [cite], and Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}.
+For each representation we tested two different choices of representation, one based on the the products minus the reactants, denoted by \textit{sub}, similar to the method used in [cite], and one based on just the reactants, denoted as \textit{AB}.
+We use the same 80\% train/20\% test split as we use throughout our studies. 
+We found that the best molecular representation across all models test, as shown in Fig. \ref{fig:classicalfuncfit}, was Morgan fingerprints using the \textit{sub} formulation.
 
-For the BSE dataset, various molecular representations are explored, and we settled on using Morgan fingerprints with X parameters. 
-80\% train 20\%test Fig. \ref{fig:classicalfuncfit} 
-\ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE}
-
-For the feature reduction, we use PCA, as explained in Section
+One challenge of applying classical molecular representations for quantum machine learning models is mapping the classical features, often containing hundreds or thousands of features per sample, to the number of qubits used.
+Using the \textit{sub}-Morgan fingerprints, we explore mapping these features to 5 and 16 qubits, the number of qubits used throughout this study, using SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017} and principal component analysis (PCA).
+We found that the most accurate models, using both 5 and 16 features, were those generated by PCA, as shown in Fig. \ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE}.
 
 \begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
 		\centering	
@@
 		\label{fig:classicalfuncfit}
-\end{figure}
-
-``All HF calculations were performed in the Psi4 \cite{parrish_psi4_2017} program.
-The MP2 and coupled-cluster calculations were performed using the Psi4Numpy \cite{smith_psi4numpy_2018} spin-factored CCSD implementation.
-\cite{stanton_direct_1991}''
-
-For the DDCC dataset, there are initially X features, reduced down to 5 and 16 features, respectively, using SHapley Additive exPlanation (SHAP) values.\cite{lundberg_unified_2017}
-
-\begin{equation}
-	t^{ab}_{ij(\text{MP2})} = \frac{\mel{ij}{}{ab}}{\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}}
-	\label{eq:MP2_t2}
-\end{equation}
-
-For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$), binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
-
-\begin{figure}[H]
-	\centering
+	\end{subfigure}
+	\hfill	
 	\begin{subfigure}[b]{0.49\textwidth}
@@
 	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
+	\caption{}
+	\label{fig:bse_classical_features}
+\end{figure}
+
+The next chemical dataset explored is based on the Data-Driven Coupled-Cluster (DDCC) methods found in Ref. \cite{townsend_data-driven_2019,jones_chapter_2023}.
+DDCC is a machine learning-based method for accelerating coupled-cluster singles and doubles (CCSD) calculations by predicting the CCSD T2-amplitudes using features generated by a lower-level method, typically Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2).
+We generate a database consisting X water molecules with y features for each molecule, using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
+
+Like with the BSE dataset, we explore how we can reduce the initial y features down to 5 and 16 features using SHAP and PCA.
+
+\begin{equation}
+	t^{ab}_{ij(\text{MP2})} = \frac{\mel{ij}{}{ab}}{\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}}
+	\label{eq:MP2_t2}
+\end{equation}
+
+For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$), binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
+
+\begin{figure}[H]
 	\centering
@@
 	\label{fig:DDCC_feature_set}
-	\end{subfigure}
-	\hfill	
-	\caption{}
-	\label{fig:chemical_classical_features}
 \end{figure}
@@
 %\end{figure}
+
+We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the sense that for every molecule you will have $N_{occ}^{2}\cdot N_{virt}^{2}$ entries.
 
@@
 		\caption{}
-		\label{fig:linear_error_mitigation}
+		\label{fig:quadratic_error_mitigation}
 	\end{subfigure}	

### 2025-01-20 manuscript/main.tex
manuscript Mon 20 Jan 2025 17:04:40 EST

@@
 
-\subsection{Dataset}
-In this study, we explore three datasets: a function fitting dataset, consisting of a noisy linear, quadratic, and sine function, used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
-
-The noisy function fitting dataset is generated by
-$f(x) = x + \varepsilon$ such that $\varepsilon \in \mathcal{N} (0, \sigma^{2} )$, where $\sigma\approx0.34$.
-The linear function is $f(x)=x$, quadratic is $f(x) = 0.3967 x^{2} - 3.2807 x + 6.7569$, and sine function is $f(x) = 0.9913 \sin(2.3838 x+0.0344)$.
-The normalized versions are shown in Fig. \ref{fig:train_vs_test}.
+\subsection{Datasets}
+In this study, we explore three datasets: a function fitting dataset, consisting of a noisy functions used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
+The function fitting dataset consists of a noisy linear (Fig. \ref{fig:linear_train_vs_test}), quadratic (Fig. \ref{fig:quadratic_train_vs_test}), and sine (\ref{fig:sine_train_vs_test}) function.  
+For each function, 90 points are generated, where 80 are used for training set and 10 for the test set.
+This dataset is used for calibration of the 168 PQCs, along with providing additional insights into the effects of circuit depth, training set size, and error mitigation on model performance.
 
@@
 	\end{subfigure}
-	\caption{}
+	\caption{The function fitting dataset which consists of 90 total points, 80 for training and 10 used for testing, for the (a) linear, (b) quadratic, and (c) sine functions.}
 	\label{fig:train_vs_test}
@@
 
-\cite{rupp_fast_2012}
-\cite{rogers_extended-connectivity_2010}
+Following model calibration using the function fitting dataset, we explore the appliciblity of PQCs for complex chemically relevant machine learning tasks.
+The first chemically motivated dataset we explore is the BSE49 dataset, which contains the bond seperation energies (BSE)  for the homolytic bond cleavage of covalently bonded molecules, such as \ce{A-B -> A^{.} + B^{.}}.\cite{prasad_bse49_2021}
+This dataset consists of 4394 datapoints (!VIKI! paper says 4502), 1951 of which are existing and 2443 are hypthoetical structures, with 49 unique A-B single bond types.
+In practice, we used 2436 of the hypothetical structures due to issues with valency exceptions when converting to RDKit mol objects which were later used for generating our features for the machine learning models.
+An important aspect of machine learning in chemistry is the choice of molecular representation, or how the molecule is represented in the machine learning models.\cite{jones_molecular_2023}
 
-The first chemical dataset we explore is the BSE49 dataset which consists of homolytic bond cleavages, such as \ce{A-B -> A^{.} + B^{.}}, of X molecules with 49 unique bond types.
-One important aspect of this dataset is the choice of molecular representation, or how the molecule is represented in the machine learning models.
+ Cite:
+DScribe\cite{himanen_dscribe_2020} CMs and SOAPs + REMatchKernel
+
+Ripser\cite{tralie_ripserpy_2018}
+RDKit\cite{noauthor_rdkit_nodate}
+
+SOAPs\cite{de_comparing_2016} were excluded due to the cost of computing the kernel
+
 To find the optimal molecular representation, we examined five different molecular representations including Coulomb Matrices \cite{rupp_fast_2012}, Molecular ACCess Systems fingerprint (MACCS)\cite{durant_reoptimization_2002}, persistence images (PIs) \cite{adams_persistence_2017,townsend_representation_2020,schiff_augmenting_2022}, RDKit [cite], and Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}.
+
+\begin{equation}
+	X_{\text{RDKit},i} = X_{\text{RDKit},i}^{\text{R}} - X_{\text{RDKit},i}^{\text{R}}
+	\label{eq:descriptor_garcia}
+\end{equation}
+
+An additional challenge for choosing a molecular representions for the BSE49 dataset is how to represent the overall chemical system
+
+ We found that the best molecular representation across all models test, as shown in Fig.
+\ref{fig:classicalfuncfit}, was Morgan fingerprints using the \textit{sub} formulation.\cite{garcia-andrade_barrier_2023}
+
 For each representation we tested two different choices of representation, one based on the the products minus the reactants, denoted by \textit{sub}, similar to the method used in [cite], and one based on just the reactants, denoted as \textit{AB}.
+
 We use the same 80\% train/20\% test split as we use throughout our studies.
-We found that the best molecular representation across all models test, as shown in Fig. \ref{fig:classicalfuncfit}, was Morgan fingerprints using the \textit{sub} formulation.
 

### 2025-01-22 manuscript/main.tex
Wed 22 Jan 2025 16:56:42 EST

@@
 In this study, we explore three datasets: a function fitting dataset, consisting of a noisy functions used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
+We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the sense that for every molecule you will have $N_{occ}^{2}\cdot N_{virt}^{2}$ entries.
+
 The function fitting dataset consists of a noisy linear (Fig. \ref{fig:linear_train_vs_test}), quadratic (Fig. \ref{fig:quadratic_train_vs_test}), and sine (\ref{fig:sine_train_vs_test}) function.  
@@
 The first chemically motivated dataset we explore is the BSE49 dataset, which contains the bond seperation energies (BSE)  for the homolytic bond cleavage of covalently bonded molecules, such as \ce{A-B -> A^{.} + B^{.}}.\cite{prasad_bse49_2021}
-This dataset consists of 4394 datapoints (!VIKI! paper says 4502), 1951 of which are existing and 2443 are hypthoetical structures, with 49 unique A-B single bond types.
+This dataset consists of 4394 datapoints, 1951 of which are existing and 2443 are hypthoetical structures, with 49 unique A-B single bond types.
 In practice, we used 2436 of the hypothetical structures due to issues with valency exceptions when converting to RDKit mol objects which were later used for generating our features for the machine learning models.
 An important aspect of machine learning in chemistry is the choice of molecular representation, or how the molecule is represented in the machine learning models.\cite{jones_molecular_2023}
-
- Cite:
-DScribe\cite{himanen_dscribe_2020} CMs and SOAPs + REMatchKernel
-
-Ripser\cite{tralie_ripserpy_2018}
-RDKit\cite{noauthor_rdkit_nodate}
-
-SOAPs\cite{de_comparing_2016} were excluded due to the cost of computing the kernel
-
-To find the optimal molecular representation, we examined five different molecular representations including Coulomb Matrices \cite{rupp_fast_2012}, Molecular ACCess Systems fingerprint (MACCS)\cite{durant_reoptimization_2002}, persistence images (PIs) \cite{adams_persistence_2017,townsend_representation_2020,schiff_augmenting_2022}, RDKit [cite], and Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}.
-
-\begin{equation}
-	X_{\text{RDKit},i} = X_{\text{RDKit},i}^{\text{R}} - X_{\text{RDKit},i}^{\text{R}}
-	\label{eq:descriptor_garcia}
-\end{equation}
-
-An additional challenge for choosing a molecular representions for the BSE49 dataset is how to represent the overall chemical system
-
- We found that the best molecular representation across all models test, as shown in Fig.
-\ref{fig:classicalfuncfit}, was Morgan fingerprints using the \textit{sub} formulation.\cite{garcia-andrade_barrier_2023}
-
-For each representation we tested two different choices of representation, one based on the the products minus the reactants, denoted by \textit{sub}, similar to the method used in [cite], and one based on just the reactants, denoted as \textit{AB}.
-
-We use the same 80\% train/20\% test split as we use throughout our studies.
+Using RDKit\cite{noauthor_rdkit_nodate} we examined three commonly applied graph-based molecular preresentations, Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002}, Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, and RDKit fingerprints.
+All three of these methods are use traversals of the molecular graphs to encode various structural details into bit vectors.
+Lastly, we explore both topology- and physics-based molecular representations, both of which encode the three-dimensional structure of molecules in various, unique ways.
+Persistent images (PIs) are a topology-based fingerprint that uses persistence homology to encode topological information of three-dimensional molecular structures into fixed dimension images.\cite{adams_persistence_2017,townsend_representation_2020,schiff_augmenting_2022}
+We use the implementation from Townsend \textit{et al.}\cite{townsend_representation_2020}, which uses the Ripser Python package to generate PIs.\cite{tralie_ripserpy_2018}
+Lastly, we explre two physics-based representations, Coulomb matrices (CMs) \cite{rupp_fast_2012} and smooth overlap of atomic positions (SOAPs), that were generated using DScribe.\cite{de_comparing_2016}
+Due to the computational cost of computing the regularized entropy match (REMatch) kernel  with the SOAPs representation, we excluded this representation in the overall discussion.
+We  also tested two different methods for representing the components of the bond separation chemical reaction, one where the feature vectors for the products are subtracted from the reactants, denoted by \textit{sub}, similar to the method used in Ref.
+\cite{garcia-andrade_barrier_2023}, and one that is composed of the reactant molecular only, denoted as \textit{AB}.
+Since we are analyzing a diverse set of PQCs, we used a set of three different classic regression models, with varying capabilities, implemented in sckit-learn.\cite{pedregosa_scikit-learn_2011}
+Based on our results shown in Fig. \ref{fig:classicalfuncfit} we found that Morgan fingerprints
+We found that the best molecular representation across all models test, as shown in Fig. \ref{fig:classicalfuncfit}, was Morgan fingerprints using the \textit{sub} formulation.
 
 One challenge of applying classical molecular representations for quantum machine learning models is mapping the classical features, often containing hundreds or thousands of features per sample, to the number of qubits used.
+
+Morgan has X featues per sample
+
 Using the \textit{sub}-Morgan fingerprints, we explore mapping these features to 5 and 16 qubits, the number of qubits used throughout this study, using SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017} and principal component analysis (PCA).
@@
 		\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
-		\caption{}
+		\caption{FIX}
 		\label{fig:classicalfuncfit}
@@
 
-The next chemical dataset explored is based on the Data-Driven Coupled-Cluster (DDCC) methods found in Ref. \cite{townsend_data-driven_2019,jones_chapter_2023}.
+The next chemical dataset explored is based on the Data-Driven Coupled-Cluster (DDCC) method found in Refs. \cite{townsend_data-driven_2019,jones_chapter_2023}.
 DDCC is a machine learning-based method for accelerating coupled-cluster singles and doubles (CCSD) calculations by predicting the CCSD T2-amplitudes using features generated by a lower-level method, typically Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2).
 We generate a database consisting X water molecules with y features for each molecule, using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
-
-Like with the BSE dataset, we explore how we can reduce the initial y features down to 5 and 16 features using SHAP and PCA.
-
+The orignal feature set consists of X 
 \begin{equation}
@@
 \end{equation}
-
+Like with the BSE dataset, we explore how we can reduce the initial y features down to 5 and 16 features using SHAP and PCA.
 For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$), binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
@@
 
-We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the sense that for every molecule you will have $N_{occ}^{2}\cdot N_{virt}^{2}$ entries.
-
 \section{Results and Discussion}
@@
 		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/linear_heatplots.png}
-		\caption{}
+		\caption{replot y axis}
 		\label{fig:linear_heatplots}

### 2025-01-24 manuscript/main.tex
$(date)

@@
 
-\usepackage{xcite}
+\usepackage{xr-hyper}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-One challenge of applying classical molecular representations for quantum machine learning models is mapping the classical features, often containing hundreds or thousands of features per sample, to the number of qubits used.
-
+One challenge of applying classical molecular representations for quantum machine learning models is mapping the classical features, often containing hundreds or thousands of features per sample, to the number of qubits used on the quantum device.
 Morgan has X featues per sample
@@
 	\end{subfigure}	
-	\caption{}
+	\caption{(a) linear, (b) quadratic, (c) sine function}
 	\label{fig:functionfitting_learning_curves}	
@@
 	\end{subfigure}	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_error_mitigation.png}
 		\caption{}
+		\label{fig:sine_error_mitigation}
+	\end{subfigure}
+	\hfill		
+	\caption{(a) linear, (b) quadratic, (c) sine function}
 	\label{fig:functionfitting_errormitigation}	

### 2025-01-24 function-calc-test/funct_error_mitigation/sine/without/quantum/circuits/Ansatz.py

@@ -1,0 +1,492 @@
+import pennylane as qml
+from .Encoders import entangle_cnot, entangle_cz
+from qiskit.circuit.library import n_local
+
+
+def rotation_layer(parameters, wires, three_rotations=True):
+    if not three_rotations:
+        if len(parameters) != 2 * len(wires):
+            raise ValueError("Unsopported number of parameters. Expected amount should be", 3 * len(wires))
+    else:
+        if len(parameters) != 3 * len(wires):
+            raise ValueError("Unsupported number of parameters. Expected amount should be", 3 * len(wires))
+    for i in range(len(wires)):
+        if three_rotations:
+            qml.RX(parameters[3 * i], wires=wires[i])
+            qml.RZ(parameters[3 * i + 1], wires=wires[i])
+            qml.RX(parameters[3 * i + 2], wires=wires[i])
+        else:
+            qml.RX(parameters[2 * i], wires=wires[i])
+            qml.RZ(parameters[2 * i + 1], wires=wires[i])
+
+
+class HardwareEfficient:
+    _entangle_types = {
+        'CNOT': entangle_cnot,
+        'CZ': entangle_cz
+    }
+
+    def __init__(self, wires: list = None, layers: int = 1, entangle_type: str = 'CNOT'):
+        self._layers = layers
+        if entangle_type not in self._entangle_types.keys():
+            raise ValueError("Unexpected entangling type. Possible types are:", self._entangle_types.keys())
+        self.entangler = self._entangle_types[entangle_type]
+        self._wires = wires
+
+    def __call__(self, parameters, wires: list = None):
+        if wires is not None:
+            self._wires = wires
+        if len(parameters) != 3 * self._layers * len(self._wires):
+            raise ValueError("Expected ", 3 * self._layers * len(self._wires), "parameters but got ", len(parameters))
+        for i in range(self._layers):
+            start_index = i * 3 * len(self._wires)
+            end_index = start_index + 3 * len(self._wires)
+            rotation_layer(parameters[start_index:end_index], self._wires)
+            self.entangler(self._wires)
+
+    @property
+    def num_params(self):
+        return 3 * self._layers * len(self._wires)
+
+    @property
+    def layers(self):
+        return self._layers
+
+    @layers.setter
+    def layers(self, val):
+        self._layers = val
+
+    def set_wires(self, wires):
+        self._wires = wires
+
+
+class EfficientSU2:
+
+    def __init__(self,
+                 wires: list = None,
[…]

### 2025-01-24 manuscript/main.tex
$(date)

@@
 
-One challenge of applying classical molecular representations for quantum machine learning models is mapping the classical features, often containing hundreds or thousands of features per sample, to the number of qubits used on the quantum device.
-Morgan has X featues per sample
+\begin{figure}[H]
+	\centering	
+	\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
+	\caption{FIX:The performance of various molecular representations is shown using different classical machine learning models.
+\textit{AB} (top row) and \textit{sub} (bottom row) denote how the chemical reaction is represented.
+Each column denotes a different classical machine learning model, where the first column, denoted as knn, refers to \textit{k}-nearest neighbors, the second column, labeled rfr, denotes random forest regression, and krr, the last column, denotes kernel ridge regression.
+The x-axis of each sub-figure denotes the various molecular representations that are analyzed: Coulomb matrices (CM), Molecular ACCess Systems (MACCS), persistence images (PIs), RDKit fingerprints (RDKit), and Morgan fingerprints (Morgan).The y-axis of each sub-figure shows the performance of each model, evaluated using the R$^{2}$, where the training set is denoted using light blue and the test set is dark blue.}
+	\label{fig:classicalfuncfit}
+\end{figure}
 
-Using the \textit{sub}-Morgan fingerprints, we explore mapping these features to 5 and 16 qubits, the number of qubits used throughout this study, using SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017} and principal component analysis (PCA).
-We found that the most accurate models, using both 5 and 16 features, were those generated by PCA, as shown in Fig. \ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE}.
+An additional challenge of applying classical molecular representations for quantum machine learning models is mapping the classical features, often containing hundreds or thousands of features per sample, to the number of qubits used on the quantum device.
+Initially, the Morgan fingerpints have 2048 features per sample, that need to be reduced down to 5 or 16 qubits.
+We choose 5 and 16 qubits for two reasons, the first is that these were the standard number of qubits on IBM quantum devices when we started the project and the second is that reducing the number of features reduces the depth of the circuits.
+To reduce the feature set from 2048 to 5 or 16 features, we explore two different methods, SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017} and principal component analysis (PCA), as implemented in scikit-learn.\cite{pedregosa_scikit-learn_2011}
+Figs. \ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE} show the results for the reductions using SHAP and PCA for the training and test set of using 5 and 16 features.
+The initial model using 2048 features has a train and test mean absolute error (MAE) of 1.91 and 4.98 kcal/mol, with train and test R$^{2}$s of 0.99 and 0.91, respectively.
+When using SHAP to reduce the feature set size to 5 features, we see that the training set has an MAE of 16.08 kcal/mol and an R$^{2}$ of 0.39, while for the test set has an MAE of 15.86 kcal/mol and an R$^{2}$ of 0.42.
+When the number of features is reduced to 16 features using SHAP, we see slight improvements with train and test MAEs of 10.48 and 11.08 kcal/mol with R$^{2}$s of 0.69 and 0.68, respectively.
+Using PCA, we see an improvement in accuracy for both 5 and 16 features, where the training sets have MAEs of 4.09 and 3.23 kcal/mol and the test sets have MAEs of 10.17 and 8.40 kcal/mol, respectively.
+The R$^{2}$s for PCA with 5 and 16 features also shows improvement over the reductions using SHAP, with R$^{2}$s of 0.95 and 0.69 for the training and test set, respectively, using 5 features and 0.97 and 0.78 for the training and test set, respectively, using 16 features.
+Due to the increased performance, despite exhibiting overfitting, we choose to use Morgan fingerprints reduced using PCA for our QML models.
 
@@
 	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering	
-		\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
-		\caption{FIX}
-		\label{fig:classicalfuncfit}
-	\end{subfigure}
-	\hfill	
 	\begin{subfigure}[b]{0.49\textwidth}
@@
 	\end{subfigure}
-	\caption{}
+	\caption{Feature reduction of the BSE dataset represented using }
 	\label{fig:bse_classical_features}
@@
 DDCC is a machine learning-based method for accelerating coupled-cluster singles and doubles (CCSD) calculations by predicting the CCSD T2-amplitudes using features generated by a lower-level method, typically Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2).
-We generate a database consisting X water molecules with y features for each molecule, using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
-The orignal feature set consists of X 
+We generate a database consisting 199 water molecules with 31 features for each molecule, using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
+
 \begin{equation}

### 2025-01-24 manuscript/main.tex
Fri Jan 24 05:01:56 PM EST 2025 manuscript mainly

@@
 \subsection{Datasets}
-In this study, we explore three datasets: a function fitting dataset, consisting of a noisy functions used for model calibration; a dataset consisting of electronic structure features to predict wavefunctions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
+In this study, we explore three datasets: a function fitting dataset, consisting of a noisy functions used for model calibration; a dataset consisting of electronic structure features to predict wave functions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
 We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the sense that for every molecule you will have $N_{occ}^{2}\cdot N_{virt}^{2}$ entries.
@@
 
-The next chemical dataset explored is based on the Data-Driven Coupled-Cluster (DDCC) method found in Refs. \cite{townsend_data-driven_2019,jones_chapter_2023}.
-DDCC is a machine learning-based method for accelerating coupled-cluster singles and doubles (CCSD) calculations by predicting the CCSD T2-amplitudes using features generated by a lower-level method, typically Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2).
-We generate a database consisting 199 water molecules with 31 features for each molecule, using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
-
+The next chemical dataset explored is based on the data-driven coupled-cluster (DDCC) method, which is a machine learning-based approach for accelerating the convergence of coupled-cluster singles and doubles (CCSD) calculations.\cite{townsend_data-driven_2019,jones_chapter_2023}
+This method works by predicting the $t_{2}$-amplitudes of the CCSD wave function (Eq.
+\ref{eq:cc_wfn}) with features generated using lower-level methods, such as Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2), which are used to initialize CCSD calculations.
+
+The coupled-cluster wave function takes the general form,
+\begin{equation}
+	\ket{\Psi_{\text{CC}}} = \exp(\hat{T}) \ket{\Psi_{0}}
+	\label{eq:cc_wfn}
+\end{equation}
+where the cluster operator is denoted as $\hat{T}$ and the reference, Hartree-Fock wave function is denoted as $\ket{\Psi_{0}}$.
+The CCSD wave function truncates the cluster operator to only include singles and doubles excitations.
+The CCSD correlation energy is defined as,
+\begin{equation}
+	E^{\text{CCSD}}_{\text{corr}} = \sum_{\substack{a<b \\ i<j}} \mel{ij}{}{ab} t^{ab}_{ij} + \sum_{\substack{a<b \\ i<j}} \mel{ij}{}{ab} t^{a}_{i} t^{b}_{j}
+	\label{eq:cc_corr}
+\end{equation}
+where $i$ and $j$ denote occupied orbitals, $a$ and $b$ denote virtual orbitals, $t^{ab}_{ij}$ are the $t_{2}$-amplitudes which correspond to two-electron excitations, 
+$t^{a}_{i}$ and $t^{b}_{j}$ are $t_{1}$-amplitudes corresponding to one-electron excitations, and $\mel{ij}{}{ab}$ are two-electron integrals.
+
+For each two-electron excitation, $t^{ab}_{ij}$, a feature set can be derived based on the MP2 $t_{2}$-amplitudes, which are used to initialize the CCSD amplitudes.
+The MP2 $t_{2}$-amplitudes take the following form,
 \begin{equation}
@@
 \end{equation}
+where $\varepsilon_{i}$ and $\varepsilon_{j}$ denote the orbital energies of the occupied orbitals $i$ and $j$, while the virtual orbitals $a$ and $b$ are denoted by $\varepsilon_{a}$ and $\varepsilon_{b}$.
+In the feature set, the MP2 $t_{2}$-amplitudes are included, along with the numerator ($\mel{ij}{}{ab}$) and denominator ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), a binary feature to denote whether the excitation goes to the same virtual orbital,
+
+We generate a database consisting 199 water molecules with 31 features for each molecule, using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
+STO-3G\cite{hehre_selfconsistent_1970} basis set due for benchmarking reasons
+
+Details regarding the feature set and implementation can be found in \cite{townsend_data-driven_2019}
+
 Like with the BSE dataset, we explore how we can reduce the initial y features down to 5 and 16 features using SHAP and PCA.

### 2025-01-25 manuscript/main.tex
Sat Jan 25 12:16:35 PM EST 2025 manuscript BSE figure

@@
 \cite{garcia-andrade_barrier_2023}, and one that is composed of the reactant molecular only, denoted as \textit{AB}.
+
+[Ridge(), Lasso(), ElasticNet(), KNeighborsRegressor(), RandomForestRegressor(), GradientBoostingRegressor(), SVR(), KernelRidge(), GaussianProcessRegressor()]
+
 Since we are analyzing a diverse set of PQCs, we used a set of three different classic regression models, with varying capabilities, implemented in sckit-learn.\cite{pedregosa_scikit-learn_2011}
-Based on our results shown in Fig. \ref{fig:classicalfuncfit} we found that Morgan fingerprints
-We found that the best molecular representation across all models test, as shown in Fig. \ref{fig:classicalfuncfit}, was Morgan fingerprints using the \textit{sub} formulation.
-
-\begin{figure}[H]
-	\centering	
-	\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
-	\caption{FIX:The performance of various molecular representations is shown using different classical machine learning models.
-\textit{AB} (top row) and \textit{sub} (bottom row) denote how the chemical reaction is represented.
-Each column denotes a different classical machine learning model, where the first column, denoted as knn, refers to \textit{k}-nearest neighbors, the second column, labeled rfr, denotes random forest regression, and krr, the last column, denotes kernel ridge regression.
-The x-axis of each sub-figure denotes the various molecular representations that are analyzed: Coulomb matrices (CM), Molecular ACCess Systems (MACCS), persistence images (PIs), RDKit fingerprints (RDKit), and Morgan fingerprints (Morgan).The y-axis of each sub-figure shows the performance of each model, evaluated using the R$^{2}$, where the training set is denoted using light blue and the test set is dark blue.}
-	\label{fig:classicalfuncfit}
+Based on our results shown in Fig. \ref{fig:classical_molrepfig} we found that Morgan fingerprints
+We found that the best molecular representation across all models test, as shown in Fig. \ref{fig:classical_molrepfig}, was Morgan fingerprints using the \textit{sub} formulation.
+
+\begin{figure}[H]
+	\centering	
+	\includegraphics[width=\linewidth]{../images/BSE/classical/classical_molrepfig.png}
+	\caption{}
+	\label{fig:classical_molrepfig}
 \end{figure}

### 2025-01-27 manuscript/main.tex
Mon 27 Jan 2025 17:13:52 EST manuscript + add iters

@@
 Within the field of chemistry, tools such as machine learning and quantum computing have become popular due to the promise of discoverying new molecules and materials.
-Machine learning in chemistry has already become a broadly applicable tool for exploring chemical compound space\cite{ramakrishnan_quantum_2014,ramakrishnan_big_2015}, accelerating wave functions\cite{townsend_data-driven_2019,jones_chapter_2023}, and for applications, such as catalysis and drug discovery.\cite{behler_perspective_2016,goh_deep_2017,sanchez-lengeling_{i}nverse_2018,butler_machine_2018,janet_machine_2020}
+Machine learning in chemistry has already become a broadly applicable tool for exploring chemical compound space\cite{ramakrishnan_quantum_2014,ramakrishnan_big_2015}, accelerating wave functions\cite{townsend_data-driven_2019,jones_chapter_2023}, and for applications, such as catalysis and drug discovery.\cite{behler_perspective_2016,goh_deep_2017,butler_machine_2018,sanchez-lengeling_inverse_2018,janet_machine_2020}
 [Sentence about quantum computing]
@@
 
+Function fitting 5: 
+Function fitting 16: all ran with 1000 iterations
+BSE 5
+BSE 16
+DDCC
+
 \subsection{Datasets}
@@
 
-For each two-electron excitation, $t^{ab}_{ij}$, a feature set can be derived based on the MP2 $t_{2}$-amplitudes, which are used to initialize the CCSD amplitudes.
-The MP2 $t_{2}$-amplitudes take the following form,
+For each two-electron excitation, $t^{ab}_{ij}$, a feature set can be generated from HF and MP2.
+The feature set includes the MP2 $t_{2}$-amplitudes, which are used to initialize the CCSD amplitudes,
 \begin{equation}
@@
 where $\varepsilon_{i}$ and $\varepsilon_{j}$ denote the orbital energies of the occupied orbitals $i$ and $j$, while the virtual orbitals $a$ and $b$ are denoted by $\varepsilon_{a}$ and $\varepsilon_{b}$.
-In the feature set, the MP2 $t_{2}$-amplitudes are included, along with the numerator ($\mel{ij}{}{ab}$) and denominator ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), a binary feature to denote whether the excitation goes to the same virtual orbital,
-
-We generate a database consisting 199 water molecules with 31 features for each molecule, using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
-STO-3G\cite{hehre_selfconsistent_1970} basis set due for benchmarking reasons
+Features related to the MP2 $t_{2}$-amplitudes that are also included in the feature set are the numerator ($\mel{ij}{}{ab}$) and denominator ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), a binary feature to denote whether the excitation goes to the same virtual orbital, and the orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$).
+The feature set also includes terms related to the individual contributes to the orbital energies are also included, such as the one-electron Hamiltonain ($h$), Coulombic matrix ($J$), and exchange matrix $K$, and Coulombic and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$).
+In total, there are 30 features for each $t_{2}$-amplitude due to the addition of features that denote the sign and magntudes of the previously mentioned features.
+
+We generate a dataset consisting of 199 water molecules from the study by Townsend and Vogiatzis 
+All calculations were performed using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018} with the STO-3G basis set\cite{hehre_selfconsistent_1970} and frozen core orbitals.
+For each water molecule there are 4 occupied orbitals ($N_{occ}$) and 2 virtual orbitals ($N_{virt}$), with a toal of 30 features for each $t_{2}$-amplitude, so each water molecule has a feature set dimension of 64 ($(N_{occ})^{2}(N_{virt})^{2}$) by 30.
+
+We generate a database consisting 199 water molecules with 30 features for each molecule.
+STO-3G basis set due for benchmarking reasons
 
@@
 Like with the BSE dataset, we explore how we can reduce the initial y features down to 5 and 16 features using SHAP and PCA.
-For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$), binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
+For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals , binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
 

### 2025-01-27 function-calc-test/fivequbit_tests/lin5qubit/count_lines.py

@@ -1,0 +1,10 @@
+import pandas as pd
+import click
+@click.command()
+@click.option('--path', required=True, type=click.Path(exists=True), help='Path to model_log.csv')
+def main(path):
+    df = pd.read_csv(path).dropna()
+    print(df.shape[0])
+
+if __name__ == "__main__":
+    main()

### 2025-01-28 manuscript/main.tex
Tue Jan 28 10:30:28 AM EST 2025 update figures for manuscript

@@
 In this study, we explore three datasets: a function fitting dataset, consisting of a noisy functions used for model calibration; a dataset consisting of electronic structure features to predict wave functions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
-We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the sense that for every molecule you will have $N_{occ}^{2}\cdot N_{virt}^{2}$ entries.
+We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the number of samples per molecule.
 
@@
 
-We generate a dataset consisting of 199 water molecules from the study by Townsend and Vogiatzis 
-All calculations were performed using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018} with the STO-3G basis set\cite{hehre_selfconsistent_1970} and frozen core orbitals.
-For each water molecule there are 4 occupied orbitals ($N_{occ}$) and 2 virtual orbitals ($N_{virt}$), with a toal of 30 features for each $t_{2}$-amplitude, so each water molecule has a feature set dimension of 64 ($(N_{occ})^{2}(N_{virt})^{2}$) by 30.
-
-We generate a database consisting 199 water molecules with 30 features for each molecule.
-STO-3G basis set due for benchmarking reasons
-
-Details regarding the feature set and implementation can be found in \cite{townsend_data-driven_2019}
-
-Like with the BSE dataset, we explore how we can reduce the initial y features down to 5 and 16 features using SHAP and PCA.
-For each $t^{ab}_{ij(\text{CCSD})}$, orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$), Coulomb and exchange integrals , binary feature whether two electrons are promoted to the same virtual orbital, the initial MP2 amplitudes, along with the numerator (two-electron integrals ($\mel{ij}{}{ab}$)) and denominator $\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$.
+Our dataset consists of 199 water molecules from the study by Townsend and Vogiatzis using the STO-3G basis set\cite{hehre_selfconsistent_1970} and frozen core orbitals.
+All data was generated using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
+As previously mentioned, the DDCC method is data intensive regarding the number of samples per molecule, for example, each water molecule has 4 occupied and 2 virtual orbitals.
+The number of $t_{2}$-amplitudes is equivalent to $(N_{occ})^{2}(N_{virt})^{2}$, where $N_{occ}$ denotes the number of occupied orbitals and $N_{virt}$ denotes the number of virtual orbitals, so the total number of $t_{2}$-amplitudes per molecule is 64.
+Further details regarding the feature set and implementation can be found in \cite{townsend_data-driven_2019}
+
+Like the BSE dataset, the 30 features from the full DDCC feature set must be reduced to 5 or 16 features using SHAP or PCA.
+Unlike the BSE dataset, we choose SHAP over PCA for the feature reduction since there is a direct correlation between the input features and output values.
+As shown in Fig. \ref{fig:DDCC_feature_set}, 5 and 16 features can accurately recover performance of the original model using 30 features, where all three models have train and test R$^{2}$s of 1.00.
+Due to the computational costs of running QML models, we will then use only 5 features for all DDCC QML models.
+The 5 most important features are the two-electron integrals ($\mel{ij}{}{ab}$), MP2 $t_{2}$-amplitudes ($t^{ab}_{ij(\text{MP2})}$), the magnitude of the MP2 $t_{2}$-amplitudes, and the difference in orbital energies ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$).
 
@@
 
+Across all three five qubit function fitting datasets, on average, the best encoders are `M-A2-CZ' with an average R$^{2}$ of 0.4599 and ansatz is `Full-CRX' with an average R$^{2}$ of 0.6731.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/five_feature_function_fitting_boxplots.png}
+	\caption{}
+	\label{fig:five_feature_function_fitting_boxplots}
+\end{figure}
+
+Across all three five qubit function fitting datasets, on average, the best encoders are `IQP' with an average R$^{2}$ of 0.4506 and ansatz is `Full-Pauli-CRZ' with an average R$^{2}$ of 0.4393.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/sixteen_feature_function_fitting_boxplots.png}
+	\caption{}
+	\label{fig:sixteen_feature_function_fitting_boxplots}
+\end{figure}
+
 \begin{figure}[H]

### 2025-01-28 manuscript/main.tex
Tue Jan 28 03:38:38 PM EST 2025 update figures for manuscript

@@
 \myexternaldocument{SI}
-\newcommand{\siref}[1]{\ref{#1}}
+\newcommand{\siref}[1]{S\ref{#1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Datasets}
-In this study, we explore three datasets: a function fitting dataset, consisting of a noisy functions used for model calibration; a dataset consisting of electronic structure features to predict wave functions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis \cite{townsend_data-driven_2019}; and a dataset of bond separation energies (BSE) of molecules, where the feature set encodes structural information of each molecule.
+In this study, we explore three datasets: a function fitting dataset (Figs.
+\ref{fig:linear_train_vs_test},\ref{fig:quadratic_train_vs_test}, and \ref{fig:sine_train_vs_test}), consisting of a noisy functions used for model calibration; a dataset of bond separation energies (BSE) of molecules (Figs.
+\ref{fig:bondtypes} and \ref{fig:BSEdistr}), where the feature set encodes structural information of each molecule;
+and a dataset consisting of electronic structure features to predict wave functions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis (Fig.
+\ref{fig:waterddccdistribution}).\cite{townsend_data-driven_2019}
 We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the number of samples per molecule.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/linear_train_vs_test.png}
+		\caption{}
+		\label{fig:linear_train_vs_test}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
+		\caption{}
+		\label{fig:quadratic_train_vs_test}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/sine_train_vs_test.png}
+		\caption{}
+		\label{fig:sine_train_vs_test}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}[b]{0.65\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/BSE/bondtypes.png}
+		\caption{}
+		\label{fig:bondtypes}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/BSE/BSE.jpg}
+		\caption{}
+		\label{fig:BSEdistr}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/manuscript_figures/waterddccdistribution.png}
+		\caption{}
+		\label{fig:waterddccdistribution}
+	\end{subfigure}	
+	\caption{Examples of the datasets explored in this study.
+The function fitting dataset used for model calibration include (a) linear (green), (b) quadratic (pink), and (c) sine (blue) functions.
+For the BSE49 dataset the distributions of the (d) bond types and the (e) bond separation energies in kcal/mol.
+For the DDCC dataset distributions of the initial MP2 $t_{2}$-amplitudes and the optimized CCSD $t_{2}$-amplitudes are shown in (f).}
+	\label{fig:bse_data}
+\end{figure}
 
@@
 
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/linear_train_vs_test.png}
-		\caption{}
-		\label{fig:linear_train_vs_test}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
-		\caption{}
-		\label{fig:quadratic_train_vs_test}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/sine_train_vs_test.png}
-		\caption{}
-		\label{fig:sine_train_vs_test}
-	\end{subfigure}
-	\caption{The function fitting dataset which consists of 90 total points, 80 for training and 10 used for testing, for the (a) linear, (b) quadratic, and (c) sine functions.}
-	\label{fig:train_vs_test}
-\end{figure}
+%\begin{figure}[H]
+%	\centering
+%	\begin{subfigure}[b]{0.3\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/linear_train_vs_test.png}
+%		\caption{}
+%		\label{fig:linear_train_vs_test}
+%	\end{subfigure}
+%	\hfill
+%	\begin{subfigure}[b]{0.3\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
+%		\caption{}
+%		\label{fig:quadratic_train_vs_test}
+%	\end{subfigure}
+%	\hfill
+%	\begin{subfigure}[b]{0.3\textwidth}
+%		\centering
+%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/sine_train_vs_test.png}
+%		\caption{}
+%		\label{fig:sine_train_vs_test}
+%	\end{subfigure}
+%	\caption{The function fitting dataset which consists of 90 total points, 80 for training and 10 used for testing, for the (a) linear, (b) quadratic, and (c) sine functions.}
+%	\label{fig:train_vs_test}
+%\end{figure}
 
@@
 
-[Ridge(), Lasso(), ElasticNet(), KNeighborsRegressor(), RandomForestRegressor(), GradientBoostingRegressor(), SVR(), KernelRidge(), GaussianProcessRegressor()]
-
-Since we are analyzing a diverse set of PQCs, we used a set of three different classic regression models, with varying capabilities, implemented in sckit-learn.\cite{pedregosa_scikit-learn_2011}
+Since we are analyzing a diverse set of PQCs, we also examine a diverse set of classic regression models, with varying capabilities, such as ridge, lasso, elastic net, \textit{k}-nearest-neighbors, random forest, gradient boosting, support vector, kernel ridge, and gaussian process regression as implemented in sckit-learn.\cite{pedregosa_scikit-learn_2011}
 Based on our results shown in Fig. \ref{fig:classical_molrepfig} we found that Morgan fingerprints
@@
 	\includegraphics[width=\linewidth]{../images/BSE/classical/classical_molrepfig.png}
-	\caption{}
+	\caption{Coulomb matrices (CMs), Molecular ACCess Systems (MACCS), persistence images (PIs), RDKit and Morgan fingerprints. Performance of a diverse set of molecular representations R$^{2}$}
 	\label{fig:classical_molrepfig}
@@
 \subsection{Function Fitting}
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/linear_heatplots.png}
-		\caption{replot y axis}
-		\label{fig:linear_heatplots}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/linear_boxplots.png}
-		\caption{}
-		\label{fig:linear_boxplots}
-	\end{subfigure}
-	\hfill	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/quadratic_heatplots.png}
-		\caption{}
-		\label{fig:quadratic_heatplots}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/quadratic_boxplots.png}
-		\caption{}
-		\label{fig:quadratic_boxplots}
-	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/sine_heatplots.png}
-		\caption{}
-		\label{fig:sine_heatplots}
-	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/sine_boxplots.png}
-		\caption{}
-		\label{fig:sine_boxplots}
-	\end{subfigure}
-	\hfill		
-	\caption{}
-	\label{fig:fivequbit_ff_heat}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/linear_heatplots.png}
-		\caption{}
-		\label{fig:sixteenlinear_heatplots}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/linear_boxplots.png}
-		\caption{}
-		\label{fig:sixteenlinear_boxplots}
-	\end{subfigure}
-	\hfill	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/quadratic_heatplots.png}
-		\caption{}
-		\label{fig:sixteenquadratic_heatplots}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/quadratic_boxplots.png}
-		\caption{}
-		\label{fig:sixteenquadratic_boxplots}
-	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/sine_heatplots.png}
-		\caption{}
-		\label{fig:sixteensine_heatplots}
-	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/sine_boxplots.png}
-		\caption{}
-		\label{fig:sixteensine_boxplots}
-	\end{subfigure}
-	\hfill		
-	\caption{}
-	\label{fig:sixteensixteenqubit_ff_heat}
-\end{figure}
-
-Across all three five qubit function fitting datasets, on average, the best encoders are `M-A2-CZ' with an average R$^{2}$ of 0.4599 and ansatz is `Full-CRX' with an average R$^{2}$ of 0.6731.
+To calibrate the PQCs, we perform an initial study of the 168 encoder-ansatz pairs using both 5 and 16 qubits.
+Individual heat maps showing the performance of the encoder-ansatz pairs and box plots showing the overall statistics for each encoder and ansatz are shown for the 5 and 16 qubit models in SI Section \siref{section:si_functionfitting}.
+
+Starting with the five qubit function fitting, we found that out of the
+168 encoder-ansatz pairs, for the linear function (Fig. \siref{fig:linear_heatplots}) is is A1\_ESU2 with a train and test R$^{2}$ of 0.9886 and 0.9893, respectively.
+Box plots for the encoders (left) and variational layers (right) are shown in Fig.
+\siref{fig:linear_boxplots}, where, the best encoder is IQP, with a mean R$^{2}$ of 0.8028, and best ansatz layer A1-A1-CNOT, with a mean R$^{2}$ of 0.5541.
+For the quadratic function, the best encoder-ansatz pair is A1-A1-CNOT\_Full-CRX with a train and test R$^{2}$ of 0.8809 and 0.7309, respectively, as shown in Fig \ref{fig:quadratic_heatplots}.
+On average the best encoder is A1-A1-CNOT with an R$^{2}$ of 0.5541 and best variational layer is Full-CRX with an R$^{2}$ of 0.5958 (Fig. \ref{fig:quadratic_boxplots}).
+For the sine function, Fig. \ref{fig:sine_heatplots}, M-M-CZ\_Full-CRX is the best encoder-ansatz pair with a train and test R$^{2}$ of 0.8887 and 0.9081, respectively.
+As shown in Fig. \ref{fig:sine_boxplots}, the best encoder is M with an average R$^{2}$ of 0.6456 and best variational layer is Full-CRX with a mean R$^{2}$ of 0.7551.
+Across all three five qubit function fitting datasets, on average, the best encoders are M-A2-CZ with an average R$^{2}$ of 0.4599 (Fig.
+\ref{fig:five_feature_function_fitting_boxplots} left) and ansatz is Full-CRX with an average R$^{2}$ of 0.6731 (Fig.
+\ref{fig:five_feature_function_fitting_boxplots} right).
 
@@
 
-Across all three five qubit function fitting datasets, on average, the best encoders are `IQP' with an average R$^{2}$ of 0.4506 and ansatz is `Full-Pauli-CRZ' with an average R$^{2}$ of 0.4393.
+Across all three sixteen qubit function fitting datasets, on average, the best encoders are `IQP' with an average R$^{2}$ of 0.4506 and ansatz is `Full-Pauli-CRZ' with an average R$^{2}$ of 0.4393.
 

### 2025-01-29 manuscript/main.tex
Wed 29 Jan 2025 17:03:39 EST manuscript

@@
 
-\subsection{Datasets}
+\subsection{Datasets}\label{subsection:datasets}
 In this study, we explore three datasets: a function fitting dataset (Figs.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../images/DDCC/DDCC_feature_set.png}
+	\includegraphics[width=0.49\textwidth]{../images/DDCC/DDCC_feature_set.png}
 	\caption{}
@@
 Starting with the five qubit function fitting, we found that out of the
-168 encoder-ansatz pairs, for the linear function (Fig. \siref{fig:linear_heatplots}) is is A1\_ESU2 with a train and test R$^{2}$ of 0.9886 and 0.9893, respectively.
-Box plots for the encoders (left) and variational layers (right) are shown in Fig.
-\siref{fig:linear_boxplots}, where, the best encoder is IQP, with a mean R$^{2}$ of 0.8028, and best ansatz layer A1-A1-CNOT, with a mean R$^{2}$ of 0.5541.
-For the quadratic function, the best encoder-ansatz pair is A1-A1-CNOT\_Full-CRX with a train and test R$^{2}$ of 0.8809 and 0.7309, respectively, as shown in Fig \ref{fig:quadratic_heatplots}.
-On average the best encoder is A1-A1-CNOT with an R$^{2}$ of 0.5541 and best variational layer is Full-CRX with an R$^{2}$ of 0.5958 (Fig. \ref{fig:quadratic_boxplots}).
-For the sine function, Fig. \ref{fig:sine_heatplots}, M-M-CZ\_Full-CRX is the best encoder-ansatz pair with a train and test R$^{2}$ of 0.8887 and 0.9081, respectively.
-As shown in Fig. \ref{fig:sine_boxplots}, the best encoder is M with an average R$^{2}$ of 0.6456 and best variational layer is Full-CRX with a mean R$^{2}$ of 0.7551.
-Across all three five qubit function fitting datasets, on average, the best encoders are M-A2-CZ with an average R$^{2}$ of 0.4599 (Fig.
-\ref{fig:five_feature_function_fitting_boxplots} left) and ansatz is Full-CRX with an average R$^{2}$ of 0.6731 (Fig.
+168 encoder-ansatz pairs, for the linear function (SI Fig. \siref{fig:linear_heatplots}) is is A1\_ESU2 with a train and test R$^{2}$ of 0.9886 and 0.9893, respectively.
+Box plots for the encoders (left) and variational layers (right) are shown in SI  Fig.
+\siref{fig:linear_boxplots}, where, the best encoder is IQP, with a mean R$^{2}$ of 0.8434, and best ansatz layer Full-CRX, with a mean R$^{2}$ of 0.7562.
+For the quadratic function, the best encoder-ansatz pair is A1-A1-CNOT\_Full-CRX with a train and test R$^{2}$ of 0.8809 and 0.7309, respectively, as shown in SI Fig \siref{fig:quadratic_heatplots}.
+On average the best encoder is A1-A1-CNOT with an R$^{2}$ of 0.5541 and best variational layer is Full-CRX with an R$^{2}$ of 0.5958 (SI  Fig. \siref{fig:quadratic_boxplots}).
+For the sine function, SI  Fig. \siref{fig:sine_heatplots}, M-M-CZ\_Full-CRX is the best encoder-ansatz pair with a train and test R$^{2}$ of 0.8887 and 0.9081, respectively.
+As shown in SI  Fig. \siref{fig:sine_boxplots}, the best encoder is M with an average R$^{2}$ of 0.6456 and best variational layer is Full-CRX with a mean R$^{2}$ of 0.7551.
+Across all three five qubit function fitting datasets, on average, the best encoders are M-A2-CZ with an average R$^{2}$ of 0.4776 (Fig.
+\ref{fig:five_feature_function_fitting_boxplots} left) and ansatz is Full-CRX with an average R$^{2}$ of 0.7023 (Fig.
 \ref{fig:five_feature_function_fitting_boxplots} right).
 
-\begin{figure}[H]
+For the sixteen qubit function fitting evaluation of the 168 encoder-ansatz pairs, we found that, similarly to the five qubit data, for the linear function the best pair is A1\_ESU2 with train and test R$^{2}$s of 0.9886 and 0.9893, respectively, as highlighted in SI Fig.
+\siref{fig:sixteenlinear_heatplots}.
+Like the five qubit data, the best encoder is also IQP with an average R$^{2}$ of 0.7800 (SI Fig.
+\siref{fig:sixteenlinear_boxplots} left), while the best ansatz varies from the five qubit data, Full-Pauli-CRZ with a mean R$^{2}$ of 0.3947 (SI Fig.
+\siref{fig:sixteenlinear_boxplots} right).
+The A1-A1-CZ\_Modified-Pauli-CRX encoder-ansatz pair has the best overall model performance, highlighted in SI Fig.
+\siref{fig:sixteenquadratic_heatplots}, where the training set has an R$^{2}$ of 0.8415 and the test set has an R$^{2}$ of  0.7722.
+As demonstrated in SI Fig. \siref{fig:sixteenquadratic_boxplots}, the best encoders and ans\"{a}tze are A1-A1-CNOT and Full-Pauli-CRX, with mean R$^{2}$s of 0.5759 and 0.4474, respectively.
+For the last sixteen qubit dataset, the sine function data (SI Fig.
+\siref{fig:sixteensine_heatplots}), the best encoder-ansatz pair is A1-A1-CZ\_Full-Pauli-CRZ	with an R$^{2}$ of 0.8147 for the training set and an R$^{2}$ of 0.8626	for the test set.
+SI Fig. \siref{fig:sixteensine_boxplots} highlights that the best encoder is M with a mean R$^{2}$ of 0.5824 and best ansatz, on average, is Full-Pauli-CRZ with an R$^{2}$ of 0.4881.
+Across all three function fitting datasets, the sixteen qubit data varies where the best encoders are IQP with an average R$^{2}$ of 0.4506 and ans\"{a}tze is Full-Pauli-CRZ with an average R$^{2}$ of 0.4393.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.49\textwidth}
 		\centering
@@
 		\label{fig:five_feature_function_fitting_boxplots}
-\end{figure}
-
-Across all three sixteen qubit function fitting datasets, on average, the best encoders are `IQP' with an average R$^{2}$ of 0.4506 and ansatz is `Full-Pauli-CRZ' with an average R$^{2}$ of 0.4393.
-
-\begin{figure}[H]
+	\end{subfigure}
+	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
 		\centering
@@
 		\label{fig:sixteen_feature_function_fitting_boxplots}
-\end{figure}
+	\end{subfigure}
+	\hfill		
+	\caption{The combined performance of all three function fitting datasets for both the (a) five and (b) sixteen qubit models is evaluated using the R$^{2}$ (y-axis) versus the encoders (left) and ans\"{a}tze (right).}
+	\label{fig:function_fitting_boxplots}
+\end{figure}
+
+Following the initially analysis of the performance of the 168 PQCs using both five and sixteen qubits, we experimented with the effect of the re-upload depth (RUD) and number of ansatz layers (AL) using the sixteen qubit circuits.
+We chose to use the sixteen qubit circuits over the five qubit circuits since these circuits have complexity more similar to when the circuits are used for the chemical dataset in terms of the number of parameters and optimization times.
+From the initial 168 PQCs, for each function fitting dataset, we choose the five best (top row), five median (middle row), and five worst (bottom row) circuits to see the effects of increasing the RUD and AL on model performance as shown in Figs.
+\ref{fig:16qubit_Linear_RUD_AL}, \ref{fig:16qubit_Quadratic_RUD_AL}, and  \ref{fig:16qubit_Sine_RUD_AL}.
+For the linear (Fig.
+\ref{fig:16qubit_Linear_RUD_AL}), quadratic (\ref{fig:16qubit_Quadratic_RUD_AL}), and sine (Fig.
+\ref{fig:16qubit_Sine_RUD_AL}) data, some generalities arise for the five best circuits.
+We see that for these circuits, increasing the number of AL from 1 to 3 or 5 improves model performance more than RUD.
+For the median performers, the RUD improves model performance more than the ansatz layers.
+And lastly, for the worse performers a general trend does not exist and increasing the RUD and AL depends on the dataset and circuit architecture.
+
+% Commented this out because it is not useful for the overall discussion
+%While an increase in the circuit depth, either by increasing the RUD or AL, is associated with an increase in model performance this is also associated with an increased computational cost. 
+%In Figs.
+\ref{fig:linear_circuitdepth_vs_R2}, \ref{fig:quadratic_circuitdepth_vs_R2}, and \ref{fig:sine_circuitdepth_vs_R2} we  highlight this trade-off, where the x-axes denote circuit depth, y-axis denotes the R$^{2}$, and the median train and test R$^{2}$ are shown in red and blue, respectively, for all 15 circuits.
+Despite these trends, we found that for the linear function, the best performing model is IQP\_Full-Pauli-CRZ  with a RUD and AL of 1.
+This circuit also has a training and test R$^{2}$ of 0.9883 and 0.9891, respectively, and a depth of 95.
+Unlike the best linear circuit, the best circuits for both the quadratic and sine data, IQP\_Full-Pauli-CRX	 and A2\_HWE-CZ, respectively,  benefit from an increased RUD, with the best models having a RUD of 5 and AL of 1.
+These two circuits differ in depth and performance, with the IQP\_Full-Pauli-CRX for the quadratic data having a circuit depth of 520, training R$^{2}$ of 0.9817, and test R$^{2}$ of 0.9609 and the A2\_HWE-CZ circuit for the sine data having a depth of 105 , training R$^{2}$ of 0.9156, and test R$^{2}$ of 0.9576.
+Following these insights, we applied these circuits for analyzing the effects of the training set size on model performance using learning curves and the effects of error mitigation using noisy simulation.
 
@@
 	\hfill	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_circuitdepth_vs_R2}
-		\caption{}
-		\label{fig:linear_circuitdepth_vs_R2}
-	\end{subfigure}
-	\hfill		
+%	\begin{subfigure}[b]{0.49\textwidth}
+%		\centering
+%		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_circuitdepth_vs_R2}
+%		\caption{}
+%		\label{fig:linear_circuitdepth_vs_R2}
+%	\end{subfigure}
+%	\hfill		
 	\begin{subfigure}[b]{0.49\textwidth}
@@
 	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_circuitdepth_vs_R2}
-		\caption{}
-		\label{fig:quadratic_circuitdepth_vs_R2}
-	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
-		\caption{}
-		\label{fig:16qubitlinearrudal}
-	\end{subfigure}	
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_circuitdepth_vs_R2}
-		\caption{}
-		\label{fig:sine_circuitdepth_vs_R2}
-	\end{subfigure}
-	\hfill		
-	\caption{}
+%	\begin{subfigure}[b]{0.49\textwidth}
+%		\centering
+%		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_circuitdepth_vs_R2}
+%		\caption{}
+%		\label{fig:quadratic_circuitdepth_vs_R2}
+%	\end{subfigure}
+%	\hfill		
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Sine_RUD_AL.png}
+		\caption{}
+		\label{fig:16qubit_Sine_RUD_AL}
+	\end{subfigure}	
+	\hfill
+%	\begin{subfigure}[b]{0.49\textwidth}
+%		\centering
+%		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_circuitdepth_vs_R2}
+%		\caption{}
+%		\label{fig:sine_circuitdepth_vs_R2}
+%	\end{subfigure}
+%	\hfill		
+	\caption{(a) linear, (b) quadratic, (c) sine}
 	\label{fig:16qubit_RUD_AL}	
@@
 
+One proposed advantage of using PQCs for ML tasks is that, in some cases, they can outperform classical ML models.\cite{hatakeyama-sato_quantum_2023}
+To explore this, we use learning curves with the best performing circuits previously described, where we hold the number of test points to 10\% of the total data points and vary the percentage of the training data.
+
+We compare the best PQCs with the classical models mentioned in subsection \ref{subsection:datasets}
+For the linear data using IQP\_Full-Pauli-CRZ  with a RUD and AL of 1, we found that the quantum circuit offers similiar performance
+
+Performance:
+Linear
+Offers comparable performance to the classical models
+
+quadratic
+Outperforms classical linear models (elastic lasso ridge)
+
+sine
+Outperforms classical linear models (elastic lasso ridge)
+
+'elastic', 'gpr', 'grad', 'knn', 'krr', 'lasso', 'rfr', 'ridge', 'svr'
+
 \begin{figure}[H]
@@
 	\end{subfigure}	
-	\caption{(a) linear, (b) quadratic, (c) sine function}
+	\caption{Learning curves of the best PQCs (right side in the subfigures) versus various classical models (left side in the subfigure) for the (a) linear, (b) quadratic, and (c) sine function datasets.}
 	\label{fig:functionfitting_learning_curves}	

### 2025-01-30 manuscript/main.tex
Thu Jan 30 04:52:31 PM EST 2025 manuscript images

@@
 
-Function fitting 5: 
+Function fitting 5: all ran with 1000 iterations
 Function fitting 16: all ran with 1000 iterations
-BSE 5
-BSE 16
+BSE 5: all ran with 1000 iterations
+BSE 16: all ran with 1000 iterations
 DDCC
@@
 %	\hfill		
-	\caption{(a) linear, (b) quadratic, (c) sine}
+	\caption{The best five (top row), median five (middle row), and worst five (bottom row) circuits for the 16 qubit (a) linear, (b) quadratic, and (c) sine data show that, in general, an increase in the re-upload depth (RUD) or ansatz layers (AL) increases model performance (R$^{2}$ shown on the y-axis).}
 	\label{fig:16qubit_RUD_AL}	
@@
 
-One proposed advantage of using PQCs for ML tasks is that, in some cases, they can outperform classical ML models.\cite{hatakeyama-sato_quantum_2023}
-To explore this, we use learning curves with the best performing circuits previously described, where we hold the number of test points to 10\% of the total data points and vary the percentage of the training data.
-
-We compare the best PQCs with the classical models mentioned in subsection \ref{subsection:datasets}
-For the linear data using IQP\_Full-Pauli-CRZ  with a RUD and AL of 1, we found that the quantum circuit offers similiar performance
-
-Performance:
-Linear
-Offers comparable performance to the classical models
-
-quadratic
-Outperforms classical linear models (elastic lasso ridge)
-
-sine
-Outperforms classical linear models (elastic lasso ridge)
-
-'elastic', 'gpr', 'grad', 'knn', 'krr', 'lasso', 'rfr', 'ridge', 'svr'
+One proposed advantage of using PQCs for ML tasks is that, in some cases, they can outperform classical ML models using less training data.\cite{hatakeyama-sato_quantum_2023}
+We examine this phenomena with learning curves using the best performing circuits previously described.
+The learning curves are generated by varying the percentage of training data from 10-80\% of the available data, while holding the number of test points to 10\% of the total data.
+The three PQCs for each data set are compared to the classical models mentioned in subsection \ref{subsection:datasets} in a statistical manner (left sub-figures in Figs.
+\ref{fig:linear_learning_curves}, \ref{fig:quadratic_learning_curves}, and \ref{fig:sine_learning_curves}).
+Across the full learning curve, IQP\_Full-Pauli-CRZ (linear function fitting) outperforms seven out of nine classical models for the training set and all of the classical models on the test set.
+On the quadratic dataset, using IQP\_Full-Pauli-CRX, offers similar performance to the classical models, despite being outperformed on the training set across the learning curve. 
+Similar to the IQP\_Full-Pauli-CRZ using the linear data, IQP\_Full-Pauli-CRX outperforms seven out of the nine classical models on the test set across the full learning curve.
+On the sine data, A2\_HWE-CZ is consistent across the learning curve, outperforming six of the nine classical models on the training set and all of the models on the test set.
+For all three datasets, this implies that the PQCs offer similar performance to classical models that do well on these datasets but provide better results on the test set.
 
@@
 
+Lastly, using the function fitting datasets we analyze the effects of error mitigation on the model accuracy by comparing state vector simulations with noisy and error mitigated simulations using the \textit{fake\_quebec} backend.
+Initially, we explored two different methods of error mitigation zero-noise extrapolation (ZNE) using MITIQ\cite{larose_mitiq_2022} and TREX, as implemented in Qiskit. 
+We found that both linear and Richardson ZNE were too costly to simulate on classical computers using 16 qubits for all three function fitting datasets and chose only to use TREX for error mitigation.
+
+IQP\_Full-Pauli-CRZ (linear function fitting)
+state vector: train 0.99/test 0.99
+TREX: train 0.98/test 0.98
+without: train 0.98/test 0.98
+\ref{fig:linear_error_mitigation}
+
+IQP\_Full-Pauli-CRX (quadratic function fitting)
+state vector: train 0.80/test 0.68
+TREX: train 0.69/test 0.60
+without: train 0.65/test 0.45
+\ref{fig:quadratic_error_mitigation}
+
+A2\_HWE-CZ (sine function fitting)
+state vector: train 0.92/test 0.96
+TREX: train 0.87/test 0.89
+without: train 0.87/test 0.91
+\ref{fig:sine_error_mitigation}
+
 \begin{figure}[H]
@@
 	\hfill		
-	\caption{(a) linear, (b) quadratic, (c) sine function}
+	\caption{Error mitigation benchmarking for the (a) linear, (b) quadratic, and (c) sine function comparing unmitigated and mitigated error using TREX with state vector simulations.}
 	\label{fig:functionfitting_errormitigation}	
@@
 \subsection{BSE}
+
+five qubit \ref{fig:5BSE_heatplots} \ref{fig:5BSE_boxplots}
+best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
+Best encoder on average train R$^{2}$/test R$^{2}$
+Best ansatz on average train R$^{2}$/test R$^{2}$
+
+sixteen qubit \ref{fig:16BSE_heatplots} \ref{fig:16BSE_boxplots}
+best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
+Best encoder on average train R$^{2}$/test R$^{2}$
+Best ansatz on average train R$^{2}$/test R$^{2}$
+
 \begin{figure}[H]
@@
 
+\ref{fig:bse5rudal}
+
+\ref{fig:bse16rudal}
+
 \begin{figure}[H]
@@
 
+A2\_HWE-CNOT Train R$^{2}$ 0.62/test R$^{2}$ 0.62 
+Best encoder average Train R$^{2}$ X/test R$^{2}$ Y
+Best ansatz HWE-CNOT average Train R$^{2}$ X/test R$^{2}$ Y
+
 \begin{figure}[H]
@@
 	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
-		\caption{}
-		\label{fig:allddcc5circuitdepthr2vsiterationtime}
-	\end{subfigure}	
+%	\begin{subfigure}[b]{0.49\textwidth}
+%		\centering
+%		\includegraphics[width=\linewidth]{../images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
+%		\caption{}
+%		\label{fig:allddcc5circuitdepthr2vsiterationtime}
+%	\end{subfigure}	
 	\caption{}
@@
 
+(AL,RUD)=(1,1) Train R$^{2}$ 0.62/test R$^{2}$ 0.62
+(AL,RUD)=(1,3) Train R$^{2}$ 0.85/test R$^{2}$ 0.85
+(AL,RUD)=(1,5) Train R$^{2}$ 0.82/test R$^{2}$ 0.83
+(AL,RUD)=(3,1) Train R$^{2}$ 0.71/test R$^{2}$ 0.71
+(AL,RUD)=(5,1) Train R$^{2}$ 0.77/test R$^{2}$ 0.77
+
 \begin{figure}[H]
@@
 	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL}
-	\caption{}
+	\caption{Model evaluation, using R$^{2}$ (y-axis), of re-upload depths (RUD) and ansatz layers (AL) of 1, 3, and 5 for the A2\_HWE-CNOT using the DDCC dataset.
+The left side of the plot denotes the training set and the right side the test set.}
 	\label{fig:ddccrudal}

### 2025-01-31 manuscript/main.tex
Fri Jan 31 05:03:11 PM EST 2025

@@
 We found that both linear and Richardson ZNE were too costly to simulate on classical computers using 16 qubits for all three function fitting datasets and chose only to use TREX for error mitigation.
-
-IQP\_Full-Pauli-CRZ (linear function fitting)
-state vector: train 0.99/test 0.99
-TREX: train 0.98/test 0.98
-without: train 0.98/test 0.98
-\ref{fig:linear_error_mitigation}
-
-IQP\_Full-Pauli-CRX (quadratic function fitting)
-state vector: train 0.80/test 0.68
-TREX: train 0.69/test 0.60
-without: train 0.65/test 0.45
-\ref{fig:quadratic_error_mitigation}
-
-A2\_HWE-CZ (sine function fitting)
-state vector: train 0.92/test 0.96
-TREX: train 0.87/test 0.89
-without: train 0.87/test 0.91
-\ref{fig:sine_error_mitigation}
+Our analysis revealed that the state vector, TREX, and unmitigated IQP\_Full-Pauli-CRZ (linear function fitting data) models all have R$^{2}$ between 0.98 and 0.99, for both the training and test sets, as highlighted in Fig.
+\ref{fig:linear_error_mitigation}.
+While the performance of the linear data can be attributed to the simiplicity of the dataset, for the quadratic function fitting data using IQP\_Full-Pauli-CRX (Fig.
+\ref{fig:quadratic_error_mitigation}), we found that the model with unmitigated error has an R$^{2}$ of 0.65 for the training set and 0.45 for the test set.
+This model is improved slightly by the incorporation of error mitigation using TREX, where the training set R$^{2}$ is 0.69 and test set R$^{2}$ is 0.60.
+Overall, the model using TREX offers results more comparable to the state vector simulations, which has a R$^{2}$s of 0.80 and 0.68 for the training and test set, respectively.
+On the sine function fitting data, using A2\_HWE-CZ (Fig.
+\ref{fig:sine_error_mitigation}), for the state vector, TREX, and unmitigated models, the training sets have R$^{2}$s of 0.92, 0.87, and 0.87, respectively, while the test sets have R$^{2}$s of 0.96, 0.89, and 0.91, respectively.
+Overall, while these results are for simple function fitting data, we concluded that TREX offers a computational efficient error mitigation method, with results similar to the state vector calculations.0
 
@@
 \subsection{BSE}
+The first chemically relevant dataset we explore in this study is the BSE49 dataset.
+As highlighted in Figs. \ref{fig:bondtypes} and \ref{fig:BSEdistr}, this dataset consists of a diverse set of representative chemical bonds and bond separation energies.
+Herein, we follow a similar analysis to the function fitting data, starting off with an analysis of a large set of PQCs using five and sixteen qubits with RUDs and ALs of 1.
+From these two sets of data, we choose the best two models to study how an increase in the RUD and AL effects model performance.
+[learning curves]
+[Conclude we do not want to run this on real hardware due to the lack of promising results using simulation]
 
@@
 
+'M-M-CNOT', '-0.0216'
+'Full-CRX', '0.1214'
+
 sixteen qubit \ref{fig:16BSE_heatplots} \ref{fig:16BSE_boxplots}
+removed the really bad ones from five qubit
 best encoder-ansatz pair: train R$^{2}$/test R$^{2}$

### 2025-02-10 images/ansatz/quantikz/Full-CRX.tex
Mon 10 Feb 2025 17:00:20 EST poster/manuscript figures

@@
 
-%Full-CRX
+%Full-CRX(	\theta)
 \resizebox{\textwidth}{!}{
 \begin{quantikz}
-	\lstick{$q_0$}& \gate{RX} & \gate{RZ} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RX} &&&&\gate{RX}&&&&\gate{RX}& &&&\gate{RX}&&&&\\
-	\lstick{$q_1$}& \gate{RX} & \gate{RZ} & \gate{RX} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&&\\
-	\lstick{$q_2$}& \gate{RX} & \gate{RZ} && \gate{RX}&&&&\gate{RX}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RX}&&&&\gate{RX}&&\\
-	\lstick{$q_3$}& \gate{RX} & \gate{RZ} &&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RX}&\\
-	\lstick{$q_4$}& \gate{RX} & \gate{RZ} &&&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&&&&\gate{RX}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
+	\lstick{$q_0$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RX(	\theta)} &&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}& &&&\gate{RX(	\theta)}&&&&\\
+	\lstick{$q_1$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} & \gate{RX(	\theta)} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&\\
+	\lstick{$q_2$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} && \gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&\\
+	\lstick{$q_3$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RX(	\theta)}&\\
+	\lstick{$q_4$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&&&&\gate{RX(	\theta)}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
 \end{quantikz}

### 2025-02-10 images/ansatz/quantikz/Full-CRZ.tex
Mon 10 Feb 2025 17:00:20 EST poster/manuscript figures

@@
 \begin{document}
-%Full-CRZ
+%Full-CRZ(	\theta)
 \resizebox{\textwidth}{!}{
 	\begin{quantikz}
-		\lstick{$q_0$}& \gate{RX} & \gate{RZ} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RZ} &&&&\gate{RZ}&&&&\gate{RZ}& &&&\gate{RZ}&&&&\\
-		\lstick{$q_1$}& \gate{RX} & \gate{RZ} & \gate{RZ} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&&\\
-		\lstick{$q_2$}& \gate{RX} & \gate{RZ} && \gate{RZ}&&&&\gate{RZ}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RZ}&&&&\gate{RZ}&&\\
-		\lstick{$q_3$}& \gate{RX} & \gate{RZ} &&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RZ}&\\
-		\lstick{$q_4$}& \gate{RX} & \gate{RZ} &&&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RZ}&&&&\gate{RX}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
+		\lstick{$q_0$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &\ctrl{1}& \ctrl{2}&\ctrl{3}&\ctrl{4}&\gate{RZ(	\theta)} &&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}& &&&\gate{RZ(	\theta)}&&&&\\
+		\lstick{$q_1$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} & \gate{RZ(	\theta)} &&&& \ctrl{-1} & \ctrl{1} & \ctrl{2} &  \ctrl{3}&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&\\
+		\lstick{$q_2$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} && \gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&& \ctrl{-2}&\ctrl{-1}&\ctrl{1}&\ctrl{2}&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&\\
+		\lstick{$q_3$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}& \ctrl{1}&&&&\gate{RZ(	\theta)}&\\
+		\lstick{$q_4$}& \gate{RX(	\theta)} & \gate{RZ(	\theta)} &&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&&\gate{RZ(	\theta)}&&&&\gate{RX(	\theta)}&\ctrl{-4}&\ctrl{-3}&\ctrl{-2}&\ctrl{-1}&\\
 	\end{quantikz}

### 2025-02-10 images/encoders/quantikz/IQP.tex
Mon 10 Feb 2025 17:00:20 EST poster/manuscript figures

@@
 \usepackage{mathtools,physics}
-\def\myvdots{\ \vdots\ }
 
@@
 	\begin{quantikz} 
-\lstick{$q_0$} & \gate{H} & \gate{R_{Z} (x_{0})} & \gate[2,disable auto height]{ZZ(x_{0},x_{1})} &  & \gate[3,disable auto height]{ZZ(x_{0},x_{2})} & \gate[5,disable auto height]{ZZ(x_{0},x_{n})}   & & &  \\
-\lstick{$q_1$} & \gate{H} & \gate{R_{Z} (x_{1})} & & \gate[2,disable auto height]{ZZ(x_{1},x_{2})}  & & &  \gate[4,disable auto height]{ZZ(x_{1},x_{n})}  &  &\\ 
-\lstick{$q_2$} & \gate{H} & \gate{R_{Z} (x_{2})} & & & & & & \gate[3,disable auto height]{ZZ(x_{2},x_{n})}  & \\ 
-\setwiretype{n} \lstick{}  & \myvdots & \myvdots & \myvdots  & \myvdots & \myvdots & \\
-\lstick{$q_n$}& \gate{H}  & \gate{R_{Z} (x_{n})} & & & & & & &\\
+	\lstick{$q_0$} & \gate{H} & \gate{R_{Z} (x_{0})} & \gate[2,disable auto height]{ZZ(x_{0},x_{1})} &   \gate[3,disable auto height]{ZZ(x_{0},x_{2})} & \gate[4,disable auto height]{ZZ(x_{0},x_{3})} &  \gate[5,disable auto height]{ZZ(x_{0},x_{4})}   & &  & & & & & \\
+	\lstick{$q_1$}& \gate{H}  & \gate{R_{Z} (x_{1})} & & & & & \gate[2,disable auto height]{ZZ(x_{1},x_{2})} & \gate[3,disable auto height]{ZZ(x_{1},x_{3})} & \gate[4,disable auto height]{ZZ(x_{1},x_{4})} & & & &\\
+	\lstick{$q_2$}& \gate{H}  & \gate{R_{Z} (x_{2})} & & & & & & & &  \gate[2,disable auto height]{ZZ(x_{2},x_{3})} &  \gate[3,disable auto height]{ZZ(x_{2},x_{4})} & & \\
+	\lstick{$q_3$}& \gate{H}  & \gate{R_{Z} (x_{3})} & & & & & & & & & & \gate[2,disable auto height]{ZZ(x_{3},x_{4})} & \\
+	\lstick{$q_4$}& \gate{H}  & \gate{R_{Z} (x_{4})} & & & & & & & & & & & \\
 	\end{quantikz}

### 2025-02-10 BSE_learning_curves/16/0.1/run.sh

@@ -7,22 +7,9 @@ name=${i%/}
 # Extracting the parent directory name
 settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
 path="${cwd}/${name}"
-cat > ${name}.sub <<EOF
-#! /bin/bash
-#SBATCH -t 0-23:59:59
-#SBATCH -J ${errorname}_${name}
-#SBATCH -N 1
-#SBATCH -n 80
-#SBATCH --account=rrg-fekl-ac
-#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
-#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
-
-
-export OMP_NUM_THREADS=80
+export OMP_NUM_THREADS=64
 cd $(pwd)/$name
-/scinet/niagara/software/2019b/opt/base/python/3.11.5/bin/python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.8_Morgan_train.bin --test_set ${cwd}/PCA16_0.8_Morgan_test.bin --scaler ${cwd}/PCA16_0.8_Morgan_scaler.bin --resume_file ${path}/partial_state_model.bin > ${name}.out 2>&1
-
+python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.1_Morgan_train.bin --test_set ${cwd}/PCA16_0.1_Morgan_test.bin --scaler ${cwd}/PCA16_0.1_Morgan_scaler.bin --resume_file ${path}/final_state_model.bin > ${name}.out 2>&1
 cd ..
 touch ${name}.done
 
-EOF

### 2025-02-10 BSE_learning_curves/16/0.5/quantum/Quantum.py

@@ -102,8 +102,8 @@ class QuantumRegressor:
             #    token = input('Enter IBMQ token')
             ## QiskitRuntimeService.save_account(channel='ibm_quantum', instance=instance, token=token, overwrite=True)
             # Or save your credentials on disk.
-            # QiskitRuntimeService.save_account(channel='ibm_quantum', instance='pinq-quebec-hub/univ-toronto/default', token='<IBM Quantum API key>')
-            service = QiskitRuntimeService(channel="ibm_quantum", instance='pinq-quebec-hub/univ-toronto/default')
+            # QiskitRuntimeService.save_account(channel='ibm_quantum', instance='pinq-quebec-hub/univ-toronto/matterlab', token='<IBM Quantum API key>')
+            service = QiskitRuntimeService(channel="ibm_quantum", instance='pinq-quebec-hub/univ-toronto/matterlab')
             self._backend = service.least_busy(operational=True, simulator=False, min_num_qubits=self.num_qubits)
             self.device = qml.device(device, wires=self.num_qubits, backend=self._backend,shots=shots)
             # Default to no noise 

### 2025-02-10 BSE_learning_curves/16/0.8/run.sh

@@ -7,22 +7,9 @@ name=${i%/}
 # Extracting the parent directory name
 settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
 path="${cwd}/${name}"
-cat > ${name}.sub <<EOF
-#! /bin/bash
-#SBATCH -t 0-23:59:59
-#SBATCH -J ${errorname}_${name}
-#SBATCH -N 1
-#SBATCH -n 80
-#SBATCH --account=rrg-fekl-ac
-#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
-#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
-
-
-export OMP_NUM_THREADS=80
+export OMP_NUM_THREADS=64
 cd $(pwd)/$name
-/scinet/niagara/software/2019b/opt/base/python/3.11.5/bin/python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.8_Morgan_train.bin --test_set ${cwd}/PCA16_0.8_Morgan_test.bin --scaler ${cwd}/PCA16_0.8_Morgan_scaler.bin --resume_file ${path}/partial_state_model.bin > ${name}.out 2>&1
-
+python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.8_Morgan_train.bin --test_set ${cwd}/PCA16_0.8_Morgan_test.bin --scaler ${cwd}/PCA16_0.8_Morgan_scaler.bin  > ${name}.out 2>&1
 cd ..
 touch ${name}.done
 
-EOF

### 2025-02-13 manuscript/main.tex
Mon  3 Feb 2025 17:14:19 EST manuscript
Thu Feb 13 06:15:42 PM EST 2025 manuscript + error mitigation

@@
 
+We introduce \textit{qregress}, a modular Python-based code built on PennyLane for exploring PQCs for regression based learning tasks.
+We analyze three datasets, a function fitting dataset, used for model calibration, and two chemically relevant datasets that offer challenging learning tasks for PQCs.
+
 \section{Methods}
@@
 \subsection{Implementation}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{../images/manuscript_figures/overview.png}
+	\caption{Make this figure highlight the modularity of \textit{qregress}}
+	\label{fig:overview_project}
+\end{figure}
+
+We introduce \textit{qregress}, a modular Python package for regression-based PQCs.
+
 We perform all simulation calculations using PennyLane\cite{bergholm_pennylane_2022}, either using Qulacs\cite{suzuki_qulacs_2021} for state vector calcualtions, while noisy calculations were performed using \textit{qiskit-aer} with the \textit{FakeQuebec} backend as implemented in the PennyLane-Qiskit plugin.\cite{javadi-abhari_quantum_2024}
@@
 
+optimization level needs to be set to 0!
+
 Lastly, using the function fitting datasets we analyze the effects of error mitigation on the model accuracy by comparing state vector simulations with noisy and error mitigated simulations using the \textit{fake\_quebec} backend.
@@
 \subsection{BSE}
-The first chemically relevant dataset we explore in this study is the BSE49 dataset.
+The first chemically relevant dataset we explore is the BSE49 dataset.
 As highlighted in Figs. \ref{fig:bondtypes} and \ref{fig:BSEdistr}, this dataset consists of a diverse set of representative chemical bonds and bond separation energies.
@@
 
-\ref{fig:bse5rudal}
-
-\ref{fig:bse16rudal}
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE5_RUDAL}
-		\caption{}
-		\label{fig:bse5rudal}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE16_RUDAL}
-		\caption{}
-		\label{fig:bse16rudal}
-	\end{subfigure}
-	\caption{}
-	\label{fig:BSE_RUD_AL}	
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\linewidth]{../images/BSE/fivequbit/BSE5_learning_curves}
-	\caption{}
-	\label{fig:bse5learningcurves}
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE5_RUDAL_lineplot}
+		\caption{}
+		\label{fig:bse5RUDAL_lineplot}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE16_RUDAL_lineplot}
+		\caption{}
+		\label{fig:bse16RUDAL_lineplot}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/distribution_parity}
+		\caption{}
+		\label{fig:BSE5_distribution_parity}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/distribution_parity}
+		\caption{}
+		\label{fig:BSE16_distribution_parity}
+	\end{subfigure}
+	\caption{}
+	\label{fig:BSE_distribution_parity}	
+\end{figure}
+
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_learningcurve}
+		\caption{}
+		\label{fig:BSE5_learning_curves}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_learningcurve}
+		\caption{}
+		\label{fig:BSE16_learningcurve}
+	\end{subfigure}
+	\caption{}
+	\label{fig:BSE_LC}	
 \end{figure}
@@
 	\centering	
-	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL_lineplot}
+		\caption{}
+		\label{fig:ddccRUDAL_lineplot}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/DDCC/distribution_parity}
+		\caption{}
+		\label{fig:ddccdistribution_parity}
+	\end{subfigure}
 	\caption{Model evaluation, using R$^{2}$ (y-axis), of re-upload depths (RUD) and ansatz layers (AL) of 1, 3, and 5 for the A2\_HWE-CNOT using the DDCC dataset.
 The left side of the plot denotes the training set and the right side the test set.}
-	\label{fig:ddccrudal}
+	\label{fig:ddcc_rud}	
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_learning_curves}
+	\caption{}
+	\label{fig:ddcclearningcurves}
 \end{figure}

### 2025-02-14 manuscript/main.tex
Fri 14 Feb 2025 15:47:44 EST manuscript, timings, etc.

@@
 Distributed QC to incorporate more features
+Noiseless simulation is costly and does not offer the desired accuracy for BSE49 or DDCC
+
+DDCC could be a useful dataset to benchmark PQC models since it is trivial to perform classically, yet hard for PQCs...
 

### 2025-02-18 manuscript/main.tex
Tue 18 Feb 2025 12:00:27 EST

@@
 \section{Introduction}
+\begin{itemize}
+	\item General background information
+	\item Specific background information
+	\item A description of the gap in our knowledge that the study was designed to fill
+	\item A statement of study objective, and (optionally) a brief summary of study
+\end{itemize}
+
 Within the field of chemistry, tools such as machine learning and quantum computing have become popular due to the promise of discoverying new molecules and materials.
@@
 For the case of quantum machine learning, the best possible performance of classical algorithms is not always known.''
-	\item DO WE SEE THIS: ``Determination of a scaling advantage contrasting quantum and classical machine learning would rely on the existence of a quantum computer and is called a ‘benchmarking’ problem.
+	\item ``Determination of a scaling advantage contrasting quantum and classical machine learning would rely on the existence of a quantum computer and is called a ‘benchmarking’ problem.
 Such advantages could include improved classification accuracy and sampling of classically inaccessible systems.
@@
 \begin{itemize}
-	\item ``Parameterized quantum circuits (PQCs) offer a concrete way to implement algorithms and demonstrate quantum supremacy in the NISQ era.
-PQCs are typically composed of fixed gates, e.g.
+	\item ``PQCs are typically composed of fixed gates, e.g.
 controlled NOTs, and adjustable gates, e.g.

### 2025-02-21 manuscript/main.tex
QCL

@@
 \subsection{BSE}
-The first chemically relevant dataset we explore is the BSE49 dataset.
-As highlighted in Figs. \ref{fig:bondtypes} and \ref{fig:BSEdistr}, this dataset consists of a diverse set of representative chemical bonds and bond separation energies.
-Herein, we follow a similar analysis to the function fitting data, starting off with an analysis of a large set of PQCs using five and sixteen qubits with RUDs and ALs of 1.
-From these two sets of data, we choose the best two models to study how an increase in the RUD and AL effects model performance.
-[learning curves]
-[Conclude we do not want to run this on real hardware due to the lack of promising results using simulation]
-
-five qubit \ref{fig:5BSE_heatplots} \ref{fig:5BSE_boxplots}
+To explore the performance of PQCs for chemically relevant datasets, the dataset we explore is the BSE49 dataset, which consists of a diverse set of bond separation energies and the related structures, as highlighted in Figs.
+\ref{fig:bondtypes} and \ref{fig:BSEdistr}.
+Initially, we study the five qubit data, Figs. \ref{fig:5BSE_heatplots} and \ref{fig:5BSE_boxplots}, due to computational considerations.
+
+five qubit 
 best encoder-ansatz pair: train R$^{2}$/test R$^{2}$

### 2025-02-24 manuscript/functionfitting.tex
Mon Feb 24 03:14:48 PM EST 2025

--- 2025-02-21 manuscript/main.tex
@@
 
-\section*{Abstract}
-Within the quantum machine learning (QML) field, parameterized quantum circuits (PQCs), built using fixed and parameterized gates, offer a hybrid approach for complex machine learning tasks.
-While many potential use cases have been proposed, the exploration of relevant datasets for chemists is lacking.
-Our study seeks to understand the possible advantages and disadvantages of PQCs for two chemically relevant datasets: one based on the bond separation energies of 49 different classes of bonds, called the BSE49 dataset, and another consisting of water confirmations, where coupled-cluster singles and doubles (CCSD) wave functions are predicted using electronic structure theory data from lower-level methods using the data-driven coupled-cluster (DDCC) method.
-In our study, we examine a combinatorial space of 14 data encoding layers and 12 variational (ansatz) layers, for a combined total of 168 PQCs.
-To calibrate our PQCs, we utilize a dataset of noisy linear, quadratic, and sine functions to explore the effects of the circuit width and depth, the effects of the feature set size, and various error mitigation techniques.
-Following this step, we similarly examine our chemically relevant datasets.
-Our work highlights the difficulties in encoding classical molecular representations in a PQC for predicting bond separation energies and the aptitude for PQCs for predicting molecular wave functions.
-\par
-
-\newpage
-\begin{itemize}
-	\item Abstract
-	\item Introduction
-	\item Methods
-	\item Datasets
-	\item Results and Discussion
-	\begin{itemize}
-		\item Function fitting 
-		\begin{itemize}
-			\item All (5 + 16 qubit)
-			\item RUD + AL (5 + 16 qubit)
-			\item Error mitigation on FakeQuebec
-		\end{itemize}
-		\item BSE
-		\begin{itemize}
-			\item All 5 qubit
-			\item Truncated 16 qubit set (cost analysis 5 qubit)
-			\item RUD + AL (5 + 16 qubit)
-			\item Real device (without error mitigation and with whatever the best is from function fitting)
-		\end{itemize}		
-		\item DDCC (5 qubit only because classically it can be done with 5 features!)
-		\begin{itemize}
-			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
-			\item RUD + AL (5 qubit)
-			\item Real device (without error mitigation and with whatever the best is from function fitting)
-		\end{itemize}				
-	\end{itemize}
-	\item Conclusion
-\end{itemize}
-
-\newpage
-\setcounter{secnumdepth}{1}
-\section{Introduction}
-\begin{itemize}
-	\item General background information
-	\item Specific background information
-	\item A description of the gap in our knowledge that the study was designed to fill
-	\item A statement of study objective, and (optionally) a brief summary of study
-\end{itemize}
-
-Within the field of chemistry, tools such as machine learning and quantum computing have become popular due to the promise of discoverying new molecules and materials.
-Machine learning in chemistry has already become a broadly applicable tool for exploring chemical compound space\cite{ramakrishnan_quantum_2014,ramakrishnan_big_2015}, accelerating wave functions\cite{townsend_data-driven_2019,jones_chapter_2023}, and for applications, such as catalysis and drug discovery.\cite{behler_perspective_2016,goh_deep_2017,butler_machine_2018,sanchez-lengeling_inverse_2018,janet_machine_2020}
-[Sentence about quantum computing]
-Another popular avenue, which combines quantum computing and machine learning, is quantum machine learning (QML).
-QML utilizes quantum algorithms during some portion of the machine learning process in an attempt to outperform classical algorithms. \cite{biamonte_quantum_2017}
-On the current era of quantum computers, parameterized quantum circuits (PQCs) offer an example of QML that is performed using a hybrid quantum-classical feedback loop, where the variational parameters are optimized classical, while the circuit is ran on quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
-
-PQCs are often composed using two different subcircuits: the encoding layer, which is used to encode the features into the quantum circuit, and variational layers, which are composed of parameterized gates which can be optimized classical.
-
-PQCs are composed of data-encoding and variational subcircuits, which can be repeated multiple times.
-
-While several examples exist for PQCs applied to chemical applications, they are largely relegated to drug discovery\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,ishiyama_noise-robust_2022,ranga_quantum_2024,alam_qnet_2022,avramouli_quantum_2023,avramouli_unlocking_2023,bhatia_quantum_2023} and experimental properties\cite{hatakeyama-sato_quantum_2023}.
-Herein, we explore two different chemical datasets: one consisting of bond separation energies of 49 unique bond types, called the BSE49 dataset\cite{prasad_bse49_2021}, and another which utilizes data-driven coupled cluster (DDCC)\cite{townsend_data-driven_2019} to predict the coupled-cluster singles and doubles wave function parameters using lower-level quantum chemistry methods.
-
-In this study, we create a robust Python code base for exploring a set of 14 data-encoding and 12 variational (ansatz) subcircuits for a total of 168 combined PQCs.
-Our work includes the single and double encoding layers found in the paper of Suzuki and Katouda\cite{suzuki_predicting_2020}, including the encoding of Mitarai \textit{et al.}\cite{mitarai_quantum_2018}, along with using instantanious quantum polynomial (IQP) as an encoding layer.
-\cite{bremner_average-case_2016}
-All of our variational (ansatz) layers can be found in the study of Sim \textit{et al.}\cite{sim_expressibility_2019}, where the expressiblity and entanglement capability of these circuits is analyzed.
-We also examine the effects of the number of re-upload and ansatz layers, the effects of feature set size, and various error mitigation techniques.
-
-\cite{krenn_artificial_2023}
-
-QML\cite{biamonte_quantum_2017}:
-\begin{itemize}
-	\item ``Quantum machine learning software makes use of quantum algorithms as part of a larger implementation.
-By analysing the steps that quantum algorithms prescribe, it becomes clear that they have the potential to outperform classical algorithms for specific problems (that is, reduce the number of steps required).
-This potential is known as quantum speedup.''
-	\item ``The notion of a quantum speedup depends on whether one takes a formal computer science perspective—which demands mathematical proofs—or a perspective based on what can be done with realistic, finitesize devices—which requires solid statistical evidence of a scaling advantage over some finite range of problem sizes.
-For the case of quantum machine learning, the best possible performance of classical algorithms is not always known.''
-	\item ``Determination of a scaling advantage contrasting quantum and classical machine learning would rely on the existence of a quantum computer and is called a ‘benchmarking’ problem.
-Such advantages could include improved classification accuracy and sampling of classically inaccessible systems.
-Accordingly, quantum speedups in machine learning are currently characterized using idealized measures from complexity theory: query complexity and gate complexity (see Box 1 and Box 1 Table).
-Query complexity measures the number of queries to the information source for the classical or quantum algorithm.
-A quantum speedup results if the number of queries needed to solve a problem is lower for the quantum algorithm than for the classical algorithm.
-To determine the gate complexity, the number of elementary quantum operations (or gates) required to obtain the desired result are counted.''
-	\item Input problem: ``Classical data must be input before being processed on a quantum computer.
-This ‘input problem’ often has little overhead but can present a serious bottleneck for certain algorithms.
-Likewise, the ‘output problem’ is faced when reading out data after being processed on a quantum device.
-Like the input problem, the output problem often causes a noticeable operational slowdown.''
-	\item  QML challenges: ``These hardware challenges are technical in nature, and clear paths exist towards overcoming them.
-They must be overcome, however, if quantum machine learning is to become a ‘killer app’ for quantum computers.
-As noted previously, most of the quantum algorithms that have been identified face a number of caveats that limits their applicability.
-We can distill the caveats mentioned above into four fundamental problems.
-(1) The input problem.
-Although quantum algorithms can provide dramatic speedups for processing data, they seldom provide advantages in reading data.
-This means that the cost of reading in the input can in some cases dominate the cost of quantum algorithms.
-Understanding this factor is an ongoing challenge.
-(2) The output problem.
-Obtaining the full solution from some quantum algorithms as a string of bits requires learning an exponential number of bits.
-This makes some applications of quantum machine learning algorithms infeasible.
-This problem can potentially be sidestepped by learning only summary statistics for the solution state.
-(3) The costing problem.
-Closely related to the input/outputproblems, at present very little is known about the true number of gates required by quantum machine learning algorithms.
-Bounds on the complexity suggest that for sufficiently large problems they will offer huge advantages, but it is still unclear when that crossover point occurs.
-(4) The benchmarking problem.
-It is often difficult to assert that a quantum algorithm is ever better than all known classical machine algorithms in practice because this would require extensive benchmarking against modern heuristic methods.
-Establishing lower bounds for quantum machine learning would partially address this issue.''
-\end{itemize}
-
-PQCs\cite{benedetti_parameterized_2019}:
-\begin{itemize}
-	\item ``PQCs are typically composed of fixed gates, e.g.
-controlled NOTs, and adjustable gates, e.g.
-qubit rotations.
-Even at low circuit depth, some classes of PQCs are capable of generating highly non-trivial outputs.
-For example, under well-believed complexity-theoretic assumptions, the class of PQCs called instantaneous quantum polynomial-time cannot be efficiently simulated by classical resources (see Lund et al [3] and Harrow and Montanaro [4] for accessible Reviews of quantum supremacy proposals).
-The demonstration of quantum supremacy is an important milestone in the development of quantum computers.
-In practice, however, it is highly desirable to demonstrate a quantum advantage on applications.
-The main approach taken by the community consists in formalizing problems of interest as variational optimization problems and use hybrid systems of quantum and classical hardware to find approximate solutions.
-The intuition is that by implementing some subroutines on classical hardware, the requirement of quantum resources is significantly reduced, particularly the number of qubits, circuit depth, and coherence time.
-Therefore, in the hybrid algorithmic approach NISQ hardware focuses entirely on the classically intractable part of the problem.''
-\end{itemize}
-
-PQCs \cite{suzuki_predicting_2020}:
-\begin{itemize}
-	\item ``More recently, quantum machine learning (QML) [26–30] is a rapidly growing research field that combines near-term quantum algorithms and machine learning techniques.
-In particular, parameterized quantum circuits (PQCs) have been considered as machine learning models with high expressive power within the hybrid quantum–classical framework [31, 32].
-PQCs are typically composed of fixed quantum gates (e.g., qubit rotations and entangling gates) in a shallow circuit layout, with variable parameters optimized in a classical feedback loop.''
-	\item ``To our knowledge, however, the application of QML to regression tasks has not been fully investigated in the literature.
-It remains unclear what kinds of quantum states should be used in order to generate the feature map with high expressibility that is suited for real-world data sets.''
-	\item ``quantitative structure–toxicity relationship (QSTR) models for predicting the toxicity of 221 phenols.
-While there are a variety of QSAR/QSTR models (e.g., 3D-QSAR [1, 4]),asafirst step we employ QSAR/QSTR models including molecular descriptors such as hydrophobicity, acidity constant, and frontier orbital energies.
-There have been quantum computations in biochemical and pharmaceutical areas, such as protein folding [43–45], molecular similarity [46], and biological data [47]; yet, there has been no study on quantum application to QSAR modeling, albeit an important part of ligand-based computer-aided drug design.''
-	\item ``PQCs have been regarded as machine learning models with high expressive power within the framework of the hybrid quantum–classical approach.
-PQCs are usually composed of one-qubit rotations and two-qubit entangling operations in a shallow circuit layout, with parameters optimized in a feedback loop.''
-	\item ``Combining near-term quantum algorithms and machine learning, QML using the framework of PQCs is sometimes referred to as quantum circuit learning (QCL)''
-	\item ``PQCs consist of three components: the encoder circuit, the variational circuit, and the measurement for the estimation of the loss function''
-
-\end{itemize}
-
-PQCs \cite{hatakeyama-sato_quantum_2023}:
-\begin{itemize}
-	\item What they do: ``ntroduce quantum circuit learning (QCL) as an emerging regression algorithm for chemo- and materials-informatics.
-The supervised model, functioning on the rule of quantum mechanics, can process linear and smooth non-linear functions from small datasets (<100 records).
-Compared with conventional algorithms, such as random forest, support vector machine, and linear regressions, the QCL can offer better predictions with some one-dimensional functions and experimental chemical databases''
-	\item ``Here, we introduce quantum circuit learning (QCL), an emerging algorithm for supervised learning.15–18 QCL works on the rule of quantum mechanics.
-It can predict various parameters likewise to classical models.
-The current quantum systems (noisy intermediate-scale quantum computers: NISQ)19,20 face the problems of calculation noise and the limited processable number of information units (qubits).''
-	\item ``Since QCL is a frontier for machine learning, few reports have been published on authentic regression tasks.
-The success of prediction with a toxicity dataset of organic molecules was reported,17 whereas the study was still conceptual.
-The prediction processes and advantages have been unclear, especially from chemical and material viewpoints.
-Here, we conducted a more comprehensive study on QCL with standard datasets of one-dimensional functions and chemical properties.
-Both simulated and actual quantum computing was undertaken to clarify the challenges of QCL.
-Various hyperparameters were optimized for higher accuracy.
-The comparison with conventional models contrasted the benefits of the new approach: capable of learning both linear and non-linear functions even from small datasets.
-The property was also favorable for predicting the so-called extrapolating data region, which is essential for chemical and material research.''
-	\item They cite \cite{takaki_learning_2021,suzuki_predicting_2020,mitarai_quantum_2018} as examples of PQCs/quantum circuit learning for regression task
-	\item Justification for starting with 1D regression: ``Preliminary optimization of quantum circuits15,17 and our optimization revealed that the following configuration was concise and practical for regression tasks (for details, see results and explanations in Fig.
-S1''
-\end{itemize}
-
-We introduce \textit{qregress}, a modular Python-based code built on PennyLane for exploring PQCs for regression based learning tasks.
-We analyze three datasets, a function fitting dataset, used for model calibration, and two chemically relevant datasets that offer challenging learning tasks for PQCs.
-
-\section{Methods}
-PQCs are often constructed of three parts: encoding layers that are used to encode the features onto a quantum circuit, variational layers which include parameters that are optimized classically, and measurements which provide numerical estimations of the regression target values.\citep{suzuki_predicting_2020}
-In this study, we utilize the Mitarai (M)\cite{mitarai_quantum_2018}, single- (A1) and double-angle (A2) encoding layers found in Ref.
-\citep{suzuki_predicting_2020}, along with the instantaneous quantum polynomial (IQP) circuit found in Refs.
-\citep{bremner_average-case_2016} and \citep{havlicek_supervised_2019}.
-In the following section, we follow the notations derived from  Ref. \citep{suzuki_predicting_2020}.
-Encoding layers work mapping a $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, normalized on the range $[-1,1]$, onto a quantum circuit using a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ are the number of qubits.
-The encoding layer takes the following general form,
-\begin{equation}
-	U_{\Phi(x)} =  \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})}
-	\label{eq:general_encoding}
-\end{equation}
-where, $E_{\text{ent}}^{l}$ denotes the entangling gates, which can be a CNOT, CZ, or identity ($\mathbf{I}$) gates,   $U_{\phi_{l}(\mathbf{x})}$ denotes the choice of encoding unitaries. 
-Like in  Ref. \citep{suzuki_predicting_2020}, we choose $l \in \{1, 2\}$, such that when $l=1$, $E_{\text{ent}}$ corresponds to an identity matrix and $U_{\Phi(x)} = U_{\phi_{1}(\mathbf{x})}$.
-
-When $l=1$, $U_{\Phi(x)}$ can be one of the following four encoding layers: $U_{\text{A1}}$, $U_{\text{A2}}$, $U_{\text{M}}$, or $U_{\text{IQP}}$.
-The single-angle encoding (Fig. \ref{fig:encoders} \textbf{(a)}) is the simplest and takes the following form,
-\begin{equation}
-	U_{\text{A1}} = \prod_{i=0}^{n} R^{Y}_{i}(x_{i}),
-	\label{eq:A1}
-\end{equation}
-where $R^{Y}_{i}$ denotes a parameterized Y rotation gate on qubit $i$.
-Like the single-angle encoding, the double-angle encoding (Fig.
-\ref{fig:encoders} \textbf{(b)}) utilizes a parameterized Y rotation gate on qubit $i$, with the addition of a parameterized Z rotation gate on qubit $i$, denoted as
-\begin{equation}
-	U_{\text{A2}} = \prod_{i=0}^{n}  R^{Z}_{i}(x_{i}) R^{Y}_{i}(x_{i}).
-	\label{eq:A2}
-\end{equation}
-The Mitarai encoding layer (Fig.
-\ref{fig:encoders} \textbf{(c)}) is a double-angle encoding layer with the addition of an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
-\begin{equation}
-	U_{\text{M}}  = \prod_{i=0}^{n} R^{Z}_{i}(\arccos (x_{i}^{2})) R^{Y}_{i}(\arcsin (x_{i}^{2})).
-	\label{eq:M}
-\end{equation}
-Following the formulation provided in the PennyLane\cite{bergholm_pennylane_2022} software package, the IQP encoding layer (Fig. \ref{fig:encoders} \textbf{(d)}) is defined as,
-\begin{equation}
-	U_{\text{IQP}}  = \prod_{i=0}^{n} H_{i} R^{Z}_{i}(x_{i})  \prod_{i<j} ZZ_{ij},
-	\label{eq:IQP}
-\end{equation}
-where $H_{i}$ denotes a Hadamard gate on qubit $i$ and $ZZ_{ij}$ denotes a two-qubit entangline gate defined as $ZZ_{ij} = e^{-i x_{i} x_{j} \sigma_{z} \otimes \sigma_{z}}$.
-
-%\begin{figure}[H]
-%       \centering
-%       \begin{subfigure}{0.3\textwidth}
-	%               \centering
-	%               \includegraphics[width=\textwidth]{../images/encoders/quantikz/A1.png}
-	%               \caption{}
-	%               \label{fig:A1}
-	%       \end{subfigure}%
-%       \hfill
-%       \begin{subfigure}{0.3\textwidth}
-	%               \centering
-	%               \includegraphics[width=\textwidth]{../images/encoders/quantikz/A2.png}
-	%               \caption{}
-	%               \label{fig:A2}
-	%       \end{subfigure}%
-%       \hfill
-%       \begin{subfigure}{0.3\textwidth}
-	%               \centering
-	%               \includegraphics[width=1\textwidth]{../images/encoders/quantikz/M.png}
-	%               \caption{}
-	%               \label{fig:M}
-	%       \end{subfigure}%
-%       \hfill
-%       \begin{subfigure}{1\textwidth}
-	%               \centering
-	%                   \includegraphics[width=\textwidth]{../images/encoders/quantikz/IQP.png}
-	%               \caption{}
-	%               \label{fig:IQP}
-	%       \end{subfigure}%
-%       \caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
-%       \label{fig:encoders}
-%\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{../images/encoders/quantikz/combined.png}
-	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
-	\label{fig:encoders}
-\end{figure}
-
-When $l=2$, like in Ref.
-\citep{suzuki_predicting_2020} we choose entanglement gates, $E_{\text{ent}}^{1}$ and $E_{\text{ent}}^{2}$ to be equivalent, and the encoding layer takes the following form, $U_{\Phi(x)} =  E_{\text{ent}} U_{\phi_{2}(\mathbf{x})} E_{\text{ent}} U_{\phi_{1}(\mathbf{x})}$ .
-We also exclude IQP encoding when $l=2$ due to the increased circuit depth, when compared to A1, A2, and M encoding.
-Therefore, there are five unique combinations of $U_{\phi_{1}(\mathbf{x})}$ and $U_{\phi_{2}(\mathbf{x})}$ (M-M, A1-A1, A2-A2, M-A1, and M-A2) and two different entanglement layer options (CNOT and CZ) for a total of 10 encoding circuits.
-These circuits are denoted as $U_{\phi_{1}(\mathbf{x})}-U_{\phi_{2}(\mathbf{x})}-E_{\text{ent}}$, for example, two example encoding circuits are M--M--CNOT and M--A1--CNOT.
-Table \ref{tab:encoders} shows all fourteen encoding circuits examined in this study.
-
-\begin{table}[htbp]
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-		\textbf{Name} & $U_{\phi_{1}(\mathbf{x})}$ & $U_{\phi_{2}(\mathbf{x})}$ & $E_{\text{ent}}$  \\
-		\hline
-		\hline
-		A1 & $U_{\text{A1}}$ & --- & --- \\
-		\hline
-		A2 & $U_{\text{A2}}$ & --- & --- \\
-		\hline		
-		M & $U_{\text{M}}$ & --- & --- \\
-		\hline
-		IQP & $U_{\text{IQP}}$ & --- & --- \\
-		\hline
-		A1--A1--CNOT & $U_{\text{A1}}$ & $U_{\text{A1}}$ & $E_{\text{CNOT}}$ \\
-		\hline
-		 A2--A2--CNOT & $U_{\text{A2}}$ & $U_{\text{A2}}$ & $E_{\text{CNOT}}$ \\
-		\hline
-		M--M--CNOT & $U_{\text{M}}$ & $U_{\text{M}}$ & $E_{\text{CNOT}}$ \\
-		\hline
-		M--A1--CNOT & $U_{\text{M}}$ & $U_{\text{A1}}$ & $E_{\text{CNOT}}$ \\
-		\hline		
-		M--A2--CNOT & $U_{\text{M}}$ & $U_{\text{A2}}$ & $E_{\text{CNOT}}$ \\
-		\hline				
-		A1--A1--CZ & $U_{\text{A1}}$ & $U_{\text{A1}}$ & $E_{\text{CZ}}$ \\
-		\hline
-		A2--A2--CZ& $U_{\text{A2}}$ & $U_{\text{A2}}$ & $E_{\text{CZ}}$ \\
-		\hline
-		M--M--CZ & $U_{\text{M}}$ & $U_{\text{M}}$ & $E_{\text{CZ}}$ \\
-		\hline
-		M--A1--CZ & $U_{\text{M}}$ & $U_{\text{A1}}$ & $E_{\text{CZ}}$ \\
-		\hline		
-		M--A2--CZ & $U_{\text{M}}$ & $U_{\text{A2}}$ & $E_{\text{CZ}}$ \\
-		\hline						
-	\end{tabular}
-	\caption{Add something smart}
-	\label{tab:encoders}
-\end{table}
-
-Following the encoding layers,variational (or ansatz) layers are used to introduce trainable parameters into the quantum circuit.
-We use a mixed notation from Refs.
-\citep{suzuki_predicting_2020} and \citep{sim_expressibility_2019}, since Ref.
-\citep{sim_expressibility_2019} contains all of the variational layers used within this work.
-We relegate the discussion of the expressibility and entanglement examined in that work to Section \ref{section:results_and_discussion}.
-A general variational layer can be denoted as,
-\begin{equation}
-	U(\bm{\theta}) = \prod_{v} U_{v}(\bm{\theta}_{v}), % E_{\text{ent}}^{v}
-	\label{eq:general_variational}
-\end{equation}
-where $\bm{\theta}$ denotes the variational parameters and $v$ denotes the number of times that the layer is repeated within the circuit. 
-As $v$ increases and the number of trainable parameters ($\bm{\theta}$) increase, the theoretical assumption is that the model expressibility should also increase.
-In our study, we choose $v \in \{1, 3, 5\}$ and refer to this as the number of ansatz layers (ALs).
-We examine 12 different variational circuits, as shown in Fig.
-\ref{fig:ansatz}, which are denoted using the following labels: Modified-Pauli-CRZ (Fig.
-\ref{fig:ansatz}\textbf{(a)}) , Modified-Pauli-CRX (Fig.
-\ref{fig:ansatz}\textbf{(b)}), Efficient-CRZ (Fig.
-\ref{fig:ansatz}\textbf{(c)}), Efficient-CRX (Fig.
-\ref{fig:ansatz}\textbf{(d)}),, HWE-CNOT (Fig.
-\ref{fig:ansatz}\textbf{(e)}), HWE-CZ (Fig.
-\ref{fig:ansatz}\textbf{(f)}), ESU2 (Fig.
-\ref{fig:ansatz}\textbf{(g)}), Full-Pauli-CRZ (Fig.
-\ref{fig:ansatz}\textbf{(h)}), Full-Pauli-CRX (Fig.
-\ref{fig:ansatz}\textbf{(i)}), Hadamard (Fig.
-\ref{fig:ansatz}\textbf{(j)}), Full-CRZ (Fig.
-\ref{fig:ansatz}\textbf{(k)}), and Full-CRX (Fig.
-\ref{fig:ansatz}\textbf{(l)}),
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{../images/ansatz/quantikz/combined.png}
-	\caption{(a) Modified-Pauli-CRZ, (b) Modified-Pauli-CRX, (c) Efficient-CRZ, (d) Efficient-CRX, (e) HWE-CNOT, (f) HWE-CZ,  (g) ESU2, (h) Full-Pauli-CRZ, (i) Full-Pauli-CRX, (j) Hadamard, (k) Full-CRZ, and (l)Full-CRX}
-	\label{fig:ansatz}
-\end{figure}
-
-Now that we have define the encoding (Eq. \ref{eq:general_encoding}) and variational (Eq. \ref{eq:general_variational}) circuits, we can then combine them to denote a general, complete circuit as,
-\begin{equation}
-	\ket{\Psi} = U(\bm{\theta}) U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n} = \prod_{k}
-	\left( \prod_{v} U_{v}(\bm{\theta}_{v}) \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})} \right)  \ket{0}^{\otimes n},
-\end{equation}
-where we choose $k \in \{1, 3, 5\}$, which denotes the re-upload depth (RUD) of the circuit.
-When a sufficient number of data re-uploading occur, it has been shown by P\'{e}rez-Salinas \textit{et al.} that data re-uploading is equivalent to the Universal Approximation Theorem for artificial neural networks.\cite{perez-salinas_data_2020}
-
-Lastly, to recover the predicted target values, $\hat{y}_{i}$, from our quantum circuits, measurement of the quantum state, $\ket{\Psi}$, must be performed.
-To perform this operation, we apply the Pauli Z operator on the first qubit denoted as,
-\begin{equation}
-	\hat{y}_{i} = \bra{\Psi}Z_{0}\ket{\Psi}_{i}.
-	\label{eq:y_pred}
-\end{equation}
-The set of predicted target values, $\bm{\hat{y}} = (\hat{y}_{1}, \ldots, \hat{y}_{N}) \in \mathbb{R}^{N}$, where $N$ is the number of samples, is then passed to the loss function, $\mathcal{L}(\bm{y}, \bm{\hat y})$, where $y_{i}$ belongs to the set of true target values $\bm{y} = (y_{1}, \ldots, y_{N}) \in \mathbb{R}^{N}$.
-In practice, $\mathcal{L}$ can be any loss function but we choose to use the mean square error loss function denoted as,
-\begin{equation}
-	\mathcal{L}(\bm{y}, \bm{\hat y}) = \frac{1}{N} \sum_{i=1}^{N} (y_{i} - \hat{y}_{i})^{2}.
-	\label{eq:isthisloss}
-\end{equation}
-
-\subsection{Implementation}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{../images/manuscript_figures/overview.png}
-	\caption{Make this figure highlight the modularity of \textit{qregress}}
-	\label{fig:overview_project}
-\end{figure}
-
-We introduce \textit{qregress}, a modular Python package for regression-based PQCs.
-
-We perform all simulation calculations using PennyLane\cite{bergholm_pennylane_2022}, either using Qulacs\cite{suzuki_qulacs_2021} for state vector calcualtions, while noisy calculations were performed using \textit{qiskit-aer} with the \textit{FakeQuebec} backend as implemented in the PennyLane-Qiskit plugin.\cite{javadi-abhari_quantum_2024}
-We perform calculations in the \textit{ibm\_quebec} device using circuits implemented using Qiskit\cite{javadi-abhari_quantum_2024}, due to issues we initially faced with running experiments on the real device using the PennyLane-Qiskit plugin.
-For the experiments using PennyLane,  we utilize the Simultaneous Perturbation Stochastic Approximation method (SPSA) as implemented in PennyLane, while for the experiments run on \textit{ibm\_quebec} utilizes the Constrained Optimization By Linear Approximation (COBYLA) optimizer as implemented ing SciPy\cite{virtanen_scipy_2020}.
-Each optimizer was chosen based on the performance for the given task.
-All features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all featues and target values are $\mathbb{R}\in [ -1,1 ]$.
-For the simulations using \textit{FakeQuebec} and experiments on \textit{ibm\_quebec} we utilize Twirled Readout Error eXtinction (TREX) error mitigation.
-
-Function fitting 5: all ran with 1000 iterations
-Function fitting 16: all ran with 1000 iterations
-BSE 5: all ran with 1000 iterations
-BSE 16: all ran with 1000 iterations
-DDCC
-
-\subsection{Datasets}\label{subsection:datasets}
-In this study, we explore three datasets: a function fitting dataset (Figs.
-\ref{fig:linear_train_vs_test},\ref{fig:quadratic_train_vs_test}, and \ref{fig:sine_train_vs_test}), consisting of a noisy functions used for model calibration; a dataset of bond separation energies (BSE) of molecules (Figs.
-\ref{fig:bondtypes} and \ref{fig:BSEdistr}), where the feature set encodes structural information of each molecule;
-and a dataset consisting of electronic structure features to predict wave functions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis (Fig.
-\ref{fig:waterddccdistribution}).\cite{townsend_data-driven_2019}
-We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the number of samples per molecule.
+\section{Dataset}	
+The function fitting dataset consists of a noisy linear (Fig. \ref{fig:linear_train_vs_test}), quadratic (Fig. \ref{fig:quadratic_train_vs_test}), and sine (\ref{fig:sine_train_vs_test}) function.  
+For each function, 90 points are generated, where 80 are used for training set and 10 for the test set.
+This dataset is used for calibration of the 168 PQCs, along with providing additional insights into the effects of circuit depth, training set size, and error mitigation on model performance.
 
@@
 		\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.65\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/bondtypes.png}
-		\caption{}
-		\label{fig:bondtypes}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/BSE.jpg}
-		\caption{}
-		\label{fig:BSEdistr}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/manuscript_figures/waterddccdistribution.png}
-		\caption{}
-		\label{fig:waterddccdistribution}
-	\end{subfigure}	
-	\caption{Examples of the datasets explored in this study.
-The function fitting dataset used for model calibration include (a) linear (green), (b) quadratic (pink), and (c) sine (blue) functions.
-For the BSE49 dataset the distributions of the (d) bond types and the (e) bond separation energies in kcal/mol.
-For the DDCC dataset distributions of the initial MP2 $t_{2}$-amplitudes and the optimized CCSD $t_{2}$-amplitudes are shown in (f).}
-	\label{fig:bse_data}
+	\caption{The function fitting dataset which consists of 90 total points, 80 for training and 10 used for testing, for the (a) linear, (b) quadratic, and (c) sine functions.}
+	\label{fig:train_vs_test}
 \end{figure}
 
-The function fitting dataset consists of a noisy linear (Fig. \ref{fig:linear_train_vs_test}), quadratic (Fig. \ref{fig:quadratic_train_vs_test}), and sine (\ref{fig:sine_train_vs_test}) function.  
-For each function, 90 points are generated, where 80 are used for training set and 10 for the test set.
-This dataset is used for calibration of the 168 PQCs, along with providing additional insights into the effects of circuit depth, training set size, and error mitigation on model performance.
-
-%\begin{figure}[H]
-%	\centering
-%	\begin{subfigure}[b]{0.3\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/linear_train_vs_test.png}
-%		\caption{}
-%		\label{fig:linear_train_vs_test}
-%	\end{subfigure}
-%	\hfill
-%	\begin{subfigure}[b]{0.3\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
-%		\caption{}
-%		\label{fig:quadratic_train_vs_test}
-%	\end{subfigure}
-%	\hfill
-%	\begin{subfigure}[b]{0.3\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/sine_train_vs_test.png}
-%		\caption{}
-%		\label{fig:sine_train_vs_test}
-%	\end{subfigure}
-%	\caption{The function fitting dataset which consists of 90 total points, 80 for training and 10 used for testing, for the (a) linear, (b) quadratic, and (c) sine functions.}
-%	\label{fig:train_vs_test}
-%\end{figure}
-
-Following model calibration using the function fitting dataset, we explore the appliciblity of PQCs for complex chemically relevant machine learning tasks.
-The first chemically motivated dataset we explore is the BSE49 dataset, which contains the bond seperation energies (BSE)  for the homolytic bond cleavage of covalently bonded molecules, such as \ce{A-B -> A^{.} + B^{.}}.\cite{prasad_bse49_2021}
-This dataset consists of 4394 datapoints, 1951 of which are existing and 2443 are hypthoetical structures, with 49 unique A-B single bond types.
-In practice, we used 2436 of the hypothetical structures due to issues with valency exceptions when converting to RDKit mol objects which were later used for generating our features for the machine learning models.
-An important aspect of machine learning in chemistry is the choice of molecular representation, or how the molecule is represented in the machine learning models.\cite{jones_molecular_2023}
-Using RDKit\cite{noauthor_rdkit_nodate} we examined three commonly applied graph-based molecular preresentations, Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002}, Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, and RDKit fingerprints.
-All three of these methods are use traversals of the molecular graphs to encode various structural details into bit vectors.
-Lastly, we explore both topology- and physics-based molecular representations, both of which encode the three-dimensional structure of molecules in various, unique ways.
-Persistent images (PIs) are a topology-based fingerprint that uses persistence homology to encode topological information of three-dimensional molecular structures into fixed dimension images.\cite{adams_persistence_2017,townsend_representation_2020,schiff_augmenting_2022}
-We use the implementation from Townsend \textit{et al.}\cite{townsend_representation_2020}, which uses the Ripser Python package to generate PIs.\cite{tralie_ripserpy_2018}
-Lastly, we explre two physics-based representations, Coulomb matrices (CMs) \cite{rupp_fast_2012} and smooth overlap of atomic positions (SOAPs), that were generated using DScribe.\cite{de_comparing_2016}
-Due to the computational cost of computing the regularized entropy match (REMatch) kernel  with the SOAPs representation, we excluded this representation in the overall discussion.
-We  also tested two different methods for representing the components of the bond separation chemical reaction, one where the feature vectors for the products are subtracted from the reactants, denoted by \textit{sub}, similar to the method used in Ref.
-\cite{garcia-andrade_barrier_2023}, and one that is composed of the reactant molecular only, denoted as \textit{AB}.
-
-Since we are analyzing a diverse set of PQCs, we also examine a diverse set of classic regression models, with varying capabilities, such as ridge, lasso, elastic net, \textit{k}-nearest-neighbors, random forest, gradient boosting, support vector, kernel ridge, and gaussian process regression as implemented in sckit-learn.\cite{pedregosa_scikit-learn_2011}
-Based on our results shown in Fig. \ref{fig:classical_molrepfig} we found that Morgan fingerprints
-We found that the best molecular representation across all models test, as shown in Fig. \ref{fig:classical_molrepfig}, was Morgan fingerprints using the \textit{sub} formulation.
-
-\begin{figure}[H]
-	\centering	
-	\includegraphics[width=\linewidth]{../images/BSE/classical/classical_molrepfig.png}
-	\caption{Coulomb matrices (CMs), Molecular ACCess Systems (MACCS), persistence images (PIs), RDKit and Morgan fingerprints. Performance of a diverse set of molecular representations R$^{2}$}
-	\label{fig:classical_molrepfig}
-\end{figure}
-
-An additional challenge of applying classical molecular representations for quantum machine learning models is mapping the classical features, often containing hundreds or thousands of features per sample, to the number of qubits used on the quantum device.
-Initially, the Morgan fingerpints have 2048 features per sample, that need to be reduced down to 5 or 16 qubits.
-We choose 5 and 16 qubits for two reasons, the first is that these were the standard number of qubits on IBM quantum devices when we started the project and the second is that reducing the number of features reduces the depth of the circuits.
-To reduce the feature set from 2048 to 5 or 16 features, we explore two different methods, SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017} and principal component analysis (PCA), as implemented in scikit-learn.\cite{pedregosa_scikit-learn_2011}
-Figs. \ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE} show the results for the reductions using SHAP and PCA for the training and test set of using 5 and 16 features.
-The initial model using 2048 features has a train and test mean absolute error (MAE) of 1.91 and 4.98 kcal/mol, with train and test R$^{2}$s of 0.99 and 0.91, respectively.
-When using SHAP to reduce the feature set size to 5 features, we see that the training set has an MAE of 16.08 kcal/mol and an R$^{2}$ of 0.39, while for the test set has an MAE of 15.86 kcal/mol and an R$^{2}$ of 0.42.
-When the number of features is reduced to 16 features using SHAP, we see slight improvements with train and test MAEs of 10.48 and 11.08 kcal/mol with R$^{2}$s of 0.69 and 0.68, respectively.
-Using PCA, we see an improvement in accuracy for both 5 and 16 features, where the training sets have MAEs of 4.09 and 3.23 kcal/mol and the test sets have MAEs of 10.17 and 8.40 kcal/mol, respectively.
-The R$^{2}$s for PCA with 5 and 16 features also shows improvement over the reductions using SHAP, with R$^{2}$s of 0.95 and 0.69 for the training and test set, respectively, using 5 features and 0.97 and 0.78 for the training and test set, respectively, using 16 features.
-Due to the increased performance, despite exhibiting overfitting, we choose to use Morgan fingerprints reduced using PCA for our QML models.
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/classical_features_MAE.png}
-		\caption{}
-		\label{fig:BSE_bse_classical_features_MAE}
-	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/classical_features_R2.png}
-		\caption{}
-		\label{fig:BSE_classical_features_R2}
-	\end{subfigure}
-	\caption{Feature reduction of the BSE dataset represented using }
-	\label{fig:bse_classical_features}
-\end{figure}
-
-The next chemical dataset explored is based on the data-driven coupled-cluster (DDCC) method, which is a machine learning-based approach for accelerating the convergence of coupled-cluster singles and doubles (CCSD) calculations.\cite{townsend_data-driven_2019,jones_chapter_2023}
-This method works by predicting the $t_{2}$-amplitudes of the CCSD wave function (Eq.
-\ref{eq:cc_wfn}) with features generated using lower-level methods, such as Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2), which are used to initialize CCSD calculations.
-
-The coupled-cluster wave function takes the general form,
-\begin{equation}
-	\ket{\Psi_{\text{CC}}} = \exp(\hat{T}) \ket{\Psi_{0}}
-	\label{eq:cc_wfn}
-\end{equation}
-where the cluster operator is denoted as $\hat{T}$ and the reference, Hartree-Fock wave function is denoted as $\ket{\Psi_{0}}$.
-The CCSD wave function truncates the cluster operator to only include singles and doubles excitations.
-The CCSD correlation energy is defined as,
-\begin{equation}
-	E^{\text{CCSD}}_{\text{corr}} = \sum_{\substack{a<b \\ i<j}} \mel{ij}{}{ab} t^{ab}_{ij} + \sum_{\substack{a<b \\ i<j}} \mel{ij}{}{ab} t^{a}_{i} t^{b}_{j}
-	\label{eq:cc_corr}
-\end{equation}
-where $i$ and $j$ denote occupied orbitals, $a$ and $b$ denote virtual orbitals, $t^{ab}_{ij}$ are the $t_{2}$-amplitudes which correspond to two-electron excitations, 
-$t^{a}_{i}$ and $t^{b}_{j}$ are $t_{1}$-amplitudes corresponding to one-electron excitations, and $\mel{ij}{}{ab}$ are two-electron integrals.
-
-For each two-electron excitation, $t^{ab}_{ij}$, a feature set can be generated from HF and MP2.
-The feature set includes the MP2 $t_{2}$-amplitudes, which are used to initialize the CCSD amplitudes,
-\begin{equation}
-	t^{ab}_{ij(\text{MP2})} = \frac{\mel{ij}{}{ab}}{\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}}
-	\label{eq:MP2_t2}
-\end{equation}
-where $\varepsilon_{i}$ and $\varepsilon_{j}$ denote the orbital energies of the occupied orbitals $i$ and $j$, while the virtual orbitals $a$ and $b$ are denoted by $\varepsilon_{a}$ and $\varepsilon_{b}$.
-Features related to the MP2 $t_{2}$-amplitudes that are also included in the feature set are the numerator ($\mel{ij}{}{ab}$) and denominator ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), a binary feature to denote whether the excitation goes to the same virtual orbital, and the orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$).
-The feature set also includes terms related to the individual contributes to the orbital energies are also included, such as the one-electron Hamiltonain ($h$), Coulombic matrix ($J$), and exchange matrix $K$, and Coulombic and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$).
-In total, there are 30 features for each $t_{2}$-amplitude due to the addition of features that denote the sign and magntudes of the previously mentioned features.
-
-Our dataset consists of 199 water molecules from the study by Townsend and Vogiatzis using the STO-3G basis set\cite{hehre_selfconsistent_1970} and frozen core orbitals.
-All data was generated using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
-As previously mentioned, the DDCC method is data intensive regarding the number of samples per molecule, for example, each water molecule has 4 occupied and 2 virtual orbitals.
-The number of $t_{2}$-amplitudes is equivalent to $(N_{occ})^{2}(N_{virt})^{2}$, where $N_{occ}$ denotes the number of occupied orbitals and $N_{virt}$ denotes the number of virtual orbitals, so the total number of $t_{2}$-amplitudes per molecule is 64.
-Further details regarding the feature set and implementation can be found in \cite{townsend_data-driven_2019}
-
-Like the BSE dataset, the 30 features from the full DDCC feature set must be reduced to 5 or 16 features using SHAP or PCA.
-Unlike the BSE dataset, we choose SHAP over PCA for the feature reduction since there is a direct correlation between the input features and output values.
-As shown in Fig. \ref{fig:DDCC_feature_set}, 5 and 16 features can accurately recover performance of the original model using 30 features, where all three models have train and test R$^{2}$s of 1.00.
-Due to the computational costs of running QML models, we will then use only 5 features for all DDCC QML models.
-The 5 most important features are the two-electron integrals ($\mel{ij}{}{ab}$), MP2 $t_{2}$-amplitudes ($t^{ab}_{ij(\text{MP2})}$), the magnitude of the MP2 $t_{2}$-amplitudes, and the difference in orbital energies ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$).
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.49\textwidth]{../images/DDCC/DDCC_feature_set.png}
-	\caption{}
-	\label{fig:DDCC_feature_set}
-\end{figure}
-
-% Make distribution plot
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=\linewidth]{../images/BSE.png}
-%	\caption{BSE}
-%	\label{fig:BSE}
-%\end{figure}
-
-\section{Results and Discussion}
-\label{section:results_and_discussion}
-
-\subsection{Function Fitting}
+\section{Function Fitting}
 To calibrate the PQCs, we perform an initial study of the 168 encoder-ansatz pairs using both 5 and 16 qubits.
@@
 
-\subsection{BSE}
-To explore the performance of PQCs for chemically relevant datasets, the dataset we explore is the BSE49 dataset, which consists of a diverse set of bond separation energies and the related structures, as highlighted in Figs.
-\ref{fig:bondtypes} and \ref{fig:BSEdistr}.
-Initially, we study the five qubit data, Figs. \ref{fig:5BSE_heatplots} and \ref{fig:5BSE_boxplots}, due to computational considerations.
-
-five qubit 
-best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
-Best encoder on average train R$^{2}$/test R$^{2}$
-Best ansatz on average train R$^{2}$/test R$^{2}$
-
-'M-M-CNOT', '-0.0216'
-'Full-CRX', '0.1214'
-
-sixteen qubit \ref{fig:16BSE_heatplots} \ref{fig:16BSE_boxplots}
-removed the really bad ones from five qubit
-best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
-Best encoder on average train R$^{2}$/test R$^{2}$
-Best ansatz on average train R$^{2}$/test R$^{2}$
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_heatplots}
-		\caption{}
-		\label{fig:5BSE_heatplots}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_boxplots}
-		\caption{}
-		\label{fig:5BSE_boxplots}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_heatplots}
-		\caption{}
-		\label{fig:16BSE_heatplots}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_boxplots}
-		\caption{}
-		\label{fig:16BSE_boxplots}
-	\end{subfigure}
-	\caption{}
-	\label{fig:BSEboxandheat}	
-\end{figure}
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE5_RUDAL_lineplot}
-		\caption{}
-		\label{fig:bse5RUDAL_lineplot}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE16_RUDAL_lineplot}
-		\caption{}
-		\label{fig:bse16RUDAL_lineplot}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/distribution_parity}
-		\caption{}
-		\label{fig:BSE5_distribution_parity}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/distribution_parity}
-		\caption{}
-		\label{fig:BSE16_distribution_parity}
-	\end{subfigure}
-	\caption{}
-	\label{fig:BSE_distribution_parity}	
-\end{figure}
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_learningcurve}
-		\caption{}
-		\label{fig:BSE5_learning_curves}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_learningcurve}
-		\caption{}
-		\label{fig:BSE16_learningcurve}
-	\end{subfigure}
-	\caption{}
-	\label{fig:BSE_LC}	
-\end{figure}
-
-\subsection{DDCC}
-
-A2\_HWE-CNOT Train R$^{2}$ 0.62/test R$^{2}$ 0.62 
-Best encoder average Train R$^{2}$ X/test R$^{2}$ Y
-Best ansatz HWE-CNOT average Train R$^{2}$ X/test R$^{2}$ Y
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_heatplots}
-		\caption{}
-		\label{fig:ddccheatplots}
-	\end{subfigure}
-	\hfill	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_boxplots}
-		\caption{}
-		\label{fig:ddccboxplots}
-	\end{subfigure}
-	\hfill
-%	\begin{subfigure}[b]{0.49\textwidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{../images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
-%		\caption{}
-%		\label{fig:allddcc5circuitdepthr2vsiterationtime}
-%	\end{subfigure}	
-	\caption{}
-	\label{fig:ddcc_all_analysis}	
-\end{figure}
-
-(AL,RUD)=(1,1) Train R$^{2}$ 0.62/test R$^{2}$ 0.62
-(AL,RUD)=(1,3) Train R$^{2}$ 0.85/test R$^{2}$ 0.85
-(AL,RUD)=(1,5) Train R$^{2}$ 0.82/test R$^{2}$ 0.83
-(AL,RUD)=(3,1) Train R$^{2}$ 0.71/test R$^{2}$ 0.71
-(AL,RUD)=(5,1) Train R$^{2}$ 0.77/test R$^{2}$ 0.77
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL_lineplot}
-		\caption{}
-		\label{fig:ddccRUDAL_lineplot}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/DDCC/distribution_parity}
-		\caption{}
-		\label{fig:ddccdistribution_parity}
-	\end{subfigure}
-	\caption{Model evaluation, using R$^{2}$ (y-axis), of re-upload depths (RUD) and ansatz layers (AL) of 1, 3, and 5 for the A2\_HWE-CNOT using the DDCC dataset.
-The left side of the plot denotes the training set and the right side the test set.}
-	\label{fig:ddcc_rud}	
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_learning_curves}
-	\caption{}
-	\label{fig:ddcclearningcurves}
-\end{figure}
-
-Ansaetze analysis \cite{sim_expressibility_2019}
-``In particular, a substantial improvement in performance of two-qubit gates in a ring or all-to-all connected arrangement, compared to thatof those on a line, is observed.''
-
-``Furthermore, improvement in both descriptors is achieved by sequences of controlled X-rotation gates compared tosequences of controlled Z-rotation gates.''
-
-``investigated howexpressibility “saturates” with increased circuit depth, finding that the rateand saturated value appear to be distinguishing features of a PQC''
-
-\section{Conclusion}
-Depth is not always better!
-Molecular representations specifically for QML
-Distributed QC to incorporate more features
-Noiseless simulation is costly and does not offer the desired accuracy for BSE49 or DDCC
-
-DDCC could be a useful dataset to benchmark PQC models since it is trivial to perform classically, yet hard for PQCs...
-
 \bibliography{achemso-demo}

### 2025-02-24 manuscript/main.tex
Mon Feb 24 03:14:48 PM EST 2025

@@
 	\begin{itemize}
-		\item Function fitting 
-		\begin{itemize}
-			\item All (5 + 16 qubit)
-			\item RUD + AL (5 + 16 qubit)
-			\item Error mitigation on FakeQuebec
-		\end{itemize}
 		\item BSE
@@
 
-Within the field of chemistry, tools such as machine learning and quantum computing have become popular due to the promise of discoverying new molecules and materials.
+In recent years, machine learning (ML) has become a popular tool for within the field of chemistry.\cite{janet_machine_2020}
+
+Force--fields
+drug discovery
+catalysis discovery
+accelerating wave functions
+
+Within the field of chemistry, tools such as machine learning and quantum computing have become popular due to the promise of discovering new molecules and materials.
 Machine learning in chemistry has already become a broadly applicable tool for exploring chemical compound space\cite{ramakrishnan_quantum_2014,ramakrishnan_big_2015}, accelerating wave functions\cite{townsend_data-driven_2019,jones_chapter_2023}, and for applications, such as catalysis and drug discovery.\cite{behler_perspective_2016,goh_deep_2017,butler_machine_2018,sanchez-lengeling_inverse_2018,janet_machine_2020}
@@
 
+\cite{jin_integrating_2025}
+\begin{itemize}
+	\item ``we designed quantum circuits as feature encoders for a classical neural network. To evaluate the
+	effectiveness of this hybrid quantum-classical model, we compared its performance with traditional ML models using a reduced
+	feature set derived from the full set. A correlation analysis showed that the quantum-encoded representations have a stronger positive
+	correlation with the target values than the original features do. As a result, the hybrid model outperformed its classical counterpart
+	and achieved consistent performance comparable to traditional ML models with the same reduced feature set on both a noiseless
+	simulator and real quantum hardware, highlighting the potential of quantum machine learning for accurate and efficient PA
+	predictions.''
+	\item Chemical QML: \cite{smaldone_quantum--classical_2024}, \cite{bhatia_quantum_2023} \cite{kao_exploring_2023} \cite{li_quantum_2021} \cite{vitz_hybrid_2024} \cite{ryu_quantum_2023}
+\end{itemize}
+
 PQCs \cite{hatakeyama-sato_quantum_2023}:
@@
 \subsection{Datasets}\label{subsection:datasets}
-In this study, we explore three datasets: a function fitting dataset (Figs.
-\ref{fig:linear_train_vs_test},\ref{fig:quadratic_train_vs_test}, and \ref{fig:sine_train_vs_test}), consisting of a noisy functions used for model calibration; a dataset of bond separation energies (BSE) of molecules (Figs.
+In this study, we explore two datasets: a dataset of bond separation energies (BSE) of molecules (Figs.
 \ref{fig:bondtypes} and \ref{fig:BSEdistr}), where the feature set encodes structural information of each molecule;
@@
 	\centering
+	\begin{subfigure}[b]{0.65\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/BSE/bondtypes.png}
+		\caption{}
+		\label{fig:bondtypes}
+	\end{subfigure}
+	\hfill
 	\begin{subfigure}[b]{0.3\textwidth}
 		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/linear_train_vs_test.png}
-		\caption{}
-		\label{fig:linear_train_vs_test}
+		\includegraphics[width=\textwidth]{../images/BSE/BSE.jpg}
+		\caption{}
+		\label{fig:BSEdistr}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
-		\caption{}
-		\label{fig:quadratic_train_vs_test}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/sine_train_vs_test.png}
-		\caption{}
-		\label{fig:sine_train_vs_test}
-	\end{subfigure}	
-	\hfill
-	\begin{subfigure}[b]{0.65\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/bondtypes.png}
-		\caption{}
-		\label{fig:bondtypes}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/BSE.jpg}
-		\caption{}
-		\label{fig:BSEdistr}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
 		\includegraphics[width=\textwidth]{../images/manuscript_figures/waterddccdistribution.png}
@@
 	\caption{Examples of the datasets explored in this study.
-The function fitting dataset used for model calibration include (a) linear (green), (b) quadratic (pink), and (c) sine (blue) functions.
 For the BSE49 dataset the distributions of the (d) bond types and the (e) bond separation energies in kcal/mol.
@@
 \end{figure}
-
-The function fitting dataset consists of a noisy linear (Fig. \ref{fig:linear_train_vs_test}), quadratic (Fig. \ref{fig:quadratic_train_vs_test}), and sine (\ref{fig:sine_train_vs_test}) function.  
-For each function, 90 points are generated, where 80 are used for training set and 10 for the test set.
-This dataset is used for calibration of the 168 PQCs, along with providing additional insights into the effects of circuit depth, training set size, and error mitigation on model performance.
-
-%\begin{figure}[H]
-%	\centering
-%	\begin{subfigure}[b]{0.3\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/linear_train_vs_test.png}
-%		\caption{}
-%		\label{fig:linear_train_vs_test}
-%	\end{subfigure}
-%	\hfill
-%	\begin{subfigure}[b]{0.3\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/quadratic_train_vs_test.png}
-%		\caption{}
-%		\label{fig:quadratic_train_vs_test}
-%	\end{subfigure}
-%	\hfill
-%	\begin{subfigure}[b]{0.3\textwidth}
-%		\centering
-%		\includegraphics[width=\textwidth]{../images/Function_Fitting/function_dataset/sine_train_vs_test.png}
-%		\caption{}
-%		\label{fig:sine_train_vs_test}
-%	\end{subfigure}
-%	\caption{The function fitting dataset which consists of 90 total points, 80 for training and 10 used for testing, for the (a) linear, (b) quadratic, and (c) sine functions.}
-%	\label{fig:train_vs_test}
-%\end{figure}
 
@@
 
-\subsection{Function Fitting}
-To calibrate the PQCs, we perform an initial study of the 168 encoder-ansatz pairs using both 5 and 16 qubits.
-Individual heat maps showing the performance of the encoder-ansatz pairs and box plots showing the overall statistics for each encoder and ansatz are shown for the 5 and 16 qubit models in SI Section \siref{section:si_functionfitting}.
-
-Starting with the five qubit function fitting, we found that out of the
-168 encoder-ansatz pairs, for the linear function (SI Fig. \siref{fig:linear_heatplots}) is is A1\_ESU2 with a train and test R$^{2}$ of 0.9886 and 0.9893, respectively.
-Box plots for the encoders (left) and variational layers (right) are shown in SI  Fig.
-\siref{fig:linear_boxplots}, where, the best encoder is IQP, with a mean R$^{2}$ of 0.8434, and best ansatz layer Full-CRX, with a mean R$^{2}$ of 0.7562.
-For the quadratic function, the best encoder-ansatz pair is A1-A1-CNOT\_Full-CRX with a train and test R$^{2}$ of 0.8809 and 0.7309, respectively, as shown in SI Fig \siref{fig:quadratic_heatplots}.
-On average the best encoder is A1-A1-CNOT with an R$^{2}$ of 0.5541 and best variational layer is Full-CRX with an R$^{2}$ of 0.5958 (SI  Fig. \siref{fig:quadratic_boxplots}).
-For the sine function, SI  Fig. \siref{fig:sine_heatplots}, M-M-CZ\_Full-CRX is the best encoder-ansatz pair with a train and test R$^{2}$ of 0.8887 and 0.9081, respectively.
-As shown in SI  Fig. \siref{fig:sine_boxplots}, the best encoder is M with an average R$^{2}$ of 0.6456 and best variational layer is Full-CRX with a mean R$^{2}$ of 0.7551.
-Across all three five qubit function fitting datasets, on average, the best encoders are M-A2-CZ with an average R$^{2}$ of 0.4776 (Fig.
-\ref{fig:five_feature_function_fitting_boxplots} left) and ansatz is Full-CRX with an average R$^{2}$ of 0.7023 (Fig.
-\ref{fig:five_feature_function_fitting_boxplots} right).
-
-For the sixteen qubit function fitting evaluation of the 168 encoder-ansatz pairs, we found that, similarly to the five qubit data, for the linear function the best pair is A1\_ESU2 with train and test R$^{2}$s of 0.9886 and 0.9893, respectively, as highlighted in SI Fig.
-\siref{fig:sixteenlinear_heatplots}.
-Like the five qubit data, the best encoder is also IQP with an average R$^{2}$ of 0.7800 (SI Fig.
-\siref{fig:sixteenlinear_boxplots} left), while the best ansatz varies from the five qubit data, Full-Pauli-CRZ with a mean R$^{2}$ of 0.3947 (SI Fig.
-\siref{fig:sixteenlinear_boxplots} right).
-The A1-A1-CZ\_Modified-Pauli-CRX encoder-ansatz pair has the best overall model performance, highlighted in SI Fig.
-\siref{fig:sixteenquadratic_heatplots}, where the training set has an R$^{2}$ of 0.8415 and the test set has an R$^{2}$ of  0.7722.
-As demonstrated in SI Fig. \siref{fig:sixteenquadratic_boxplots}, the best encoders and ans\"{a}tze are A1-A1-CNOT and Full-Pauli-CRX, with mean R$^{2}$s of 0.5759 and 0.4474, respectively.
-For the last sixteen qubit dataset, the sine function data (SI Fig.
-\siref{fig:sixteensine_heatplots}), the best encoder-ansatz pair is A1-A1-CZ\_Full-Pauli-CRZ	with an R$^{2}$ of 0.8147 for the training set and an R$^{2}$ of 0.8626	for the test set.
-SI Fig. \siref{fig:sixteensine_boxplots} highlights that the best encoder is M with a mean R$^{2}$ of 0.5824 and best ansatz, on average, is Full-Pauli-CRZ with an R$^{2}$ of 0.4881.
-Across all three function fitting datasets, the sixteen qubit data varies where the best encoders are IQP with an average R$^{2}$ of 0.4506 and ans\"{a}tze is Full-Pauli-CRZ with an average R$^{2}$ of 0.4393.
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/fivequbit/five_feature_function_fitting_boxplots.png}
-		\caption{}
-		\label{fig:five_feature_function_fitting_boxplots}
-	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/Function_Fitting/sixteenqubit/sixteen_feature_function_fitting_boxplots.png}
-		\caption{}
-		\label{fig:sixteen_feature_function_fitting_boxplots}
-	\end{subfigure}
-	\hfill		
-	\caption{The combined performance of all three function fitting datasets for both the (a) five and (b) sixteen qubit models is evaluated using the R$^{2}$ (y-axis) versus the encoders (left) and ans\"{a}tze (right).}
-	\label{fig:function_fitting_boxplots}
-\end{figure}
-
-Following the initially analysis of the performance of the 168 PQCs using both five and sixteen qubits, we experimented with the effect of the re-upload depth (RUD) and number of ansatz layers (AL) using the sixteen qubit circuits.
-We chose to use the sixteen qubit circuits over the five qubit circuits since these circuits have complexity more similar to when the circuits are used for the chemical dataset in terms of the number of parameters and optimization times.
-From the initial 168 PQCs, for each function fitting dataset, we choose the five best (top row), five median (middle row), and five worst (bottom row) circuits to see the effects of increasing the RUD and AL on model performance as shown in Figs.
-\ref{fig:16qubit_Linear_RUD_AL}, \ref{fig:16qubit_Quadratic_RUD_AL}, and  \ref{fig:16qubit_Sine_RUD_AL}.
-For the linear (Fig.
-\ref{fig:16qubit_Linear_RUD_AL}), quadratic (\ref{fig:16qubit_Quadratic_RUD_AL}), and sine (Fig.
-\ref{fig:16qubit_Sine_RUD_AL}) data, some generalities arise for the five best circuits.
-We see that for these circuits, increasing the number of AL from 1 to 3 or 5 improves model performance more than RUD.
-For the median performers, the RUD improves model performance more than the ansatz layers.
-And lastly, for the worse performers a general trend does not exist and increasing the RUD and AL depends on the dataset and circuit architecture.
-
-% Commented this out because it is not useful for the overall discussion
-%While an increase in the circuit depth, either by increasing the RUD or AL, is associated with an increase in model performance this is also associated with an increased computational cost. 
-%In Figs.
-\ref{fig:linear_circuitdepth_vs_R2}, \ref{fig:quadratic_circuitdepth_vs_R2}, and \ref{fig:sine_circuitdepth_vs_R2} we  highlight this trade-off, where the x-axes denote circuit depth, y-axis denotes the R$^{2}$, and the median train and test R$^{2}$ are shown in red and blue, respectively, for all 15 circuits.
-Despite these trends, we found that for the linear function, the best performing model is IQP\_Full-Pauli-CRZ  with a RUD and AL of 1.
-This circuit also has a training and test R$^{2}$ of 0.9883 and 0.9891, respectively, and a depth of 95.
-Unlike the best linear circuit, the best circuits for both the quadratic and sine data, IQP\_Full-Pauli-CRX	 and A2\_HWE-CZ, respectively,  benefit from an increased RUD, with the best models having a RUD of 5 and AL of 1.
-These two circuits differ in depth and performance, with the IQP\_Full-Pauli-CRX for the quadratic data having a circuit depth of 520, training R$^{2}$ of 0.9817, and test R$^{2}$ of 0.9609 and the A2\_HWE-CZ circuit for the sine data having a depth of 105 , training R$^{2}$ of 0.9156, and test R$^{2}$ of 0.9576.
-Following these insights, we applied these circuits for analyzing the effects of the training set size on model performance using learning curves and the effects of error mitigation using noisy simulation.
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Linear_RUD_AL}
-		\caption{}
-		\label{fig:16qubit_Linear_RUD_AL}
-	\end{subfigure}
-	\hfill	
-%	\begin{subfigure}[b]{0.49\textwidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_circuitdepth_vs_R2}
-%		\caption{}
-%		\label{fig:linear_circuitdepth_vs_R2}
-%	\end{subfigure}
-%	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Quadratic_RUD_AL}
-		\caption{}
-		\label{fig:16qubit_Quadratic_RUD_AL}
-	\end{subfigure}
-	\hfill
-%	\begin{subfigure}[b]{0.49\textwidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_circuitdepth_vs_R2}
-%		\caption{}
-%		\label{fig:quadratic_circuitdepth_vs_R2}
-%	\end{subfigure}
-%	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/sixteenqubit/16qubit_Sine_RUD_AL.png}
-		\caption{}
-		\label{fig:16qubit_Sine_RUD_AL}
-	\end{subfigure}	
-	\hfill
-%	\begin{subfigure}[b]{0.49\textwidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_circuitdepth_vs_R2}
-%		\caption{}
-%		\label{fig:sine_circuitdepth_vs_R2}
-%	\end{subfigure}
-%	\hfill		
-	\caption{The best five (top row), median five (middle row), and worst five (bottom row) circuits for the 16 qubit (a) linear, (b) quadratic, and (c) sine data show that, in general, an increase in the re-upload depth (RUD) or ansatz layers (AL) increases model performance (R$^{2}$ shown on the y-axis).}
-	\label{fig:16qubit_RUD_AL}	
-\end{figure}
-
-One proposed advantage of using PQCs for ML tasks is that, in some cases, they can outperform classical ML models using less training data.\cite{hatakeyama-sato_quantum_2023}
-We examine this phenomena with learning curves using the best performing circuits previously described.
-The learning curves are generated by varying the percentage of training data from 10-80\% of the available data, while holding the number of test points to 10\% of the total data.
-The three PQCs for each data set are compared to the classical models mentioned in subsection \ref{subsection:datasets} in a statistical manner (left sub-figures in Figs.
-\ref{fig:linear_learning_curves}, \ref{fig:quadratic_learning_curves}, and \ref{fig:sine_learning_curves}).
-Across the full learning curve, IQP\_Full-Pauli-CRZ (linear function fitting) outperforms seven out of nine classical models for the training set and all of the classical models on the test set.
-On the quadratic dataset, using IQP\_Full-Pauli-CRX, offers similar performance to the classical models, despite being outperformed on the training set across the learning curve. 
-Similar to the IQP\_Full-Pauli-CRZ using the linear data, IQP\_Full-Pauli-CRX outperforms seven out of the nine classical models on the test set across the full learning curve.
-On the sine data, A2\_HWE-CZ is consistent across the learning curve, outperforming six of the nine classical models on the training set and all of the models on the test set.
-For all three datasets, this implies that the PQCs offer similar performance to classical models that do well on these datasets but provide better results on the test set.
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_learning_curves.png}
-		\caption{}
-		\label{fig:linear_learning_curves}
-	\end{subfigure}
-	\hfill	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_learning_curves.png}
-		\caption{}
-		\label{fig:quadratic_learning_curves}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_learning_curves.png}
-		\caption{}
-		\label{fig:sine_learning_curves}
-	\end{subfigure}	
-	\caption{Learning curves of the best PQCs (right side in the subfigures) versus various classical models (left side in the subfigure) for the (a) linear, (b) quadratic, and (c) sine function datasets.}
-	\label{fig:functionfitting_learning_curves}	
-\end{figure}
-
-optimization level needs to be set to 0!
-
-Lastly, using the function fitting datasets we analyze the effects of error mitigation on the model accuracy by comparing state vector simulations with noisy and error mitigated simulations using the \textit{fake\_quebec} backend.
-Initially, we explored two different methods of error mitigation zero-noise extrapolation (ZNE) using MITIQ\cite{larose_mitiq_2022} and TREX, as implemented in Qiskit. 
-We found that both linear and Richardson ZNE were too costly to simulate on classical computers using 16 qubits for all three function fitting datasets and chose only to use TREX for error mitigation.
-Our analysis revealed that the state vector, TREX, and unmitigated IQP\_Full-Pauli-CRZ (linear function fitting data) models all have R$^{2}$ between 0.98 and 0.99, for both the training and test sets, as highlighted in Fig.
-\ref{fig:linear_error_mitigation}.
-While the performance of the linear data can be attributed to the simiplicity of the dataset, for the quadratic function fitting data using IQP\_Full-Pauli-CRX (Fig.
-\ref{fig:quadratic_error_mitigation}), we found that the model with unmitigated error has an R$^{2}$ of 0.65 for the training set and 0.45 for the test set.
-This model is improved slightly by the incorporation of error mitigation using TREX, where the training set R$^{2}$ is 0.69 and test set R$^{2}$ is 0.60.
-Overall, the model using TREX offers results more comparable to the state vector simulations, which has a R$^{2}$s of 0.80 and 0.68 for the training and test set, respectively.
-On the sine function fitting data, using A2\_HWE-CZ (Fig.
-\ref{fig:sine_error_mitigation}), for the state vector, TREX, and unmitigated models, the training sets have R$^{2}$s of 0.92, 0.87, and 0.87, respectively, while the test sets have R$^{2}$s of 0.96, 0.89, and 0.91, respectively.
-Overall, while these results are for simple function fitting data, we concluded that TREX offers a computational efficient error mitigation method, with results similar to the state vector calculations.0
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_error_mitigation.png}
-		\caption{}
-		\label{fig:linear_error_mitigation}
-	\end{subfigure}
-	\hfill	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_error_mitigation.png}
-		\caption{}
-		\label{fig:quadratic_error_mitigation}
-	\end{subfigure}	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/Function_Fitting/sine_error_mitigation.png}
-		\caption{}
-		\label{fig:sine_error_mitigation}
-	\end{subfigure}
-	\hfill		
-	\caption{Error mitigation benchmarking for the (a) linear, (b) quadratic, and (c) sine function comparing unmitigated and mitigated error using TREX with state vector simulations.}
-	\label{fig:functionfitting_errormitigation}	
-\end{figure}
-
 \subsection{BSE}

### 2025-02-24 manuscript/main.tex
$(date) manuscript

@@
 \section{Introduction}
-\begin{itemize}
-	\item General background information
-	\item Specific background information
-	\item A description of the gap in our knowledge that the study was designed to fill
-	\item A statement of study objective, and (optionally) a brief summary of study
-\end{itemize}
 
-In recent years, machine learning (ML) has become a popular tool for within the field of chemistry.\cite{janet_machine_2020}
+In recent years, machine learning (ML) has become a popular tool within the field of chemistry for exploring chemical compound space\cite{ramakrishnan_quantum_2014,ramakrishnan_big_2015}, accelerating wave functions\cite{townsend_data-driven_2019,jones_chapter_2023}, and for applications, such as catalysis and drug discovery.\cite{behler_perspective_2016,goh_deep_2017,butler_machine_2018,sanchez-lengeling_inverse_2018,janet_machine_2020}
+Often, the goal of machine learning in chemistry is to reveal new patterns in data, provide new insights beyond simple models and human experience, and to accelerate computations and analysis of chemical space.\cite{janet_machine_2020}
+Additionally, interest in quantum computing (QC) for chemical applications have become increasingly popular due to the inherent quantum nature of chemistry.\cite{cao_quantum_2019}
+An approach that combines both ML and QC, is quantum machine learning (QML).
+QML has has shown potential for quantum speedups, either through formal mathematical proofs or numerical experiments based on empirical observations.
+In practice, determining theoretical quantum speedups can be difficult to determine and numerical experiments must be used to quantify the computational complexity.\cite{biamonte_quantum_2017}
 
-Force--fields
-drug discovery
-catalysis discovery
-accelerating wave functions
+In the context of chemistry, quantum machine learning (QML) has gained traction for tasks such as drug discovery\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,bhatia_quantum_2023,kao_exploring_2023,li_quantum_2021,avramouli_quantum_2023,avramouli_unlocking_2023}, materials discovery\cite{ishiyama_noise-robust_2022,ryu_quantum_2023,vitz_hybrid_2024}, proton affinities\cite{jin_integrating_2025}, and experimental molecular properties, including the log solubility in water, melting point, octanol/water distribution coefficient, hydration free energy of small molecules in water.\cite{hatakeyama-sato_quantum_2023}
 
-Within the field of chemistry, tools such as machine learning and quantum computing have become popular due to the promise of discovering new molecules and materials.
-Machine learning in chemistry has already become a broadly applicable tool for exploring chemical compound space\cite{ramakrishnan_quantum_2014,ramakrishnan_big_2015}, accelerating wave functions\cite{townsend_data-driven_2019,jones_chapter_2023}, and for applications, such as catalysis and drug discovery.\cite{behler_perspective_2016,goh_deep_2017,butler_machine_2018,sanchez-lengeling_inverse_2018,janet_machine_2020}
-[Sentence about quantum computing]
-Another popular avenue, which combines quantum computing and machine learning, is quantum machine learning (QML).
-QML utilizes quantum algorithms during some portion of the machine learning process in an attempt to outperform classical algorithms. \cite{biamonte_quantum_2017}
-On the current era of quantum computers, parameterized quantum circuits (PQCs) offer an example of QML that is performed using a hybrid quantum-classical feedback loop, where the variational parameters are optimized classical, while the circuit is ran on quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
+One class of QML algorithms, based on a hybrid quantum--classical feedback loop, are parameterized quantum circuits (PQCs).
+PQCs offer flexible QML models where the variational parameters are optimized classically, while the quantum circuit can be ran on near-term quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
+Often, PQCs are composed of two parts: an encoding circuit, used to encode the features, and a variational (ansatz) circuit, composed of trainable machine learning parameters.
 
-PQCs are often composed using two different subcircuits: the encoding layer, which is used to encode the features into the quantum circuit, and variational layers, which are composed of parameterized gates which can be optimized classical.
-
-PQCs are composed of data-encoding and variational subcircuits, which can be repeated multiple times.
-
-While several examples exist for PQCs applied to chemical applications, they are largely relegated to drug discovery\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,ishiyama_noise-robust_2022,ranga_quantum_2024,alam_qnet_2022,avramouli_quantum_2023,avramouli_unlocking_2023,bhatia_quantum_2023} and experimental properties\cite{hatakeyama-sato_quantum_2023}.
 Herein, we explore two different chemical datasets: one consisting of bond separation energies of 49 unique bond types, called the BSE49 dataset\cite{prasad_bse49_2021}, and another which utilizes data-driven coupled cluster (DDCC)\cite{townsend_data-driven_2019} to predict the coupled-cluster singles and doubles wave function parameters using lower-level quantum chemistry methods.
@@
 We also examine the effects of the number of re-upload and ansatz layers, the effects of feature set size, and various error mitigation techniques.
-
-\cite{krenn_artificial_2023}
-
-QML\cite{biamonte_quantum_2017}:
-\begin{itemize}
-	\item ``Quantum machine learning software makes use of quantum algorithms as part of a larger implementation.
-By analysing the steps that quantum algorithms prescribe, it becomes clear that they have the potential to outperform classical algorithms for specific problems (that is, reduce the number of steps required).
-This potential is known as quantum speedup.''
-	\item ``The notion of a quantum speedup depends on whether one takes a formal computer science perspective—which demands mathematical proofs—or a perspective based on what can be done with realistic, finitesize devices—which requires solid statistical evidence of a scaling advantage over some finite range of problem sizes.
-For the case of quantum machine learning, the best possible performance of classical algorithms is not always known.''
-	\item ``Determination of a scaling advantage contrasting quantum and classical machine learning would rely on the existence of a quantum computer and is called a ‘benchmarking’ problem.
-Such advantages could include improved classification accuracy and sampling of classically inaccessible systems.
-Accordingly, quantum speedups in machine learning are currently characterized using idealized measures from complexity theory: query complexity and gate complexity (see Box 1 and Box 1 Table).
-Query complexity measures the number of queries to the information source for the classical or quantum algorithm.
-A quantum speedup results if the number of queries needed to solve a problem is lower for the quantum algorithm than for the classical algorithm.
-To determine the gate complexity, the number of elementary quantum operations (or gates) required to obtain the desired result are counted.''
-	\item Input problem: ``Classical data must be input before being processed on a quantum computer.
-This ‘input problem’ often has little overhead but can present a serious bottleneck for certain algorithms.
-Likewise, the ‘output problem’ is faced when reading out data after being processed on a quantum device.
-Like the input problem, the output problem often causes a noticeable operational slowdown.''
-	\item  QML challenges: ``These hardware challenges are technical in nature, and clear paths exist towards overcoming them.
-They must be overcome, however, if quantum machine learning is to become a ‘killer app’ for quantum computers.
-As noted previously, most of the quantum algorithms that have been identified face a number of caveats that limits their applicability.
-We can distill the caveats mentioned above into four fundamental problems.
-(1) The input problem.
-Although quantum algorithms can provide dramatic speedups for processing data, they seldom provide advantages in reading data.
-This means that the cost of reading in the input can in some cases dominate the cost of quantum algorithms.
-Understanding this factor is an ongoing challenge.
-(2) The output problem.
-Obtaining the full solution from some quantum algorithms as a string of bits requires learning an exponential number of bits.
-This makes some applications of quantum machine learning algorithms infeasible.
-This problem can potentially be sidestepped by learning only summary statistics for the solution state.
-(3) The costing problem.
-Closely related to the input/outputproblems, at present very little is known about the true number of gates required by quantum machine learning algorithms.
-Bounds on the complexity suggest that for sufficiently large problems they will offer huge advantages, but it is still unclear when that crossover point occurs.
-(4) The benchmarking problem.
-It is often difficult to assert that a quantum algorithm is ever better than all known classical machine algorithms in practice because this would require extensive benchmarking against modern heuristic methods.
-Establishing lower bounds for quantum machine learning would partially address this issue.''
-\end{itemize}
-
-PQCs\cite{benedetti_parameterized_2019}:
-\begin{itemize}
-	\item ``PQCs are typically composed of fixed gates, e.g.
-controlled NOTs, and adjustable gates, e.g.
-qubit rotations.
-Even at low circuit depth, some classes of PQCs are capable of generating highly non-trivial outputs.
-For example, under well-believed complexity-theoretic assumptions, the class of PQCs called instantaneous quantum polynomial-time cannot be efficiently simulated by classical resources (see Lund et al [3] and Harrow and Montanaro [4] for accessible Reviews of quantum supremacy proposals).
-The demonstration of quantum supremacy is an important milestone in the development of quantum computers.
-In practice, however, it is highly desirable to demonstrate a quantum advantage on applications.
-The main approach taken by the community consists in formalizing problems of interest as variational optimization problems and use hybrid systems of quantum and classical hardware to find approximate solutions.
-The intuition is that by implementing some subroutines on classical hardware, the requirement of quantum resources is significantly reduced, particularly the number of qubits, circuit depth, and coherence time.
-Therefore, in the hybrid algorithmic approach NISQ hardware focuses entirely on the classically intractable part of the problem.''
-\end{itemize}
-
-PQCs \cite{suzuki_predicting_2020}:
-\begin{itemize}
-	\item ``More recently, quantum machine learning (QML) [26–30] is a rapidly growing research field that combines near-term quantum algorithms and machine learning techniques.
-In particular, parameterized quantum circuits (PQCs) have been considered as machine learning models with high expressive power within the hybrid quantum–classical framework [31, 32].
-PQCs are typically composed of fixed quantum gates (e.g., qubit rotations and entangling gates) in a shallow circuit layout, with variable parameters optimized in a classical feedback loop.''
-	\item ``To our knowledge, however, the application of QML to regression tasks has not been fully investigated in the literature.
-It remains unclear what kinds of quantum states should be used in order to generate the feature map with high expressibility that is suited for real-world data sets.''
-	\item ``quantitative structure–toxicity relationship (QSTR) models for predicting the toxicity of 221 phenols.
-While there are a variety of QSAR/QSTR models (e.g., 3D-QSAR [1, 4]),asafirst step we employ QSAR/QSTR models including molecular descriptors such as hydrophobicity, acidity constant, and frontier orbital energies.
-There have been quantum computations in biochemical and pharmaceutical areas, such as protein folding [43–45], molecular similarity [46], and biological data [47]; yet, there has been no study on quantum application to QSAR modeling, albeit an important part of ligand-based computer-aided drug design.''
-	\item ``PQCs have been regarded as machine learning models with high expressive power within the framework of the hybrid quantum–classical approach.
-PQCs are usually composed of one-qubit rotations and two-qubit entangling operations in a shallow circuit layout, with parameters optimized in a feedback loop.''
-	\item ``Combining near-term quantum algorithms and machine learning, QML using the framework of PQCs is sometimes referred to as quantum circuit learning (QCL)''
-	\item ``PQCs consist of three components: the encoder circuit, the variational circuit, and the measurement for the estimation of the loss function''
-
-\end{itemize}
-
-\cite{jin_integrating_2025}
-\begin{itemize}
-	\item ``we designed quantum circuits as feature encoders for a classical neural network. To evaluate the
-	effectiveness of this hybrid quantum-classical model, we compared its performance with traditional ML models using a reduced
-	feature set derived from the full set. A correlation analysis showed that the quantum-encoded representations have a stronger positive
-	correlation with the target values than the original features do. As a result, the hybrid model outperformed its classical counterpart
-	and achieved consistent performance comparable to traditional ML models with the same reduced feature set on both a noiseless
-	simulator and real quantum hardware, highlighting the potential of quantum machine learning for accurate and efficient PA
-	predictions.''
-	\item Chemical QML: \cite{smaldone_quantum--classical_2024}, \cite{bhatia_quantum_2023} \cite{kao_exploring_2023} \cite{li_quantum_2021} \cite{vitz_hybrid_2024} \cite{ryu_quantum_2023}
-\end{itemize}
-
-PQCs \cite{hatakeyama-sato_quantum_2023}:
-\begin{itemize}
-	\item What they do: ``ntroduce quantum circuit learning (QCL) as an emerging regression algorithm for chemo- and materials-informatics.
-The supervised model, functioning on the rule of quantum mechanics, can process linear and smooth non-linear functions from small datasets (<100 records).
-Compared with conventional algorithms, such as random forest, support vector machine, and linear regressions, the QCL can offer better predictions with some one-dimensional functions and experimental chemical databases''
-	\item ``Here, we introduce quantum circuit learning (QCL), an emerging algorithm for supervised learning.15–18 QCL works on the rule of quantum mechanics.
-It can predict various parameters likewise to classical models.
-The current quantum systems (noisy intermediate-scale quantum computers: NISQ)19,20 face the problems of calculation noise and the limited processable number of information units (qubits).''
-	\item ``Since QCL is a frontier for machine learning, few reports have been published on authentic regression tasks.
-The success of prediction with a toxicity dataset of organic molecules was reported,17 whereas the study was still conceptual.
-The prediction processes and advantages have been unclear, especially from chemical and material viewpoints.
-Here, we conducted a more comprehensive study on QCL with standard datasets of one-dimensional functions and chemical properties.
-Both simulated and actual quantum computing was undertaken to clarify the challenges of QCL.
-Various hyperparameters were optimized for higher accuracy.
-The comparison with conventional models contrasted the benefits of the new approach: capable of learning both linear and non-linear functions even from small datasets.
-The property was also favorable for predicting the so-called extrapolating data region, which is essential for chemical and material research.''
-	\item They cite \cite{takaki_learning_2021,suzuki_predicting_2020,mitarai_quantum_2018} as examples of PQCs/quantum circuit learning for regression task
-	\item Justification for starting with 1D regression: ``Preliminary optimization of quantum circuits15,17 and our optimization revealed that the following configuration was concise and practical for regression tasks (for details, see results and explanations in Fig.
-S1''
-\end{itemize}
 
@@
 where $H_{i}$ denotes a Hadamard gate on qubit $i$ and $ZZ_{ij}$ denotes a two-qubit entangline gate defined as $ZZ_{ij} = e^{-i x_{i} x_{j} \sigma_{z} \otimes \sigma_{z}}$.
+
+Quantum advantage of IQP: ``For example, under well-believed complexity-theoretic assumptions, the class of PQCs called instantaneous quantum polynomial-time cannot be efficiently simulated by classical resources (see Lund et al [3] and Harrow and Montanaro [4] for accessible Reviews of quantum supremacy proposals).''\cite{benedetti_parameterized_2019}
 

### 2025-02-25 manuscript/main.tex
work on manuscript

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications}
+\title{A Combinatorial Search of Parameterized Quantum Circuit Learning for Quantum Chemical Applications}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\newpage
-\begin{itemize}
-	\item Abstract
-	\item Introduction
-	\item Methods
-	\item Datasets
-	\item Results and Discussion
-	\begin{itemize}
-		\item BSE
-		\begin{itemize}
-			\item All 5 qubit
-			\item Truncated 16 qubit set (cost analysis 5 qubit)
-			\item RUD + AL (5 + 16 qubit)
-			\item Real device (without error mitigation and with whatever the best is from function fitting)
-		\end{itemize}		
-		\item DDCC (5 qubit only because classically it can be done with 5 features!)
-		\begin{itemize}
-			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
-			\item RUD + AL (5 qubit)
-			\item Real device (without error mitigation and with whatever the best is from function fitting)
-		\end{itemize}				
-	\end{itemize}
-	\item Conclusion
-\end{itemize}
-
-\newpage
 \setcounter{secnumdepth}{1}
 \section{Introduction}
+[FOCUS ON QUANTUM CHEMISTRY]
 
-In recent years, machine learning (ML) has become a popular tool within the field of chemistry for exploring chemical compound space\cite{ramakrishnan_quantum_2014,ramakrishnan_big_2015}, accelerating wave functions\cite{townsend_data-driven_2019,jones_chapter_2023}, and for applications, such as catalysis and drug discovery.\cite{behler_perspective_2016,goh_deep_2017,butler_machine_2018,sanchez-lengeling_inverse_2018,janet_machine_2020}
-Often, the goal of machine learning in chemistry is to reveal new patterns in data, provide new insights beyond simple models and human experience, and to accelerate computations and analysis of chemical space.\cite{janet_machine_2020}
-Additionally, interest in quantum computing (QC) for chemical applications have become increasingly popular due to the inherent quantum nature of chemistry.\cite{cao_quantum_2019}
-An approach that combines both ML and QC, is quantum machine learning (QML).
-QML has has shown potential for quantum speedups, either through formal mathematical proofs or numerical experiments based on empirical observations.
-In practice, determining theoretical quantum speedups can be difficult to determine and numerical experiments must be used to quantify the computational complexity.\cite{biamonte_quantum_2017}
-
+In recent years, machine learning (ML) has emerged as a popular tool in chemistry to reveal new patterns in data, provide new insights beyond simple models and human experience, and to accelerate computations and analysis of chemical space.
+Often, the goal of ML for chemists is to bypass the explicit calculation of molecular properties that can be expensive to calculate.\cite{janet_machine_2020}
+Applications of ML in chemistry include accelerating molecular simulations\cite{behler_perspective_2016,ssmith_ani-1_2017,gao_torchani_2020}, determining molecular properties\cite{yang_analyzing_2019,ramakrishnan_quantum_2014,ramakrishnan_big_2015,hansen_machine_2015,unke_physnet_2019}, and for the discovery of new catalysis\cite{zhong_accelerated_2020,nandy_computational_2021,mjones_data-driven_2023}, drugs\cite{goh_deep_2017,yang_concepts_2019}, and materials.\cite{butler_machine_2018,sanchez-lengeling_inverse_2018,raccuglia_machine-learning-assisted_2016}
+Similarly, interest in quantum computing (QC) for chemical applications has become increasingly popular due possible quantum speedups for quantum chemical calculations.\cite{cao_quantum_2019}
+An approach that combines both ML and QC, is quantum machine learning (QML), which has shown potential for quantum speedups, either through formal mathematical proofs or numerical experiments based on empirical observations.\cite{biamonte_quantum_2017}
+Among the classes of QML algorithms, parameterized quantum circuits (PQCs), which are based on a hybrid quantum--classical optimization loop, have shown promise as flexible QML models, capable of achieving non-trivial results on near-term quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
 In the context of chemistry, quantum machine learning (QML) has gained traction for tasks such as drug discovery\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,bhatia_quantum_2023,kao_exploring_2023,li_quantum_2021,avramouli_quantum_2023,avramouli_unlocking_2023}, materials discovery\cite{ishiyama_noise-robust_2022,ryu_quantum_2023,vitz_hybrid_2024}, proton affinities\cite{jin_integrating_2025}, and experimental molecular properties, including the log solubility in water, melting point, octanol/water distribution coefficient, hydration free energy of small molecules in water.\cite{hatakeyama-sato_quantum_2023}
 
-One class of QML algorithms, based on a hybrid quantum--classical feedback loop, are parameterized quantum circuits (PQCs).
-PQCs offer flexible QML models where the variational parameters are optimized classically, while the quantum circuit can be ran on near-term quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
-Often, PQCs are composed of two parts: an encoding circuit, used to encode the features, and a variational (ansatz) circuit, composed of trainable machine learning parameters.
+[NOTE most of the previous studies are NOT quantum chemistry!]
 
-Herein, we explore two different chemical datasets: one consisting of bond separation energies of 49 unique bond types, called the BSE49 dataset\cite{prasad_bse49_2021}, and another which utilizes data-driven coupled cluster (DDCC)\cite{townsend_data-driven_2019} to predict the coupled-cluster singles and doubles wave function parameters using lower-level quantum chemistry methods.
+Motivated by these recent studies, we wanted to perform an exhaustive benchmark of a large set of PQCs on chemically relevant datasets.
+To this end,  we introduce \textit{qregress}, a modular Python-based code built on PennyLane for exploring PQCs for regression based learning tasks.
+Our code base includes a set of 14 data-encoding and 12 variational (ansatz) subcircuits for a total of 168 PQCs.
+We include support for state-vector simulation using Qulacs, noisy fake backends, and real devices---along with error mitigation techniques implemented in Qiskit. 
+We explore two datasets related to classical machine learning in chemistry tasks, which includes the BSE49 dataset\cite{prasad_bse49_2021}, which consists of bond separation energies of 49 unique bond types, and a dataset of water confirmers using data-driven coupled cluster (DDCC)\cite{townsend_data-driven_2019}, a machine learning approach for predicting the coupled-cluster singles and doubles wave function parameters using lower-level quantum chemistry methods.
 
-In this study, we create a robust Python code base for exploring a set of 14 data-encoding and 12 variational (ansatz) subcircuits for a total of 168 combined PQCs.
-Our work includes the single and double encoding layers found in the paper of Suzuki and Katouda\cite{suzuki_predicting_2020}, including the encoding of Mitarai \textit{et al.}\cite{mitarai_quantum_2018}, along with using instantanious quantum polynomial (IQP) as an encoding layer.
-\cite{bremner_average-case_2016}
-All of our variational (ansatz) layers can be found in the study of Sim \textit{et al.}\cite{sim_expressibility_2019}, where the expressiblity and entanglement capability of these circuits is analyzed.
-We also examine the effects of the number of re-upload and ansatz layers, the effects of feature set size, and various error mitigation techniques.
+Chose two datasets for which the authors are familiar with their classical performance
+[cite the classification schemes quantum in/quantum out and classical in/quantum out]
+The BSE49 dataset is a classical input-quantum output problem
+The DDCC is a quantum input-quantum output problem
 
-We introduce \textit{qregress}, a modular Python-based code built on PennyLane for exploring PQCs for regression based learning tasks.
-We analyze three datasets, a function fitting dataset, used for model calibration, and two chemically relevant datasets that offer challenging learning tasks for PQCs.
+Using these datasets, we benchmark the initial set of PQCs, followed by taking the best performing circuits and exploring the effects of circuit depth on model performance.
+Lastly, we use the best circuit to run on a real device, \textit{ibm\textunderscore quebec}, to...?
+
+[Explore in what contexts quantum advantage can be achieved]
 
@@
 \section{Conclusion}
+Quantum advantage in terms of computational complexity but not in model performance?
+
 Depth is not always better!

### 2025-02-27 Pennylane_to_Qiskit/test_qiskit/runall.sh
test fakequebec resilience and opt

@@ -1,0 +1,17 @@
+#!/bin/bash
+#optimization_level = 3
+#shots = 1024.0
+#resilience_level = 1
+
+for ol in {1..3};do
+ for rl in {1..2};do
+  dirname="ol${ol}_rl${rl}"
+  if [ ! -d ${dirname} ] ; then
+    echo "${dirname} does not exist"
+    mkdir ${dirname}
+  else
+    echo "${dirname} does exist"
+  fi
+  papermill convert_ML_batched.ipynb ${dirname}/convert_ML_batched.ipynb -r optimization_level ${ol} -r resilience_level ${rl} 
+ done
+done

### 2025-03-03 manuscript/main.tex
test fakequebec resilience and opt
prep real
work on manuscript

@@
 \section{Introduction}
+[Problem: QML methods related to quantum chemistry are rarely studied so we chose two different sets of data, one that's classical in-quantum out and the other that is quantum in-quantum out]
+
 [FOCUS ON QUANTUM CHEMISTRY]
 
-In recent years, machine learning (ML) has emerged as a popular tool in chemistry to reveal new patterns in data, provide new insights beyond simple models and human experience, and to accelerate computations and analysis of chemical space.
-Often, the goal of ML for chemists is to bypass the explicit calculation of molecular properties that can be expensive to calculate.\cite{janet_machine_2020}
-Applications of ML in chemistry include accelerating molecular simulations\cite{behler_perspective_2016,ssmith_ani-1_2017,gao_torchani_2020}, determining molecular properties\cite{yang_analyzing_2019,ramakrishnan_quantum_2014,ramakrishnan_big_2015,hansen_machine_2015,unke_physnet_2019}, and for the discovery of new catalysis\cite{zhong_accelerated_2020,nandy_computational_2021,mjones_data-driven_2023}, drugs\cite{goh_deep_2017,yang_concepts_2019}, and materials.\cite{butler_machine_2018,sanchez-lengeling_inverse_2018,raccuglia_machine-learning-assisted_2016}
-Similarly, interest in quantum computing (QC) for chemical applications has become increasingly popular due possible quantum speedups for quantum chemical calculations.\cite{cao_quantum_2019}
-An approach that combines both ML and QC, is quantum machine learning (QML), which has shown potential for quantum speedups, either through formal mathematical proofs or numerical experiments based on empirical observations.\cite{biamonte_quantum_2017}
+In recent years, machine learning (ML) has emerged as a popular tool in chemistry to reveal new patterns in data, provide new insights beyond simple models and human experience, and to accelerate computations and the analysis of chemical space.
+Applications of ML in chemistry include accelerating molecular simulations\cite{behler_perspective_2016,ssmith_ani-1_2017,gao_torchani_2020}, determining molecular properties\cite{yang_analyzing_2019,ramakrishnan_quantum_2014,ramakrishnan_big_2015,hansen_machine_2015,unke_physnet_2019}, and for the discovery of new catalysts\cite{zhong_accelerated_2020,nandy_computational_2021,mjones_data-driven_2023}, drugs\cite{goh_deep_2017,yang_concepts_2019}, and materials.\cite{butler_machine_2018,sanchez-lengeling_inverse_2018,raccuglia_machine-learning-assisted_2016}
+Often, the goal of ML in chemistry is to bypass the explicit calculation of molecular properties that can be expensive to calculate for large sets of data.\cite{janet_machine_2020}
+
+Similar to the aforementioned machine learning methods, quantum computing (QC) for chemical applications has become increasingly popular due to possible quantum speedups for quantum chemical calculations.\cite{cao_quantum_2019}
+While most quantum computing studies focus on creating new and more efficient electronic structure methods on quantum computers\cite{romero_strategies_2019,mcardle_quantum_2020,bauer_quantum_2020,cao_quantum_2019}, an approach that combines both ML and QC, is quantum machine learning (QML).
+In recent years, QML has shown potential for quantum speedups, either through formal mathematical proofs or numerical experiments based on empirical observations.\cite{biamonte_quantum_2017}
 Among the classes of QML algorithms, parameterized quantum circuits (PQCs), which are based on a hybrid quantum--classical optimization loop, have shown promise as flexible QML models, capable of achieving non-trivial results on near-term quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
@@
 
-[NOTE most of the previous studies are NOT quantum chemistry!]
+Like the previously mentioned studies, we wanted to determine whether QML, specifically using PQCs, can offer a quantum advantage (or speedup) on chemical applications.
+Herein, we explore two datasets that require the explicit calculation of (RO)CBS-QB3 and CCSD
+(RO)CBS-QB3  can be used for X Y and Z as found in the Wood et al pub
+CCSD can be used for energies and properties
+
+Despite the broad range of applications covered in the previously mentioned studies,
+
+A common feature among most of the previously mentioned studies is that these studies do not focus on aspects related to quantum chemistry, such as the calculation of correlation energies or bond separation energies, which require the explicit calculation using quantum chemical methods.
+Motivated by this, we analyze two datasets related to quantum chemistry, one of which requires the use of classical molecular representations as output and predicts the bond separation energies
+
+the BSE49 dataset\cite{prasad_bse49_2021}, which consists of bond separation energies of 49 unique bond types calculated using a high-level composite method called (RO)CBS-QB3
+
+, and a dataset of water confirmers using data-driven coupled cluster (DDCC)\cite{townsend_data-driven_2019}, a machine learning approach for predicting the coupled-cluster singles and doubles wave function parameters using lower-level quantum chemistry methods.
 
@@
 We include support for state-vector simulation using Qulacs, noisy fake backends, and real devices---along with error mitigation techniques implemented in Qiskit. 
-We explore two datasets related to classical machine learning in chemistry tasks, which includes the BSE49 dataset\cite{prasad_bse49_2021}, which consists of bond separation energies of 49 unique bond types, and a dataset of water confirmers using data-driven coupled cluster (DDCC)\cite{townsend_data-driven_2019}, a machine learning approach for predicting the coupled-cluster singles and doubles wave function parameters using lower-level quantum chemistry methods.
+We explore two datasets related to classical machine learning in chemistry tasks, which includes
 
@@
 For the simulations using \textit{FakeQuebec} and experiments on \textit{ibm\_quebec} we utilize Twirled Readout Error eXtinction (TREX) error mitigation.
+
+Used QisKit for Fake backend
 

### 2025-03-04 manuscript/main.tex
update flow

@@
 \section{Introduction}
+Four paragraph structure:
+\begin{itemize}
+	\item General problem and classical machine learning 
+	\item quantum computing and qml
+	\item Parameterized quantum circuits
+	\item What we introduce
+\end{itemize}
+
 [Problem: QML methods related to quantum chemistry are rarely studied so we chose two different sets of data, one that's classical in-quantum out and the other that is quantum in-quantum out]
@@
 \subsection{DDCC}
+Structure
+\begin{itemize}
+	\item Broad set
+	\item RUD/AL tests
+	\item learning curve (maybe)
+	\item real device 
+\end{itemize}
 

### 2025-03-04 manuscript/main.tex
validate on real device + figures

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{A Combinatorial Search of Parameterized Quantum Circuit Learning for Quantum Chemical Applications}
+\title{Benchmarking Parameterized Quantum Circuit Learning for Quantum Chemical Applications}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-[Problem: QML methods related to quantum chemistry are rarely studied so we chose two different sets of data, one that's classical in-quantum out and the other that is quantum in-quantum out]
-
-[FOCUS ON QUANTUM CHEMISTRY]
+[General problem and classical machine learning]
 
@@
 
+[quantum computing and qml]
+
 Similar to the aforementioned machine learning methods, quantum computing (QC) for chemical applications has become increasingly popular due to possible quantum speedups for quantum chemical calculations.\cite{cao_quantum_2019}
@@
 In recent years, QML has shown potential for quantum speedups, either through formal mathematical proofs or numerical experiments based on empirical observations.\cite{biamonte_quantum_2017}
+
+[Parameterized quantum circuits]
+
 Among the classes of QML algorithms, parameterized quantum circuits (PQCs), which are based on a hybrid quantum--classical optimization loop, have shown promise as flexible QML models, capable of achieving non-trivial results on near-term quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
 In the context of chemistry, quantum machine learning (QML) has gained traction for tasks such as drug discovery\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,bhatia_quantum_2023,kao_exploring_2023,li_quantum_2021,avramouli_quantum_2023,avramouli_unlocking_2023}, materials discovery\cite{ishiyama_noise-robust_2022,ryu_quantum_2023,vitz_hybrid_2024}, proton affinities\cite{jin_integrating_2025}, and experimental molecular properties, including the log solubility in water, melting point, octanol/water distribution coefficient, hydration free energy of small molecules in water.\cite{hatakeyama-sato_quantum_2023}
+
+[What we introduce; Problem: QML methods related to quantum chemistry are rarely studied so we chose two different sets of data, one that's classical in-quantum out and the other that is quantum in-quantum out; FOCUS ON QUANTUM CHEMISTRY]
 
@@
 where, $E_{\text{ent}}^{l}$ denotes the entangling gates, which can be a CNOT, CZ, or identity ($\mathbf{I}$) gates,   $U_{\phi_{l}(\mathbf{x})}$ denotes the choice of encoding unitaries. 
-Like in  Ref. \citep{suzuki_predicting_2020}, we choose $l \in \{1, 2\}$, such that when $l=1$, $E_{\text{ent}}$ corresponds to an identity matrix and $U_{\Phi(x)} = U_{\phi_{1}(\mathbf{x})}$.
+Like in  Ref. \citep{suzuki_predicting_2020}, $E_{\text{ent}}$ corresponds to an identity matrix and $U_{\Phi(x)} = U_{\phi_{1}(\mathbf{x})}$.
+
+%Like in  Ref. \citep{suzuki_predicting_2020}, we choose $l \in \{1, 2\}$, such that when $l=1$, $E_{\text{ent}}$ corresponds to an identity matrix and $U_{\Phi(x)} = U_{\phi_{1}(\mathbf{x})}$.
 
@@
 As $v$ increases and the number of trainable parameters ($\bm{\theta}$) increase, the theoretical assumption is that the model expressibility should also increase.
-In our study, we choose $v \in \{1, 3, 5\}$ and refer to this as the number of ansatz layers (ALs).
+In our study, we the number of variational layers as the number of ansatz layers (ALs).
+%In our study, we choose $v \in \{1, 3, 5\}$ and refer to this as the number of ansatz layers (ALs).
 We examine 12 different variational circuits, as shown in Fig.
@@
 
-Used QisKit for Fake backend
+Used QisKit for real and fake back end using Qiskit Batches
+
+optimization levels
+none (0)
+
+``No optimization: typically used for hardware characterization
+Basic translation and Layout/Routing: TrivialLayout, where it selects the same physical qubit numbers as virtual and inserts SWAPs to make it work (using StochasticSwap)''
+
+light (1)
+``Light optimization: Layout/Routing: Layout is first attempted with TrivialLayout.
+If additional SWAPs are required, a layout with a minimum number of SWAPs is found by using SabreSWAP, then it uses VF2LayoutPostLayout to try to select the best qubits in the graph, InverseCancellation, 1Q gate optimization''
+
+medium (2)
+``Medium optimization: Layout/Routing: Optimization level 1 (without trivial) + heuristic optimized with greater search depth and trials of optimization function.
+Because TrivialLayout is not used, there is no attempt to use the same physical and virtual qubit numbers.
+CommutativeCancellation''
+
+high (3)
+``High Optimization:
+Optimization level 2 + heuristic optimized on layout/routing further with greater effort/trials
+Resynthesis of two-qubit blocks using Cartan's KAK Decomposition.
+Unitarity-breaking passes:
+OptimizeSwapBeforeMeasure: Moves the measurements around to avoid SWAPs
+RemoveDiagonalGatesBeforeMeasure: Removes gates before measurements that would not effect the measurements''
+
+resilience levels (error mitigation)
+none (0) 
+1 ``Minimal mitigation costs: Mitigate error associated with readout errors'' ``Twirled Readout Error eXtinction (TREX) measurement twirling''
+Medium mitigation cost medium 
+2 ``Medium mitigation costs. Typically reduces bias in estimators, but is not guaranteed to be zero-bias.'' ``Level 1 + Zero Noise Extrapolation (ZNE) and gate twirling''
 
@@
 
+Talk about the cost of going wider, and inherently deeper
+
 \begin{figure}[H]
@@
 
+Ran using the state vector model parameters for one iteration to test the optimization and resilience levels using Fake Quebec before running on the real device
+
+$\{1024 \times x \vert  x \in [1,10]\}$
+
+Optimization level 2 
+resilience level 0
+
+Regarding the number of circuit executions vs performance 3072 (1024 times 3) is the best number of shots
+
+Fig. \ref{fig:optresfakequebec}
+Fig. \ref{fig:shotsfakequebec}
+
 \section{Conclusion}

### 2025-03-04 Pennylane_to_Qiskit/real_qiskit/runall.sh

@@ -11,6 +11,6 @@ for rl in {0..2};do
  else
    echo "${dirname} does exist"
  fi
- papermill convert_ML_batched.ipynb ${dirname}/convert_ML_batched.ipynb -r optimization_level 2 -r resilience_level ${rl} -r shots "6144"
+ papermill convert_ML_batched.ipynb ${dirname}/convert_ML_batched.ipynb -r optimization_level 2 -r resilience_level ${rl} -r shots 3072
  mv ./model_log.csv ./final_state_model.bin ./A2_HWE-CNOT_plot.svg ./A2_HWE-CNOT_results.json ./A2_HWE-CNOT_predicted_values.csv ${dirname}/ 
 done

### 2025-03-04 Pennylane_to_Qiskit/test_qiskit/runall.sh

@@ -3,8 +3,8 @@
 #shots = 1024.0
 #resilience_level = 1
 
-for ol in {1..3};do
- for rl in {1..2};do
+for ol in 0;do
+ for rl in {0..2};do
   dirname="ol${ol}_rl${rl}"
   if [ ! -d ${dirname} ] ; then
     echo "${dirname} does not exist"

### 2025-03-04 manuscript/main.tex
manuscript

@@
 
+Expand on all of these to make a proper case for what we are doing.
+
 Among the classes of QML algorithms, parameterized quantum circuits (PQCs), which are based on a hybrid quantum--classical optimization loop, have shown promise as flexible QML models, capable of achieving non-trivial results on near-term quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
@@
 Herein, we explore two datasets that require the explicit calculation of (RO)CBS-QB3 and CCSD
-(RO)CBS-QB3  can be used for X Y and Z as found in the Wood et al pub
+
+BSE49
+
 CCSD can be used for energies and properties
@@
 none (0) 
-1 ``Minimal mitigation costs: Mitigate error associated with readout errors'' ``Twirled Readout Error eXtinction (TREX) measurement twirling''
-Medium mitigation cost medium 
-2 ``Medium mitigation costs. Typically reduces bias in estimators, but is not guaranteed to be zero-bias.'' ``Level 1 + Zero Noise Extrapolation (ZNE) and gate twirling''
+level 1 readout error mitigation and measurement twirling using Twirled Readout Error eXtinction (TREX) \cite{van_den_berg_model-free_2022}
+level 2 level 1 + gate twirling and zero noise extrapolation (ZNE)\cite{kandala_error_2019,li_efficient_2017,temme_error_2017}
 
@@
 \end{figure}
+
+BSE49
+``This work addresses the aforementioned gap in the literature by constructing a large dataset (4502 datapoints) of computationally predicted BSEs of 49 unique bond types, all of which are determined with a high-level composite theoretical procedure denoted as (RO)CBS-QB3.
+This approach ensures uniform, high-quality reference data and eliminates the need to collect and verify data gathered from various sources, which may differ substantially in their accuracy.
+The (RO)CBS-QB3 method is known to produce BDEs of high accuracy.
+Therefore, it is suitable for developing a database of BSEs that can be used to test and parametrize low-cost computational methods.
+One particular target application of our dataset is for the training of cost-effective computational approaches like atom-centered potentials (ACPs) or machine learning potentials.''
+(RO)CBS-QB3\cite{wood_restricted-open-shell_2006,montgomery_complete_1999,montgomery_complete_2000}
+
+```The structures obtained from the workflow described above were then used for the final step of reference data calculation, using the composite (RO)CBS-QB331,32,33 method.
+The restricted-open-shell61 CBS-QB3 or ROCBS-QB3 was employed for the open-shell radical fragments, while restricted closed-shell calculations were performed for the closed-shell parent molecules with CBS-QB3.
+The composite (RO)CBS-QB3 method approximates energies at the complete-basis-set CCSD(T) level, using a series of computationally lower-cost methods including: (i) geometry optimization followed by vibration frequency calculation using the unrestricted-open-shell62 B3LYP/6-311G(2d,d,p) method46,47,48,49,50,51,63, (ii) ROMP2/6-311+G(3d2f,2df,2p) level63,64,65 energy extrapolated to the complete-basis-set limit, (iii) energy calculation at ROMP4(SDQ)/6-31+G(d(f),p) level63,64,66, and (iv) energy calculation at ROCCSD(T)/6-31+G† level63,64,67 (where 6-31+G† is a modified 6-31+G(d) basis set).
+Note that the final (RO)CBS-QB3 energy includes additional empirical correction terms described in Reference33.
+Structures were screened to remove any system for which the imaginary frequencies were obtained.
+The (RO)CBS-QB3 energies for the structures associated with a particular bond breaking reaction were used to obtain the bond separation energies for the dataset.'''
 
@@
 
+5 qubit/5 ansatz layers: 2*5 + 3 * 5 * 5 = 85 parameters (75 trainable, 5 * 2 features)
+A2 $2n$ parameters
+HWE-CNOT $3nL$ parameters
+2 qubit gates $nL$
+Number of parameters (2n+3nL)=(2+3L)*n
+
+$n$, number of qubits and $L$, number of circuit layers
+
+To efficiently run DDCC on IBM Quebec, splitting the data into batches of $\approx 4$ samples with 64 $t_{2}$-amplitudes each.
+
+One iteration would require approximately $N_{\text{samples}} * N_{occ}^{2} * N_{virt}^{2} * N_{\text{shots}} * N_{\text{observables}}$ circuit executions (+ whatever SPSA costs to run per iteration)
+
 Ran using the state vector model parameters for one iteration to test the optimization and resilience levels using Fake Quebec before running on the real device

### 2025-03-06 Pennylane_to_Qiskit/real_qiskit/runall.sh
DDCC 9RUD + real device opt/res test

@@ -4,14 +4,17 @@
 #resilience_level = 1
 
 for rl in {0..2};do
- dirname="ol2_rl${rl}"
- if [ ! -d ${dirname} ] ; then
-   echo "${dirname} does not exist"
-   mkdir ${dirname}
- else
-   echo "${dirname} does exist"
- fi
- papermill convert_ML_batched.ipynb ${dirname}/convert_ML_batched.ipynb -r optimization_level 2 -r resilience_level ${rl} -r shots 3072
- mv ./model_log.csv ./final_state_model.bin ./A2_HWE-CNOT_plot.svg ./A2_HWE-CNOT_results.json ./A2_HWE-CNOT_predicted_values.csv ${dirname}/ 
- mv ./job*txt ${dirname}/ 
+ for ol in {0..3};do
+  dirname="ol${ol}_rl${rl}"
+  if [ ! -d ${dirname} ] ; then
+    echo "${dirname} does not exist"
+    mkdir ${dirname}
+    papermill convert_ML_batched.ipynb ${dirname}/convert_ML_batched.ipynb -r optimization_level 2 -r resilience_level ${rl} -r shots 3072 
+    mv ./model_log.csv ./final_state_model.bin ./A2_HWE-CNOT_plot.svg ./A2_HWE-CNOT_results.json ./A2_HWE-CNOT_predicted_values.csv ${dirname}/ 
+    mv ./job*txt ${dirname}/ 
+  else
+    echo "${dirname} does exist"
+  fi
+ 
+ done
 done

### 2025-03-07 manuscript/main.tex
DDCC 9RUD + real device opt/res test
Fri  7 Mar 2025 14:29:09 EST introduction

@@
 \section{Introduction}
-Four paragraph structure:
-\begin{itemize}
-	\item General problem and classical machine learning 
-	\item quantum computing and qml
-	\item Parameterized quantum circuits
-	\item What we introduce
-\end{itemize}
 
-[General problem and classical machine learning]
+In recent years, machine learning (ML) has emerged as a popular tool in chemistry for revealing new patterns in data, providing new insights beyond simple models and human experience, accelerating computations, and analyzing chemical space.
+For computational chemists, the primary goal of applying ML is often to bypass the explicit calculation of molecular properties, which can be computationally expensive for large datasets.\cite{janet_machine_2020}
+ML can be applied to a diverse set of applications including, but not limited to, accelerating molecular simulations\cite{behler_perspective_2016,ssmith_ani-1_2017,gao_torchani_2020}, determining molecular properties\cite{yang_analyzing_2019,ramakrishnan_quantum_2014,ramakrishnan_big_2015,hansen_machine_2015,unke_physnet_2019}, and for discovering new catalysts\cite{zhong_accelerated_2020,nandy_computational_2021,mjones_data-driven_2023}, drugs\cite{goh_deep_2017,yang_concepts_2019}, and materials.\cite{butler_machine_2018,sanchez-lengeling_inverse_2018,raccuglia_machine-learning-assisted_2016}
+Since these applications can become resource intensive, regarding the generation of training data using traditional computational chemistry approaches and the training of large-scale ML models, computational chemistry and ML practitioners have explored new acceleration platforms, such as graphical processing units (GPUs) and tensor processing units (TPUs).\cite{ufimtsev_graphical_2008,gotz_chapter_2010,pederson_large_2023,goh_deep_2017,gawehn_advancing_2018,pandey_transformational_2022,ssmith_ani-1_2017}
 
-In recent years, machine learning (ML) has emerged as a popular tool in chemistry to reveal new patterns in data, provide new insights beyond simple models and human experience, and to accelerate computations and the analysis of chemical space.
-Applications of ML in chemistry include accelerating molecular simulations\cite{behler_perspective_2016,ssmith_ani-1_2017,gao_torchani_2020}, determining molecular properties\cite{yang_analyzing_2019,ramakrishnan_quantum_2014,ramakrishnan_big_2015,hansen_machine_2015,unke_physnet_2019}, and for the discovery of new catalysts\cite{zhong_accelerated_2020,nandy_computational_2021,mjones_data-driven_2023}, drugs\cite{goh_deep_2017,yang_concepts_2019}, and materials.\cite{butler_machine_2018,sanchez-lengeling_inverse_2018,raccuglia_machine-learning-assisted_2016}
-Often, the goal of ML in chemistry is to bypass the explicit calculation of molecular properties that can be expensive to calculate for large sets of data.\cite{janet_machine_2020}
+Alternatively, computational approaches incorporating the quantum mechanical principles of superposition and entanglement, called quantum computing (QC),  have become increasingly popular for chemical applications due to possible quantum speedups for quantum chemical calculations.\cite{cao_quantum_2019}
+For computational chemistry, methods such as the quantum phase estimation (QPE)\cite{abrams_simulation_1997,abrams_quantum_1999,aspuru-guzik_simulated_2005,lanyon_towards_2010,whitfield_simulation_2011,aspuru-guzik_photonic_2012} algorithm have been shown to offer exponential speedups over classical methods.
+Despite the promising speedups, QPE requires long coherence times, while the current generation of quantum processing units (QPUs), are often too noisy for practical applications.
+Alternatively, methods based on the variational principle, such as the variational quantum eigensolver (VQE)\cite{peruzzo_variational_2014,cerezo_variational_2021,mcclean_theory_2016,bharti_noisy_2022}, have been proposed as a quantum-classical hybrid approach, capable of running on noisy, near-term quantum devices.
 
-[quantum computing and qml]
+While most QC studies that are relevant to computational chemists focus on creating more efficient electronic structure methods on quantum computers\cite{romero_strategies_2019,mcardle_quantum_2020,bauer_quantum_2020,cao_quantum_2019}, an approach that combines both ML and QC, is quantum machine learning (QML).
+Using either formal mathematical proofs or numerical results based on empirical observations, QML has shown potential quantum speedups for various applications using a diverse set of implementations.\cite{biamonte_quantum_2017}
+While several classes of QML algorithms have shown promise for providing flexible ML models, parameterized quantum circuits (PQCs) are capable of achieving non-trivial results on near-term quantum hardware.
+PQCs formulate the ML algorithm as a variational problem optimized using a hybrid approach using both classical and quantum hardware.\cite{benedetti_parameterized_2019}
+Like classical ML approaches, PQC has been applied for several chemistry use cases such as drug\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,bhatia_quantum_2023,kao_exploring_2023,li_quantum_2021,avramouli_quantum_2023,avramouli_unlocking_2023} and materials discovery\cite{ishiyama_noise-robust_2022,ryu_quantum_2023,vitz_hybrid_2024}, the prediction of proton affinities\cite{jin_integrating_2025}, and experimental molecular properties, including the log solubility in water, melting point, octanol/water distribution coefficient, hydration free energy of small molecules in water.\cite{hatakeyama-sato_quantum_2023}
+Despite the broad range of topics covered in these studies and the interest among computational chemists in exploring PQCs for chemical applications, studies analyzing the potential benefits or drawbacks of using QML for quantum chemistry are lacking.
 
-Similar to the aforementioned machine learning methods, quantum computing (QC) for chemical applications has become increasingly popular due to possible quantum speedups for quantum chemical calculations.\cite{cao_quantum_2019}
-While most quantum computing studies focus on creating new and more efficient electronic structure methods on quantum computers\cite{romero_strategies_2019,mcardle_quantum_2020,bauer_quantum_2020,cao_quantum_2019}, an approach that combines both ML and QC, is quantum machine learning (QML).
-In recent years, QML has shown potential for quantum speedups, either through formal mathematical proofs or numerical experiments based on empirical observations.\cite{biamonte_quantum_2017}
-
-[Parameterized quantum circuits]
-
-Expand on all of these to make a proper case for what we are doing.
-
-Among the classes of QML algorithms, parameterized quantum circuits (PQCs), which are based on a hybrid quantum--classical optimization loop, have shown promise as flexible QML models, capable of achieving non-trivial results on near-term quantum hardware.\cite{benedetti_parameterized_2019,suzuki_predicting_2020}
-In the context of chemistry, quantum machine learning (QML) has gained traction for tasks such as drug discovery\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,bhatia_quantum_2023,kao_exploring_2023,li_quantum_2021,avramouli_quantum_2023,avramouli_unlocking_2023}, materials discovery\cite{ishiyama_noise-robust_2022,ryu_quantum_2023,vitz_hybrid_2024}, proton affinities\cite{jin_integrating_2025}, and experimental molecular properties, including the log solubility in water, melting point, octanol/water distribution coefficient, hydration free energy of small molecules in water.\cite{hatakeyama-sato_quantum_2023}
-
-[What we introduce; Problem: QML methods related to quantum chemistry are rarely studied so we chose two different sets of data, one that's classical in-quantum out and the other that is quantum in-quantum out; FOCUS ON QUANTUM CHEMISTRY]
-
-Like the previously mentioned studies, we wanted to determine whether QML, specifically using PQCs, can offer a quantum advantage (or speedup) on chemical applications.
-Herein, we explore two datasets that require the explicit calculation of (RO)CBS-QB3 and CCSD
-
-BSE49
-
-CCSD can be used for energies and properties
-
-Despite the broad range of applications covered in the previously mentioned studies,
-
-A common feature among most of the previously mentioned studies is that these studies do not focus on aspects related to quantum chemistry, such as the calculation of correlation energies or bond separation energies, which require the explicit calculation using quantum chemical methods.
-Motivated by this, we analyze two datasets related to quantum chemistry, one of which requires the use of classical molecular representations as output and predicts the bond separation energies
-
-the BSE49 dataset\cite{prasad_bse49_2021}, which consists of bond separation energies of 49 unique bond types calculated using a high-level composite method called (RO)CBS-QB3
-
-, and a dataset of water confirmers using data-driven coupled cluster (DDCC)\cite{townsend_data-driven_2019}, a machine learning approach for predicting the coupled-cluster singles and doubles wave function parameters using lower-level quantum chemistry methods.
-
-Motivated by these recent studies, we wanted to perform an exhaustive benchmark of a large set of PQCs on chemically relevant datasets.
-To this end,  we introduce \textit{qregress}, a modular Python-based code built on PennyLane for exploring PQCs for regression based learning tasks.
-Our code base includes a set of 14 data-encoding and 12 variational (ansatz) subcircuits for a total of 168 PQCs.
-We include support for state-vector simulation using Qulacs, noisy fake backends, and real devices---along with error mitigation techniques implemented in Qiskit. 
-We explore two datasets related to classical machine learning in chemistry tasks, which includes
-
-Chose two datasets for which the authors are familiar with their classical performance
-[cite the classification schemes quantum in/quantum out and classical in/quantum out]
-The BSE49 dataset is a classical input-quantum output problem
-The DDCC is a quantum input-quantum output problem
-
-Using these datasets, we benchmark the initial set of PQCs, followed by taking the best performing circuits and exploring the effects of circuit depth on model performance.
-Lastly, we use the best circuit to run on a real device, \textit{ibm\textunderscore quebec}, to...?
-
-[Explore in what contexts quantum advantage can be achieved]
+In this study, we address this by analyzing a diverse set of PQCs using two datasets related to computational chemistry.
+The first dataset, BSE49 consists of bond separation energies (BSEs) of 49 unique bond types, calculated using the highly accurate (RO)CBS-QB3 composite method.\cite{prasad_bse49_2021}
+The second dataset consists of water conformers calculated with coupled-cluster singles and doubles (CCSD) using the data-driven coupled-cluster (DDCC) scheme of Townsend and Vogiatzis.\cite{townsend_data-driven_2019,jones_chapter_2023}
+Both datasets offer a unique perspective on the aptitude of applying PQCs on classical and quantum data\cite{cerezo_challenges_2022} since the models based on BSE49 rely on classical molecular representations\cite{jones_molecular_2023}, such as Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002} or Morgan fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, as input, while the input features in the DDCC method encode explicit quantum information related to molecular wave function.
+In our study, we introduce \textit{qregress} a modular Python framework, based on PennyLane\cite{bergholm_pennylane_2022} and Qiskit\cite{javadi-abhari_quantum_2024}, for exploring PQCs for regression-based QML tasks.
+To this end, we explore 168 unique PQCs, based on a combination of 14 data encoding and 12 variational layers, and then perform an analysis of how circuit depth effects model performance using two different expansion stategies.
+We also provide insights into the performance of PQCs on quantum chemical tasks using fake and real Qiskit backends.
+Lastly, we provide a detailed discussion on the efficiency, performance, and the importance of clearly defining what quantum advantage means in the context of QML models with respect to classical ML.
 
@@
 	\hfill
-	\begin{subfigure}[b]{\textwidth}
+	\begin{subfigure}[b]{0.49\textwidth}
 		\centering
@@
 		\centering
-		\includegraphics[width=\linewidth]{../images/DDCC/distribution_parity}
+		\includegraphics[width=0.49\linewidth]{../images/DDCC/distribution_parity}
 		\caption{}
@@
 
+Fake
 Optimization level 2 
@@
 Fig. \ref{fig:shotsfakequebec}
+
+Real
+Optimization level 2 
+resilience level 1
+3072
+
+resilience level 2 is too expensive on the real device
+Regarding the number of circuit executions vs performance 3072 (1024 times 3) is the best number of shots
 

### 2025-03-07 manuscript/main.tex
Fri  7 Mar 2025 17:04:43 EST manuscript

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Benchmarking Parameterized Quantum Circuit Learning for Quantum Chemical Applications}
+\title{Understanding Quantum Advantage using Parameterized Quantum Circuit Learning for Quantum Chemical Applications}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 PQCs formulate the ML algorithm as a variational problem optimized using a hybrid approach using both classical and quantum hardware.\cite{benedetti_parameterized_2019}
-Like classical ML approaches, PQC has been applied for several chemistry use cases such as drug\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,bhatia_quantum_2023,kao_exploring_2023,li_quantum_2021,avramouli_quantum_2023,avramouli_unlocking_2023} and materials discovery\cite{ishiyama_noise-robust_2022,ryu_quantum_2023,vitz_hybrid_2024}, the prediction of proton affinities\cite{jin_integrating_2025}, and experimental molecular properties, including the log solubility in water, melting point, octanol/water distribution coefficient, hydration free energy of small molecules in water.\cite{hatakeyama-sato_quantum_2023}
+Like classical ML approaches, PQCs have been applied for several chemistry use cases such as drug\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,bhatia_quantum_2023,kao_exploring_2023,li_quantum_2021,avramouli_quantum_2023,avramouli_unlocking_2023} and materials discovery\cite{ishiyama_noise-robust_2022,ryu_quantum_2023,vitz_hybrid_2024}, the prediction of proton affinities\cite{jin_integrating_2025}, and experimental molecular properties, including the log solubility in water, melting point, octanol/water distribution coefficient, and hydration free energy of small molecules in water.\cite{hatakeyama-sato_quantum_2023}
 Despite the broad range of topics covered in these studies and the interest among computational chemists in exploring PQCs for chemical applications, studies analyzing the potential benefits or drawbacks of using QML for quantum chemistry are lacking.
@@
 The second dataset consists of water conformers calculated with coupled-cluster singles and doubles (CCSD) using the data-driven coupled-cluster (DDCC) scheme of Townsend and Vogiatzis.\cite{townsend_data-driven_2019,jones_chapter_2023}
-Both datasets offer a unique perspective on the aptitude of applying PQCs on classical and quantum data\cite{cerezo_challenges_2022} since the models based on BSE49 rely on classical molecular representations\cite{jones_molecular_2023}, such as Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002} or Morgan fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, as input, while the input features in the DDCC method encode explicit quantum information related to molecular wave function.
-In our study, we introduce \textit{qregress} a modular Python framework, based on PennyLane\cite{bergholm_pennylane_2022} and Qiskit\cite{javadi-abhari_quantum_2024}, for exploring PQCs for regression-based QML tasks.
-To this end, we explore 168 unique PQCs, based on a combination of 14 data encoding and 12 variational layers, and then perform an analysis of how circuit depth effects model performance using two different expansion stategies.
-We also provide insights into the performance of PQCs on quantum chemical tasks using fake and real Qiskit backends.
-Lastly, we provide a detailed discussion on the efficiency, performance, and the importance of clearly defining what quantum advantage means in the context of QML models with respect to classical ML.
+Both datasets offer a unique perspective on the aptitude of applying PQCs on classical and quantum data\cite{cerezo_challenges_2022} since the models based on BSE49 rely on classical molecular representations\cite{jones_molecular_2023}, such as Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002} or Morgan fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, as input, while the input features in the DDCC method encode explicit quantum information related to the molecular electronic structure.
+In this study, we introduce \textit{qregress} a modular Python framework, based on PennyLane\cite{bergholm_pennylane_2022} and Qiskit\cite{javadi-abhari_quantum_2024}, for exploring PQCs for regression-based QML tasks.
+To this end, we explore the effects of classical and quantum data using a broad set of 168 unique PQCs, based on a combination of 14 data encoding and 12 variational layers.
+We then  perform an analysis of circuit depth on model performance, using two different expansion stategies, one based on data re-uploading\cite{perez-salinas_data_2020} and the other based on increasing the number of model parameters using additional variational layers.
+Using these insights, we then analyze how the best model performs using fake and real Qiskit backends.
+Lastly, we provide a detailed discussion on the efficiency and performance of PQCs, with insights to what quantum advantage could mean with respect to classical ML models.
 
 \section{Methods}
-PQCs are often constructed of three parts: encoding layers that are used to encode the features onto a quantum circuit, variational layers which include parameters that are optimized classically, and measurements which provide numerical estimations of the regression target values.\citep{suzuki_predicting_2020}
-In this study, we utilize the Mitarai (M)\cite{mitarai_quantum_2018}, single- (A1) and double-angle (A2) encoding layers found in Ref.
+PQCs typically consist of three components: encoding layers that map features onto a quantum circuit, variational layers with classically optimized parameters, and measurement layers that provide numerical estimates of the regression target values.\citep{suzuki_predicting_2020}
+Choosing the optimal encoding layer can be a challenging tasks due to costs associated with mapping the input data to qubits.\cite{biamonte_quantum_2017} 
+Due to this fact, we choose existing encoding layers that have shown promising results for regression tasks such as Mitarai (M)\cite{mitarai_quantum_2018}, single- (A1) and double-angle (A2) encoding layers found in Ref.
 \citep{suzuki_predicting_2020}, along with the instantaneous quantum polynomial (IQP) circuit found in Refs.
 \citep{bremner_average-case_2016} and \citep{havlicek_supervised_2019}.
-In the following section, we follow the notations derived from  Ref. \citep{suzuki_predicting_2020}.
-Encoding layers work mapping a $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, normalized on the range $[-1,1]$, onto a quantum circuit using a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ are the number of qubits.
-The encoding layer takes the following general form,
+
+To maintain a general notation, in the following section we follow the notations derived from  Ref. \citep{suzuki_predicting_2020}.
+Encoding layers work by mapping a given $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, normalized on the range $[-1,1]$, onto a quantum circuit using a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ are the number of qubits.
+More generally, the encoding layer can also incorporate both unitary and entanglement gates, such that 
 \begin{equation}
-	U_{\Phi(x)} =  \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})}
+	U_{\Phi(x)} =  \prod_{l} E_{\text{ent}}^{l} U_{\phi_{l}(\mathbf{x})},
 	\label{eq:general_encoding}
 \end{equation}
-where, $E_{\text{ent}}^{l}$ denotes the entangling gates, which can be a CNOT, CZ, or identity ($\mathbf{I}$) gates,   $U_{\phi_{l}(\mathbf{x})}$ denotes the choice of encoding unitaries. 
-Like in  Ref. \citep{suzuki_predicting_2020}, $E_{\text{ent}}$ corresponds to an identity matrix and $U_{\Phi(x)} = U_{\phi_{1}(\mathbf{x})}$.
+where, $E_{\text{ent}}^{l}$ denotes the entangling gates, e.g., CNOT or CZ, and  $U_{\phi_{l}(\mathbf{x})}$ denotes the choice of encoding unitaries.
 
-%Like in  Ref. \citep{suzuki_predicting_2020}, we choose $l \in \{1, 2\}$, such that when $l=1$, $E_{\text{ent}}$ corresponds to an identity matrix and $U_{\Phi(x)} = U_{\phi_{1}(\mathbf{x})}$.
-
-When $l=1$, $U_{\Phi(x)}$ can be one of the following four encoding layers: $U_{\text{A1}}$, $U_{\text{A2}}$, $U_{\text{M}}$, or $U_{\text{IQP}}$.
-The single-angle encoding (Fig. \ref{fig:encoders} \textbf{(a)}) is the simplest and takes the following form,
+In this study, like in Ref. \citep{suzuki_predicting_2020}, we explore encoders with $l={1,2}$. 
+When $l=1$, this forms the simplest encoding layers with $E_{\text{ent}}^{1}$ being absent, e.g. corresponding to the indenty ($\mathbf{I}$). 
+Using the previously defined general notation, the simplist encoding layer, single-angle encoding (Fig. \ref{fig:encoders} \textbf{(a)}), is then defined as,
 \begin{equation}
@@
 where $R^{Y}_{i}$ denotes a parameterized Y rotation gate on qubit $i$.
-Like the single-angle encoding, the double-angle encoding (Fig.
-\ref{fig:encoders} \textbf{(b)}) utilizes a parameterized Y rotation gate on qubit $i$, with the addition of a parameterized Z rotation gate on qubit $i$, denoted as
+Single-angle encoding, or qubit encoding, is structured similarly to a product of unentangled quantum states and have a similar mathematical structure as a product of local kernels where each $x_{i}$ is encoded in a local feature map.\cite{stoudenmire_supervised_2016,benedetti_parameterized_2019}
+
+The next encoder, double-angle encoding (Fig.
+\ref{fig:encoders} \textbf{(b)}) utilizes a parameterized Y rotation gate on qubit $i$, similar to $A1$, with the addition of a parameterized Z rotation gate on qubit $i$, denoted as
 \begin{equation}
-	U_{\text{A2}} = \prod_{i=0}^{n}  R^{Z}_{i}(x_{i}) R^{Y}_{i}(x_{i}).
+	U_{\text{A2}} = \prod_{i=0}^{n}  R^{Z}_{i}(x_{i}) R^{Y}_{i}(x_{i}),
 	\label{eq:A2}
 \end{equation}
-The Mitarai encoding layer (Fig.
-\ref{fig:encoders} \textbf{(c)}) is a double-angle encoding layer with the addition of an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
+which introduces additional redundancy by encoding two angles on the Bloch sphere.
+An extension of the double-angle encoding is the Mitarai encoding layer (Fig.
+\ref{fig:encoders} \textbf{(c)}), which includes an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
 \begin{equation}
@@
 \end{equation}
-Following the formulation provided in the PennyLane\cite{bergholm_pennylane_2022} software package, the IQP encoding layer (Fig. \ref{fig:encoders} \textbf{(d)}) is defined as,
+This unitary is physically motivated by expanding a density operator in terms of a set of Pauli operators, as highlighted in Ref. \cite{mitarai_quantum_2018}.
+
+The last and most complex encoding layer is the instantaneous quantum polynomial (IQP) (Fig. \ref{fig:encoders} \textbf{(d)}) proposed by Havlicek \textit{et al.}\cite{havlicek_supervised_2019},
 \begin{equation}
@@
 \end{equation}
-where $H_{i}$ denotes a Hadamard gate on qubit $i$ and $ZZ_{ij}$ denotes a two-qubit entangline gate defined as $ZZ_{ij} = e^{-i x_{i} x_{j} \sigma_{z} \otimes \sigma_{z}}$.
-
-Quantum advantage of IQP: ``For example, under well-believed complexity-theoretic assumptions, the class of PQCs called instantaneous quantum polynomial-time cannot be efficiently simulated by classical resources (see Lund et al [3] and Harrow and Montanaro [4] for accessible Reviews of quantum supremacy proposals).''\cite{benedetti_parameterized_2019}
-
-%\begin{figure}[H]
-%       \centering
-%       \begin{subfigure}{0.3\textwidth}
-	%               \centering
-	%               \includegraphics[width=\textwidth]{../images/encoders/quantikz/A1.png}
-	%               \caption{}
-	%               \label{fig:A1}
-	%       \end{subfigure}%
-%       \hfill
-%       \begin{subfigure}{0.3\textwidth}
-	%               \centering
-	%               \includegraphics[width=\textwidth]{../images/encoders/quantikz/A2.png}
-	%               \caption{}
-	%               \label{fig:A2}
-	%       \end{subfigure}%
-%       \hfill
-%       \begin{subfigure}{0.3\textwidth}
-	%               \centering
-	%               \includegraphics[width=1\textwidth]{../images/encoders/quantikz/M.png}
-	%               \caption{}
-	%               \label{fig:M}
-	%       \end{subfigure}%
-%       \hfill
-%       \begin{subfigure}{1\textwidth}
-	%               \centering
-	%                   \includegraphics[width=\textwidth]{../images/encoders/quantikz/IQP.png}
-	%               \caption{}
-	%               \label{fig:IQP}
-	%       \end{subfigure}%
-%       \caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
-%       \label{fig:encoders}
-%\end{figure}
+where $H_{i}$ denotes a Hadamard gate on qubit $i$ and $ZZ_{ij}$ denotes a two-qubit entangling gate defined as $ZZ_{ij} = e^{-i x_{i} x_{j} \sigma_{z} \otimes \sigma_{z}}$.
+It should be noted that under specific complexity and theoretic assumptions, IQP circuits cannot be efficiently simulated using classical resources and therefore offer a circuit that can only be simulted efficiently using quantum resources.\cite{lund_quantum_2017,harrow_quantum_2017}
 
@@
 	\includegraphics[width=\textwidth]{../images/encoders/quantikz/combined.png}
-	\caption{(a) Single angle (A1) encoding, (b) double angle (A2) encoding, (c) Mitarai (M) encoding, and (d) Instantaneous Quantum Polynomial (IQP) encoding}
+	\caption{Five qubit examples of the (a) single angle (A1), (b) double angle (A2), (c) Mitarai (M), and (d) Instantaneous Quantum Polynomial (IQP) encoders used in this study.}
 	\label{fig:encoders}
@@
 
-When $l=2$, like in Ref.
-\citep{suzuki_predicting_2020} we choose entanglement gates, $E_{\text{ent}}^{1}$ and $E_{\text{ent}}^{2}$ to be equivalent, and the encoding layer takes the following form, $U_{\Phi(x)} =  E_{\text{ent}} U_{\phi_{2}(\mathbf{x})} E_{\text{ent}} U_{\phi_{1}(\mathbf{x})}$ .
-We also exclude IQP encoding when $l=2$ due to the increased circuit depth, when compared to A1, A2, and M encoding.
-Therefore, there are five unique combinations of $U_{\phi_{1}(\mathbf{x})}$ and $U_{\phi_{2}(\mathbf{x})}$ (M-M, A1-A1, A2-A2, M-A1, and M-A2) and two different entanglement layer options (CNOT and CZ) for a total of 10 encoding circuits.
-These circuits are denoted as $U_{\phi_{1}(\mathbf{x})}-U_{\phi_{2}(\mathbf{x})}-E_{\text{ent}}$, for example, two example encoding circuits are M--M--CNOT and M--A1--CNOT.
-Table \ref{tab:encoders} shows all fourteen encoding circuits examined in this study.
+When $l=2$, more complex circuits can be generated, like in Ref.
+\citep{suzuki_predicting_2020}, where we choose the entanglement gates, $E_{\text{ent}}^{1}$ and $E_{\text{ent}}^{2}$, to be equivalent and the encoding layer takes the following form, $U_{\Phi(x)} =  E_{\text{ent}} U_{\phi_{2}(\mathbf{x})} E_{\text{ent}} U_{\phi_{1}(\mathbf{x})}$ .
+Additionally, we exclude IQP encoding when $l=2$ due to the increased computational costs associated with the circuit depth when compared to the expanded models based on A1, A2, and M encoding.
+Therefore, when we exclude IQP, there are five unique combinations of $U_{\phi_{1}(\mathbf{x})}$ and $U_{\phi_{2}(\mathbf{x})}$ (M-M, A1-A1, A2-A2, M-A1, and M-A2) and two different entanglement layer options (CNOT and CZ) for a total of 10 encoding circuits with $l=2$.
+The common notation for these circuits is $U_{\phi_{1}(\mathbf{x})}-U_{\phi_{2}(\mathbf{x})}-E_{\text{ent}}$ where two example encoding circuits are M--M--CNOT and M--A1--CNOT.
+The 14 encoding circuits used throughout this study are shown in Table \ref{tab:encoders}, where the first column shows the label, second column the first unitary ($U_{\phi_{1}(\mathbf{x})}$), third column the second unitary ($U_{\phi_{2}(\mathbf{x})}$), and last column the entanglement gates ($E_{\text{ent}}$).
 
@@
 	\end{tabular}
-	\caption{Add something smart}
+	\caption{The 14 encoding layers used in this study where the first column shows the encoding circuit name, second column the unitary for $l=1$, third column the unitary for $l=2$, and last column the corresponding entanglement gates.}
 	\label{tab:encoders}
@@
 
-Following the encoding layers,variational (or ansatz) layers are used to introduce trainable parameters into the quantum circuit.
-We use a mixed notation from Refs.
-\citep{suzuki_predicting_2020} and \citep{sim_expressibility_2019}, since Ref.
-\citep{sim_expressibility_2019} contains all of the variational layers used within this work.
-We relegate the discussion of the expressibility and entanglement examined in that work to Section \ref{section:results_and_discussion}.
-A general variational layer can be denoted as,
+The next layer in a PQC that follow the encoding layer, are the variational layers.
+The variational layers introduce trainable parameters, that can be optimized using classical compute resources, into the quantum circuit and provide flexiblity to the QML models.
+These layers have a general form, defined as,
 \begin{equation}
@@
 \end{equation}
-where $\bm{\theta}$ denotes the variational parameters and $v$ denotes the number of times that the layer is repeated within the circuit. 
-As $v$ increases and the number of trainable parameters ($\bm{\theta}$) increase, the theoretical assumption is that the model expressibility should also increase.
-In our study, we the number of variational layers as the number of ansatz layers (ALs).
-%In our study, we choose $v \in \{1, 3, 5\}$ and refer to this as the number of ansatz layers (ALs).
-We examine 12 different variational circuits, as shown in Fig.
-\ref{fig:ansatz}, which are denoted using the following labels: Modified-Pauli-CRZ (Fig.
+where $\bm{\theta}$ denote the variational parameters, $v$ denote the number of times that the layer is repeated within the circuit, and all entanglement gates are implicitly included in $U_{v}(\bm{\theta}_{v})$.
+In our study, we examine 12 variational circuits, found in \cite{sim_expressibility_2019}, as shown in Fig. \ref{fig:ansatz}.
+The unique names of the 12 variational circuits are as follows: Modified-Pauli-CRZ (Fig.
 \ref{fig:ansatz}\textbf{(a)}) , Modified-Pauli-CRX (Fig.
@@
 \ref{fig:ansatz}\textbf{(k)}), and Full-CRX (Fig.
-\ref{fig:ansatz}\textbf{(l)}),
+\ref{fig:ansatz}\textbf{(l)}).
 
@@
 	\includegraphics[width=\textwidth]{../images/ansatz/quantikz/combined.png}
-	\caption{(a) Modified-Pauli-CRZ, (b) Modified-Pauli-CRX, (c) Efficient-CRZ, (d) Efficient-CRX, (e) HWE-CNOT, (f) HWE-CZ,  (g) ESU2, (h) Full-Pauli-CRZ, (i) Full-Pauli-CRX, (j) Hadamard, (k) Full-CRZ, and (l)Full-CRX}
+	\caption{The 12 variational circuits include (a) Modified-Pauli-CRZ, (b) Modified-Pauli-CRX, (c) Efficient-CRZ, (d) Efficient-CRX, (e) HWE-CNOT, (f) HWE-CZ, (g) ESU2, (h) Full-Pauli-CRZ, (i) Full-Pauli-CRX, (j) Hadamard, (k) Full-CRZ, and (l)Full-CRX}
 	\label{fig:ansatz}
@@
 
-Now that we have define the encoding (Eq. \ref{eq:general_encoding}) and variational (Eq. \ref{eq:general_variational}) circuits, we can then combine them to denote a general, complete circuit as,
+To introduce more model parameters and increase the expressibility and nonlinearity of the PQCs, two expansion strategies can be explored.
+The first we denoted as the number of ansatz layers (AL), where $v$ can be increased to introduce more unique trainable parameters into the PQC.
+The second expansion strategy builds on the work of P\'{e}rez-Salinas \textit{et al.} that showed data re-uploading in PQCs is equivalent to the Universal Approximation Theorem for artificial neural networks.\cite{perez-salinas_data_2020}
+This is achieved combining Eqs. \ref{eq:general_encoding} and \ref{eq:general_variational} into a general circuit,
+
 \begin{equation}
@@
 \end{equation}
-where we choose $k \in \{1, 3, 5\}$, which denotes the re-upload depth (RUD) of the circuit.
-When a sufficient number of data re-uploading occur, it has been shown by P\'{e}rez-Salinas \textit{et al.} that data re-uploading is equivalent to the Universal Approximation Theorem for artificial neural networks.\cite{perez-salinas_data_2020}
+where $k$ denotes the re-upload depth (RUD) of the circuit.
 
-Lastly, to recover the predicted target values, $\hat{y}_{i}$, from our quantum circuits, measurement of the quantum state, $\ket{\Psi}$, must be performed.
-To perform this operation, we apply the Pauli Z operator on the first qubit denoted as,
+The last component of a PQC is measurement, which is required to recover the predicted target values, $\hat{y}_{i}$, of the machine learning model that are used to update the model parameters.
+This is performed by measuring the quantum state, $\ket{\Psi}$, using the Pauli Z operator on the first qubit denoted as,
 \begin{equation}
-	\hat{y}_{i} = \bra{\Psi}Z_{0}\ket{\Psi}_{i}.
+	\hat{y}_{i} = \bra{\Psi}Z_{0}\ket{\Psi}_{i},
 	\label{eq:y_pred}
 \end{equation}
-The set of predicted target values, $\bm{\hat{y}} = (\hat{y}_{1}, \ldots, \hat{y}_{N}) \in \mathbb{R}^{N}$, where $N$ is the number of samples, is then passed to the loss function, $\mathcal{L}(\bm{y}, \bm{\hat y})$, where $y_{i}$ belongs to the set of true target values $\bm{y} = (y_{1}, \ldots, y_{N}) \in \mathbb{R}^{N}$.
-In practice, $\mathcal{L}$ can be any loss function but we choose to use the mean square error loss function denoted as,
+and passing the set of predicted target values, $\bm{\hat{y}} = (\hat{y}_{1}, \ldots, \hat{y}_{N}) \in \mathbb{R}^{N}$, where $N$ is the number of samples, to the loss function, $\mathcal{L}(\bm{y}, \bm{\hat y})$, where $y_{i}$ belongs to the set of true target values $\bm{y} = (y_{1}, \ldots, y_{N}) \in \mathbb{R}^{N}$.
+While $\mathcal{L}$ can be any loss function relevant for regression-based ML tasks, we choose to mean square error to be the loss function,
 \begin{equation}
@@
 \subsection{Implementation}
+To facilitate the exploration of the large design space of the PQCs, we created a modular Python-based workflow called \textit{qregress}.
+\textit{qregress} incorporates circuits generated using both PennyLane\cite{bergholm_pennylane_2022} and Qiskit\cite{javadi-abhari_quantum_2024}, along with state-vector simulation using Qulacs\cite{suzuki_qulacs_2021}, noisy simulation using \textit{qiskit-aer} with the \textit{FakeQuebec} backend  backend as implemented in  Qiskit\cite{javadi-abhari_quantum_2024}, and real using \textit{ibm\_quebec}.
+All state-vector simulations are performed using the PennyLane code base, while all calculations using \textit{FakeQuebec} and \textit{ibm\_quebec} are ran using Qiskit due to the PennyLane-Qiskit plugin not including Batch execution modes.
+Additionally, state-vector simulations use the PennyLane implementation of the Simultaneous Perturbation Stochastic Approximation method (SPSA), while for the experiments run using \textit{FakeQuebec} and  \textit{ibm\_quebec} utilizes the Constrained Optimization By Linear Approximation (COBYLA) optimizer, as implemented ing SciPy\cite{virtanen_scipy_2020}.
+
 \begin{figure}[H]
@@
 	\includegraphics[width=\linewidth]{../images/manuscript_figures/overview.png}
-	\caption{Make this figure highlight the modularity of \textit{qregress}}
+	\caption{REMAKE to include cool code pic. Make this figure highlight the modularity of \textit{qregress}}
 	\label{fig:overview_project}
@@
 
-We introduce \textit{qregress}, a modular Python package for regression-based PQCs.
-
-We perform all simulation calculations using PennyLane\cite{bergholm_pennylane_2022}, either using Qulacs\cite{suzuki_qulacs_2021} for state vector calcualtions, while noisy calculations were performed using \textit{qiskit-aer} with the \textit{FakeQuebec} backend as implemented in the PennyLane-Qiskit plugin.\cite{javadi-abhari_quantum_2024}
-We perform calculations in the \textit{ibm\_quebec} device using circuits implemented using Qiskit\cite{javadi-abhari_quantum_2024}, due to issues we initially faced with running experiments on the real device using the PennyLane-Qiskit plugin.
-For the experiments using PennyLane,  we utilize the Simultaneous Perturbation Stochastic Approximation method (SPSA) as implemented in PennyLane, while for the experiments run on \textit{ibm\_quebec} utilizes the Constrained Optimization By Linear Approximation (COBYLA) optimizer as implemented ing SciPy\cite{virtanen_scipy_2020}.
 Each optimizer was chosen based on the performance for the given task.

### 2025-03-12 manuscript/main.tex
towards a proper class with error handling
manuscript

@@
 
-In this study, we address this by analyzing a diverse set of PQCs using two datasets related to computational chemistry.
+In this study, we address this by analyzing a diverse set of PQCs using two datasets related to quantum chemistry.
 The first dataset, BSE49 consists of bond separation energies (BSEs) of 49 unique bond types, calculated using the highly accurate (RO)CBS-QB3 composite method.\cite{prasad_bse49_2021}
@@
 
-\subsection{Implementation}
-To facilitate the exploration of the large design space of the PQCs, we created a modular Python-based workflow called \textit{qregress}.
-\textit{qregress} incorporates circuits generated using both PennyLane\cite{bergholm_pennylane_2022} and Qiskit\cite{javadi-abhari_quantum_2024}, along with state-vector simulation using Qulacs\cite{suzuki_qulacs_2021}, noisy simulation using \textit{qiskit-aer} with the \textit{FakeQuebec} backend  backend as implemented in  Qiskit\cite{javadi-abhari_quantum_2024}, and real using \textit{ibm\_quebec}.
-All state-vector simulations are performed using the PennyLane code base, while all calculations using \textit{FakeQuebec} and \textit{ibm\_quebec} are ran using Qiskit due to the PennyLane-Qiskit plugin not including Batch execution modes.
-Additionally, state-vector simulations use the PennyLane implementation of the Simultaneous Perturbation Stochastic Approximation method (SPSA), while for the experiments run using \textit{FakeQuebec} and  \textit{ibm\_quebec} utilizes the Constrained Optimization By Linear Approximation (COBYLA) optimizer, as implemented ing SciPy\cite{virtanen_scipy_2020}.
+\section{Implementation}
+To explore the large combination of PQCs previously mentinoed, we introduce \textit{qregress} (Fig.
+\ref{fig:overview_project}), a modular Python package based on PennyLane\cite{bergholm_pennylane_2022} and Qiskit\cite{javadi-abhari_quantum_2024}.
+The portion of the code based on PennyLane is capable of performing state-vector simulation using Qulacs\cite{suzuki_qulacs_2021}, noisy simulation using \textit{qiskit-aer} with the \textit{FakeQuebec} backend, along with access to real devices assessible on the IBM Quantum Platform using the PennyLane-Qiskit plugin.
+Additionally, to train and test regression models that require many circuit executions, we ported our PennyLane code to Qiskit to use the Qiskit Batch Execution mode.
+This was a vital step for running on \textit{ibm\_quebec} since Qiskit Sessions, as implemented in the PennyLane-Qiskit plugin is too cumbersome to train PQC as $N$ increases.
+In practice, all state-vector simulations were performed using the PennyLane, while all calculations using \textit{FakeQuebec} and \textit{ibm\_quebec}  are ran using Qiskit.
+State-vector simulations were also optimized using the PennyLane implementation of the Simultaneous Perturbation Stochastic Approximation method (SPSA) since we found that SPSA requires less steps to optimize when compared to other optimizers.
+For the experiments ran using \textit{FakeQuebec} and  \textit{ibm\_quebec}, we utilized the Constrained Optimization By Linear Approximation (COBYLA) optimizer, as implemented in SciPy\cite{virtanen_scipy_2020}.
+For all models, features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler, as implemented in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all featues and target values are $\mathbb{R}\in [ -1,1 ]$.
+
+All experiments were ran using 1000 iterations...
+BSE 5: all ran with 1000 iterations
+BSE 16: all ran with 1000 iterations
+DDCC 5:
 
@@
 
-Each optimizer was chosen based on the performance for the given task.
-All features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all featues and target values are $\mathbb{R}\in [ -1,1 ]$.
-For the simulations using \textit{FakeQuebec} and experiments on \textit{ibm\_quebec} we utilize Twirled Readout Error eXtinction (TREX) error mitigation.
+\section{Datasets}\label{subsection:datasets}
 
-Used QisKit for real and fake back end using Qiskit Batches
+The first quantum chemistry dataset we explore is BSE49, which contains bond seperation energies (BSEs), for homolytic bond cleavage of covalently bonded molecules, such as \ce{A-B -> A^{.} + B^{.}}.\cite{prasad_bse49_2021}
+This dataset consists of 49 unique A-B type bonds with 4394 datapoints, 1951 of which are existing structures, while the remaining 2443 are hypthoetical structures. 
+BSE49 provides highly accurate BSEs, calculated using the  (RO)CBS-QB3\cite{wood_restricted-open-shell_2006,montgomery_complete_1999,montgomery_complete_2000} composite quantum chemistry method, that are useful for benchmarking ML based applications.
 
-optimization levels
-none (0)
+An important aspect of machine learning in chemistry is the choice of molecular representation, or how the molecule is represented in the machine learning models.\cite{jones_molecular_2023}
+In general, molecular representations can be partitioned into three groups, graph-, topology-, and physics-based representations, all of which were explored to provide a comprehensive overview of how they perform using classical models as a baseline.
+During the preprocessing stage, before converting to the xyz coordinates into our molecular representation of choice, the set of hypothetical structures was reduced to 2436 molecules due to issues with valency exceptions when converting xyz coordinates into RDKit mol objects.
+Using RDKit\cite{noauthor_rdkit_nodate} we examined three commonly applied graph-based molecular preresentations, Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002}, Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, and RDKit fingerprints.
+All three of these methods use traversals of the molecular graphs to encode various structural details into bit vectors.
 
-``No optimization: typically used for hardware characterization
-Basic translation and Layout/Routing: TrivialLayout, where it selects the same physical qubit numbers as virtual and inserts SWAPs to make it work (using StochasticSwap)''
-
-light (1)
-``Light optimization: Layout/Routing: Layout is first attempted with TrivialLayout.
-If additional SWAPs are required, a layout with a minimum number of SWAPs is found by using SabreSWAP, then it uses VF2LayoutPostLayout to try to select the best qubits in the graph, InverseCancellation, 1Q gate optimization''
-
-medium (2)
-``Medium optimization: Layout/Routing: Optimization level 1 (without trivial) + heuristic optimized with greater search depth and trials of optimization function.
-Because TrivialLayout is not used, there is no attempt to use the same physical and virtual qubit numbers.
-CommutativeCancellation''
-
-high (3)
-``High Optimization:
-Optimization level 2 + heuristic optimized on layout/routing further with greater effort/trials
-Resynthesis of two-qubit blocks using Cartan's KAK Decomposition.
-Unitarity-breaking passes:
-OptimizeSwapBeforeMeasure: Moves the measurements around to avoid SWAPs
-RemoveDiagonalGatesBeforeMeasure: Removes gates before measurements that would not effect the measurements''
-
-resilience levels (error mitigation)
-none (0) 
-level 1 readout error mitigation and measurement twirling using Twirled Readout Error eXtinction (TREX) \cite{van_den_berg_model-free_2022}
-level 2 level 1 + gate twirling and zero noise extrapolation (ZNE)\cite{kandala_error_2019,li_efficient_2017,temme_error_2017}
-
-Function fitting 5: all ran with 1000 iterations
-Function fitting 16: all ran with 1000 iterations
-BSE 5: all ran with 1000 iterations
-BSE 16: all ran with 1000 iterations
-DDCC
-
-\subsection{Datasets}\label{subsection:datasets}
-In this study, we explore two datasets: a dataset of bond separation energies (BSE) of molecules (Figs.
-\ref{fig:bondtypes} and \ref{fig:BSEdistr}), where the feature set encodes structural information of each molecule;
-and a dataset consisting of electronic structure features to predict wave functions using the data-driven coupled-cluster scheme of Townsend and Vogiatzis (Fig.
-\ref{fig:waterddccdistribution}).\cite{townsend_data-driven_2019}
-We utilize the BSE49 and DDCC databases for two different reasons: the BSE49 database consists of a hard chemical property to predict using few features, while the DDCC dataset can be predicted easily using few features classically but is data intensive in the number of samples per molecule.
-
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.65\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/bondtypes.png}
-		\caption{}
-		\label{fig:bondtypes}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/BSE.jpg}
-		\caption{}
-		\label{fig:BSEdistr}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.3\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/manuscript_figures/waterddccdistribution.png}
-		\caption{}
-		\label{fig:waterddccdistribution}
-	\end{subfigure}	
-	\caption{Examples of the datasets explored in this study.
-For the BSE49 dataset the distributions of the (d) bond types and the (e) bond separation energies in kcal/mol.
-For the DDCC dataset distributions of the initial MP2 $t_{2}$-amplitudes and the optimized CCSD $t_{2}$-amplitudes are shown in (f).}
-	\label{fig:bse_data}
-\end{figure}
-
-BSE49
-``This work addresses the aforementioned gap in the literature by constructing a large dataset (4502 datapoints) of computationally predicted BSEs of 49 unique bond types, all of which are determined with a high-level composite theoretical procedure denoted as (RO)CBS-QB3.
-This approach ensures uniform, high-quality reference data and eliminates the need to collect and verify data gathered from various sources, which may differ substantially in their accuracy.
-The (RO)CBS-QB3 method is known to produce BDEs of high accuracy.
-Therefore, it is suitable for developing a database of BSEs that can be used to test and parametrize low-cost computational methods.
-One particular target application of our dataset is for the training of cost-effective computational approaches like atom-centered potentials (ACPs) or machine learning potentials.''
-(RO)CBS-QB3\cite{wood_restricted-open-shell_2006,montgomery_complete_1999,montgomery_complete_2000}
-
-```The structures obtained from the workflow described above were then used for the final step of reference data calculation, using the composite (RO)CBS-QB331,32,33 method.
-The restricted-open-shell61 CBS-QB3 or ROCBS-QB3 was employed for the open-shell radical fragments, while restricted closed-shell calculations were performed for the closed-shell parent molecules with CBS-QB3.
-The composite (RO)CBS-QB3 method approximates energies at the complete-basis-set CCSD(T) level, using a series of computationally lower-cost methods including: (i) geometry optimization followed by vibration frequency calculation using the unrestricted-open-shell62 B3LYP/6-311G(2d,d,p) method46,47,48,49,50,51,63, (ii) ROMP2/6-311+G(3d2f,2df,2p) level63,64,65 energy extrapolated to the complete-basis-set limit, (iii) energy calculation at ROMP4(SDQ)/6-31+G(d(f),p) level63,64,66, and (iv) energy calculation at ROCCSD(T)/6-31+G† level63,64,67 (where 6-31+G† is a modified 6-31+G(d) basis set).
-Note that the final (RO)CBS-QB3 energy includes additional empirical correction terms described in Reference33.
-Structures were screened to remove any system for which the imaginary frequencies were obtained.
-The (RO)CBS-QB3 energies for the structures associated with a particular bond breaking reaction were used to obtain the bond separation energies for the dataset.'''
-
-Following model calibration using the function fitting dataset, we explore the appliciblity of PQCs for complex chemically relevant machine learning tasks.
-The first chemically motivated dataset we explore is the BSE49 dataset, which contains the bond seperation energies (BSE)  for the homolytic bond cleavage of covalently bonded molecules, such as \ce{A-B -> A^{.} + B^{.}}.\cite{prasad_bse49_2021}
-This dataset consists of 4394 datapoints, 1951 of which are existing and 2443 are hypthoetical structures, with 49 unique A-B single bond types.
-In practice, we used 2436 of the hypothetical structures due to issues with valency exceptions when converting to RDKit mol objects which were later used for generating our features for the machine learning models.
-An important aspect of machine learning in chemistry is the choice of molecular representation, or how the molecule is represented in the machine learning models.\cite{jones_molecular_2023}
-Using RDKit\cite{noauthor_rdkit_nodate} we examined three commonly applied graph-based molecular preresentations, Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002}, Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, and RDKit fingerprints.
-All three of these methods are use traversals of the molecular graphs to encode various structural details into bit vectors.
 Lastly, we explore both topology- and physics-based molecular representations, both of which encode the three-dimensional structure of molecules in various, unique ways.
@@
 We found that the best molecular representation across all models test, as shown in Fig. \ref{fig:classical_molrepfig}, was Morgan fingerprints using the \textit{sub} formulation.
-
-\begin{figure}[H]
-	\centering	
-	\includegraphics[width=\linewidth]{../images/BSE/classical/classical_molrepfig.png}
-	\caption{Coulomb matrices (CMs), Molecular ACCess Systems (MACCS), persistence images (PIs), RDKit and Morgan fingerprints. Performance of a diverse set of molecular representations R$^{2}$}
-	\label{fig:classical_molrepfig}
-\end{figure}
 
@@
 
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/classical_features_MAE.png}
-		\caption{}
-		\label{fig:BSE_bse_classical_features_MAE}
-	\end{subfigure}
-	\hfill		
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../images/BSE/classical_features_R2.png}
-		\caption{}
-		\label{fig:BSE_classical_features_R2}
-	\end{subfigure}
-	\caption{Feature reduction of the BSE dataset represented using }
-	\label{fig:bse_classical_features}
-\end{figure}
+The second is a dataset of 199 water conformers generated at the CCSD/STO-3G level of theory using the data-driven coupled-cluster scheme of Townsend and Vogiatzis (Fig.
+\ref{fig:waterddccdistribution}).\cite{townsend_data-driven_2019}
 
@@
 	\centering
-	\includegraphics[width=0.49\textwidth]{../images/DDCC/DDCC_feature_set.png}
+	\begin{subfigure}[b]{0.65\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/BSE/bondtypes.png}
 		\caption{}
-	\label{fig:DDCC_feature_set}
+		\label{fig:bondtypes}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/BSE/BSE.jpg}
+		\caption{}
+		\label{fig:BSEdistr}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.3\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../images/manuscript_figures/waterddccdistribution.png}
+		\caption{}
+		\label{fig:waterddccdistribution}
+	\end{subfigure}	
+	\caption{REMAKE: Examples of the datasets explored in this study.
+For the BSE49 dataset the distributions of the (d) bond types and the (e) bond separation energies in kcal/mol.
+For the DDCC dataset distributions of the initial MP2 $t_{2}$-amplitudes and the optimized CCSD $t_{2}$-amplitudes are shown in (f).}
+	\label{fig:bse_data}
 \end{figure}
-
-% Make distribution plot
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=\linewidth]{../images/BSE.png}
-%	\caption{BSE}
-%	\label{fig:BSE}
-%\end{figure}
 
@@
 
+Error handling for real run with iter>1
+
+For the experiments using the \textit{FakeQuebec} and \textit{ibm\_quebec} backends, we performed small tests, initialized using the state-vector parameters with one iteration, to determine the best circuit optimization and error mitigation (resilience) levels.
+
+optimization levels
+none (0), light (1), medium (2), high (3)
+
+resilience levels (error mitigation)
+none (0) 
+level 1 readout error mitigation and measurement twirling using Twirled Readout Error eXtinction (TREX) \cite{van_den_berg_model-free_2022}
+level 2 level 1 + gate twirling and zero noise extrapolation (ZNE)\cite{kandala_error_2019,li_efficient_2017,temme_error_2017}
+
 \section{Conclusion}

### 2025-03-17 manuscript/main.tex
rerun bse
man.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Understanding Quantum Advantage using Parameterized Quantum Circuit Learning for Quantum Chemical Applications}
+\title{Understanding Parameterized Quantum Circuit Learning for Quantum Chemical Applications}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For computational chemistry, methods such as the quantum phase estimation (QPE)\cite{abrams_simulation_1997,abrams_quantum_1999,aspuru-guzik_simulated_2005,lanyon_towards_2010,whitfield_simulation_2011,aspuru-guzik_photonic_2012} algorithm have been shown to offer exponential speedups over classical methods.
-Despite the promising speedups, QPE requires long coherence times, while the current generation of quantum processing units (QPUs), are often too noisy for practical applications.
+Despite the promising speedups, QPE requires long coherence times, while the current generation of quantum processing units (QPUs) are often too noisy for practical applications.
 Alternatively, methods based on the variational principle, such as the variational quantum eigensolver (VQE)\cite{peruzzo_variational_2014,cerezo_variational_2021,mcclean_theory_2016,bharti_noisy_2022}, have been proposed as a quantum-classical hybrid approach, capable of running on noisy, near-term quantum devices.
@@
 To this end, we explore the effects of classical and quantum data using a broad set of 168 unique PQCs, based on a combination of 14 data encoding and 12 variational layers.
-We then  perform an analysis of circuit depth on model performance, using two different expansion stategies, one based on data re-uploading\cite{perez-salinas_data_2020} and the other based on increasing the number of model parameters using additional variational layers.
+We then perform an analysis of circuit depth on model performance, using two different expansion strategies, one based on data re-uploading\cite{perez-salinas_data_2020} and the other based on increasing the number of model parameters using additional variational layers.
 Using these insights, we then analyze how the best model performs using fake and real Qiskit backends.
-Lastly, we provide a detailed discussion on the efficiency and performance of PQCs, with insights to what quantum advantage could mean with respect to classical ML models.
+Lastly, we provide a detailed discussion on the efficiency and performance of PQCs, with insights into what quantum advantage could mean concerning classical ML models.
 
@@
 PQCs typically consist of three components: encoding layers that map features onto a quantum circuit, variational layers with classically optimized parameters, and measurement layers that provide numerical estimates of the regression target values.\citep{suzuki_predicting_2020}
-Choosing the optimal encoding layer can be a challenging tasks due to costs associated with mapping the input data to qubits.\cite{biamonte_quantum_2017} 
+Choosing the optimal encoding layer can be a challenging task due to the costs associated with mapping the input data to qubits.\cite{biamonte_quantum_2017} 
 Due to this fact, we choose existing encoding layers that have shown promising results for regression tasks such as Mitarai (M)\cite{mitarai_quantum_2018}, single- (A1) and double-angle (A2) encoding layers found in Ref.
@@
 
-To maintain a general notation, in the following section we follow the notations derived from  Ref. \citep{suzuki_predicting_2020}.
-Encoding layers work by mapping a given $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, normalized on the range $[-1,1]$, onto a quantum circuit using a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ are the number of qubits.
+To maintain a general notation, in the following section, we follow the notations derived from  Ref. \citep{suzuki_predicting_2020}.
+Encoding layers work by mapping a given $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, normalized on the range $[-1,1]$, onto a quantum circuit using a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ is the number of qubits.
 More generally, the encoding layer can also incorporate both unitary and entanglement gates, such that 
@@
 When $l=1$, this forms the simplest encoding layers with $E_{\text{ent}}^{1}$ being absent, e.g. corresponding to the indenty ($\mathbf{I}$). 
-Using the previously defined general notation, the simplist encoding layer, single-angle encoding (Fig. \ref{fig:encoders} \textbf{(a)}), is then defined as,
+Using the previously defined general notation, the simplest encoding layer, single-angle encoding (Fig. \ref{fig:encoders} \textbf{(a)}), is then defined as,
 \begin{equation}
@@
 An extension of the double-angle encoding is the Mitarai encoding layer (Fig.
-\ref{fig:encoders} \textbf{(c)}), which includes an arcosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
+\ref{fig:encoders} \textbf{(c)}), which includes an arccosine function on the parameterized Z gate and arcsine on the parameterized Y gate,
 \begin{equation}
@@
 where $H_{i}$ denotes a Hadamard gate on qubit $i$ and $ZZ_{ij}$ denotes a two-qubit entangling gate defined as $ZZ_{ij} = e^{-i x_{i} x_{j} \sigma_{z} \otimes \sigma_{z}}$.
-It should be noted that under specific complexity and theoretic assumptions, IQP circuits cannot be efficiently simulated using classical resources and therefore offer a circuit that can only be simulted efficiently using quantum resources.\cite{lund_quantum_2017,harrow_quantum_2017}
+It should be noted that under specific complexity and theoretic assumptions, IQP circuits cannot be efficiently simulated using classical resources and therefore offer a circuit that can only be simulated efficiently using quantum resources.\cite{lund_quantum_2017,harrow_quantum_2017}
 
@@
 
-The next layer in a PQC that follow the encoding layer, are the variational layers.
-The variational layers introduce trainable parameters, that can be optimized using classical compute resources, into the quantum circuit and provide flexiblity to the QML models.
+The next layer in a PQC which follows the encoding layer, is the variational layer.
+The variational layers introduce trainable parameters, that can be optimized using classical compute resources, into the quantum circuit and provide flexibility to the QML models.
 These layers have a general form, defined as,
@@
 The second expansion strategy builds on the work of P\'{e}rez-Salinas \textit{et al.} that showed data re-uploading in PQCs is equivalent to the Universal Approximation Theorem for artificial neural networks.\cite{perez-salinas_data_2020}
-This is achieved combining Eqs. \ref{eq:general_encoding} and \ref{eq:general_variational} into a general circuit,
+This is achieved by combining Eqs. \ref{eq:general_encoding} and \ref{eq:general_variational} into a general circuit,
 
@@
 
-The last component of a PQC is measurement, which is required to recover the predicted target values, $\hat{y}_{i}$, of the machine learning model that are used to update the model parameters.
+The last component of a PQC is measurement, which is required to recover the predicted target values, $\hat{y}_{i}$, of the machine learning model that is used to update the model parameters.
 This is performed by measuring the quantum state, $\ket{\Psi}$, using the Pauli Z operator on the first qubit denoted as,
@@
 \section{Implementation}
-To explore the large combination of PQCs previously mentinoed, we introduce \textit{qregress} (Fig.
+To explore the large combination of PQCs previously mentioned, we introduce \textit{qregress} (Fig.
 \ref{fig:overview_project}), a modular Python package based on PennyLane\cite{bergholm_pennylane_2022} and Qiskit\cite{javadi-abhari_quantum_2024}.
-The portion of the code based on PennyLane is capable of performing state-vector simulation using Qulacs\cite{suzuki_qulacs_2021}, noisy simulation using \textit{qiskit-aer} with the \textit{FakeQuebec} backend, along with access to real devices assessible on the IBM Quantum Platform using the PennyLane-Qiskit plugin.
-Additionally, to train and test regression models that require many circuit executions, we ported our PennyLane code to Qiskit to use the Qiskit Batch Execution mode.
-This was a vital step for running on \textit{ibm\_quebec} since Qiskit Sessions, as implemented in the PennyLane-Qiskit plugin is too cumbersome to train PQC as $N$ increases.
-In practice, all state-vector simulations were performed using the PennyLane, while all calculations using \textit{FakeQuebec} and \textit{ibm\_quebec}  are ran using Qiskit.
-State-vector simulations were also optimized using the PennyLane implementation of the Simultaneous Perturbation Stochastic Approximation method (SPSA) since we found that SPSA requires less steps to optimize when compared to other optimizers.
+The portion of the code based on PennyLane is capable of performing state-vector simulation using Qulacs\cite{suzuki_qulacs_2021}, noisy simulation using \textit{qiskit-aer} with the \textit{FakeQuebec} backend, along with access to real devices accessible on the IBM Quantum Platform using the PennyLane-Qiskit plugin.
+Additionally, to train and test regression models that require many circuit executions, we ported our PennyLane code to Qiskit so that the Qiskit Batch Execution mode could be utilized.
+This was a vital step for running on \textit{ibm\_quebec} since Qiskit Sessions, as implemented in the PennyLane-Qiskit plugin, are too cumbersome to train PQCs as $N$, the number of training samples, increases.
+In practice, all state-vector simulations were performed using PennyLane, while all calculations using \textit{FakeQuebec} and \textit{ibm\_quebec}  are run using Qiskit.
+State-vector simulations were also optimized using 1000 iterations with the Simultaneous Perturbation Stochastic Approximation method (SPSA), as implemented in PennyLane since we found that SPSA requires less steps to optimize when compared to other optimizers for state-vector simulation.
 For the experiments ran using \textit{FakeQuebec} and  \textit{ibm\_quebec}, we utilized the Constrained Optimization By Linear Approximation (COBYLA) optimizer, as implemented in SciPy\cite{virtanen_scipy_2020}.
-For all models, features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler, as implemented in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all featues and target values are $\mathbb{R}\in [ -1,1 ]$.
-
-All experiments were ran using 1000 iterations...
-BSE 5: all ran with 1000 iterations
-BSE 16: all ran with 1000 iterations
-DDCC 5:
+For all models, features ($\mathbf{x}$) and target values ($\mathbf{y}$) were scaled using the MinMaxScaler, as implemented in Scikit-learn\cite{pedregosa_scikit-learn_2011}, such that all features and target values are $\mathbb{R}\in [ -1,1 ]$.
 
@@
 
-The first quantum chemistry dataset we explore is BSE49, which contains bond seperation energies (BSEs), for homolytic bond cleavage of covalently bonded molecules, such as \ce{A-B -> A^{.} + B^{.}}.\cite{prasad_bse49_2021}
-This dataset consists of 49 unique A-B type bonds with 4394 datapoints, 1951 of which are existing structures, while the remaining 2443 are hypthoetical structures. 
-BSE49 provides highly accurate BSEs, calculated using the  (RO)CBS-QB3\cite{wood_restricted-open-shell_2006,montgomery_complete_1999,montgomery_complete_2000} composite quantum chemistry method, that are useful for benchmarking ML based applications.
+The first quantum chemistry dataset we explore is BSE49, which contains bond separation energies (BSEs), for homolytic bond cleavage of covalently bonded molecules, such as \ce{A-B -> A^{.} + B^{.}}.\cite{prasad_bse49_2021}
+This dataset consists of 49 unique A-B type bonds with 4394 datapoints, 1951 of which are existing structures, while the remaining 2443 are hypothetical structures. 
+BSE49 provides highly accurate BSEs, calculated using the  (RO)CBS-QB3\cite{wood_restricted-open-shell_2006,montgomery_complete_1999,montgomery_complete_2000} composite quantum chemistry method, that is useful for benchmarking ML-based applications.
 
-An important aspect of machine learning in chemistry is the choice of molecular representation, or how the molecule is represented in the machine learning models.\cite{jones_molecular_2023}
+An important aspect of ML in chemistry is the choice of molecular representation, or how the molecule is represented in the machine learning models.\cite{jones_molecular_2023}
 In general, molecular representations can be partitioned into three groups, graph-, topology-, and physics-based representations, all of which were explored to provide a comprehensive overview of how they perform using classical models as a baseline.
-During the preprocessing stage, before converting to the xyz coordinates into our molecular representation of choice, the set of hypothetical structures was reduced to 2436 molecules due to issues with valency exceptions when converting xyz coordinates into RDKit mol objects.
+During the preprocessing stage, before converting to the XYZ coordinates into our molecular representation of choice, the set of hypothetical structures was reduced to 2436 molecules due to issues with valency exceptions when converting XYZ coordinates into RDKit mol objects.
 Using RDKit\cite{noauthor_rdkit_nodate} we examined three commonly applied graph-based molecular preresentations, Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002}, Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, and RDKit fingerprints.
 All three of these methods use traversals of the molecular graphs to encode various structural details into bit vectors.
+Lastly, we explore both topology- and physics-based molecular representations, both of which encode the three-dimensional structure of molecules in various, unique ways.
+Persistent images (PIs) are a topology-based fingerprint that uses persistence homology to encode topological information of three-dimensional molecular structures into fixed-dimension images.\cite{adams_persistence_2017,townsend_representation_2020,schiff_augmenting_2022}
+We use the implementation from Townsend \textit{et al.}\cite{townsend_representation_2020}, which uses the Ripser Python package to generate PIs.\cite{tralie_ripserpy_2018}
+Lastly, we explore two physics-based representations, Coulomb matrices (CMs) \cite{rupp_fast_2012} and smooth overlap of atomic positions (SOAPs), that were generated using DScribe.\cite{de_comparing_2016}
+Both methods encode physical information regarding the atomic environments of each molecule, where CMs encode the Coulomb repulsion between atoms using nuclear charges, while SOAPs encode the similarities between atomic neighborhoods using kernels.
+Due to the computational cost associated with computing the regularized entropy match (REMatch) kernel over the set of 2436 molecules with the SOAPs representation, we excluded SOAPs from the overall discussion.
+For each of the molecular representations, we analyzed two different methods for representing the components of the BSE reaction.
+The first represents the feature vector as the products subtracted from the reactants, denoted as \textit{sub} (e.g., $\text{CM}_{\mathit{sub}} = (\text{CM}_{\text{A}^{.}} + \text{CM}_{\text{B}^{.}}) - \text{CM}_{\text{A-B}}$), similar to the method used in Ref.
+\cite{garcia-andrade_barrier_2023}, and the second represents the feature vector using only the reactant (A-B), denoted as \textit{AB} (e.g., $\text{CM}_{\mathit{AB}} =  \text{CM}_{\text{A-B}}$).
 
-Lastly, we explore both topology- and physics-based molecular representations, both of which encode the three-dimensional structure of molecules in various, unique ways.
-Persistent images (PIs) are a topology-based fingerprint that uses persistence homology to encode topological information of three-dimensional molecular structures into fixed dimension images.\cite{adams_persistence_2017,townsend_representation_2020,schiff_augmenting_2022}
-We use the implementation from Townsend \textit{et al.}\cite{townsend_representation_2020}, which uses the Ripser Python package to generate PIs.\cite{tralie_ripserpy_2018}
-Lastly, we explre two physics-based representations, Coulomb matrices (CMs) \cite{rupp_fast_2012} and smooth overlap of atomic positions (SOAPs), that were generated using DScribe.\cite{de_comparing_2016}
-Due to the computational cost of computing the regularized entropy match (REMatch) kernel  with the SOAPs representation, we excluded this representation in the overall discussion.
-We  also tested two different methods for representing the components of the bond separation chemical reaction, one where the feature vectors for the products are subtracted from the reactants, denoted by \textit{sub}, similar to the method used in Ref.
-\cite{garcia-andrade_barrier_2023}, and one that is composed of the reactant molecular only, denoted as \textit{AB}.
+Using this set of molecular representations, we also examine a diverse set of classical regression models to help choose the optimal representation for our diverse set of PQCs.
+The classical models we analyze include ridge, lasso, elastic net, \textit{k}-nearest-neighbors, random forest, gradient boosting, support vector machines, kernel ridge, and Gaussian process regression as implemented in sckit-learn.\cite{pedregosa_scikit-learn_2011}
+As highlighted in Fig.
+\ref{fig:classical_molrepfig}, we found that the best molecular representation across all models test was Morgan fingerprints using the \textit{sub} formulation, which we use for all experiments using the PQCs.
+Additionally, one challenge of applying classical molecular representations for ML tasks using PQCs is reducing the set of features, often containing hundreds or thousands of features per sample, to the number of qubits used on the quantum device.
+For example, at the onset of this project the standard number of qubits on the IBM quantum devices was 5 or 16 qubits, which requires reducing the initial set of 2048 features per sample for Morgan fingerprints down to 5 or 16 features.
+To perform this reduction, we explored two different methods, SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017}, which uses cooperative game theory to determine feature importance, and principal component analysis (PCA), a linear algebra-based dimensionality reduction technique, as implemented in scikit-learn.\cite{pedregosa_scikit-learn_2011}
+In Figs.
+\ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE}, we compare the two reduction techniques, for both 5 and 16 features, with the initial model containing 2048 features.
+The initial model has mean absolute errors (MAE) of 1.91 and 4.98 kcal/mol and R$^{2}$s of 0.99 and 0.91 for the training and test set, respectively.
+Using SHAP, we found that the model containing 5 features has an MAE of 16.08 kcal/mol and an R$^{2}$ of 0.39 for the training set, while the test set has an MAE of 15.86 kcal/mol and an R$^{2}$ of 0.42.
+For the model with 16 features, we observe improvements in both the training and test sets, with MAEs of 10.48 and 11.08 kcal/mol and R$^{2}$ values of 0.69 and 0.68, respectively.
+For the models using 5 and 16 features reduced through PCA, the training sets yield MAEs of 4.09 and 3.23 kcal/mol, while the test sets have MAEs of 10.17 and 8.40 kcal/mol, respectively.
+The R$^{2}$s also show slight improvement over the feature reductions using SHAP, where the R$^{2}$s using 5 features are 0.95 and 0.69 for the training and test set, respectively, and the model using 16 features has R$^{2}$s of 0.97 and 0.78 for the training and test set, respectively.
+Overall, the models using SHAP to reduce the feature set offer models with less overfitting, while sacrificing accuracy, when compared to the models reduced using PCA, which offer more accurate models that are more overfit.
+Based on these insights, for the experiments using PQCs, all BSE49 data is reduced to 5 or 16 qubits using PCA applied on Morgan fingerprint using the \textit{sub} formulation.
 
-Since we are analyzing a diverse set of PQCs, we also examine a diverse set of classic regression models, with varying capabilities, such as ridge, lasso, elastic net, \textit{k}-nearest-neighbors, random forest, gradient boosting, support vector, kernel ridge, and gaussian process regression as implemented in sckit-learn.\cite{pedregosa_scikit-learn_2011}
-Based on our results shown in Fig. \ref{fig:classical_molrepfig} we found that Morgan fingerprints
-We found that the best molecular representation across all models test, as shown in Fig. \ref{fig:classical_molrepfig}, was Morgan fingerprints using the \textit{sub} formulation.
-
-An additional challenge of applying classical molecular representations for quantum machine learning models is mapping the classical features, often containing hundreds or thousands of features per sample, to the number of qubits used on the quantum device.
-Initially, the Morgan fingerpints have 2048 features per sample, that need to be reduced down to 5 or 16 qubits.
-We choose 5 and 16 qubits for two reasons, the first is that these were the standard number of qubits on IBM quantum devices when we started the project and the second is that reducing the number of features reduces the depth of the circuits.
-To reduce the feature set from 2048 to 5 or 16 features, we explore two different methods, SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017} and principal component analysis (PCA), as implemented in scikit-learn.\cite{pedregosa_scikit-learn_2011}
-Figs. \ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE} show the results for the reductions using SHAP and PCA for the training and test set of using 5 and 16 features.
-The initial model using 2048 features has a train and test mean absolute error (MAE) of 1.91 and 4.98 kcal/mol, with train and test R$^{2}$s of 0.99 and 0.91, respectively.
-When using SHAP to reduce the feature set size to 5 features, we see that the training set has an MAE of 16.08 kcal/mol and an R$^{2}$ of 0.39, while for the test set has an MAE of 15.86 kcal/mol and an R$^{2}$ of 0.42.
-When the number of features is reduced to 16 features using SHAP, we see slight improvements with train and test MAEs of 10.48 and 11.08 kcal/mol with R$^{2}$s of 0.69 and 0.68, respectively.
-Using PCA, we see an improvement in accuracy for both 5 and 16 features, where the training sets have MAEs of 4.09 and 3.23 kcal/mol and the test sets have MAEs of 10.17 and 8.40 kcal/mol, respectively.
-The R$^{2}$s for PCA with 5 and 16 features also shows improvement over the reductions using SHAP, with R$^{2}$s of 0.95 and 0.69 for the training and test set, respectively, using 5 features and 0.97 and 0.78 for the training and test set, respectively, using 16 features.
-Due to the increased performance, despite exhibiting overfitting, we choose to use Morgan fingerprints reduced using PCA for our QML models.
-
-The second is a dataset of 199 water conformers generated at the CCSD/STO-3G level of theory using the data-driven coupled-cluster scheme of Townsend and Vogiatzis (Fig.
-\ref{fig:waterddccdistribution}).\cite{townsend_data-driven_2019}
-
-The next chemical dataset explored is based on the data-driven coupled-cluster (DDCC) method, which is a machine learning-based approach for accelerating the convergence of coupled-cluster singles and doubles (CCSD) calculations.\cite{townsend_data-driven_2019,jones_chapter_2023}
-This method works by predicting the $t_{2}$-amplitudes of the CCSD wave function (Eq.
+The second quantum chemistry dataset we analyze in this paper is generated using the data-driven coupled-cluster (DDCC) scheme of Townsend and Vogiatzis.\cite{townsend_data-driven_2019}
+DDCC is an ML-based approach for accelerating the convergence of coupled-cluster singles and doubles (CCSD) calculations by predicting the $t_{2}$-amplitudes of the CCSD wave function (Eq.
 \ref{eq:cc_wfn}) with features generated using lower-level methods, such as Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2), which are used to initialize CCSD calculations.
-
 The coupled-cluster wave function takes the general form,
@@
 Features related to the MP2 $t_{2}$-amplitudes that are also included in the feature set are the numerator ($\mel{ij}{}{ab}$) and denominator ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), a binary feature to denote whether the excitation goes to the same virtual orbital, and the orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$).
-The feature set also includes terms related to the individual contributes to the orbital energies are also included, such as the one-electron Hamiltonain ($h$), Coulombic matrix ($J$), and exchange matrix $K$, and Coulombic and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$).
-In total, there are 30 features for each $t_{2}$-amplitude due to the addition of features that denote the sign and magntudes of the previously mentioned features.
+The feature set also includes terms related to the individual contributions to the orbital energies are also included, such as the one-electron Hamiltonian ($h$), Coulomb matrix ($J$), and exchange matrix $K$, and Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$).
+In total, there are 30 features for each $t_{2}$-amplitude due to the addition of features that denote the sign and magnitudes of the previously mentioned features.
 
@@
 Unlike the BSE dataset, we choose SHAP over PCA for the feature reduction since there is a direct correlation between the input features and output values.
-As shown in Fig. \ref{fig:DDCC_feature_set}, 5 and 16 features can accurately recover performance of the original model using 30 features, where all three models have train and test R$^{2}$s of 1.00.
+As shown in Fig.
+\ref{fig:DDCC_feature_set}, 5 and 16 features can accurately recover the performance of the original model using 30 features, where all three models have train and test R$^{2}$s of 1.00.
 Due to the computational costs of running QML models, we will then use only 5 features for all DDCC QML models.

### 2025-03-18 manuscript/main.tex
SHAP DDCC save

@@
 For example, at the onset of this project the standard number of qubits on the IBM quantum devices was 5 or 16 qubits, which requires reducing the initial set of 2048 features per sample for Morgan fingerprints down to 5 or 16 features.
-To perform this reduction, we explored two different methods, SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017}, which uses cooperative game theory to determine feature importance, and principal component analysis (PCA), a linear algebra-based dimensionality reduction technique, as implemented in scikit-learn.\cite{pedregosa_scikit-learn_2011}
+To perform this reduction, we explored two different methods, SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017}, which uses cooperative game theory to determine feature importance, and principal component analysis (PCA), which is a dimensionality reduction technique that captures the direction a datasets variance, as implemented in scikit-learn.\cite{pedregosa_scikit-learn_2011}
 In Figs.
@@
 DDCC is an ML-based approach for accelerating the convergence of coupled-cluster singles and doubles (CCSD) calculations by predicting the $t_{2}$-amplitudes of the CCSD wave function (Eq.
-\ref{eq:cc_wfn}) with features generated using lower-level methods, such as Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2), which are used to initialize CCSD calculations.
-The coupled-cluster wave function takes the general form,
+\ref{eq:cc_wfn}) with features generated using lower-level methods, such as Hartree-Fock (HF) and M{\o}ller-Plesset second-order perturbation theory (MP2), that are used to initialize CCSD calculations.
+Herein, we provide a brief overview of the equations required to understand the DDCC method, starting with the coupled-cluster wave function, which takes the general form,
 \begin{equation}
@@
 \end{equation}
-where the cluster operator is denoted as $\hat{T}$ and the reference, Hartree-Fock wave function is denoted as $\ket{\Psi_{0}}$.
-The CCSD wave function truncates the cluster operator to only include singles and doubles excitations.
-The CCSD correlation energy is defined as,
+where $\hat{T}$ is the cluster operator and $\ket{\Psi_{0}}$ is the reference (Hartree-Fock) wave function.
+In CCSD, the $\hat{T}$ operator is truncated to only include single ($\hat{T}_{1}$) and double ($\hat{T}_{2}$) excitations.
+After solving the coupled-cluster equations, the CCSD correlation energy can be formulated as,
 \begin{equation}
@@
 \end{equation}
-where $i$ and $j$ denote occupied orbitals, $a$ and $b$ denote virtual orbitals, $t^{ab}_{ij}$ are the $t_{2}$-amplitudes which correspond to two-electron excitations, 
-$t^{a}_{i}$ and $t^{b}_{j}$ are $t_{1}$-amplitudes corresponding to one-electron excitations, and $\mel{ij}{}{ab}$ are two-electron integrals.
-
-For each two-electron excitation, $t^{ab}_{ij}$, a feature set can be generated from HF and MP2.
-The feature set includes the MP2 $t_{2}$-amplitudes, which are used to initialize the CCSD amplitudes,
+where $i$ and $j$ denote occupied orbitals, $a$ and $b$ denote virtual orbitals, $t^{ab}_{ij}$ correspond to two-electron excitation amplitudes ($t_{2}$-amplitudes), $t^{a}_{i}$ and $t^{b}_{j}$ correspond to one-electron excitation amplitudes ($t_{1}$-amplitudes), and $\mel{ij}{}{ab}$ are two-electron integrals.
+The objective of the DDCC method is to learn the CCSD $t_{2}$-amplitudes using features generated using HF and MP2, since the CCSD $t_{2}$-amplitudes are initialized using MP2 $t_{2}$-amplitudes, defined as,
 \begin{equation}
@@
 where $\varepsilon_{i}$ and $\varepsilon_{j}$ denote the orbital energies of the occupied orbitals $i$ and $j$, while the virtual orbitals $a$ and $b$ are denoted by $\varepsilon_{a}$ and $\varepsilon_{b}$.
-Features related to the MP2 $t_{2}$-amplitudes that are also included in the feature set are the numerator ($\mel{ij}{}{ab}$) and denominator ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), a binary feature to denote whether the excitation goes to the same virtual orbital, and the orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$).
-The feature set also includes terms related to the individual contributions to the orbital energies are also included, such as the one-electron Hamiltonian ($h$), Coulomb matrix ($J$), and exchange matrix $K$, and Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$).
-In total, there are 30 features for each $t_{2}$-amplitude due to the addition of features that denote the sign and magnitudes of the previously mentioned features.
+Due to this important relationship, MP2 $t_{2}$-amplitudes are included in the DDCC feature set, along with the numerator ($\mel{ij}{}{ab}$), denominator ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), a binary feature to denote whether the excitation goes to the same virtual orbital, and the orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$).
+Additionally, the feature set includes terms related to the individual contributions to the orbital energies, such as the one-electron Hamiltonian ($h$), Coulomb matrix ($J$), exchange matrix $K$, and Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$).
+In total, there are 30 features for each CCSD $t_{2}$-amplitude due to the addition of features that denote the sign and magnitude of the MP2 $t_{2}$-amplitudes.
 
-Our dataset consists of 199 water molecules from the study by Townsend and Vogiatzis using the STO-3G basis set\cite{hehre_selfconsistent_1970} and frozen core orbitals.
-All data was generated using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
-As previously mentioned, the DDCC method is data intensive regarding the number of samples per molecule, for example, each water molecule has 4 occupied and 2 virtual orbitals.
-The number of $t_{2}$-amplitudes is equivalent to $(N_{occ})^{2}(N_{virt})^{2}$, where $N_{occ}$ denotes the number of occupied orbitals and $N_{virt}$ denotes the number of virtual orbitals, so the total number of $t_{2}$-amplitudes per molecule is 64.
-Further details regarding the feature set and implementation can be found in \cite{townsend_data-driven_2019}
+Using the DDCC method, we generate a dataset consisting of 199 water molecules obtained from the study of Townsend and Vogiatzis using the STO-3G basis set\cite{hehre_selfconsistent_1970}  with the frozen core approximation.
+All HF, MP2, and CCSD data was generated using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
+We will also note that despite using a minimal basis set, this is a data intensive quantum chemistry application for PQCs since for each molecule there are $(N_{occ})^{2}(N_{virt})^{2}$ $t_{2}$-amplitudes, where $N_{occ}$ denotes the number of occupied orbitals and $N_{virt}$ denotes the number of virtual orbitals.
+For the water confirmers with 4 occupied and 2 virtual orbitals, there are a total of 64 $t_{2}$-amplitudes per molecule.
+Further details regarding the feature set and implementation can be found in Ref.  \cite{townsend_data-driven_2019}
 
-Like the BSE dataset, the 30 features from the full DDCC feature set must be reduced to 5 or 16 features using SHAP or PCA.
-Unlike the BSE dataset, we choose SHAP over PCA for the feature reduction since there is a direct correlation between the input features and output values.
-As shown in Fig.
-\ref{fig:DDCC_feature_set}, 5 and 16 features can accurately recover the performance of the original model using 30 features, where all three models have train and test R$^{2}$s of 1.00.
-Due to the computational costs of running QML models, we will then use only 5 features for all DDCC QML models.
-The 5 most important features are the two-electron integrals ($\mel{ij}{}{ab}$), MP2 $t_{2}$-amplitudes ($t^{ab}_{ij(\text{MP2})}$), the magnitude of the MP2 $t_{2}$-amplitudes, and the difference in orbital energies ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$).
+Lastly, like the BSE49 dataset, the 30 DDCC features must be reduced to 5 or 16 features using either SHAP or PCA.
+Unlike the BSE49 dataset, SHAP outperforms PCA due to the direct relationship between the feature set and target values.
+Additionally, as highlighted in Fig. \ref{fig:DDCC_feature_set}, when the feature set is reduced to 5 or 16 features, both models have train and test R$^{2}$s of 1.00.
+Due to the computational costs of simulating state-vector models on a broad set of PQCs, we will only perform our DDCC models with 5 features, which includes the two-electron integrals ($\mel{ij}{}{ab}$), MP2 $t_{2}$-amplitudes ($t^{ab}_{ij(\text{MP2})}$), the magnitude of the MP2 $t_{2}$-amplitudes, and the difference in orbital energies ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$).
+[update... missing one feature]
 

### 2025-03-18 manuscript/main.tex
towards the pip package

@@
 Additionally, as highlighted in Fig. \ref{fig:DDCC_feature_set}, when the feature set is reduced to 5 or 16 features, both models have train and test R$^{2}$s of 1.00.
-Due to the computational costs of simulating state-vector models on a broad set of PQCs, we will only perform our DDCC models with 5 features, which includes the two-electron integrals ($\mel{ij}{}{ab}$), MP2 $t_{2}$-amplitudes ($t^{ab}_{ij(\text{MP2})}$), the magnitude of the MP2 $t_{2}$-amplitudes, and the difference in orbital energies ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$).
-[update... missing one feature]
+Due to the computational costs of simulating state-vector models on a broad set of PQCs, we will only perform our DDCC models with 5 features, which includes the two-electron integrals ($\mel{ij}{}{ab}$), MP2 $t_{2}$-amplitudes ($t^{ab}_{ij(\text{MP2})}$), the magnitude of the MP2 $t_{2}$-amplitudes, the difference in orbital energies ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), and the binary feature denoting whether two-electrons are promoted to the same virtual orbital ($a=b$).
 
@@
 \label{section:results_and_discussion}
-
-\subsection{BSE}
-To explore the performance of PQCs for chemically relevant datasets, the dataset we explore is the BSE49 dataset, which consists of a diverse set of bond separation energies and the related structures, as highlighted in Figs.
-\ref{fig:bondtypes} and \ref{fig:BSEdistr}.
-Initially, we study the five qubit data, Figs. \ref{fig:5BSE_heatplots} and \ref{fig:5BSE_boxplots}, due to computational considerations.
+In this section, we discuss the initial analysis of the 168 PQCs with 5 qubits, using the PCA reduced \textit{sub}-Morgan fingerprints.
 
@@
 Best ansatz on average train R$^{2}$/test R$^{2}$
+
+M-M-CZ{\_}HWE-CNOT
 
@@
 Best ansatz on average train R$^{2}$/test R$^{2}$
+A2_Hadamard
 
@@
 
-\subsection{DDCC}
 Structure

### 2025-03-18 src/qregress/quantum/Quantum.py

@@ -1,0 +1,408 @@
+from pennylane import numpy as np
+from pennylane_qiskit import qiskit_session
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from scipy.optimize import minimize, basinhopping
+from sklearn.metrics import mean_squared_error
+from tqdm import tqdm
+import joblib
+import json
+import numpy as np
+import os
+import pennylane as qml
+import time
+
+
+class BasinBounds:
+    def __init__(self, xmax=np.pi, xmin=-np.pi):
+        self.xmax = xmax
+        self.xmin = xmin
+
+    def __call__(self, **kwargs):
+        x = kwargs["x_new"]
+        tmax = bool(np.all(x <= self.xmax))
+        tmin = bool(np.all(x >= self.xmin))
+        return tmax and tmin
+class QuantumRegressor:
+    """
+    Machine learning model based on quantum circuit learning.
+
+    Methods
+    ------
+    fit(x, y, initial_parameters=None, detailed_results=False, load_state=None, callback_interval=None)
+        Fits the model instance to the given x and y data.
+    predict(x)
+        Predicts y values for a given array of input data based on previous training.
+
+    """
+
+    def __init__(
+            self,
+            encoder,
+            variational,
+            num_qubits,
+            optimizer: str = 'COBYLA',
+            max_iterations: int = None,
+            tol: float = 1e-8,
+            device: str = 'default.qubit',
+            backend: str = None,
+            postprocess: str = None,
+            error_mitigation=None,
+            scale_factors: list = None,
+            
+            shots: int = None,
+            re_upload_depth: int = 1,
+            f: float = 1.,
+            alpha: float = 0.,
+            beta: float = 0,
+            token: str = None,
+            batch_size: int=None,
+            njobs: int=None):
+        self.hyperparameters = {'f': f, 'alpha': alpha, 'beta': beta}
+        if scale_factors is None:
+            scale_factors = [1, 3, 5]
+        self.callback_interval = None
+        self.x = None
+        self.y = None
+        self.params = None
+        self._batch_size = batch_size
+        self._re_upload_depth = re_upload_depth
+        self.error_mitigation = error_mitigation
+        self.num_qubits = num_qubits
+        self.max_iterations = max_iterations
+        if postprocess == 'None':
[…]

### 2025-03-18 src/qregress/quantum/circuits/__init__.py

@@ -1,0 +1,5 @@
+# src/quantum/circuits/__init__.py
+from . import Ansatz
+from . import Encoders
+from . import Old_Ansatz
+

### 2025-03-18 vikiscript.sh

@@ -1,29 +1,0 @@
-#! /bin/bash
-
-for i in */; do
-    name=${i%/}
-    
-    # Extracting the parent directory name
-    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
-    
-    cat > ${name}.sub <<EOF
-#! /bin/bash
-#SBATCH -t 23:59:00
-#SBATCH -J ${name}
-#SBATCH -N 1
-#SBATCH -n 80
-#SBATCH --account=def-fekl
-
-module load python/3.9.8
-source /home/j/jacobsen/vikikrpd/Softwares/qregress/qregress_env/bin/activate 
-
-cd $(pwd)/$name
-
-python /home/j/jacobsen/vikikrpd/Softwares/qregress/main.py --settings ${name}.json --train_set /home/j/jacobsen/vikikrpd/Softwares/qregress/database/processed/16feats/${settings_folder}/BSE49_16feats_train.bin --test_set /home/j/jacobsen/vikikrpd/Softwares/qregress/database/processed/16feats/${settings_folder}/BSE49_16feats_test.bin --scaler /home/j/jacobsen/vikikrpd/Softwares/qregress/database/processed/16feats/${settings_folder}/BSE49_16feats_scaler.bin >> ${name}.out 2>&1
-
-cd ..
-touch ${name}.done
-
-EOF
-    echo "Done ${name}.sub"
-done

### 2025-03-19 manuscript/main.tex
spring cleaning

@@
 Best ansatz on average train R$^{2}$/test R$^{2}$
-A2_Hadamard
+A2{\_}Hadamard
 

### 2025-03-19 BSE_learning_curves/16/0.1/bs.sh

@@ -1,5 +1,0 @@
-#!/bin/bash
-export OMP_NUM_THREADS=16
-cd /home/grierjones/5qubit/A1-A1-CZ_Efficient-CRZ
-python3 /home/grierjones/5qubit/main.py --settings /home/grierjones/5qubit/A1-A1-CZ_Efficient-CRZ/A1-A1-CZ_Efficient-CRZ.json --train_set /home/grierjones/5qubit/PCA5_0.8_Morgan_train.bin --test_set /home/grierjones/5qubit/PCA5_0.8_Morgan_test.bin --scaler /home/grierjones/5qubit/PCA5_0.8_Morgan_scaler.bin --save_path /home/grierjones/5qubit/A1-A1-CZ_Efficient-CRZ --save_circuits True 
-cd /home/grierjones/5qubit/

### 2025-03-19 BSE_learning_curves/16/0.3/onemore/checkall.sh

@@ -1,5 +1,0 @@
-dir=$(find . -mindepth 1 -maxdepth 1 -type d)
-
-for d in $dir; do
- python3 ../view_loss.py --path $d/1_model_log.csv
-done

### 2025-03-19 BSE_learning_curves/16/0.7/rerun.sh

@@ -1,29 +1,0 @@
-#!/bin/bash
-# Grab iteration informations
-dir=$(find . -maxdepth 2 -name "partial*")
-#month="Sep"
-#month=$(date +%b)
-
-
-# Loop over directories
-for i in $dir; do
- path=$(dirname $i)
- echo $path
- sumiter=0
- # Loop over existing model_log.csv files to find the final iterations
- for j in ${path}/*model_log.csv; do
-   echo $j
-   raniter=$(cat $j  | grep -iE "Sep|Oct" | tail -n 1  | cut -d',' -f2)
-   sumiter=$((sumiter + raniter + 1)) 
-   echo "$j has $raniter iterations"
-   echo $sumiter
- done
- # Write the remaining iterations to file
- remain=$((1000 - sumiter))
- echo "Iterations left: $remain"
- #mv ${path}/model_log.csv ${path}/1_model_log.csv
- #sed -i 's/"MAX_ITER": 1000/"MAX_ITER": '$remain'/g' ${path}/*.json
- echo $(cat ${path}/*.json)
- echo 
-done
-

### 2025-03-19 BSE_learning_curves/16/0.7/salloc.sh

@@ -1,2 +1,0 @@
-#! /bin/bash
-salloc -t 7-00:00:00 -J ${errorname}_linear_${name} -N 1 -n 64 --account=rrg-jacobsen-ab

### 2025-03-19 BSE_learning_curves/16/0.8/run.sh

@@ -1,15 +1,0 @@
-#! /bin/bash
-cwd=$(pwd)
-errorname=$(basename `pwd`)
-echo $cwd
-i="A2_Hadamard/"
-name=${i%/}
-# Extracting the parent directory name
-settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
-path="${cwd}/${name}"
-export OMP_NUM_THREADS=64
-cd $(pwd)/$name
-python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.8_Morgan_train.bin --test_set ${cwd}/PCA16_0.8_Morgan_test.bin --scaler ${cwd}/PCA16_0.8_Morgan_scaler.bin  > ${name}.out 2>&1
-cd ..
-touch ${name}.done
-

### 2025-03-19 BSE_learning_curves/16/16/0.5/movedone.sh

@@ -1,7 +1,0 @@
-finished=$(find . -name "*results.json")
-
-for i in $finished; do
-  fin=$(dirname $i)
-  echo $fin
-  mv -f $fin finished/
-done

### 2025-03-19 BSE_learning_curves/16/16/0.5/run.sh

@@ -1,15 +1,0 @@
-#! /bin/bash
-cwd=$(pwd)
-errorname=$(basename `pwd`)
-echo $cwd
-i="A2_Hadamard/"
-name=${i%/}
-# Extracting the parent directory name
-settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
-path="${cwd}/${name}"
-export OMP_NUM_THREADS=64
-cd $(pwd)/$name
-python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.5_Morgan_train.bin --test_set ${cwd}/PCA16_0.5_Morgan_test.bin --scaler ${cwd}/PCA16_0.5_Morgan_scaler.bin  --resume_file ${path}/partial_state_model.bin > ${name}.out 2>&1
-cd ..
-touch ${name}.done
-

### 2025-03-19 BSE_learning_curves/16/16/0.8/kill.sh

@@ -1,9 +1,0 @@
-#!/bin/bash
-mkdir onemore
-mv -f ./A2-A2-CNOT_HWE-CZ onemore/
-mv -f ./A2-A2-CZ_HWE-CZ  onemore/
-mv -f ./M-A2-CZ_HWE-CNOT onemore/
-mv -f ./M-A2-CZ_HWE-CZ onemore/
-mv -f ./M-M-CNOT_HWE-CNOT onemore/
-mv -f ./M-M-CNOT_HWE-CZ onemore/
-mv -f ./M-M-CZ_Hadamard onemore/

### 2025-03-19 BSE_learning_curves/16/16/done/0.1/run.sh

@@ -1,15 +1,0 @@
-#! /bin/bash
-cwd=$(pwd)
-errorname=$(basename `pwd`)
-echo $cwd
-i="A2_Hadamard/"
-name=${i%/}
-# Extracting the parent directory name
-settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
-path="${cwd}/${name}"
-export OMP_NUM_THREADS=64
-cd $(pwd)/$name
-python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_0.1_Morgan_train.bin --test_set ${cwd}/PCA16_0.1_Morgan_test.bin --scaler ${cwd}/PCA16_0.1_Morgan_scaler.bin --resume_file ${path}/final_state_model.bin > ${name}.out 2>&1
-cd ..
-touch ${name}.done
-

### 2025-03-19 BSE_learning_curves/16/runall.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-dirs=$(find .  -maxdepth 1 -mindepth 1 -type d | sort)
-
-for i in $dirs; do
- if [[ "$i" != "./done" ]]; then
-  echo $i
-  cd $i
-  bash run.sh
-  cd ../
- fi
-done

### 2025-03-19 BSE_learning_curves/5/submitall.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-for i in 0.1 0.3 0.5 0.7 0.8; do
-  echo $i
-  cd $i
-  echo $(pwd)
-  rm *done *.o* *.e* *sub
-  bash run.sh
-  rm __pycache__.sub quantum.sub helperfiles.sub
-  find . -name "*sub" -exec sbatch {} \;
-  cd ../
-done

### 2025-03-19 Pennylane_to_Qiskit/convert_ML.py

@@ -1,456 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-# In[ ]:
-
-
-import os
-n_jobs = 16
-os.environ["OMP_NUM_THREADS"] = str(n_jobs)
-import joblib
-import click
-import json
-import time
-
-import itertools
-import collections.abc
-import sys
-from tqdm import tqdm
-# !{sys.executable} -m pip install pylatexenc
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-import pennylane as qml
-from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
-from scipy.optimize import minimize
-# Qiskit
-from qiskit import QuantumCircuit
-from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
-from qiskit.primitives import StatevectorEstimator
-from qiskit.circuit import Parameter, ParameterVector
-from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
-from qiskit.quantum_info import SparsePauliOp
-from qiskit_ibm_runtime import EstimatorV2 as Estimator
-from qiskit_ibm_runtime import QiskitRuntimeService
-from qiskit_aer.noise import NoiseModel
-from qiskit_ibm_runtime.fake_provider import FakeQuebec
-from qiskit_ibm_runtime import Session
-
-
-from joblib import dump, load
-
-
-# In[ ]:
-
-
-def mitarai(quantumcircuit,num_wires,paramname='x'):
-    # encoding as proposed by Mitarai et al.
-    num_features = num_wires
-    features = ParameterVector(paramname,num_features*2)
-    for i in range(num_wires):
-        feature_idx = i % num_features  # Calculate the feature index using modulo
-        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
-        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
-
-
-def double_angle(quantumcircuit, num_wires,paramname='x'):
-    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
-    #  the features are encoded 1-1 onto the qubits
-    #  if more wires are passed then features the remaining wires will be filled from the beginning of the feature list
-    num_features = num_wires
[…]

### 2025-03-19 Pennylane_to_Qiskit/convert_ML_SPSA.py

@@ -1,443 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-# In[1]:
-
-
-import os
-n_jobs = 16
-os.environ["OMP_NUM_THREADS"] = str(n_jobs)
-import joblib
-import click
-import json
-import time
-
-import itertools
-import collections.abc
-import sys
-from tqdm import tqdm
-# !{sys.executable} -m pip install qiskit-machine-learning
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-import pennylane as qml
-from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
-from scipy.optimize import minimize
-# Qiskit
-from qiskit import QuantumCircuit
-from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
-from qiskit.primitives import StatevectorEstimator
-from qiskit.circuit import Parameter, ParameterVector
-from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
-from qiskit.quantum_info import SparsePauliOp
-from qiskit_ibm_runtime import EstimatorV2 as Estimator
-from qiskit_ibm_runtime import QiskitRuntimeService
-from qiskit_aer.noise import NoiseModel
-from qiskit_ibm_runtime.fake_provider import FakeQuebec
-from qiskit_ibm_runtime import Session, Batch
-from qiskit_machine_learning.optimizers import SPSA, Minimizer
-
-
-from joblib import dump, load
-
-
-# In[2]:
-
-
-def mitarai(quantumcircuit,num_wires,paramname='x'):
-    # encoding as proposed by Mitarai et al.
-    num_features = num_wires
-    features = ParameterVector(paramname,num_features*2)
-    for i in range(num_wires):
-        feature_idx = i % num_features  # Calculate the feature index using modulo
-        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
-        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
-
-
-def double_angle(quantumcircuit, num_wires,paramname='x'):
-    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
-    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-03-19 Pennylane_to_Qiskit/convert_ML_batched.py

@@ -1,543 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-# In[ ]:
-
-
-import os
-n_jobs = 16
-os.environ["OMP_NUM_THREADS"] = str(n_jobs)
-import joblib
-import click
-import json
-import time
-
-import itertools
-import collections.abc
-import sys
-from tqdm import tqdm
-# !{sys.executable} -m pip install --upgrade qiskit-machine-learning
-
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-import pennylane as qml
-from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
-from scipy.optimize import minimize
-# Qiskit
-from qiskit import QuantumCircuit
-from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
-from qiskit.primitives import StatevectorEstimator
-from qiskit.circuit import Parameter, ParameterVector
-from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
-from qiskit.quantum_info import SparsePauliOp
-from qiskit_ibm_runtime import EstimatorV2 as Estimator
-from qiskit_ibm_runtime import QiskitRuntimeService
-from qiskit_aer.noise import NoiseModel
-from qiskit_ibm_runtime.fake_provider import FakeQuebec
-from qiskit_ibm_runtime import Session, Batch
-# from qiskit_machine_learning.optimizers import SPSA, Minimizer
-
-
-from joblib import dump, load
-
-
-# In[ ]:
-
-
-def mitarai(quantumcircuit,num_wires,paramname='x'):
-    # encoding as proposed by Mitarai et al.
-    num_features = num_wires
-    features = ParameterVector(paramname,num_features*2)
-    for i in range(num_wires):
-        feature_idx = i % num_features  # Calculate the feature index using modulo
-        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
-        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
-
-
-def double_angle(quantumcircuit, num_wires,paramname='x'):
-    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
-    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-03-19 Pennylane_to_Qiskit/linear_tests/opt_level/move.sh

@@ -1,7 +1,0 @@
-dir="./3"
-mv partial_state_model.bin ${dir}
-mv model_log.csv ${dir}
-mv IQP_Full-Pauli-CRZ_plot.svg ${dir}
-mv IQP_Full-Pauli-CRZ_1D_plot.svg ${dir}
-mv IQP_Full-Pauli-CRZ_results.json ${dir}
-mv IQP_Full-Pauli-CRZ_predicted_values.csv ${dir}

### 2025-03-19 Pennylane_to_Qiskit/real_qiskit_class/QiskitRegressor.py

@@ -1,417 +1,0 @@
-import numpy as np
-import time
-import joblib
-from joblib import dump, load
-import os
-from tqdm.notebook import tqdm
-from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
-from scipy.optimize import minimize
-from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
-from qiskit.primitives import StatevectorEstimator
-from qiskit.circuit import Parameter, ParameterVector
-from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
-from qiskit.quantum_info import SparsePauliOp
-from qiskit_ibm_runtime import EstimatorV2 as Estimator
-from qiskit_ibm_runtime import QiskitRuntimeService
-from qiskit_aer import AerSimulator
-from qiskit_aer.noise import NoiseModel
-from qiskit_ibm_runtime.fake_provider import FakeQuebec
-from qiskit_ibm_runtime import Batch
-
-class QiskitRegressor:
-    def __init__(self,
-                 quantumcircuit,
-                 numqubits,
-                 ansatz_layers,
-                 reuploaddepth,
-                 backend,
-                 observables_labels,
-                 channel = None,
-                 instance = None,
-                 parameterpath = None,
-                 optimization_level = 2,
-                 resilience_level = 1,
-                 shots = 1024,
-                 iterations = 1000,
-                 verbose = False,
-                 n_jobs = None
-                ):
-        '''
-        parameters
-        ----------
-        quantumcircuit: 
-            Qiskit quantum circuit
-
-        numqubits: int
-            Number of qubits before mapping
-            
-        ansatz_layers: int
-            Number of ansatz layers (AL)
-
-        reuploaddepth: int
-            Re-upload depth (RUD)
-
-        backend: str
-            Options: statevector, fake, real
-
-        observables_labels: str
-            Observables mapped to original circuit before ISA pass
-
-        channel: str
-            IBM Quantum channel
-
-        instance: str
-            IBM Quantum instance
-
-        parameterpath: str
-        
-        optimization_level: int
-            Qiskit circuit optimization level (default=2; details at "https://docs.quantum.ibm.com/guides/set-optimization")
-            
-        resilience_level: int
-            Qiskit error mitigation level (default=2; details at "https://docs.quantum.ibm.com/guides/configure-error-mitigation"       
-        
-        shots: int
-            Number of shots (multiples of 1024 preferred)
-
-        iterations: int
-            Number of training cycles
-
-        verbose: bool
[…]

### 2025-03-19 Pennylane_to_Qiskit/serverless_run/machine_learning.py

@@ -1,339 +1,0 @@
-import time
-import json
-import joblib
-import os
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-from tqdm import tqdm
-from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
-from sklearn.exceptions import InconsistentVersionWarning
-from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
-from scipy.optimize import minimize
-from qiskit_ibm_runtime import (Batch, EstimatorV2 as Estimator)
-import warnings
-warnings.filterwarnings("ignore", category=UserWarning, module="qiskit_ibm_runtime")
-warnings.filterwarnings("ignore",category=DeprecationWarning,module="qiskit_aer.backends.aer_compiler")
-warnings.filterwarnings("ignore", category=InconsistentVersionWarning)
-
-def map2qiskit(quantum_circuit, num_qubits, X):
-    '''
-    Map features to Qiskit Circuit
-    
-    parameters
-    ----------
-    quantum_circuit: qiskit.circuit.quantumcircuit.QuantumCircuit
-        Qiskit Quantum Circuit
-        
-    num_qubits: int
-        Number of qubits
-        
-    X: numpy.ndarray
-        Feature matrix
-
-    returns
-    -------
-    quantum_circuit: qiskit.circuit.quantumcircuit.QuantumCircuit
-        Qiskit Quantum Circuit
-    
-    '''
-    featparameters = dict([(i,X[idx % num_qubits]) for idx,i in enumerate(quantum_circuit.parameters) if 'x' in i.name])
-    quantum_circuit = quantum_circuit.assign_parameters(featparameters)
-    return quantum_circuit
-
-
-def get_results(job):
-    '''
-    Get the results of a quantum job from IBM Quantum
-    
-    parameters
-    ----------
-    job: qiskit.primitives.primitive_job.PrimitiveJob
-        Job submitted to the IBM Quantum device
-
-    returns
-    -------
-    pred: numpy.ndarray
-        Predicted values
-    
-    '''
-    result = job.result()
-    pred = np.vstack([r.data.evs for r in result]).flatten()
-    return pred    
-
-def batched_pred(parameters, quantum_circuit, hamiltonian, num_qubits, X, backend, shots, resilience_level, n_jobs):
-    '''
-    Function to predict quantum circuits in batches
-
-    parameters
-    ----------
[…]

### 2025-03-19 Pennylane_to_Qiskit/serverless_run/transpile_remote.py

@@ -1,43 +1,0 @@
-from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
-from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
-
-def transpile_remote(initial_circuit,backend,optimization_level=0):
-    '''
-    Remote transpilation based on https://docs.quantum.ibm.com/guides/serverless-first-program
-
-    parameters
-    ----------
-    initial_circuit: qiskit.circuit.quantumcircuit.QuantumCircuit
-        Unmapped circuit
-        
-    optimization_level: int
-        Circuit optimization level
-    
-    backend: qiskit_ibm_runtime.ibm_backend.IBMBackend
-
-        Backend can be real (e.g. qiskit_ibm_runtime.ibm_backend.IBMBackend) or fake (e.g. qiskit_ibm_runtime.fake_provider.backends.quebec.fake_quebec.FakeQuebec)
-
-    returns
-    -------
-    qc: qiskit.circuit.quantumcircuit.QuantumCircuit
-        Mapped circuit
-
-    
-    mapped_observables: list
-        Contains the desired mapped observables 
-    
-    '''            
-    
-    num_qubits = initial_circuit.num_qubits
-    
-    # Generate pass manager
-    target = backend.target
-    pm = generate_preset_pass_manager(target=target, optimization_level=optimization_level)
-    qc = pm.run(initial_circuit)
-
-    # Observables
-    observables_labels = ''.join(['I']*(num_qubits-1))+"Z"
-    observables = [SparsePauliOp(observables_labels)]
-    mapped_observables = [observable.apply_layout(qc.layout) for observable in observables]
-    
-    return qc, mapped_observables

### 2025-03-19 Pennylane_to_Qiskit/test_qiskit/runall.sh

@@ -1,18 +1,0 @@
-#!/bin/bash
-#optimization_level = 3
-#shots = 1024.0
-#resilience_level = 1
-
-for ol in 0;do
- for rl in {0..2};do
-  dirname="ol${ol}_rl${rl}"
-  if [ ! -d ${dirname} ] ; then
-    echo "${dirname} does not exist"
-    mkdir ${dirname}
-  else
-    echo "${dirname} does exist"
-  fi
-  papermill convert_ML_batched.ipynb ${dirname}/convert_ML_batched.ipynb -r optimization_level ${ol} -r resilience_level ${rl}
-  mv ./model_log.csv ./final_state_model.bin ./A2_HWE-CNOT_plot.svg ./A2_HWE-CNOT_results.json ./A2_HWE-CNOT_predicted_values.csv ${dirname}/ 
- done
-done

### 2025-03-19 debug/dummy.py

@@ -1,35 +1,0 @@
-import sys
-# !{sys.executable} -m pip install "git+https://github.com/PennyLaneAI/pennylane-qiskit.git#egg=pennylane-qiskit" --force-reinstall
-import pennylane as qml
-from pennylane import numpy as pnp
-from qiskit_ibm_runtime import QiskitRuntimeService
-from pennylane_qiskit.qiskit_device import qiskit_session
-# QiskitRuntimeService.save_account(channel="ibm_quantum", token=token, overwrite=True)
-# To access saved credentials for the IBM quantum channel and select an instance
-service = QiskitRuntimeService(channel="ibm_quantum")
-backend = service.backend(name= 'ibm_quebec')
-dev = qml.device(
-    "qiskit.remote",
-    wires=127,
-    backend=backend,
-    resilience_level=1,
-    optimization_level=1,
-    seed_transpiler=42
-)
-
-with qiskit_session(dev,max_time='2h') as session:
-    print(session.details())
-
-    # Add your code here
-    
-    @qml.qnode(dev)
-    def circuit(theta):
-      qml.RX(theta,wires=0)
-      return qml.expval(qml.PauliZ(0))
-    
-    opt = qml.GradientDescentOptimizer(stepsize=0.3)
-    
-    theta = pnp.array(0.5)
-    for i in range(10):
-      theta = opt.step(circuit,theta)
-      print('theta: ', theta, 'circuit: ', circuit(theta))

### 2025-03-19 debug/min_ex.py

@@ -1,211 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-
-
-#!/usr/bin/env python
-# coding: utf-8
-import sys 
-# !{sys.executable} -m pip install qiskit"[qasm3-import]"
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from torch.utils.data import Dataset, DataLoader
-import numpy as np
-from sklearn.metrics import mean_squared_error, mean_absolute_error, r2_score
-from sklearn.model_selection import train_test_split
-from sklearn.preprocessing import StandardScaler
-import joblib
-import click
-import json
-import time
-import os
-import itertools
-import collections.abc
-import pandas as pd
-import pennylane as qml
-from pennylane_qiskit import qiskit_device
-from tqdm import tqdm
-from qiskit_ibm_runtime import QiskitRuntimeService, Session
-from qiskit_ibm_runtime.fake_provider import FakeQuebec
-from qiskit_aer.noise import NoiseModel
-from qiskit_aer import AerSimulator
-
-os.environ["OMP_NUM_THREADS"] = "12"
-
-
-
-
-
-# Set random seed for reproducibility
-np.random.seed(42)
-torch.manual_seed(42)
-generator = np.random.default_rng(12958234)
-
-# Synthetic data
-X=generator.uniform(-1, 1, (100,5))
-y=generator.uniform(-1, 1, (100,))
-X_train, X_test, y_train, y_test = X[:80,:],X[80:,:],y[:80],y[80:]
-print(X_train.shape,X_test.shape)
-
-
-
-# Define custom Dataset
-class RegressionDataset(Dataset):
-    def __init__(self, features, targets):
-        self.X = torch.from_numpy(features).float()
-        self.y = torch.from_numpy(targets).float()
-    
-    def __len__(self):
-        return len(self.X)
-    
-    def __getitem__(self, idx):
-        return self.X[idx], self.y[idx]
-
-# Create DataLoaders
-batch_size = None 
-train_dataset = RegressionDataset(X_train, y_train)
-test_dataset = RegressionDataset(X_test, y_test)
-train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
-test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=False)
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-# Initial ize device and circuit
-num_qubits=5
-re_upload_depth=1
-n_layers=1
-
[…]

### 2025-03-19 debug/pytorch.py

@@ -1,142 +1,0 @@
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from torch.utils.data import Dataset, DataLoader
-import numpy as np
-import matplotlib.pyplot as plt
-from sklearn.metrics import mean_squared_error, mean_absolute_error
-from sklearn.model_selection import train_test_split
-from sklearn.preprocessing import StandardScaler
-
-# Set random seed for reproducibility
-np.random.seed(42)
-torch.manual_seed(42)
-
-# 1. Generate synthetic data
-def generate_data(n_samples=1000):
-    X = np.random.uniform(-10, 10, (n_samples, 1))
-    y = 3 * X.squeeze()**2 + 2 * X.squeeze() + 1 + np.random.normal(0, 10, n_samples)
-    return X.astype(np.float32), y.astype(np.float32)
-
-X, y = generate_data(n_samples=1000)
-
-# 2. Split into training and testing
-X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2, random_state=42)
-
-# 3. Standardize features
-scaler = StandardScaler()
-X_train = scaler.fit_transform(X_train)
-X_test = scaler.transform(X_test)
-
-# 4. Define custom Dataset
-class RegressionDataset(Dataset):
-    def __init__(self, features, targets):
-        self.X = torch.from_numpy(features)
-        self.y = torch.from_numpy(targets).unsqueeze(1)
-    
-    def __len__(self):
-        return len(self.X)
-    
-    def __getitem__(self, idx):
-        return self.X[idx], self.y[idx]
-
-# 5. Create DataLoaders
-batch_size = 32
-train_dataset = RegressionDataset(X_train, y_train)
-test_dataset = RegressionDataset(X_test, y_test)
-train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
-test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=False)
-
-# 6. Define the model
-class SimpleRegressor(nn.Module):
-    def __init__(self, input_dim, hidden_dim):
-        super(SimpleRegressor, self).__init__()
-        self.net = nn.Sequential(
-            nn.Linear(input_dim, hidden_dim),
-            nn.ReLU(),
-            nn.Linear(hidden_dim, hidden_dim),
-            nn.ReLU(),
[…]

### 2025-03-19 debug/pytorch_test.py

@@ -1,488 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-# In[1]:
-
-
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from torch.utils.data import Dataset, DataLoader
-import numpy as np
-import matplotlib.pyplot as plt
-from sklearn.metrics import mean_squared_error, mean_absolute_error, r2_score
-from sklearn.model_selection import train_test_split
-from sklearn.preprocessing import StandardScaler
-import joblib
-# Set random seed for reproducibility
-np.random.seed(42)
-torch.manual_seed(42)
-
-
-import click
-import json
-import time
-import os
-import itertools
-import collections.abc
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import pennylane as qml
-from sklearn.metrics import mean_squared_error
-from sklearn.model_selection import KFold
-# from qiskit_ibm_provider import IBMProvider
-
-from quantum.Evaluate import evaluate
-from settings import ANSATZ_LIST, ENCODER_LIST
-from quantum.Quantum import QuantumRegressor
-
-from tqdm import tqdm
-
-os.environ["OMP_NUM_THREADS"] = "12"
-
-
-# In[2]:
-
-
-settings="./A2_HWE-CNOT/A2_HWE-CNOT.json"
-train_set="./PCA5_0.8_Morgan_train.bin"
-test_set="./PCA5_0.8_Morgan_test.bin"
-scaler="./PCA5_0.8_Morgan_scaler.bin"
-
-
-# In[3]:
-
-
-with open(train_set,'rb') as f:
-    TRAIN = joblib.load(f)
-
-with open(test_set,'rb') as f:
-    TEST = joblib.load(f)
-
-with open(scaler,'rb') as f:
-    SCALER = joblib.load(f)
-
-
-
-# In[4]:
-
-
-X_train, X_test, y_train, y_test = TRAIN['X'],TEST['X'],TRAIN['y'],TEST['y']
-
-
-# In[5]:
-
-
-# 4. Define custom Dataset
-class RegressionDataset(Dataset):
-    def __init__(self, features, targets):
-        self.X = torch.from_numpy(features).float()
-        self.y = torch.from_numpy(targets).float()
-    
-    def __len__(self):
-        return len(self.X)
-    
-    def __getitem__(self, idx):
-        return self.X[idx], self.y[idx]
-
-# 5. Create DataLoaders
[…]

### 2025-03-19 debug/view_combined.py

@@ -1,34 +1,0 @@
-#!/usr/bin/env python3
-import click
-import numpy as np
-import matplotlib.pyplot as plt
-from glob import glob
-import os
-
-@click.command()
-@click.option('--path', required=True, type=click.Path(exists=True), help='Path to model_log.csv; e.g. A2_HWE-CNOT/')
-def main(path):
-    loss = []
-    for i in sorted(glob(os.path.join(path, '*log.csv'))):
-        print(f"Processing file: {i}")
-        loss.append(split(i)[:, 1])  # Get only the loss values (assumed to be in the second column)
-    plt.plot(np.hstack(loss))
-    plt.xlabel("Iteration")
-    plt.ylabel("Loss")
-    plt.title("Loss Curve")
-    plt.show()
-
-def split(path):
-    """Helper function to read CSV file and extract required columns."""
-    save = []
-    with open(path, 'r') as f:
-        for line in f:
-            if ':' in line:
-                split_line = line.strip().split(',')
-                # Assuming the structure of each line is: [timestamp, loss_value, ...]
-                save.append((float(split_line[1]), float(split_line[2])))
-    return np.array(save)
-
-if __name__ == '__main__':
-    main()
-

### 2025-03-19 dev/Pennylane_to_Qiskit/convert_ML.py

@@ -1,0 +1,456 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[ ]:
+
+
+import os
+n_jobs = 16
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm import tqdm
+# !{sys.executable} -m pip install pylatexenc
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+from scipy.optimize import minimize
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Session
+
+
+from joblib import dump, load
+
+
+# In[ ]:
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
+    #  if more wires are passed then features the remaining wires will be filled from the beginning of the feature list
+    num_features = num_wires
[…]

### 2025-03-19 dev/Pennylane_to_Qiskit/convert_ML_batched.py

@@ -1,0 +1,543 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[ ]:
+
+
+import os
+n_jobs = 16
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm import tqdm
+# !{sys.executable} -m pip install --upgrade qiskit-machine-learning
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+from scipy.optimize import minimize
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Session, Batch
+# from qiskit_machine_learning.optimizers import SPSA, Minimizer
+
+
+from joblib import dump, load
+
+
+# In[ ]:
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-03-19 dev/Pennylane_to_Qiskit/linear_tests/error_mitigation/without/quantum/Quantum.py

@@ -1,0 +1,380 @@
+import pennylane as qml
+import numpy as np
+from pennylane import numpy as np
+from sklearn.metrics import mean_squared_error
+from scipy.optimize import minimize, basinhopping
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+
+
+
+from qiskit_aer import AerSimulator
+import joblib
+
+import os
+import json
+import time
+from tqdm import tqdm
+
+
+class BasinBounds:
+    def __init__(self, xmax=np.pi, xmin=-np.pi):
+        self.xmax = xmax
+        self.xmin = xmin
+
+    def __call__(self, **kwargs):
+        x = kwargs["x_new"]
+        tmax = bool(np.all(x <= self.xmax))
+        tmin = bool(np.all(x >= self.xmin))
+        return tmax and tmin
+
+
+class QuantumRegressor:
+    """
+    Machine learning model based on quantum circuit learning.
+
+    Methods
+    ------
+    fit(x, y, initial_parameters=None, detailed_results=False, load_state=None, callback_interval=None)
+        Fits the model instance to the given x and y data.
+    predict(x)
+        Predicts y values for a given array of input data based on previous training.
+
+    """
+
+    def __init__(
+            self,
+            encoder,
+            variational,
+            num_qubits,
+            optimizer: str = 'COBYLA',
+            max_iterations: int = None,
+            tol: float = 1e-8,
+            device: str = 'default.qubit',
+            backend: str = None,
+            postprocess: str = None,
+            error_mitigation=None,
+            scale_factors: list = None,
+            
+            shots: int = None,
+            re_upload_depth: int = 1,
+            f: float = 1.,
+            alpha: float = 0.,
+            beta: float = 0,
+            token: str = None,
+            batch_size: int=None,
+            njobs: int=None):
+        self.hyperparameters = {'f': f, 'alpha': alpha, 'beta': beta}
+        if scale_factors is None:
+            scale_factors = [1, 3, 5]
+        self.callback_interval = None
+        self.x = None
+        self.y = None
+        self.params = None
+        self._batch_size = batch_size
+        self._re_upload_depth = re_upload_depth
+        self.error_mitigation = error_mitigation
+        self.num_qubits = num_qubits
+        self.max_iterations = max_iterations
+        if postprocess == 'None':
+            postprocess = None
[…]

### 2025-03-19 dev/Pennylane_to_Qiskit/serverless_run/circuit.py

@@ -1,0 +1,132 @@
+import numpy as np
+from qiskit import QuantumCircuit
+from qiskit.circuit import Parameter, ParameterVector
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    """
+    parameters
+    ----------
+    quantumcircuit: qiskit.circuit.quantumcircuit.QuantumCircuit
+        Quantum circuit
+        
+    num_wires: int
+        Number of wires
+        
+    paramname: str
+        (default:'x')
+    """
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    """
+    parameters
+    ----------
+    quantumcircuit: qiskit.circuit.quantumcircuit.QuantumCircuit
+        Quantum circuit
+        
+    num_wires: int
+        Number of wires
+        
+    """    
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
+    #  if more wires are passed then features the remaining wires will be filled from the beginning of the feature list
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_index = i % num_features
+        quantumcircuit.ry(features[feature_index], i)
+        quantumcircuit.rz(features[feature_index], i)
+
+def entangle_cnot(quantumcircuit,num_wires):
+    """
+    parameters
+    ----------
+    quantumcircuit: qiskit.circuit.quantumcircuit.QuantumCircuit
+        Quantum circuit
+        
+    num_wires: int
+        Number of wires
+        
+    paramname: str
+        (default:'x')
+    """    
+    #  entangles all of the wires in a circular fashion using cnot gates
+    for i in range(num_wires):
+        
+        if i == num_wires - 1:
+            quantumcircuit.cx(i, 0)
+        else:
+            quantumcircuit.cx(i, i+1)
+
+
[…]

### 2025-03-19 dev/Pennylane_to_Qiskit/test_qiskit/runall.sh

@@ -1,0 +1,18 @@
+#!/bin/bash
+#optimization_level = 3
+#shots = 1024.0
+#resilience_level = 1
+
+for ol in 0;do
+ for rl in {0..2};do
+  dirname="ol${ol}_rl${rl}"
+  if [ ! -d ${dirname} ] ; then
+    echo "${dirname} does not exist"
+    mkdir ${dirname}
+  else
+    echo "${dirname} does exist"
+  fi
+  papermill convert_ML_batched.ipynb ${dirname}/convert_ML_batched.ipynb -r optimization_level ${ol} -r resilience_level ${rl}
+  mv ./model_log.csv ./final_state_model.bin ./A2_HWE-CNOT_plot.svg ./A2_HWE-CNOT_results.json ./A2_HWE-CNOT_predicted_values.csv ${dirname}/ 
+ done
+done

### 2025-03-19 dev/debug/min_ex.py

@@ -1,0 +1,211 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+
+#!/usr/bin/env python
+# coding: utf-8
+import sys 
+# !{sys.executable} -m pip install qiskit"[qasm3-import]"
+import torch
+import torch.nn as nn
+import torch.optim as optim
+from torch.utils.data import Dataset, DataLoader
+import numpy as np
+from sklearn.metrics import mean_squared_error, mean_absolute_error, r2_score
+from sklearn.model_selection import train_test_split
+from sklearn.preprocessing import StandardScaler
+import joblib
+import click
+import json
+import time
+import os
+import itertools
+import collections.abc
+import pandas as pd
+import pennylane as qml
+from pennylane_qiskit import qiskit_device
+from tqdm import tqdm
+from qiskit_ibm_runtime import QiskitRuntimeService, Session
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_aer.noise import NoiseModel
+from qiskit_aer import AerSimulator
+
+os.environ["OMP_NUM_THREADS"] = "12"
+
+
+
+
+
+# Set random seed for reproducibility
+np.random.seed(42)
+torch.manual_seed(42)
+generator = np.random.default_rng(12958234)
+
+# Synthetic data
+X=generator.uniform(-1, 1, (100,5))
+y=generator.uniform(-1, 1, (100,))
+X_train, X_test, y_train, y_test = X[:80,:],X[80:,:],y[:80],y[80:]
+print(X_train.shape,X_test.shape)
+
+
+
+# Define custom Dataset
+class RegressionDataset(Dataset):
+    def __init__(self, features, targets):
+        self.X = torch.from_numpy(features).float()
+        self.y = torch.from_numpy(targets).float()
+    
+    def __len__(self):
+        return len(self.X)
+    
+    def __getitem__(self, idx):
+        return self.X[idx], self.y[idx]
+
+# Create DataLoaders
+batch_size = None 
+train_dataset = RegressionDataset(X_train, y_train)
+test_dataset = RegressionDataset(X_test, y_test)
+train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
+test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=False)
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+# Initial ize device and circuit
+num_qubits=5
+re_upload_depth=1
+n_layers=1
+
[…]

### 2025-03-19 dev/debug/pytorch.py

@@ -1,0 +1,142 @@
+import torch
+import torch.nn as nn
+import torch.optim as optim
+from torch.utils.data import Dataset, DataLoader
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.metrics import mean_squared_error, mean_absolute_error
+from sklearn.model_selection import train_test_split
+from sklearn.preprocessing import StandardScaler
+
+# Set random seed for reproducibility
+np.random.seed(42)
+torch.manual_seed(42)
+
+# 1. Generate synthetic data
+def generate_data(n_samples=1000):
+    X = np.random.uniform(-10, 10, (n_samples, 1))
+    y = 3 * X.squeeze()**2 + 2 * X.squeeze() + 1 + np.random.normal(0, 10, n_samples)
+    return X.astype(np.float32), y.astype(np.float32)
+
+X, y = generate_data(n_samples=1000)
+
+# 2. Split into training and testing
+X_train, X_test, y_train, y_test = train_test_split(X, y, test_size=0.2, random_state=42)
+
+# 3. Standardize features
+scaler = StandardScaler()
+X_train = scaler.fit_transform(X_train)
+X_test = scaler.transform(X_test)
+
+# 4. Define custom Dataset
+class RegressionDataset(Dataset):
+    def __init__(self, features, targets):
+        self.X = torch.from_numpy(features)
+        self.y = torch.from_numpy(targets).unsqueeze(1)
+    
+    def __len__(self):
+        return len(self.X)
+    
+    def __getitem__(self, idx):
+        return self.X[idx], self.y[idx]
+
+# 5. Create DataLoaders
+batch_size = 32
+train_dataset = RegressionDataset(X_train, y_train)
+test_dataset = RegressionDataset(X_test, y_test)
+train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
+test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=False)
+
+# 6. Define the model
+class SimpleRegressor(nn.Module):
+    def __init__(self, input_dim, hidden_dim):
+        super(SimpleRegressor, self).__init__()
+        self.net = nn.Sequential(
+            nn.Linear(input_dim, hidden_dim),
+            nn.ReLU(),
+            nn.Linear(hidden_dim, hidden_dim),
+            nn.ReLU(),
[…]

### 2025-03-19 earlystopping/runtest.sh

@@ -1,5 +1,0 @@
-#!/bin/bash
-#python3 main.py --settings IQP_Full-Pauli-CRX/IQP_Full-Pauli-CRX.json --train_set 5_DDCC_train.bin --test_set 5_DDCC_test.bin --scaler 5_DDCC_scaler.bin --save_path ./IQP_Full-Pauli-CRX 
-python3 main.py --settings IQP_Full-Pauli-CRX/IQP_Full-Pauli-CRX.json --train_set PCA5_Morgan_train.bin --test_set PCA5_Morgan_test.bin --scaler PCA5_Morgan_scaler.bin --save_path ./IQP_Full-Pauli-CRX 
-#python3 main.py --settings IQP_Full-Pauli-CRX/IQP_Full-Pauli-CRX.json --train_set linear_train.bin --test_set linear_test.bin --scaler linear_scaler.bin --save_path ./IQP_Full-Pauli-CRX 
-#python3 main.py --settings IQP_Full-Pauli-CRX/IQP_Full-Pauli-CRX.json --train_set linear_train.bin --test_set linear_test.bin --scaler linear_scaler.bin --save_path ./IQP_Full-Pauli-CRX > IQP_Full-Pauli-CRX.out

### 2025-03-19 helperfiles/dockerhelp/test_docker.sh

@@ -1,0 +1,1 @@
+docker build -t deb . && docker run deb && docker run -it deb /bin/bash

### 2025-03-19 src/qregress/__init__.py

@@ -1,7 +1,5 @@
-# src/__init__.py
-from . import Classical
-from . import cli_classical
-from . import main
-from . import settings
+from . import scripts
 from . import quantum
+
+__all__ = ["scripts", "quantum"]
 

### 2025-03-19 src/qregress/scripts/settings.py

@@ -1,0 +1,191 @@
+import json
+import click
+import os
+from ..quantum.circuits.Encoders import double_angle, single_angle, iqp_embedding, mitarai, composer, entangle_cz, entangle_cnot
+from ..quantum.circuits.Ansatz import HardwareEfficient, EfficientSU2, TwoLocal, ModifiedPauliTwo, HadamardAnsatz
+
+############################################
+#  Lists of acceptable values
+############################################
+
+
+ERROR_MITIGATION_LIST = {
+    'None': None,
+    'MITIQ_LINEAR': 'MITIQ_LINEAR',
+    'MITIQ_Richardson': 'MITIQ_Richardson',
+    'M3': 'M3',
+    'TREX': 'TREX'
+}
+
+POSTPROCESS_LIST = {
+    'None': None,
+    'simple': 'simple',
+    'ridge': 'ridge',
+    'lasso': 'lasso'
+}
+
+ENCODER_LIST = {
+    'M': mitarai,
+    'A1': single_angle,
+    'A2': double_angle,
+    'IQP': iqp_embedding,
+    'M-M-CNOT': composer(mitarai, entangle_cnot, mitarai, entangle_cnot),
+    'A1-A1-CNOT': composer(single_angle, entangle_cnot, single_angle, entangle_cnot),
+    'A2-A2-CNOT': composer(double_angle, entangle_cnot, double_angle, entangle_cnot),
+    'M-A1-CNOT': composer(mitarai, entangle_cnot, single_angle, entangle_cnot),
+    'M-A2-CNOT': composer(mitarai, entangle_cnot, double_angle, entangle_cnot),
+    'M-M-CZ': composer(mitarai, entangle_cz, mitarai, entangle_cz),
+    'A1-A1-CZ': composer(single_angle, entangle_cz, single_angle, entangle_cz),
+    'A2-A2-CZ': composer(double_angle, entangle_cz, double_angle, entangle_cz),
+    'M-A1-CZ': composer(mitarai, entangle_cz, single_angle, entangle_cz),
+    'M-A2-CZ': composer(mitarai, entangle_cz, double_angle, entangle_cz),
+}
+
+# TODO: Create a full list of ansatz to be used in the experiment
+ANSATZ_LIST = {
+    'HWE-CNOT': HardwareEfficient(),
+    'HWE-CZ': HardwareEfficient(entangle_type='CZ'),
[…]

### 2025-03-19 manuscript/main.tex
reset soft

--- 2025-03-18 manuscript/main.tex
@@
 Canada L5L 1C6}
+\alsoaffiliation[UT DSI]{
+	Data Science Institute, 
+	University of Toronto, 
+	700 University Ave 10th floor,
+	 Toronto, ON M7A 2S4}
+\alsoaffiliation[UCalg]{Current Affiliation: Department of Chemistry, 
+	University of Calgary, 
+	2500 University Drive NW,
+	 Calgary, AB T2N 1N4}
 
@@
 In practice, all state-vector simulations were performed using PennyLane, while all calculations using \textit{FakeQuebec} and \textit{ibm\_quebec}  are run using Qiskit.
-State-vector simulations were also optimized using 1000 iterations with the Simultaneous Perturbation Stochastic Approximation method (SPSA), as implemented in PennyLane since we found that SPSA requires less steps to optimize when compared to other optimizers for state-vector simulation.
+All state-vector simulations with 5 qubits were optimized using 1000 iterations, while 16 qubit simulations utilized early stopping due to computational cost considerations.
+State-vector simulations were also optimized using the Simultaneous Perturbation Stochastic Approximation method (SPSA), as implemented in PennyLane since we found that SPSA requires less steps to optimize when compared to other optimizers for state-vector simulation.
 For the experiments ran using \textit{FakeQuebec} and  \textit{ibm\_quebec}, we utilized the Constrained Optimization By Linear Approximation (COBYLA) optimizer, as implemented in SciPy\cite{virtanen_scipy_2020}.
@@
 \label{section:results_and_discussion}
-In this section, we discuss the initial analysis of the 168 PQCs with 5 qubits, using the PCA reduced \textit{sub}-Morgan fingerprints.
+[introduction paragraph]
+In this section, for both the DDCC and BSE49 datasets, we start our analysis of by examining the performance of the initial set of 168 PQCs with re-upload depths of 1 ($k=1$) and the number ansatz layers set to 1 ($v=1$).
+Using this data, we select the best encoder-ansatz pair and increase the re-upload depth and number of ansatz layers to 3 and 5 ($k,v \in {3,5}$) to determine how model performance is effected by circuit depth.
+We then analyze how the best circuit from this set performs using a learning curve, where we hold the number of test points set to 20\% and vary the number of training points, to determine how PQCs behave with varying numbers of training data.
+Lastly, we provide insights into how the best PQC model behaves on simulated and real IBM backends using \textit{FakeQuebec} and \textit{ibm{\_}quebec}.
 
-five qubit 
-best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
-Best encoder on average train R$^{2}$/test R$^{2}$
-Best ansatz on average train R$^{2}$/test R$^{2}$
+%old A1-A1-CNOT_Full-CRX (0.19/0.20)
+Starting with the 5 qubit BSE49 data, Fig.
+\ref{fig:5BSE_heatplots} highlights the performance of the 168 PQCs using a heat plot of the coefficients of determination (R$^{2}$) of the training (left) and test sets (right).
+The training set R$^2$ values range from a minimum of -1.4673 to a maximum of 0.1566, with a mean of -0.2131 and a standard deviation of 0.3463.
+For the test set, the R$^2$ values range from a minimum of -1.4774 to a maximum of 0.1740, with a mean of -0.2031 and a standard deviation of 0.3475.
+General trends regarding the performance of the encoders (left) and ansatz (right) layers are highlighted in Fig. \ref{fig:5BSE_boxplots} using box plots.
+On average, the best encoding layer is M-M-CNOT with a training and test R$^{2}$s of -0.0242 and -0.0229, respectively.
+The best ansatz layer, is HWE-CNOT with an average training  R$^{2}$ of 0.0360 and test R$^{2}$ of 0.0473.
+Overall, for the BSE49 dataset using 5 qubits, the best encoder-ansatz pair is M-M-CZ{\_}HWE-CNOT with a training set R$^{2}$ of 0.1566 and test set R$^{2}$ of 0.1740.
 
-M-M-CZ{\_}HWE-CNOT
+[This is bad; the 70 removed were originally ran with 250 iter... not 1000 like the rest...]
+Following this analysis, 70 PQCs were removed based on performance regarding the computational costs of state-vector simulation and model accuracy.
 
-'M-M-CNOT', '-0.0216'
-'Full-CRX', '0.1214'
+Using the remaining 98 PQCs, we perform a similar analysis using 16 qubits.
 
@@
 removed the really bad ones from five qubit
-best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
-Best encoder on average train R$^{2}$/test R$^{2}$
-Best ansatz on average train R$^{2}$/test R$^{2}$
-A2_Hadamard
+
+pair A2{\_}Hadamard train R$^{2}$      0.0028 test R$^{2}$       0.0140 train MAE    19.8071 kcal/mol test MAE     20.0745 kcal/mol
+
+Encoder A1 train R$^{2}$     -0.0501 test R$^{2}$      -0.0458 train MAE    20.7795 kcal/mol test MAE     21.3186 kcal/mol
+
+variational HWE-CNOT train R$^{2}$     -0.0147 test R$^{2}$      -0.0025 train MAE    20.1601 kcal/mol test MAE     20.5422 kcal/mol
 
@@
 
-A2\_HWE-CNOT Train R$^{2}$ 0.62/test R$^{2}$ 0.62 
+ Train R$^{2}$     0.6191
+Test R$^{2}$      0.6184
+train MAE    5.9739 $mE_{h}$ 
+test MAE     5.9660 $mE_{h}$
+pair: A2{\_}HWE-CNOT
+
+ Train R$^{2}$     0.0163
+Test R$^{2}$      0.0183
+train MAE    12.7282 $mE_{h}$
+test MAE    12.7116 $mE_{h}$
+encoder: A1
+
+ Train R$^{2}$     0.2817
+Test R$^{2}$      0.2853
+train MAE    11.6967 $mE_{h}$
+test MAE    11.6871 $mE_{h}$
+variational: HWE-CNOT
+
 Best encoder average Train R$^{2}$ X/test R$^{2}$ Y
@@
 
+\section{Acknowledgements}
+We would like to acknowledge the Government of Canada’s New Frontiers in Research Fund (NFRF), for grant NFRFE-2022-00226, and the Quantum Software Consortium (QSC), financed under grant \#ALLRP587590-23 from the National Sciences and Engineering Research Council of Canada (NSERC) Alliance Consortia Quantum Grants.
+This research was enabled in part by support provided by IBM Quantum via the Quantum Software Consortium and the Digital Research Alliance of Canada.
+The authors would also like to acknowledge Aviraj Newatia, who provided valuable insights with preliminary results excluded from this work.
+[somethings were ran on the MSRG cloud... do we need to cite the funders of our cloud???]
+[Viki: Did Nick have any special undergrad funding?]
+
 \bibliography{achemso-demo}

### 2025-03-19 BSE-calc-test/5rerun/add_params.py

@@ -1,30 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-# In[1]:
-
-
-from glob import glob
-import sys
-import os
-import shutil
-import joblib
-import json
-
-
-# In[2]:
-
-
-for p in glob('*/*.json'):
-    print(p)
-    with open(p,'r') as f:
-        olddt=json.load(f)
-    
-    
-    olddt["BATCH_SIZE"]=1
-    olddt["NUM_CORES"]=16
-    print(olddt)    
-
-    with open(p,'w') as g:
-        json.dump(olddt,g)
-

### 2025-03-19 BSE-calc-test/old/16qubit/apprun.sh

@@ -1,0 +1,34 @@
+#! /bin/bash
+cwd=$(pwd)
+errorname=$(basename `pwd`)
+echo $cwd
+for i in */; do
+    name=${i%/}
+    # Extracting the parent directory name
+    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
+    path="${cwd}/${name}"
+    if [ ! -f ${path}/${name}_results.json ]; then
+        echo "${name}.done not found!"
+    	cat > ${name}.sub <<EOF
+#! /bin/bash
+#SBATCH -t 7-00:00:00
+#SBATCH -J ${errorname}_PCA16_${name}
+#SBATCH -N 1
+#SBATCH -n 36
+#SBATCH --mem-per-cpu=300           # memory per cpu
+#SBATCH --account=rrg-jacobsen-ab
+#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
+#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
+
+module load apptainer
+cd $(pwd)/$name
+
+apptainer run -C -B ${cwd} /home/gjones/projects/def-jacobsen/gjones/deb.sif /opt/miniconda/bin/python ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA16_Morgan_train.bin --test_set ${cwd}/PCA16_Morgan_test.bin --scaler ${cwd}/PCA16_Morgan_scaler.bin --resume_file ${path}/final_state_model.bin  > ${name}.out 2>&1
+
+cd ..
+touch ${name}.done
+
+EOF
+    fi
+    echo "Done ${name}.sub"
+done

### 2025-03-19 BSE-calc-test/old/16qubit/broke.sh

@@ -1,0 +1,5 @@
+sbatch A1_HWE-CNOT.sub
+sbatch A2-A2-CZ_Full-Pauli-CRZ.sub
+sbatch IQP_Full-CRX.sub
+sbatch M-M-CZ_Modified-Pauli-CRX.sub
+sbatch M_Modified-Pauli-CRX.sub

### 2025-03-19 BSE-calc-test/old/16qubit/helperfiles/quantum/circuits/Ansatz.py

@@ -1,0 +1,492 @@
+import pennylane as qml
+from .Encoders import entangle_cnot, entangle_cz
+from qiskit.circuit.library import n_local
+
+
+def rotation_layer(parameters, wires, three_rotations=True):
+    if not three_rotations:
+        if len(parameters) != 2 * len(self._wires):
+            raise ValueError("Unsopported number of parameters. Expected amount should be", 3 * len(self._wires))
+    else:
+        if len(parameters) != 3 * len(self._wires):
+            raise ValueError("Unsupported number of parameters. Expected amount should be", 3 * len(self._wires))
+    for i in range(len(self._wires)):
+        if three_rotations:
+            qml.RX(parameters[3 * i], wires=wires[i])
+            qml.RZ(parameters[3 * i + 1], wires=wires[i])
+            qml.RX(parameters[3 * i + 2], wires=wires[i])
+        else:
+            qml.RX(parameters[2 * i], wires=wires[i])
+            qml.RZ(parameters[2 * i + 1], wires=wires[i])
+
+
+class HardwareEfficient:
+    _entangle_types = {
+        'CNOT': entangle_cnot,
+        'CZ': entangle_cz
+    }
+
+    def __init__(self, wires: list = None, layers: int = 1, entangle_type: str = 'CNOT'):
+        self._layers = layers
+        if entangle_type not in self._entangle_types.keys():
+            raise ValueError("Unexpected entangling type. Possible types are:", self._entangle_types.keys())
+        self.entangler = self._entangle_types[entangle_type]
+        self._wires = wires
+
+    def __call__(self, parameters, wires: list = None):
+        if wires is not None:
+            self._wires = wires
+        if len(parameters) != 3 * self._layers * len(self._wires):
+            raise ValueError("Expected ", 3 * self._layers * len(self._wires), "parameters but got ", len(parameters))
+        for i in range(self._layers):
+            start_index = i * 3 * len(self._wires)
+            end_index = start_index + 3 * len(self._wires)
+            rotation_layer(parameters[start_index:end_index], self._wires)
+            self.entangler(self._wires)
+
+    @property
+    def num_params(self):
+        return 3 * self._layers * len(self._wires)
+
+    @property
+    def layers(self):
+        return self._layers
+
+    @layers.setter
+    def layers(self, val):
+        self._layers = val
+
+    def set_wires(self, wires):
+        self._wires = wires
+
+
+class EfficientSU2:
+
+    def __init__(self,
[…]

### 2025-03-19 BSE-calc-test/old/16qubit/quantum/Quantum.py

@@ -1,0 +1,386 @@
+import pennylane as qml
+import numpy as np
+from pennylane import numpy as np
+from sklearn.metrics import mean_squared_error
+from scipy.optimize import minimize, basinhopping
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_ibm_provider import IBMProvider
+from qiskit_ibm_runtime.fake_provider import FakeCairoV2
+from mitiq.zne.scaling import fold_global
+from mitiq.zne.inference import RichardsonFactory, LinearFactory
+import joblib
+import mthree
+import os
+import json
+import time
+
+
+
+class BasinBounds:
+    def __init__(self, xmax=np.pi, xmin=-np.pi):
+        self.xmax = xmax
+        self.xmin = xmin
+
+    def __call__(self, **kwargs):
+        x = kwargs["x_new"]
+        tmax = bool(np.all(x <= self.xmax))
+        tmin = bool(np.all(x >= self.xmin))
+        return tmax and tmin
+
+
+class QuantumRegressor:
+    """
+    Machine learning model based on quantum circuit learning.
+
+    Methods
+    ------
+    fit(x, y, initial_parameters=None, detailed_results=False, load_state=None, callback_interval=None)
+        Fits the model instance to the given x and y data.
+    predict(x)
+        Predicts y values for a given array of input data based on previous training.
+
+    """
+
+    def __init__(
+            self,
+            encoder,
+            variational,
+            num_qubits,
+            optimizer: str = 'COBYLA',
+            max_iterations: int = None,
+            tol: float = 1e-8,
+            device: str = 'default.qubit',
+            backend: str = None,
+            postprocess: str = None,
+            error_mitigation=None,
+            scale_factors: list = None,
+            folding=fold_global,
+            shots: int = None,
+            re_upload_depth: int = 1,
+            f: float = 1.,
+            alpha: float = 0.,
+            beta: float = 0,
+            provider=None,
+            token: str = None,
+            batch_size: int=None,
+            njobs: int=None):
+        self.hyperparameters = {'f': f, 'alpha': alpha, 'beta': beta}
+        if scale_factors is None:
+            scale_factors = [1, 3, 5]
+        self.callback_interval = None
+        self.x = None
+        self.y = None
+        self.params = None
+        self._batch_size = batch_size
+        self._re_upload_depth = re_upload_depth
+        self.error_mitigation = error_mitigation
+        self.num_qubits = num_qubits
[…]

### 2025-03-24 manuscript/main.tex
Mon 24 Mar 2025 17:04:25 EDT

@@
 
-The second quantum chemistry dataset we analyze in this paper is generated using the data-driven coupled-cluster (DDCC) scheme of Townsend and Vogiatzis.\cite{townsend_data-driven_2019}
+The second quantum chemistry dataset we analyze in this paper is generated using the data-driven coupled-cluster (DDCC) scheme of Townsend and Vogiatzis.\cite{townsend_data-driven_2019,jones_chapter_2023}
 DDCC is an ML-based approach for accelerating the convergence of coupled-cluster singles and doubles (CCSD) calculations by predicting the $t_{2}$-amplitudes of the CCSD wave function (Eq.

### 2025-03-25 manuscript/main.tex
5qubit 1000/partial 16 qubit

@@
 In practice, all state-vector simulations were performed using PennyLane, while all calculations using \textit{FakeQuebec} and \textit{ibm\_quebec}  are run using Qiskit.
-All state-vector simulations with 5 qubits were optimized using 1000 iterations, while 16 qubit simulations utilized early stopping due to computational cost considerations.
+All state-vector simulations with 5 qubits were optimized using 1000 iterations, while 16 qubit are initially ran using 250 iterations and longer runs, using 1000 iterations, use early stopping due to computational cost considerations.
 State-vector simulations were also optimized using the Simultaneous Perturbation Stochastic Approximation method (SPSA), as implemented in PennyLane since we found that SPSA requires less steps to optimize when compared to other optimizers for state-vector simulation.
@@
 \ref{fig:5BSE_heatplots} highlights the performance of the 168 PQCs using a heat plot of the coefficients of determination (R$^{2}$) of the training (left) and test sets (right).
-The training set R$^2$ values range from a minimum of -1.4673 to a maximum of 0.1566, with a mean of -0.2131 and a standard deviation of 0.3463.
-For the test set, the R$^2$ values range from a minimum of -1.4774 to a maximum of 0.1740, with a mean of -0.2031 and a standard deviation of 0.3475.
+The training set R$^2$ values range from a minimum of -1.4673 to a maximum of 0.1775, with a mean of -0.1865 and a standard deviation of 0.3433. 
+For the test set, the R$^2$ values range from a minimum of -1.4774 to a maximum of 0.1974, with a mean of -0.1765 and a standard deviation of 0.3446.
 General trends regarding the performance of the encoders (left) and ansatz (right) layers are highlighted in Fig. \ref{fig:5BSE_boxplots} using box plots.
-On average, the best encoding layer is M-M-CNOT with a training and test R$^{2}$s of -0.0242 and -0.0229, respectively.
-The best ansatz layer, is HWE-CNOT with an average training  R$^{2}$ of 0.0360 and test R$^{2}$ of 0.0473.
-Overall, for the BSE49 dataset using 5 qubits, the best encoder-ansatz pair is M-M-CZ{\_}HWE-CNOT with a training set R$^{2}$ of 0.1566 and test set R$^{2}$ of 0.1740.
+On average, the best encoding layer is M-M-CNOT with a training and test R$^{2}$s of -0.0173 and -0.0157, respectively.
+The best ansatz layer, is Full-CRX with an average training  R$^{2}$ of 0.1054 and test R$^{2}$ of 0.1165.
+Overall, for the BSE49 dataset using 5 qubits, the best encoder-ansatz pair is A1-A1-CNOT{\_}Full-CRX training set R$^{2}$ of 0.1775 and test set R$^{2}$ of 0.1974.
+Despite A1-A1-CNOT{\_}Full-CRX being the best encoder-ansatz pair, for explorations of the circuit depth, we chose M-M-CZ{\_}HWE-CNOT, which offers similar performance training set R$^{2}$ of 0.1566 and test set R$^{2}$ of 0.1740 but has offers a less deep circuit that is less costly to perform state-vector simulations on.
 

### 2025-03-25 BSE-calc-test/5/checkfinish.sh

@@ -1,13 +1,0 @@
-#!/bin/bash
-RED='\033[0;31m'
-NC='\033[0m' # No Color
-printf "I ${RED}love${NC} Stack Overflow\n"
-
-for i in */; do
- extension=${i%/}
- if [ -f "${extension}/${extension}_results.json" ]; then
-  echo "$extension done" 
- else
-  echo -e "${RED}$extension${NC} not done" 
- fi
-done

### 2025-03-25 BSE-calc-test/5/newrun.sh

@@ -1,41 +1,0 @@
-#! /bin/bash
-
-# Get the current year and month
-current_year=$(date +%Y)
-current_month=$(date +%m)
-
-# Find directories to process
-dirs=$(find . -mindepth 1 -maxdepth 1 -type d)
-for i in ./M-A2-CZ_HWE-CZ; do
-#for i in $dirs; do
-    name=${i//.\//}
-    topdir=$(pwd)
-    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
-    path="${topdir}/${name}"
-
-#   echo $path
-    # Check for model_log.csv modified in the current month
-#   if find "$path" -maxdepth 1 -name "model_log.csv" -newermt "$(date +%Y)-$(date +%m)-01" ! -newermt "$(date +%Y)-$(date +%m)-06" | grep -q .; then
-#       echo "Skipping $path because model_log.csv was modified this month."
-#       continue
-#   fi
-
-
-    echo $path
-    cd $i
-
-    if [ ! -f "${path}/partial_state_model.bin" ]; then
-        python ${topdir}/main.py --save_path ${path} --settings ${path}/${name}.json \
-        --train_set ${topdir}/PCA5_0.8_Morgan_train.bin --test_set ${topdir}/PCA5_0.8_Morgan_test.bin \
-        --scaler ${topdir}/PCA5_0.8_Morgan_scaler.bin --save_circuits True \
-        --resume_file ${path}/final_state_model.bin > ${path}/${name}.out 2>&1
-    else
-        python ${topdir}/main.py --save_path ${path} --settings ${path}/${name}.json \
-        --train_set ${topdir}/PCA5_0.8_Morgan_train.bin --test_set ${topdir}/PCA5_0.8_Morgan_test.bin \
-        --scaler ${topdir}/PCA5_0.8_Morgan_scaler.bin --save_circuits True \
-        --resume_file ${path}/partial_state_model.bin > ${path}/${name}.out 2>&1
-    fi
-
-    cd ../
-done
-

### 2025-03-25 BSE-calc-test/5qubit/run.sh

@@ -1,71 +1,0 @@
-#! /bin/bash
-cwd=$(pwd)
-errorname=$(basename `pwd`)
-echo $cwd
-for i in */; do
-    name=${i%/}
-    # Extracting the parent directory name
-    settings_folder=${name#M-A1-CNOT_Efficient-CRX_}
-    path="${cwd}/${name}"
-    if [ -f "${name}/final_state_model.bin" ]; then
-    	cat > ${name}.sub <<EOF
-#! /bin/bash
-#SBATCH -t 2-00:00:00
-#SBATCH -J ${errorname}_PCA5_0.8_Morgan_${name}
-#SBATCH -N 1
-#SBATCH -n 64
-#SBATCH --account=rrg-jacobsen-ab
-#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
-#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
-
-cd $(pwd)/$name
-
-/lustre06/project/6006115/gjones/env/bin/python3 ${cwd}/main.py --save_path ${path}  --settings ${path}/${name}.json --train_set ${cwd}/PCA5_0.8_Morgan_train.bin --test_set ${cwd}/PCA5_0.8_Morgan_test.bin --scaler ${cwd}/PCA5_0.8_Morgan_scaler.bin --save_circuits True --resume_file ${path}/final_state_model.bin > ${name}.out 2>&1
-
-cd ..
-touch ${name}.done
-
-EOF
-    elif [ -f "${name}/partial_state_model.bin" ]; then
-    	cat > ${name}.sub <<EOF
-#! /bin/bash
-#SBATCH -t 2-00:00:00
-#SBATCH -J ${errorname}_PCA5_0.8_Morgan_${name}
-#SBATCH -N 1
-#SBATCH -n 64
-#SBATCH --account=rrg-jacobsen-ab
-#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
-#SBATCH --output=${name}.o%J               # The file where the output of the terminal will be dumped
-
-cd $(pwd)/$name
-
[…]

### 2025-03-25 BSE-calc-test/5qubitbackup/5/checkloss.sh

@@ -1,9 +1,0 @@
-#!/bin/bash
-dir=$(find . -mindepth 1 -maxdepth 1 -type d)
-for i in $dir; do
- extension=${i#./}
- echo $extension
- if [ -f "${extension}/${extension}_results.json" ]; then
-   python3 view_loss.py --path ${extension}/model_log.csv
- fi
-done  

### 2025-03-25 BSE-calc-test/5qubitbackup/5/fixrun.sh

@@ -1,49 +1,0 @@
-#! /bin/bash
-cwd=$(pwd)
-errorname=$(basename "$cwd")
-echo "Current working directory: $cwd"
-
-# List of specific directories to loop over
-dirs=(
-    "./A1_Efficient-CRX/"
-    "./A1_Efficient-CRZ/"
-    "./A1_Full-CRZ/"
-    "./A2-A2-CNOT_Efficient-CRZ/"
-    "./A2-A2-CZ_Efficient-CRZ/"
-    "./A2_ESU2/"
-    "./IQP_Efficient-CRZ/"
-    "./M-A1-CZ_ESU2/"
-    "./M-A2-CNOT_Efficient-CRX/"
-    "./M-A2-CNOT_Efficient-CRZ/"
-    "./M-A2-CNOT_ESU2/"
-    "./M-A2-CZ_Efficient-CRX/"
-    "./M-M-CZ_Efficient-CRX/"
-)
-
-for i in "${dirs[@]}"; do
-    # Remove trailing slash and extract name
-    name=$(basename "$i")
-    path="${cwd}/${name}"
-    
-    cat > "${name}.sub" <<EOF
-#! /bin/bash
-#SBATCH -t 2-00:00:00
-#SBATCH -J ${errorname}_PCA5_0.8_Morgan_${name}
-#SBATCH -N 1
-#SBATCH -n 64
-#SBATCH --account=rrg-jacobsen-ab
-#SBATCH --error=${name}.e%J        # The file where run time errors will be dumped
-#SBATCH --output=${name}.o%J       # The file where the output of the terminal will be dumped
-
-cd $path
-
-/lustre06/project/6006115/gjones/env/bin/python3 ${cwd}/main.py --save_path ${path} --settings ${path}/${name}.json --train_set ${cwd}/PCA5_0.8_Morgan_train.bin --test_set ${cwd}/PCA5_0.8_Morgan_test.bin --scaler ${cwd}/PCA5_0.8_Morgan_scaler.bin --save_circuits True > ${name}.out 2>&1
-
-cd ..
-touch ${name}.done
-EOF
-
-    echo "Done ${name}.sub"
-    sbatch "${name}.sub"
-done
-

### 2025-03-25 BSE-calc-test/5rerun/checkiter.sh

@@ -1,12 +1,0 @@
-#!/bin/bash
-RED='\033[0;31m'
-NC='\033[0m' # No Color
-files=$(find . -name "model_log.csv" | sort -h )
-for i in $files; do
-   #echo $i
-    iters=$(awk -F',' '{print $2}' $i | grep -Eo '[0-9]+' | tail -n 1)
-    if (( $iters !=  999  )); then
-     echo -e "${RED}$i: $iters${NC}"
-    fi
-done
-

### 2025-03-25 BSE-calc-test/5rerun/clean.sh

@@ -1,6 +1,0 @@
-rm */*.svg
-rm */*model_log.csv
-rm */*_state_model.bin
-rm */*_predicted_values.csv
-rm */*_results.json
-rm */*.out

### 2025-03-25 BSE-calc-test/5rerun/rerun.sh

@@ -1,37 +1,0 @@
-#!/bin/bash
-# Grab iteration information
-dir=$(find . -maxdepth 2 -name "model*.csv")
-
-# Loop over directories
-for i in $dir; do
-    path=$(dirname "$i")
-    echo "$path"
-    sumiter=0
-
-    # Loop over existing model_log.csv files to find the final iterations
-    for j in "${path}"/*model_log.csv; do
-        echo "$j"
-        raniter=$(awk -F',' 'END {gsub(/^[[:space:]]+|[[:space:]]+$/, "", $2); print $2}' "$j")
-
-        # Ensure raniter is a valid integer
-        if [[ "$raniter" =~ ^[0-9]+$ ]]; then
-            sumiter=$((sumiter + raniter + 1))
-            echo "$j has $raniter iterations"
-            echo "$sumiter"
-        else
-            echo "Warning: Could not extract valid iteration from $j"
-        fi
-    done
-
-    # Write the remaining iterations to file
-    remain=$((1000 - sumiter))
-    echo "Iterations left: $remain"
-
-    # Uncomment these lines to apply changes if needed:
-    # mv "${path}/model_log.csv" "${path}/1_model_log.csv"
-    # sed -i 's/"MAX_ITER": 1000/"MAX_ITER": '$remain'/g' "${path}"/*.json
-
-    echo "$(cat "${path}"/*.json)"
-    echo
-done
-

### 2025-03-31 manuscript/main.tex
Mon 31 Mar 2025 17:06:36 EDT

@@
 For each of the molecular representations, we analyzed two different methods for representing the components of the BSE reaction.
-The first represents the feature vector as the products subtracted from the reactants, denoted as \textit{sub} (e.g., $\text{CM}_{\mathit{sub}} = (\text{CM}_{\text{A}^{.}} + \text{CM}_{\text{B}^{.}}) - \text{CM}_{\text{A-B}}$), similar to the method used in Ref.
-\cite{garcia-andrade_barrier_2023}, and the second represents the feature vector using only the reactant (A-B), denoted as \textit{AB} (e.g., $\text{CM}_{\mathit{AB}} =  \text{CM}_{\text{A-B}}$).
+The first represents the feature vector as the products subtracted from the reactants, denoted as \textit{sub} (e.g., $\mathbf{X}_{\mathit{sub}} = (\mathbf{X}_{\text{A}^{.}} + \mathbf{X}_{\text{B}^{.}}) - \mathbf{X}_{\text{A-B}}$), similar to the method used in Ref.
+\cite{garcia-andrade_barrier_2023}, and the second represents the feature vector using only the reactant (A-B), denoted as \textit{AB} (e.g., $\mathbf{X}_{\mathit{AB}} =  \mathbf{X}_{\text{A-B}}$).
 

### 2025-04-01 manuscript/main.tex
manuscipt

@@
 
-%old A1-A1-CNOT_Full-CRX (0.19/0.20)
 Starting with the 5 qubit BSE49 data, Fig.
@@
 Overall, for the BSE49 dataset using 5 qubits, the best encoder-ansatz pair is A1-A1-CNOT{\_}Full-CRX training set R$^{2}$ of 0.1775 and test set R$^{2}$ of 0.1974.
-Despite A1-A1-CNOT{\_}Full-CRX being the best encoder-ansatz pair, for explorations of the circuit depth, we chose M-M-CZ{\_}HWE-CNOT, which offers similar performance training set R$^{2}$ of 0.1566 and test set R$^{2}$ of 0.1740 but has offers a less deep circuit that is less costly to perform state-vector simulations on.
+Despite A1-A1-CNOT{\_}Full-CRX being the best encoder-ansatz pair, for explorations of the circuit depth, we chose M-M-CZ{\_}HWE-CNOT, which offers similar performance training set R$^{2}$ of 0.1566 and test set R$^{2}$ of 0.1740 but has offers a more shallow circuit, which is more computationally efficient for state-vector simulations.
 
-[This is bad; the 70 removed were originally ran with 250 iter... not 1000 like the rest...]
-Following this analysis, 70 PQCs were removed based on performance regarding the computational costs of state-vector simulation and model accuracy.
-
-Using the remaining 98 PQCs, we perform a similar analysis using 16 qubits.
-
-sixteen qubit \ref{fig:16BSE_heatplots} \ref{fig:16BSE_boxplots}
-removed the really bad ones from five qubit
-
-pair A2{\_}Hadamard train R$^{2}$      0.0028 test R$^{2}$       0.0140 train MAE    19.8071 kcal/mol test MAE     20.0745 kcal/mol
-
-Encoder A1 train R$^{2}$     -0.0501 test R$^{2}$      -0.0458 train MAE    20.7795 kcal/mol test MAE     21.3186 kcal/mol
-
-variational HWE-CNOT train R$^{2}$     -0.0147 test R$^{2}$      -0.0025 train MAE    20.1601 kcal/mol test MAE     20.5422 kcal/mol
-
-Talk about the cost of going wider, and inherently deeper
+Following the 5 qubit models, we tested the BSE49 dataset on the set of 168 PQCs using 16 qubits.
+Fig.
+\ref{fig:16BSE_heatplots} shows the performance in R$^{2}$ for the training (left) and test (right) sets, where the best encoder-ansatz pair is A1{\_}Efficient-CRZ with an R$^{2}$ of -0.0007 for the training set and -0.0050 for the test set.
+Across the 168 PQCs, the training and test sets have a minimum R$^{2}$ -1.8104 and -1.7752, a mean of -0.4045 and -0.4022, a maximum of -0.0007 and -0.0004, and a standard deviation of 0.4161 and 0.4235,respectively.
+Overall, as highlighted in Fig. \ref{fig:16BSE_boxplots} (left), the best encoder is IQP with a mean R$^{2}$ of -0.0942 for the training set and -0.0882 for the test set.
+The best ansatz circuit (Fig. \ref{fig:16BSE_boxplots} right) is HWE-CNOT with a mean R$^{2}$ of -0.0148 and -0.0025 for the training and test set, respectively.
+Due to the overall poorer performance and high computational expense of state-vector simulation using 16 qubits, we use only the best 5-qubit PQC, M-M-CZ{\_}HWE-CNOT, for the additional experiments with the BSE49 dataset.
 
@@
 		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_boxplots}
+		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_heatplots}
 		\caption{}
-		\label{fig:5BSE_boxplots}
+		\label{fig:16BSE_heatplots}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_heatplots}
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_boxplots}
 		\caption{}
-		\label{fig:16BSE_heatplots}
+		\label{fig:5BSE_boxplots}
 	\end{subfigure}
@@
 	\end{subfigure}
-	\caption{}
+	\caption{The model performance (in R$^{2}$) of the 168 parameterized quantum circuits for BSE49 using (a) 5 and (b) 16 qubits, where the x-axis denotes the ansatz and the y-axis denotes the encoders.
+Box plots are used to highlight the general performance of the encoder (left) and ansatz (right) circuits for the (c) 5 and (d) 16 qubit BSE49 models.}
 	\label{fig:BSEboxandheat}	
@@
 
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE5_RUDAL_lineplot}
-		\caption{}
-		\label{fig:bse5RUDAL_lineplot}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE16_RUDAL_lineplot}
-		\caption{}
-		\label{fig:bse16RUDAL_lineplot}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/distribution_parity}
-		\caption{}
-		\label{fig:BSE5_distribution_parity}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/distribution_parity}
-		\caption{}
-		\label{fig:BSE16_distribution_parity}
-	\end{subfigure}
-	\caption{}
-	\label{fig:BSE_distribution_parity}	
-\end{figure}
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_learningcurve}
-		\caption{}
-		\label{fig:BSE5_learning_curves}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/BSE/sixteenqubit/BSE_learningcurve}
-		\caption{}
-		\label{fig:BSE16_learningcurve}
-	\end{subfigure}
-	\caption{}
-	\label{fig:BSE_LC}	
-\end{figure}
-
-Structure
-\begin{itemize}
-	\item Broad set
-	\item RUD/AL tests
-	\item learning curve (maybe)
-	\item real device 
-\end{itemize}
-
- Train R$^{2}$     0.6191
-Test R$^{2}$      0.6184
-train MAE    5.9739 $mE_{h}$ 
-test MAE     5.9660 $mE_{h}$
-pair: A2{\_}HWE-CNOT
-
- Train R$^{2}$     0.0163
-Test R$^{2}$      0.0183
-train MAE    12.7282 $mE_{h}$
-test MAE    12.7116 $mE_{h}$
-encoder: A1
-
- Train R$^{2}$     0.2817
-Test R$^{2}$      0.2853
-train MAE    11.6967 $mE_{h}$
-test MAE    11.6871 $mE_{h}$
-variational: HWE-CNOT
-
-Best encoder average Train R$^{2}$ X/test R$^{2}$ Y
-Best ansatz HWE-CNOT average Train R$^{2}$ X/test R$^{2}$ Y
+Following the evaluation of the 168 PQCs using the BSE49 dataset, we used a reduced set of 98 PQCs for the DDCC dataset.
+Fig.
+\ref{fig:ddccheatplots} highlights the improved performance of the PQCs on the DDCC dataset over the BSE49 dataset, where the R$^{2}$s of the training set have a minimum, mean, maximum, and standard deviation of -2.1302, -0.3050, 0.6191, and 0.4422, respectively.
+While the R$^{2}$s of the test set have a minimum of -2.1007, a mean of -0.3046, a maximum of 0.6184, and a standard deviation of 0.4411.
+The best encoder-ansatz pair is A2{\_}HWE-CNOT with R$^{2}$s of 0.6191 and 0.6184, for the training and test sets, respectively.
+We found that the PQCs offer better model performance when ran on the DDCC dataset, with A1 offering the best average performance of the encoders with an R$^{2}$ of 0.0163 for the training set and 0.0183 for the test set (Fig.
+\ref{fig:ddccboxplots} left).
+Like the 16 qubit BSE49 data, the best ansatz layer is HWE-CNOT (Fig. \ref{fig:ddccboxplots} right).
+Unlike the 16 qubit BSE49 data, HWE-CNOT offers a training and test set R$^{2}$ of 0.2817 and 0.2853, respectively.
+Overall, the DDCC models offer more accurate models, with less overfitting, when compared to the BSE49 models.
 
@@
 	\end{subfigure}
-	\hfill
-%	\begin{subfigure}[b]{0.49\textwidth}
-%		\centering
-%		\includegraphics[width=\linewidth]{../images/DDCC/AllDDCC5_circuitdepth_R2_vs_iterationtime}
-%		\caption{}
-%		\label{fig:allddcc5circuitdepthr2vsiterationtime}
-%	\end{subfigure}	
-	\caption{}
+	\caption{(a) Heat maps for the 98 PQCs using the DDCC data set for the training (left) and test set (right). (b) Shows box plots for the encoder (left) and ansatz (right) circuits.}
 	\label{fig:ddcc_all_analysis}	
 \end{figure}
+
+After analyzing the initial set of PQCs using the BSE49 and DDCC datasets, we examine how increasing the re-upload depth (RUD) and number of ansatz layers (AL) affects model performance.
+For the BSE49 data, we examine RUDs of $k=\{1,3,5\}$ and for the ALs $v=\{1,3,5\}$.
+We examine this data in two ways, the first is a simple line plot, shown in Fig.
+\ref{fig:bse5RUDAL_lineplot}, where the number of ALs and the RUD layers are plotted on the x-axis, the y-axis denotes the model accuracy in R$^{2}$, and the training set is denoted in light blue, while the test set is shown in dark blue.
+The second is by analyzing the regression parity plots, Fig.
+\ref{fig:BSE5_distribution_parity}, with the addition of kernel density estimation (KDE) plots on the axes to highlight the distributions of the values.
+Overall, for M-M-CZ{\_}HWE-CNOT using the BSE49 dataset, increasing the number of ALs and RUD offer negligible improvements over the base model, which as R$^{s}$ of 0.16 and 0.17 for the training and test set, respectively.
+The model with the best R$^{2}$ for the training set is the model initial model using an AL of 1 and RUD 1, while the model with the best R$^{2}$ for the test set uses a AL of 1 and RUD of 5 where the R$^{2}$ is 0.18.
+When we analyze the distributions in \ref{fig:BSE5_distribution_parity}, we find that the reference target values have a wide distribution, ranging from 9.3800 to 177.2400 kcal/mol with a standard deviation of 27.4877 kcal/mol.
+For the predicted values, all of the models struggle with predicting an accurate range, where the model with the worst spread is AL=3/RUD=1 with a minimum of 67.6736 kcal/mol, maximum of 115.6791 kcal/mol, and standard deviation of 6.7346 kcal/mol.
+The best model, regarding the spread of the predicted data, is the AL=1/RUD=5, with a minimum of 49.8978 kcal/mol, maximum of 127.8078 kcal/mol, and standard deviation of 14.0201 kcal/mol. 
+Overall, all models, regardless of the number of ALs and RUD, tend to regress towards the mean value of the reference data, 90.6916 kcal/mol.
+
+Unlike the 5 qubit BSE49 data, we see that when we increase the number of ALs and RUD, A2{\_}HWE-CNOT with the DDCC dataset, shows improved model performance (Figs.
+\ref{fig:ddccRUDAL_lineplot} and \ref{fig:ddccdistribution_parity}).
+For this dataset, we go beyond ALs and RUDs of 5 due to the initial improvements shown as both values increased.
+Fig.
+\ref{fig:ddccRUDAL_lineplot} highlights an interesting trend where as the number of ALs increases the model performance increases from R$^{2}$s of 0.62 to R$^{2}$s of $\approx 0.80$, for both the training and test sets.
+For the RUD, the R$^{2}$s show marginal improvements at $k=5,9$, while showing increased performance for $k=3,5$. 
+Overall, the best model for A2{\_}HWE-CNOT with the DDCC dataset is the model with an AL of 5 and RUD of 1.
+This is highlighted in Fig.
+\ref{fig:ddccdistribution_parity}, where we see that the distribution of the predicted target values are closer to the spread of the reference values than the initial model with AL=1/RUD=1.
+
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE5_RUDAL_lineplot}
+		\caption{}
+		\label{fig:bse5RUDAL_lineplot}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL_lineplot}
+		\caption{}
+		\label{fig:ddccRUDAL_lineplot}
+	\end{subfigure}
+	\hfill	
+	\begin{subfigure}[b]{0.65\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/distribution_parity}
+		\caption{}
+		\label{fig:BSE5_distribution_parity}
+	\end{subfigure}
+	\hfill
+
+	\begin{subfigure}[b]{0.65\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/DDCC/distribution_parity}
+		\caption{}
+		\label{fig:ddccdistribution_parity}
+	\end{subfigure}	
+	\caption{Line plots to highlight the performance as the number of ansatz layers (AL; left) and re-upload depth (RUD; right) increases for the 5 qubit (a) BSE49 and (b) DDCC data.
+Additionally, regression parity plots for each AL and RUD are shown for the (c) BSE49 and (d) DDCC data, where the x-axis denotes the predicted target values and the y-axis denotes the reference data.}
+	\label{fig:BSE_distribution_parity}	
+\end{figure}
+
+The last experiments we use state-vector for are learning curves since previous studies have mentioned that PQCs can outperform traditional models with fewer data points \cite{suzuki_predicting_2020,hatakeyama-sato_quantum_2023} \textbf{[double check]}
+\siref{table:5BSE49_LC}
+\siref{table:DDCC_LC}
+
+Error bars show the min and max values
+
+\begin{figure}[H]
+	\centering	
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/BSE/fivequbit/BSE_learningcurve}
+		\caption{}
+		\label{fig:BSE5_learning_curves}
+	\end{subfigure}	
+	\hfill
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_learning_curves}
+		\caption{}
+		\label{fig:ddcclearningcurves}
+	\end{subfigure}
+	\caption{}
+	\label{fig:learningcurves}
+
+\end{figure}
+
+\textbf{DDCC}
 
@@
 Talk about the cost of going wider, and inherently deeper
-
-\begin{figure}[H]
-	\centering	
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{../images/DDCC/DDCC_RUDAL_lineplot}
-		\caption{}
-		\label{fig:ddccRUDAL_lineplot}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{\textwidth}
-		\centering
-		\includegraphics[width=0.49\linewidth]{../images/DDCC/distribution_parity}
-		\caption{}
-		\label{fig:ddccdistribution_parity}
-	\end{subfigure}
-	\caption{Model evaluation, using R$^{2}$ (y-axis), of re-upload depths (RUD) and ansatz layers (AL) of 1, 3, and 5 for the A2\_HWE-CNOT using the DDCC dataset.
-The left side of the plot denotes the training set and the right side the test set.}
-	\label{fig:ddcc_rud}	
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{../images/DDCC/DDCC_learning_curves}
-	\caption{}
-	\label{fig:ddcclearningcurves}
-\end{figure}
 
@@
 
+It should also be noted that the majority of the $t_{2}$-amplitudes will be centered near zero since the $t^{ab}_{ij}$ tensor will contain many small contributions.
+Models that exclude small amplitudes, such as those found in Ref\cite{pathirage_exploration_2024}, could be used for increased performance but are out of the scope of this work.
+
 \section{Conclusion}

### 2025-04-03 manuscript/main.tex
Thu  3 Apr 2025 16:59:44 EDT

@@
 
-It should also be noted that the majority of the $t_{2}$-amplitudes will be centered near zero since the $t^{ab}_{ij}$ tensor will contain many small contributions.
+\textcolor{blue}{DDCC Discussion points}
+\begin{itemize}
+	\item Using multiple feature encoding qubits\cite{suzuki_predicting_2020} is unfeasible with DDCC due to the number of samples
+	\item DDCC is a \textit{trivial} task for classical ML (long time to train QML)
+	\item It should also be noted that the majority of the $t_{2}$-amplitudes will be centered near zero since the $t^{ab}_{ij}$ tensor will contain many small contributions.
 Models that exclude small amplitudes, such as those found in Ref\cite{pathirage_exploration_2024}, could be used for increased performance but are out of the scope of this work.
+\end{itemize}
 
@@
 
-Depth is not always better!
-Molecular representations specifically for QML
-Distributed QC to incorporate more features
-Noiseless simulation is costly and does not offer the desired accuracy for BSE49 or DDCC
-
-DDCC could be a useful dataset to benchmark PQC models since it is trivial to perform classically, yet hard for PQCs...
+PQCs for the BSE49 and DDCC datasets do not exhibit an advantage concerning model accuracy, the number of training points, or time to train the models
+Poor performance on the BSE49 dataset could be explained by the feature space reduction, we are compressing the feature space from 2048 to 5 features (structure-based ML reps.
+require more features than physics-based reps.)
+While the physics-based feature set of DDCC outperforms the structure-based feature set of BSE49, DDCC requires too many device executions to be useful on the current generation of devices
+For practitioners of quantum chemistry, who work on machine learning-related tasks, like Viki and me, several options exist:
+Use hybrid classical-quantum machine learning approaches to exploit entanglement on the QPU, while using a CPU/GPU/TPU for efficient classical tasks
+Classical machine learning assisted quantum computing (like I have proposed for a DDCC-LUCJ project for two undergraduates for summer 2025)
+Using distributed QML to maintain short circuit depths, while increasing the number of features
+Explore molecular representations designed for QML (e.g., BSE49 is a classic-in/quantum-out case)
+Stick to quantum-in/quantum-out approaches (e.g., DDCC falls into this category, but could this be reformulated to better exploit the QPU?)
 

### 2025-04-03 Pennylane_to_Qiskit/big_qiskit_run/QiskitRegressor.py

@@ -1,0 +1,418 @@
+import numpy as np
+import time
+import joblib
+from joblib import dump, load
+import os
+from tqdm.notebook import tqdm
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+from scipy.optimize import minimize
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+
+class QiskitRegressor:
+    def __init__(self,
+                 quantumcircuit,
+                 numqubits,
+                 ansatz_layers,
+                 reuploaddepth,
+                 backend,
+                 observables_labels,
+                 channel = None,
+                 instance = None,
+                 parameterpath = None,
+                 optimization_level = 2,
+                 resilience_level = 1,
+                 shots = 1024,
+                 iterations = 1000,
+                 verbose = False,
+                 n_jobs = None
+                ):
+        '''
+        parameters
+        ----------
+        quantumcircuit: 
+            Qiskit quantum circuit
+
+        numqubits: int
+            Number of qubits before mapping
+            
+        ansatz_layers: int
+            Number of ansatz layers (AL)
+
+        reuploaddepth: int
+            Re-upload depth (RUD)
+
+        backend: str
+            Options: statevector, fake, real
+
+        observables_labels: str
+            Observables mapped to original circuit before ISA pass
+
+        channel: str
+            IBM Quantum channel
+
+        instance: str
+            IBM Quantum instance
+
+        parameterpath: str
+        
+        optimization_level: int
+            Qiskit circuit optimization level (default=2; details at "https://docs.quantum.ibm.com/guides/set-optimization")
+            
+        resilience_level: int
+            Qiskit error mitigation level (default=2; details at "https://docs.quantum.ibm.com/guides/configure-error-mitigation"       
+        
+        shots: int
+            Number of shots (multiples of 1024 preferred)
+
+        iterations: int
+            Number of training cycles
+
+        verbose: bool
[…]

### 2025-04-03 src/qregress/scripts/Classical.py

@@ -1,185 +1,0 @@
-import time
-import matplotlib.pyplot as plt
-
-from sklearn.ensemble import RandomForestRegressor, GradientBoostingRegressor
-from sklearn.gaussian_process import GaussianProcessRegressor
-from sklearn.gaussian_process.kernels import RBF
-from sklearn.kernel_ridge import KernelRidge
-from sklearn.linear_model import Ridge, Lasso, ElasticNet
-from sklearn.neighbors import KNeighborsRegressor
-from sklearn.model_selection import GridSearchCV
-from sklearn.svm import SVR
-
-from .quantum.Evaluate import evaluate
-
-gaussian_kernel = RBF()
-
-models = {
-    'ridge': Ridge(),
-    'lasso': Lasso(),
-    'elastic': ElasticNet(),
-    'knn': KNeighborsRegressor(),
-    'rfr': RandomForestRegressor(),
-    'grad': GradientBoostingRegressor(),
-    'svr': SVR(),
-    'krr': KernelRidge(),
-    'gpr': GaussianProcessRegressor()
-}
-
-param_grid = {
-    'ridge': {
-        'alpha': [0.001, 0.01, 0.1, 1, 10, 50, 100, 1000]
-    },
-    'knn': {
-        'n_neighbors': range(1, 10),
-        'weights': ['uniform', 'distance']
-    },
-    'rfr': {
-        'n_estimators': [100, 200, 300],
-        'max_depth': [None, 5, 10],
-        'min_samples_split': [2, 5, 10]
-    },
-    'grad': {
-        'n_estimators': [100, 200, 300],
-        'learning_rate': [0.1, 0.01, 0.001],
-        'max_depth': [3, 5, 7]
-    },
-    'svr': {
-        'kernel': ['linear', 'rbf'],
-        'C': [0.1, 1, 10],
-        'epsilon': [0.1, 0.01, 0.001]
-    },
-    'krr': {
-        'kernel': ['linear', 'poly', 'rbf'],
-        'alpha': [0.001, 0.01, 0.1, 1],
-        'gamma': [1, 0.1, 0.01, 0.001]
-    },
-    'gpr': {
-        'alpha': [0.0001, 0.001, 0.01, 0.1, 1],
-        'kernel': [gaussian_kernel]
-    },
-    'lasso': {
-        'alpha': [0.001, 0.01, 0.1, 1],
[…]

### 2025-04-07 manuscript/main.tex
Fri  4 Apr 2025 14:29:29 EDT
Mon  7 Apr 2025 15:56:12 EDT

@@
 
-The last experiments we use state-vector for are learning curves since previous studies have mentioned that PQCs can outperform traditional models with fewer data points \cite{suzuki_predicting_2020,hatakeyama-sato_quantum_2023} \textbf{[double check]}
-\siref{table:5BSE49_LC}
-\siref{table:DDCC_LC}
+Next, we use learning curves, where the number of training points is varied, while the number of training points is varied to explore claims that PQCs offer better model performance using fewer training points and hyperparameters.\cite{schuld_circuit-centric_2020,du_expressive_2020,suzuki_predicting_2020}
+For the BSE49 dataset, using 5 qubits, we found that M-M-CZ{\_}HWE-CNOT offers less overfit models, but offer poorer performance regarding the training and test set R$^{2}$s, as highlighted in Fig.
+\ref{fig:BSE5_learning_curves}.
+Across the learning curve, the \textit{k}-NN model has a mean R$^{2}$s of 0.9998 for the training set and 0.5822 test set, while M-M-CZ{\_}HWE-CNOT has a mean R$^{2}$ of 0.1405 for the training set and R$^{2}$ of 0.136 for the test set.
+For M-M-CZ{\_}HWE-CNOT, the training set performance peaks when using 10\% of the training data with an R$^{2}$ of 0.2015, dips to an R$^{2}$ of -0.0172 using 30\% of the training data, and then maintains an R$^{2}$ less than 0.2 for the remaining percentages of the training data.
+Unlike the training points, the test reaches peak performance when 70\% of the total data is used in the training set, with a test R$^{2}$ of 0.2064.
 
-Error bars show the min and max values
+When we analyze the effects of the number of training points on the DDCC dataset using the A2{\_}HWE-CNOT PQC, we found that
+
+A2{\_}HWE-CNOT has $3nvk$ trainable parameters
+
+Minimum number of classical parameters is $n+1$
 
@@
 	\end{subfigure}
-	\caption{}
+	\caption{Learning curves for the (a) BSE49 database using the M-M-CZ{\_}HWE-CNOT circuit and (b) the DDCC dataset using the A2{\_}HWE-CNOT circuit.
+The x-axis denotes the percentage of training points, while the test set is held to 20\% of the total data.
+The y-axis denotes the R$^{2}$ of the training and test learning curves.
+Inlay plots show the training and test data for the classical models examined, where the bottom error bar denotes the minimum value, line the mean value, and top error bar the maximum value.}
 	\label{fig:learningcurves}
@@
 \textbf{DDCC}
-
-(AL,RUD)=(1,1) Train R$^{2}$ 0.62/test R$^{2}$ 0.62
-(AL,RUD)=(1,3) Train R$^{2}$ 0.85/test R$^{2}$ 0.85
-(AL,RUD)=(1,5) Train R$^{2}$ 0.82/test R$^{2}$ 0.83
-(AL,RUD)=(3,1) Train R$^{2}$ 0.71/test R$^{2}$ 0.71
-(AL,RUD)=(5,1) Train R$^{2}$ 0.77/test R$^{2}$ 0.77
-
-Talk about the cost of going wider, and inherently deeper
 
@@
 
-\textcolor{blue}{DDCC Discussion points}
-\begin{itemize}
-	\item Using multiple feature encoding qubits\cite{suzuki_predicting_2020} is unfeasible with DDCC due to the number of samples
-	\item DDCC is a \textit{trivial} task for classical ML (long time to train QML)
-	\item It should also be noted that the majority of the $t_{2}$-amplitudes will be centered near zero since the $t^{ab}_{ij}$ tensor will contain many small contributions.
-Models that exclude small amplitudes, such as those found in Ref\cite{pathirage_exploration_2024}, could be used for increased performance but are out of the scope of this work.
-\end{itemize}
+\begin{table}[h!]
+	\centering
+	\small
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		\textbf{Model} & \textbf{\# of Trainable Parameters} & \textbf{\# of Two-Qubit Gates} & \textbf{Circuit Depth} \\
+		\hline
+		A2\_HWE-CNOT & \(3nvk\) & \(nvk\) & \(vnk + 3vk + 2kl\) \\
+		\hline
+		M-M-CZ\_HWE-CNOT & \(3nvk\) & \(2nkl + nvk\) & \(2nkl + 2kl + nvk + 3vk\) \\
+		\hline
+		Linear, Ridge, Lasso, ElasticNet & \(n + 1\) & --- & --- \\
+		\hline
+	\end{tabular}
+	\caption{Comparison of models with respect to parameter count, two-qubit gate count, and circuit depth.}
+\end{table}
 
@@
 
+\textcolor{blue}{DDCC Discussion points}
+\begin{itemize}
+	\item Using multiple feature encoding qubits\cite{suzuki_predicting_2020} is unfeasible with DDCC due to the number of samples
+	\item DDCC is a \textit{trivial} task for classical ML (long time to train QML)
+	\item It should also be noted that the majority of the $t_{2}$-amplitudes will be centered near zero since the $t^{ab}_{ij}$ tensor will contain many small contributions.
+Models that exclude small amplitudes, such as those found in Ref\cite{pathirage_exploration_2024}, could be used for increased performance but are out of the scope of this work.
+\end{itemize}
+
 \section{Acknowledgements}

### 2025-04-07 src/qregress/quantum/Quantum.py

@@ -412,4 +412,3 @@ class QuantumRegressor:
 __all__ = ["QuantumRegressor"]
 
 
-del qiskit_session, AerSimulator, NoiseModel, QiskitRuntimeService, FakeQuebec, minimize, basinhopping, mean_squared_error, tqdm, joblib, json, np, os, qml, time,

### 2025-04-07 manuscript/main.tex
fix hashing tomorrow

@@
 
-Next, we use learning curves, where the number of training points is varied, while the number of training points is varied to explore claims that PQCs offer better model performance using fewer training points and hyperparameters.\cite{schuld_circuit-centric_2020,du_expressive_2020,suzuki_predicting_2020}
+Following the analysis of the RUD and number of ALs for both 5 qubit models, we explored claims that PQCs offer better model performance using fewer training points and hyperparameters\cite{schuld_circuit-centric_2020,du_expressive_2020,suzuki_predicting_2020} using learning curves.
+Our learning curves are generated varying the number of training points from 10-80\% of the total data, while fixing the number of test points to 20\% of the total dataset.
+In Fig.
+\ref{fig:learningcurves}, we analyze the effects of the number of training points of the best 5 qubit BSE49 and DDCC circuits, M-M-CZ{\_}HWE-CNOT using a RUD and AL of 1 and A2{\_}HWE-CNOT using a RUD of
+Next, we use learning curves, where the number of training points is varied, while the number of training points is varied to 
 For the BSE49 dataset, using 5 qubits, we found that M-M-CZ{\_}HWE-CNOT offers less overfit models, but offer poorer performance regarding the training and test set R$^{2}$s, as highlighted in Fig.

### 2025-04-07 src/qregress/__init__.py

@@ -1,9 +1,11 @@
-from . import scripts
-from . import Classical 
+from . import cli_classical
+from . import qregressrun
+from . import settings
+from . import Classical
 from . import quantum
 from .quantum.QiskitRegressor import QiskitRegressor
 from .quantum.Quantum import QuantumRegressor
 
 
-__all__ = ["scripts", "quantum","QiskitRegressor","Classical","QuantumRegressor"]
+__all__ = ["quantum","QiskitRegressor","QuantumRegressor","cli_classical", "qregressrun", "settings", "Classical"]
 

### 2025-04-07 src/qregress/qregressrun.py

@@ -1,0 +1,337 @@
+from glob import glob
+from .quantum.Evaluate import evaluate
+from .quantum.Quantum import QuantumRegressor
+from .settings import ANSATZ_LIST, ENCODER_LIST
+from shutil import copy,SameFileError
+from sklearn.exceptions import InconsistentVersionWarning
+from sklearn.metrics import mean_squared_error
+from sklearn.model_selection import KFold
+from sklearn.utils._testing import ignore_warnings
+import click
+import collections.abc
+import itertools
+import joblib
+import json
+import matplotlib.pyplot as plt
+import numpy as np
+import os
+import pandas as pd
+import pennylane as qml
+import time
+
+# Global variables
+OPTIMIZER = None
+SHOTS = None
+X_DIM = None
+BACKEND = None
+DEVICE = None
+SCALE_FACTORS = None
+ANSATZ = None
+ENCODER = None
+POSTPROCESS = None
+ERROR_MITIGATION = None
+LAYERS = None
+TOKEN = None
+HYPERPARAMETERS = None
+RE_UPLOAD_DEPTH = None
+MAX_ITER = None
+TOLERANCE = None
+NUM_QUBITS = None
+BATCH_SIZE = None
+NUM_CORES = None
+############################################
+# Utility functions
+############################################
+
+
+def parse_settings(settings_file):
+    with open(settings_file, 'r') as fp:
+        settings = json.load(fp)
+
+    global OPTIMIZER
+    OPTIMIZER = settings['OPTIMIZER']
+
+    global SHOTS
+    SHOTS = settings['SHOTS']
+                
+    global BACKEND
+    BACKEND = settings['BACKEND']
+
+    global DEVICE
+    DEVICE = settings['DEVICE']
+
+    global SCALE_FACTORS
+    SCALE_FACTORS = settings['SCALE_FACTORS']
+
+    global POSTPROCESS
+    POSTPROCESS = settings['POSTPROCESS']
+
+    global ERROR_MITIGATION
+    ERROR_MITIGATION = settings['ERROR_MITIGATION']
+
+    global LAYERS
+    LAYERS = settings['LAYERS']
+
+    global HYPERPARAMETERS
+    HYPERPARAMETERS = settings['HYPERPARAMETERS']
+    # f was removed from HYPERPARAMETERS, this ensures old settings files can still run.
[…]

### 2025-04-07 src/qregress/quantum/QiskitRegressor.py

@@ -417,12 +417,3 @@ class QiskitRegressor:
 
 
 
-
-__all__ = ["QiskitRegressor"]
-
-# Clean up the module namespace
-# del np, time, joblib, dump, load, os, tqdm, mean_squared_error, r2_score
-# del mean_absolute_error, minimize, Pauli, SparsePauliOp, Operator
-# del StatevectorEstimator, Parameter, ParameterVector, generate_preset_pass_manager
-# del Estimator, QiskitRuntimeService, AerSimulator, NoiseModel, FakeQuebec, Batch
-

### 2025-04-07 src/qregress/scripts/cli_classical.py

@@ -1,53 +1,0 @@
-import click
-import joblib
-import json
-import pandas as pd
-import numpy as np
-
-from .Classical import run_models
-
-
-@click.command()
-@click.option('--scaler', type=click.Path(exists=True), required=True, help='File for y scaler to unscale after '
-                                                                            'prediction')
-@click.option('--train_set', type=click.Path(exists=True), required=True, help='File for train set')
-@click.option('--test_set', type=click.Path(exists=True), required=True, help='File for test set')
-@click.option('--save_plots', default=False, help="Don't use: depreceating soon... ")
-def main(scaler, train_set, test_set, save_plots):
-    train = joblib.load(train_set)
-    test = joblib.load(test_set)
-    X_tr = train['X']
-    X_te = test['X']
-    y_tr = np.array(train['y']).reshape(-1)
-    y_te = np.array(test['y']).reshape(-1)
-    scaler = joblib.load(scaler)
-
-    scores, y_tr_pred, y_te_pred = run_models(scaler, X_tr, y_tr, X_te, y_te, save_plots)
-
-    y_tr = scaler.inverse_transform(y_tr.reshape(-1, 1))
-    y_te = scaler.inverse_transform(y_te.reshape(-1, 1))
-
-    for (model_name, train_pred), (test_pred) in zip(y_tr_pred.items(), y_te_pred.values()):
-        name = model_name + '_predicted_values.csv'
-        train_pred = np.array(train_pred).reshape(-1).tolist()
-        y_tr = np.array(y_tr).reshape(-1).tolist()
-        test_pred = np.array(test_pred).reshape(-1).tolist()
-        y_te = np.array(y_te).reshape(-1).tolist()
-
-        df_train = pd.DataFrame({'Predicted': train_pred, 'Reference': y_tr})
-        df_train['Data'] = 'Train'
-        df_test = pd.DataFrame({'Predicted': test_pred, 'Reference': y_te})
-        df_test['Data'] = 'Test'
-        df = pd.concat([df_train, df_test], ignore_index=True)
-        df = df[['Data', 'Predicted', 'Reference']]
-
-        df.to_csv(name, index=False)
-        print(f'Saved predicted values as {name}')
-
-    with open('scores.json', 'w') as outfile:
-        json.dump(scores, outfile)
-        print(f'Scores saved as {outfile.name}. ')
-
-
-if __name__ == '__main__':
-    main()

### 2025-04-07 src/qregress/scripts/settings.py

@@ -1,191 +1,0 @@
-import json
-import click
-import os
-from ..quantum.circuits.Encoders import double_angle, single_angle, iqp_embedding, mitarai, composer, entangle_cz, entangle_cnot
-from ..quantum.circuits.Ansatz import HardwareEfficient, EfficientSU2, TwoLocal, ModifiedPauliTwo, HadamardAnsatz
-
-############################################
-#  Lists of acceptable values
-############################################
-
-
-ERROR_MITIGATION_LIST = {
-    'None': None,
-    'MITIQ_LINEAR': 'MITIQ_LINEAR',
-    'MITIQ_Richardson': 'MITIQ_Richardson',
-    'M3': 'M3',
-    'TREX': 'TREX'
-}
-
-POSTPROCESS_LIST = {
-    'None': None,
-    'simple': 'simple',
-    'ridge': 'ridge',
-    'lasso': 'lasso'
-}
-
-ENCODER_LIST = {
-    'M': mitarai,
-    'A1': single_angle,
-    'A2': double_angle,
-    'IQP': iqp_embedding,
-    'M-M-CNOT': composer(mitarai, entangle_cnot, mitarai, entangle_cnot),
-    'A1-A1-CNOT': composer(single_angle, entangle_cnot, single_angle, entangle_cnot),
-    'A2-A2-CNOT': composer(double_angle, entangle_cnot, double_angle, entangle_cnot),
-    'M-A1-CNOT': composer(mitarai, entangle_cnot, single_angle, entangle_cnot),
-    'M-A2-CNOT': composer(mitarai, entangle_cnot, double_angle, entangle_cnot),
-    'M-M-CZ': composer(mitarai, entangle_cz, mitarai, entangle_cz),
-    'A1-A1-CZ': composer(single_angle, entangle_cz, single_angle, entangle_cz),
-    'A2-A2-CZ': composer(double_angle, entangle_cz, double_angle, entangle_cz),
-    'M-A1-CZ': composer(mitarai, entangle_cz, single_angle, entangle_cz),
-    'M-A2-CZ': composer(mitarai, entangle_cz, double_angle, entangle_cz),
-}
-
-# TODO: Create a full list of ansatz to be used in the experiment
-ANSATZ_LIST = {
-    'HWE-CNOT': HardwareEfficient(),
-    'HWE-CZ': HardwareEfficient(entangle_type='CZ'),
[…]

### 2025-04-08 manuscript/main.tex
Tue  8 Apr 2025 14:18:37 EDT

@@
 Following the analysis of the RUD and number of ALs for both 5 qubit models, we explored claims that PQCs offer better model performance using fewer training points and hyperparameters\cite{schuld_circuit-centric_2020,du_expressive_2020,suzuki_predicting_2020} using learning curves.
-Our learning curves are generated varying the number of training points from 10-80\% of the total data, while fixing the number of test points to 20\% of the total dataset.
+We generate the learning curves by varying the number of training points from 10-80\% of the total data, while holding the number of test points to 20\% of the total dataset.
 In Fig.
 \ref{fig:learningcurves}, we analyze the effects of the number of training points of the best 5 qubit BSE49 and DDCC circuits, M-M-CZ{\_}HWE-CNOT using a RUD and AL of 1 and A2{\_}HWE-CNOT using a RUD of
-Next, we use learning curves, where the number of training points is varied, while the number of training points is varied to 
 For the BSE49 dataset, using 5 qubits, we found that M-M-CZ{\_}HWE-CNOT offers less overfit models, but offer poorer performance regarding the training and test set R$^{2}$s, as highlighted in Fig.
@@
 Unlike the training points, the test reaches peak performance when 70\% of the total data is used in the training set, with a test R$^{2}$ of 0.2064.
-
-When we analyze the effects of the number of training points on the DDCC dataset using the A2{\_}HWE-CNOT PQC, we found that
-
-A2{\_}HWE-CNOT has $3nvk$ trainable parameters
-
-Minimum number of classical parameters is $n+1$
+The A2{\_}HWE-CNOT circuit on the DDCC dataset has some similarities and difference when compared to M-M-CZ{\_}HWE-CNOT on the BSE49 dataset.
+One difference is that A2{\_}HWE-CNOT improves across the learning curve, with maximum R$^{2}$ of 0.8470 and 0.8492 for the training and test sets, respectively.
+A common feature between both models is that the classical models outperform the PQCs in both cases, but with the DDCC dataset the classical models do not exhibit overfitting and have R$^{2}$s greater than 0.98 across the full learning curve.
 

### 2025-04-09 manuscript/main.tex
Wed  9 Apr 2025 17:01:28 EDT

@@
 Using either formal mathematical proofs or numerical results based on empirical observations, QML has shown potential quantum speedups for various applications using a diverse set of implementations.\cite{biamonte_quantum_2017}
-While several classes of QML algorithms have shown promise for providing flexible ML models, parameterized quantum circuits (PQCs) are capable of achieving non-trivial results on near-term quantum hardware.
-PQCs formulate the ML algorithm as a variational problem optimized using a hybrid approach using both classical and quantum hardware.\cite{benedetti_parameterized_2019}
+While several classes of QML algorithms have shown promise for providing flexible ML models, parameterized quantum circuits (PQCs) can achieve non-trivial results on near-term quantum hardware.
+PQCs formulate the ML algorithm as a variational problem optimized using a hybrid approach using classical and quantum hardware.\cite{benedetti_parameterized_2019}
 Like classical ML approaches, PQCs have been applied for several chemistry use cases such as drug\cite{suzuki_predicting_2020,smaldone_quantum--classical_2024,bhatia_quantum_2023,kao_exploring_2023,li_quantum_2021,avramouli_quantum_2023,avramouli_unlocking_2023} and materials discovery\cite{ishiyama_noise-robust_2022,ryu_quantum_2023,vitz_hybrid_2024}, the prediction of proton affinities\cite{jin_integrating_2025}, and experimental molecular properties, including the log solubility in water, melting point, octanol/water distribution coefficient, and hydration free energy of small molecules in water.\cite{hatakeyama-sato_quantum_2023}
@@
 
-To maintain a general notation, in the following section, we follow the notations derived from  Ref. \citep{suzuki_predicting_2020}.
+In the following section, we adopt the notations derived from Ref. \citep{suzuki_predicting_2020} to maintain consistency.
 Encoding layers work by mapping a given $d$-dimensional feature vector, $\mathbf{x}=(x_{1}, x_{2}, \ldots, x_{d})^{T} \in \mathbb{R}^{d}$, normalized on the range $[-1,1]$, onto a quantum circuit using a unitary matrix, denoted as $U_{\Phi(\mathbf{x})}$, to produce the quantum state $U_{\Phi(\mathbf{x})}\ket{0}^{\otimes n}$, where $n$ is the number of qubits.
@@
 where $R^{Y}_{i}$ denotes a parameterized Y rotation gate on qubit $i$.
-Single-angle encoding, or qubit encoding, is structured similarly to a product of unentangled quantum states and have a similar mathematical structure as a product of local kernels where each $x_{i}$ is encoded in a local feature map.\cite{stoudenmire_supervised_2016,benedetti_parameterized_2019}
+Single-angle encoding, or qubit encoding, is structured similarly to a product of unentangled quantum states and has a similar mathematical structure as a product of local kernels where each $x_{i}$ is encoded in a local feature map.\cite{stoudenmire_supervised_2016,benedetti_parameterized_2019}
 
@@
 When $l=2$, more complex circuits can be generated, like in Ref.
-\citep{suzuki_predicting_2020}, where we choose the entanglement gates, $E_{\text{ent}}^{1}$ and $E_{\text{ent}}^{2}$, to be equivalent and the encoding layer takes the following form, $U_{\Phi(x)} =  E_{\text{ent}} U_{\phi_{2}(\mathbf{x})} E_{\text{ent}} U_{\phi_{1}(\mathbf{x})}$ .
+\citep{suzuki_predicting_2020}, where we choose the entanglement gates, $E_{\text{ent}}^{1}$ and $E_{\text{ent}}^{2}$, to be equivalent and the encoding layer takes the following form, $U_{\Phi(x)} =  E_{\text{ent}} U_{\phi_{2}(\mathbf{x})} E_{\text{ent}} U_{\phi_{1}(\mathbf{x})}$.
 Additionally, we exclude IQP encoding when $l=2$ due to the increased computational costs associated with the circuit depth when compared to the expanded models based on A1, A2, and M encoding.
@@
 	\end{tabular}
-	\caption{The 14 encoding layers used in this study where the first column shows the encoding circuit name, second column the unitary for $l=1$, third column the unitary for $l=2$, and last column the corresponding entanglement gates.}
+	\caption{The 14 encoding layers used in this study where the first column shows the encoding circuit name, the second column the unitary for $l=1$, the third column the unitary for $l=2$, and the last column the corresponding entanglement gates.}
 	\label{tab:encoders}
@@
 
-The last component of a PQC is measurement, which is required to recover the predicted target values, $\hat{y}_{i}$, of the machine learning model that is used to update the model parameters.
+The last component of a PQC is the measurement, which is required to recover the predicted target values, $\hat{y}_{i}$, of the machine learning model that is used to update the model parameters.
 This is performed by measuring the quantum state, $\ket{\Psi}$, using the Pauli Z operator on the first qubit denoted as,
@@
 In practice, all state-vector simulations were performed using PennyLane, while all calculations using \textit{FakeQuebec} and \textit{ibm\_quebec}  are run using Qiskit.
-All state-vector simulations with 5 qubits were optimized using 1000 iterations, while 16 qubit are initially ran using 250 iterations and longer runs, using 1000 iterations, use early stopping due to computational cost considerations.
-State-vector simulations were also optimized using the Simultaneous Perturbation Stochastic Approximation method (SPSA), as implemented in PennyLane since we found that SPSA requires less steps to optimize when compared to other optimizers for state-vector simulation.
+All state-vector simulations with 5 qubits were optimized using 1000 iterations, while 16 qubits were initially run using 250 iterations.
+State-vector simulations were also optimized using the Simultaneous Perturbation Stochastic Approximation method (SPSA), as implemented in PennyLane since we found that SPSA requires fewer steps to optimize when compared to other optimizers for state-vector simulation.
 For the experiments ran using \textit{FakeQuebec} and  \textit{ibm\_quebec}, we utilized the Constrained Optimization By Linear Approximation (COBYLA) optimizer, as implemented in SciPy\cite{virtanen_scipy_2020}.
@@
 In general, molecular representations can be partitioned into three groups, graph-, topology-, and physics-based representations, all of which were explored to provide a comprehensive overview of how they perform using classical models as a baseline.
-During the preprocessing stage, before converting to the XYZ coordinates into our molecular representation of choice, the set of hypothetical structures was reduced to 2436 molecules due to issues with valency exceptions when converting XYZ coordinates into RDKit mol objects.
+During the preprocessing stage, before converting the XYZ coordinates into our molecular representation of choice, the set of hypothetical structures was reduced to 2436 molecules due to issues with valency exceptions when converting XYZ coordinates into RDKit mol objects.
 Using RDKit\cite{noauthor_rdkit_nodate} we examined three commonly applied graph-based molecular preresentations, Molecular ACCess Systems (MACCS)\cite{durant_reoptimization_2002}, Morgan or extended-connectivity fingerprints \cite{morgan_generation_1965,rogers_extended-connectivity_2010}, and RDKit fingerprints.
@@
 As highlighted in Fig.
-\ref{fig:classical_molrepfig}, we found that the best molecular representation across all models test was Morgan fingerprints using the \textit{sub} formulation, which we use for all experiments using the PQCs.
+\ref{fig:classical_molrepfig}, we found that the best molecular representation across all models tested was Morgan fingerprints using the \textit{sub} formulation, which we use for all experiments using the PQCs.
 Additionally, one challenge of applying classical molecular representations for ML tasks using PQCs is reducing the set of features, often containing hundreds or thousands of features per sample, to the number of qubits used on the quantum device.
-For example, at the onset of this project the standard number of qubits on the IBM quantum devices was 5 or 16 qubits, which requires reducing the initial set of 2048 features per sample for Morgan fingerprints down to 5 or 16 features.
+For example, at the onset of this project, the standard number of qubits on the IBM quantum devices was 5 or 16 qubits, which requires reducing the initial set of 2048 features per sample for Morgan fingerprints down to 5 or 16 features.
 To perform this reduction, we explored two different methods, SHapley Additive ExPlanation analysis (SHAP)\cite{lundberg_unified_2017}, which uses cooperative game theory to determine feature importance, and principal component analysis (PCA), which is a dimensionality reduction technique that captures the direction a datasets variance, as implemented in scikit-learn.\cite{pedregosa_scikit-learn_2011}
@@
 Due to this important relationship, MP2 $t_{2}$-amplitudes are included in the DDCC feature set, along with the numerator ($\mel{ij}{}{ab}$), denominator ($\varepsilon_{i}+\varepsilon_{j}-\varepsilon_{a}-\varepsilon_{b}$), a binary feature to denote whether the excitation goes to the same virtual orbital, and the orbital energies ($\varepsilon_{i},\varepsilon_{j},\varepsilon_{a},\varepsilon_{b}$).
-Additionally, the feature set includes terms related to the individual contributions to the orbital energies, such as the one-electron Hamiltonian ($h$), Coulomb matrix ($J$), exchange matrix $K$, and Coulomb and exchange integrals ($J^{i}_{a},J^{j}_{b},K^{a}_{i},K^{b}_{j}$).
+Additionally, the feature set includes terms related to the individual contributions to the orbital energies, such as the one-electron Hamiltonian ($h$), Coulomb matrix ($J$), exchange matrix $K$, and Coulomb and exchange integrals ($J^{i}_{a}, J^{j}_{b}, K^{a}_{i}, K^{b}_{j}$).
 In total, there are 30 features for each CCSD $t_{2}$-amplitude due to the addition of features that denote the sign and magnitude of the MP2 $t_{2}$-amplitudes.
@@
 All HF, MP2, and CCSD data was generated using Psi4\cite{parrish_psi4_2017} and Psi4Numpy\cite{smith_psi4numpy_2018}.
-We will also note that despite using a minimal basis set, this is a data intensive quantum chemistry application for PQCs since for each molecule there are $(N_{occ})^{2}(N_{virt})^{2}$ $t_{2}$-amplitudes, where $N_{occ}$ denotes the number of occupied orbitals and $N_{virt}$ denotes the number of virtual orbitals.
+We will also note that despite using a minimal basis set, this is a data-intensive quantum chemistry application for PQCs since for each molecule there are $(N_{occ})^{2}(N_{virt})^{2}$ $t_{2}$-amplitudes, where $N_{occ}$ denotes the number of occupied orbitals and $N_{virt}$ denotes the number of virtual orbitals.
 For the water confirmers with 4 occupied and 2 virtual orbitals, there are a total of 64 $t_{2}$-amplitudes per molecule.
@@
 [introduction paragraph]
-In this section, for both the DDCC and BSE49 datasets, we start our analysis of by examining the performance of the initial set of 168 PQCs with re-upload depths of 1 ($k=1$) and the number ansatz layers set to 1 ($v=1$).
-Using this data, we select the best encoder-ansatz pair and increase the re-upload depth and number of ansatz layers to 3 and 5 ($k,v \in {3,5}$) to determine how model performance is effected by circuit depth.
+In this section, for both the DDCC and BSE49 datasets, we start our analysis by examining the performance of the initial set of 168 PQCs with re-upload depths of 1 ($k=1$) and the number ansatz layers set to 1 ($v=1$).
+Using this data, we select the best encoder-ansatz pair and increase the re-upload depth and number of ansatz layers to 3 and 5 ($k,v \in {3,5}$) to determine how model performance is affected by circuit depth.
 We then analyze how the best circuit from this set performs using a learning curve, where we hold the number of test points set to 20\% and vary the number of training points, to determine how PQCs behave with varying numbers of training data.
@@
 
-Starting with the 5 qubit BSE49 data, Fig.
+Starting with the 5 qubits BSE49 data, Fig.
 \ref{fig:5BSE_heatplots} highlights the performance of the 168 PQCs using a heat plot of the coefficients of determination (R$^{2}$) of the training (left) and test sets (right).
@@
 On average, the best encoding layer is M-M-CNOT with a training and test R$^{2}$s of -0.0173 and -0.0157, respectively.
-The best ansatz layer, is Full-CRX with an average training  R$^{2}$ of 0.1054 and test R$^{2}$ of 0.1165.
+The best ansatz layer is Full-CRX with an average training  R$^{2}$ of 0.1054 and test R$^{2}$ of 0.1165.
 Overall, for the BSE49 dataset using 5 qubits, the best encoder-ansatz pair is A1-A1-CNOT{\_}Full-CRX training set R$^{2}$ of 0.1775 and test set R$^{2}$ of 0.1974.
-Despite A1-A1-CNOT{\_}Full-CRX being the best encoder-ansatz pair, for explorations of the circuit depth, we chose M-M-CZ{\_}HWE-CNOT, which offers similar performance training set R$^{2}$ of 0.1566 and test set R$^{2}$ of 0.1740 but has offers a more shallow circuit, which is more computationally efficient for state-vector simulations.
+Despite A1-A1-CNOT{\_}Full-CRX being the best encoder-ansatz pair, for explorations of the circuit depth, we chose M-M-CZ{\_}HWE-CNOT, which offers similar performance training set R$^{2}$ of 0.1566 and test set R$^{2}$ of 0.1740 but has offered a more shallow circuit, which is more computationally efficient for state-vector simulations.
 
@@
 \ref{fig:16BSE_heatplots} shows the performance in R$^{2}$ for the training (left) and test (right) sets, where the best encoder-ansatz pair is A1{\_}Efficient-CRZ with an R$^{2}$ of -0.0007 for the training set and -0.0050 for the test set.
-Across the 168 PQCs, the training and test sets have a minimum R$^{2}$ -1.8104 and -1.7752, a mean of -0.4045 and -0.4022, a maximum of -0.0007 and -0.0004, and a standard deviation of 0.4161 and 0.4235,respectively.
+Across the 168 PQCs, the training and test sets have a minimum R$^{2}$ -1.8104 and -1.7752, a mean of -0.4045 and -0.4022, a maximum of -0.0007 and -0.0004, and a standard deviation of 0.4161 and 0.4235, respectively.
 Overall, as highlighted in Fig. \ref{fig:16BSE_boxplots} (left), the best encoder is IQP with a mean R$^{2}$ of -0.0942 for the training set and -0.0882 for the test set.
@@
 The best encoder-ansatz pair is A2{\_}HWE-CNOT with R$^{2}$s of 0.6191 and 0.6184, for the training and test sets, respectively.
-We found that the PQCs offer better model performance when ran on the DDCC dataset, with A1 offering the best average performance of the encoders with an R$^{2}$ of 0.0163 for the training set and 0.0183 for the test set (Fig.
+We found that the PQCs offer better model performance when run on the DDCC dataset, with A1 offering the best average performance of the encoders with an R$^{2}$ of 0.0163 for the training set and 0.0183 for the test set (Fig.
 \ref{fig:ddccboxplots} left).
@@
 Overall, for M-M-CZ{\_}HWE-CNOT using the BSE49 dataset, increasing the number of ALs and RUD offer negligible improvements over the base model, which as R$^{s}$ of 0.16 and 0.17 for the training and test set, respectively.
-The model with the best R$^{2}$ for the training set is the model initial model using an AL of 1 and RUD 1, while the model with the best R$^{2}$ for the test set uses a AL of 1 and RUD of 5 where the R$^{2}$ is 0.18.
+The model with the best R$^{2}$ for the training set is the model initial model using an AL of 1 and RUD 1, while the model with the best R$^{2}$ for the test set uses an AL of 1 and RUD of 5 where the R$^{2}$ is 0.18.
 When we analyze the distributions in \ref{fig:BSE5_distribution_parity}, we find that the reference target values have a wide distribution, ranging from 9.3800 to 177.2400 kcal/mol with a standard deviation of 27.4877 kcal/mol.
 For the predicted values, all of the models struggle with predicting an accurate range, where the model with the worst spread is AL=3/RUD=1 with a minimum of 67.6736 kcal/mol, maximum of 115.6791 kcal/mol, and standard deviation of 6.7346 kcal/mol.
-The best model, regarding the spread of the predicted data, is the AL=1/RUD=5, with a minimum of 49.8978 kcal/mol, maximum of 127.8078 kcal/mol, and standard deviation of 14.0201 kcal/mol. 
+The best model, regarding the spread of the predicted data, is the AL=1/RUD=5, with a minimum of 49.8978 kcal/mol, a maximum of 127.8078 kcal/mol, and standard deviation of 14.0201 kcal/mol. 
 Overall, all models, regardless of the number of ALs and RUD, tend to regress towards the mean value of the reference data, 90.6916 kcal/mol.
@@
 Fig.
-\ref{fig:ddccRUDAL_lineplot} highlights an interesting trend where as the number of ALs increases the model performance increases from R$^{2}$s of 0.62 to R$^{2}$s of $\approx 0.80$, for both the training and test sets.
-For the RUD, the R$^{2}$s show marginal improvements at $k=5,9$, while showing increased performance for $k=3,5$. 
+\ref{fig:ddccRUDAL_lineplot} highlights an interesting trend whereas the number of ALs increases the model performance increases from R$^{2}$s of 0.62 to R$^{2}$s of $\approx 0.80$, for both the training and test sets.
+For the RUD, the R$^{2}$s show marginal improvements at $k=5,9$ while showing increased performance for $k=3,5$. 
 Overall, the best model for A2{\_}HWE-CNOT with the DDCC dataset is the model with an AL of 5 and RUD of 1.
 This is highlighted in Fig.
-\ref{fig:ddccdistribution_parity}, where we see that the distribution of the predicted target values are closer to the spread of the reference values than the initial model with AL=1/RUD=1.
+\ref{fig:ddccdistribution_parity}, where we see that the distribution of the predicted target values is closer to the spread of the reference values than the initial model with AL=1/RUD=1.
 
@@
 	\end{subfigure}	
-	\caption{Line plots to highlight the performance as the number of ansatz layers (AL; left) and re-upload depth (RUD; right) increases for the 5 qubit (a) BSE49 and (b) DDCC data.
+	\caption{Line plots to highlight the performance as the number of ansatz layers (AL; left) and re-upload depth (RUD; right) increases for the 5 qubits (a) BSE49 and (b) DDCC data.
 Additionally, regression parity plots for each AL and RUD are shown for the (c) BSE49 and (d) DDCC data, where the x-axis denotes the predicted target values and the y-axis denotes the reference data.}
@@
 Following the analysis of the RUD and number of ALs for both 5 qubit models, we explored claims that PQCs offer better model performance using fewer training points and hyperparameters\cite{schuld_circuit-centric_2020,du_expressive_2020,suzuki_predicting_2020} using learning curves.
-We generate the learning curves by varying the number of training points from 10-80\% of the total data, while holding the number of test points to 20\% of the total dataset.
+We generate the learning curves by varying the number of training points from 10-80\% of the total data while holding the number of test points to 20\% of the total dataset.
 In Fig.
-\ref{fig:learningcurves}, we analyze the effects of the number of training points of the best 5 qubit BSE49 and DDCC circuits, M-M-CZ{\_}HWE-CNOT using a RUD and AL of 1 and A2{\_}HWE-CNOT using a RUD of
-For the BSE49 dataset, using 5 qubits, we found that M-M-CZ{\_}HWE-CNOT offers less overfit models, but offer poorer performance regarding the training and test set R$^{2}$s, as highlighted in Fig.
+\ref{fig:learningcurves}, we analyze the effects of the number of training points of the best 5 qubits BSE49 and DDCC circuits, M-M-CZ{\_}HWE-CNOT using a RUD and AL of 1 and A2{\_}HWE-CNOT using a RUD of
+For the BSE49 dataset, using 5 qubits, we found that M-M-CZ{\_}HWE-CNOT offers less overfit models, but offers poorer performance regarding the training and test set R$^{2}$s, as highlighted in Fig.
 \ref{fig:BSE5_learning_curves}.
@@
 Unlike the training points, the test reaches peak performance when 70\% of the total data is used in the training set, with a test R$^{2}$ of 0.2064.
-The A2{\_}HWE-CNOT circuit on the DDCC dataset has some similarities and difference when compared to M-M-CZ{\_}HWE-CNOT on the BSE49 dataset.
+The A2{\_}HWE-CNOT circuit on the DDCC dataset has some similarities and differences when compared to M-M-CZ{\_}HWE-CNOT on the BSE49 dataset.
 One difference is that A2{\_}HWE-CNOT improves across the learning curve, with maximum R$^{2}$ of 0.8470 and 0.8492 for the training and test sets, respectively.
-A common feature between both models is that the classical models outperform the PQCs in both cases, but with the DDCC dataset the classical models do not exhibit overfitting and have R$^{2}$s greater than 0.98 across the full learning curve.
+A common feature between both models is that the classical models outperform the PQCs in both cases, but with the DDCC dataset, the classical models do not exhibit overfitting and have R$^{2}$s greater than 0.98 across the full learning curve.
 
@@
 The y-axis denotes the R$^{2}$ of the training and test learning curves.
-Inlay plots show the training and test data for the classical models examined, where the bottom error bar denotes the minimum value, line the mean value, and top error bar the maximum value.}
+Inlay plots show the training and test data for the classical models examined, where the bottom error bar denotes the minimum value, the line is the mean value, and the top error bar is the maximum value.}
 	\label{fig:learningcurves}
@@
 
-\textbf{DDCC}
+1 iteration: 25004.5437 s
 
 Ansaetze analysis \cite{sim_expressibility_2019}
-``In particular, a substantial improvement in performance of two-qubit gates in a ring or all-to-all connected arrangement, compared to thatof those on a line, is observed.''
+``In particular, a substantial improvement in performance of two-qubit gates in a ring or all-to-all connected arrangement, compared to that of those on a line, is observed.''
 
-``Furthermore, improvement in both descriptors is achieved by sequences of controlled X-rotation gates compared tosequences of controlled Z-rotation gates.''
+``Furthermore, improvement in both descriptors is achieved by sequences of controlled X-rotation gates compared to sequences of controlled Z-rotation gates.''
 
-``investigated howexpressibility “saturates” with increased circuit depth, finding that the rateand saturated value appear to be distinguishing features of a PQC''
+``investigated how expressibility “saturates” with increased circuit depth, finding that the rate and saturated value appear to be distinguishing features of a PQC''
 
@@
 
+For the circuits we perform experiments with, there exists a quantum advantage regarding the time complexity of training the quantum circuit classically versus on the quantum hardware. 
+There is a very big caveat that must be addressed regarding the DDCC dataset.
+Classically the DDCC method can be efficiently optimized in $\mathcal{O}(n)$ to $\mathcal{O}(t \log n)$ time, versus the quantum algorithm that would require $\mathcal{O}(n 2^{2m})$ time.
+
 \begin{table}[h!]
@@
 	\end{tabular}
-	\caption{Comparison of models with respect to parameter count, two-qubit gate count, and circuit depth.}
+	\caption{Comparison of models concerning parameter count, two-qubit gate count, and circuit depth.}
 \end{table}
@@
 
-PQCs for the BSE49 and DDCC datasets do not exhibit an advantage concerning model accuracy, the number of training points, or time to train the models
+PQCs for the BSE49 and DDCC datasets do not exhibit an advantage concerning model accuracy, the number of training points, or the time to train the models.
 Poor performance on the BSE49 dataset could be explained by the feature space reduction, we are compressing the feature space from 2048 to 5 features (structure-based ML reps.
 require more features than physics-based reps.)
-While the physics-based feature set of DDCC outperforms the structure-based feature set of BSE49, DDCC requires too many device executions to be useful on the current generation of devices
+While the physics-based feature set of DDCC outperforms the structure-based feature set of BSE49, DDCC requires too many device executions to be useful in the current generation of devices
 For practitioners of quantum chemistry, who work on machine learning-related tasks, like Viki and me, several options exist:
@@
 The authors would also like to acknowledge Aviraj Newatia, who provided valuable insights with preliminary results excluded from this work.
-[somethings were ran on the MSRG cloud... do we need to cite the funders of our cloud???]
+[Some things were running on the MSRG cloud... do we need to cite the funders of our cloud???]
 [Viki: Did Nick have any special undergrad funding?]

### 2025-04-11 Pennylane_to_Qiskit/0.10_run/QiskitRegressor.py
update QiskitRegressor.py

@@ -205,7 +205,6 @@ class QiskitRegressor:
         else:
             with open(filename,'r') as f:
                 pred = np.hstack([np.vstack([r.data.evs for r in self.service.job(jid.strip()).result()]) for jid in f.readlines()])
-            print("GMJ get_results pred",len(pred),pred.shape)
              
         return pred   
 
@@ -292,11 +291,7 @@ class QiskitRegressor:
             mapped_circuits = [[[self._map2qiskit(x_i) for x_i in xi ] for xi in X[i : i + 4]] for i in range(0, len(X), 4)]
             tiled_params = np.tile(parameters,(X.shape[0],X.shape[1])).reshape(X.shape[0],X.shape[1],-1)
             batched_params = [tiled_params[i : i + 4] for i in range(0, len(X), 4)]
-            print("GMJ mapped_circuits",len(mapped_circuits))
-            print("GMJ tiled_params",tiled_params.shape,len(tiled_params))
-            print("GMJ batched_params",len(batched_params))
             #  Set some parameters to assist with writing to file
-            print("GMJ isinstance",isinstance(self._backend, str),self._backend)
             if isinstance(self._backend, str):
                 filename = None
                 file = None
@@ -306,7 +301,7 @@ class QiskitRegressor:
             # Submit jobs
             t0 = time.perf_counter()
             jobs = joblib.Parallel(n_jobs=self.n_jobs,verbose=0, prefer="threads")(joblib.delayed(self._batchmap)(idx,anz,pars,file) for idx, (anz, pars) in tqdm(enumerate(zip(mapped_circuits,batched_params)),desc="Mappings"))
-            print("GMJ jobs",len(jobs))
+            
             if isinstance(self._backend, str)==False:
                 # Close file after writing            
                 file.close() 
@@ -317,13 +312,13 @@ class QiskitRegressor:
         
 
             self.jobs = jobs
-            print("GMJ self.jobs",self.jobs)            
+                      
             t1 = time.perf_counter()
             if self.backendstr=='statevector' or self.backendstr=='fake':
                 y_pred = np.hstack(joblib.Parallel(n_jobs=self.n_jobs,verbose=0, prefer="threads")(joblib.delayed(self.get_results)(filename,job) for job in tqdm(self.jobs,desc="Running batch: "))).T
             else:
                 y_pred = self.get_results(filename)
-            print('GMJ predict',y_pred.shape)
+            
[…]

### 2025-04-11 src/qregress/quantum/QiskitRegressor.py

@@ -1,23 +1,24 @@
+import numpy as np
+import time
+import joblib
+from joblib import dump, load
+import os
+from tqdm.notebook import tqdm
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+from scipy.optimize import minimize
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+
 class QiskitRegressor:
-    import numpy as np
-    import time
-    import joblib
-    from joblib import dump, load
-    import os
-    from tqdm.notebook import tqdm
-    from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
-    from scipy.optimize import minimize
-    from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
-    from qiskit.primitives import StatevectorEstimator
-    from qiskit.circuit import Parameter, ParameterVector
-    from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
-    from qiskit.quantum_info import SparsePauliOp
-    from qiskit_ibm_runtime import EstimatorV2 as Estimator
-    from qiskit_ibm_runtime import QiskitRuntimeService
-    from qiskit_aer import AerSimulator
-    from qiskit_aer.noise import NoiseModel
-    from qiskit_ibm_runtime.fake_provider import FakeQuebec
-    from qiskit_ibm_runtime import Batch
     def __init__(self,
                  quantumcircuit,
                  numqubits,
@@ -290,7 +291,6 @@ class QiskitRegressor:
             mapped_circuits = [[[self._map2qiskit(x_i) for x_i in xi ] for xi in X[i : i + 4]] for i in range(0, len(X), 4)]
             tiled_params = np.tile(parameters,(X.shape[0],X.shape[1])).reshape(X.shape[0],X.shape[1],-1)
[…]

### 2025-04-11 manuscript/main.tex
update QiskitRegressor.py
upload manuscript

@@
 	\hfill	
-	\begin{subfigure}[b]{0.65\textwidth}
+	\begin{subfigure}[b]{0.49\textwidth}
 		\centering
@@
 
-	\begin{subfigure}[b]{0.65\textwidth}
+	\begin{subfigure}[b]{0.49\textwidth}
 		\centering
@@
 
-1 iteration: 25004.5437 s
+Following the evaluation of the learning curves, we decided to only run the A2{\_}HWE-CNOT circuit on real quantum hardware.
+Before running on the real hardware (\textit{ibm{\_}quebec}), we optimize the number of shots, the resilience level, and optimization using the \textit{FakeQuebec} backend with the \textit{qiskit-aer} plugin.
+Based on the results from the observations provided by the state vector learning curves (Fig.
+\ref{fig:ddcclearningcurves}), along with considerations regarding the computational cost associated with the query time to the IBM Quantum platform, number of training points ($N_{\text{occ}}^{2}N_{\text{virt}}^{2}$ $t_{2}$-amplitudes), along with the potential number of device executions associated with the number of shots, resilience (error mitigation) and optimization levels the total number of training data is reduced from 80\% to 10\% of the total training data.
+We validated this assumption using the \textit{ibm{\_}quebec} device using Twirled Readout Error eXtinction (TREX) \cite{van_den_berg_model-free_2022} error mitigation (resilience level 1), an optimization level of 2, with 3072 shots for both 10\%  and 80\% of the training data.
+Using one iteration, we found that one iteration using 10\% of the training data took 1824 s of wall time, versus one iteration using 80\% of the training data taking 25004 s of wall time.
+For a model that requires 500 or 1000 iterations to train, this would require approximately 145 to 289 days to train an end-to-end model using \textit{ibm{\_}quebec} using 80\% of the training data, versus 10 to 21 days required to train the model containing 10\% of the total data.
+While this is still much longer than the classical models, the value of running on real hardware is still a worthwhile experiment to show how these models behave on the current generation of hardware.
+
+To efficiently run the DDCC model on \textit{ibm{\_}quebec} the data is split into batches of 4 molecules per sample with 64 $t_{2}$-amplitudes each.
+The motivation for batching the data is to reduce the number of circuit executions per primitive unified blocs (PUBs).
+We found that for 500 iterations, an optimization level of X, with a resilience level of Y, using Z shots was adequate to reach satisfactory model performance using the \textit{FakeQuebec} backend (\textbf{Update these figures} Figs.
+\ref{fig:optresfakequebec} and \ref{fig:shotsfakequebec}).
+When applied on \textit{ibm{\_}quebec} we found that the models had R$^{2}$s of X and Y, for the training and test set, respectively, and took a total of X QPU time and Y wall time to complete.
 
@@
 
-5 qubit/5 ansatz layers: 2*5 + 3 * 5 * 5 = 85 parameters (75 trainable, 5 * 2 features)
-A2 $2n$ parameters
-HWE-CNOT $3nL$ parameters
-2 qubit gates $nL$
-Number of parameters (2n+3nL)=(2+3L)*n
-
-$n$, number of qubits and $L$, number of circuit layers
-
-To efficiently run DDCC on IBM Quebec, splitting the data into batches of $\approx 4$ samples with 64 $t_{2}$-amplitudes each.
-
-One iteration would require approximately $N_{\text{samples}} * N_{occ}^{2} * N_{virt}^{2} * N_{\text{shots}} * N_{\text{observables}}$ circuit executions (+ whatever SPSA costs to run per iteration)
-
-Ran using the state vector model parameters for one iteration to test the optimization and resilience levels using Fake Quebec before running on the real device
-
-$\{1024 \times x \vert  x \in [1,10]\}$
-
-Fake
-Optimization level 2 
-resilience level 0
-
-Regarding the number of circuit executions vs performance 3072 (1024 times 3) is the best number of shots
-
-Fig. \ref{fig:optresfakequebec}
-Fig. \ref{fig:shotsfakequebec}
-
-Real
-Optimization level 2 
-resilience level 1
-3072
-
-resilience level 2 is too expensive on the real device
-Regarding the number of circuit executions vs performance 3072 (1024 times 3) is the best number of shots
-
-Error handling for real run with iter>1
-
-For the experiments using the \textit{FakeQuebec} and \textit{ibm\_quebec} backends, we performed small tests, initialized using the state-vector parameters with one iteration, to determine the best circuit optimization and error mitigation (resilience) levels.
-
-optimization levels
-none (0), light (1), medium (2), high (3)
-
-resilience levels (error mitigation)
-none (0) 
 level 1 readout error mitigation and measurement twirling using Twirled Readout Error eXtinction (TREX) \cite{van_den_berg_model-free_2022}

### 2025-04-11 Pennylane_to_Qiskit/0.10_run/fake/ol0_rl0/fake.py

@@ -1,0 +1,217 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+
+import os
+n_jobs = 64
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm.notebook import tqdm
+# !{sys.executable} -m pip install qcircuit
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+from qiskit_ibm_runtime import exceptions
+# from qiskit_machine_learning.optimizers import SPSA, Minimizer
+
+
+from joblib import dump, load
+from QiskitRegressor import QiskitRegressor
+
+
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-04-11 Pennylane_to_Qiskit/0.10_run/fake/ol0_rl2/fake.py

@@ -1,0 +1,217 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+
+import os
+n_jobs = 64
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm.notebook import tqdm
+# !{sys.executable} -m pip install qcircuit
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+from qiskit_ibm_runtime import exceptions
+# from qiskit_machine_learning.optimizers import SPSA, Minimizer
+
+
+from joblib import dump, load
+from QiskitRegressor import QiskitRegressor
+
+
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-04-11 Pennylane_to_Qiskit/0.10_run/fake/ol1_rl0/fake.py

@@ -1,0 +1,217 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+
+import os
+n_jobs = 64
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm.notebook import tqdm
+# !{sys.executable} -m pip install qcircuit
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+from qiskit_ibm_runtime import exceptions
+# from qiskit_machine_learning.optimizers import SPSA, Minimizer
+
+
+from joblib import dump, load
+from QiskitRegressor import QiskitRegressor
+
+
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-04-11 Pennylane_to_Qiskit/0.10_run/fake/ol1_rl2/fake.py

@@ -1,0 +1,217 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+
+import os
+n_jobs = 64
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm.notebook import tqdm
+# !{sys.executable} -m pip install qcircuit
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+from qiskit_ibm_runtime import exceptions
+# from qiskit_machine_learning.optimizers import SPSA, Minimizer
+
+
+from joblib import dump, load
+from QiskitRegressor import QiskitRegressor
+
+
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-04-11 Pennylane_to_Qiskit/0.10_run/fake/ol2_rl0/fake.py

@@ -1,0 +1,217 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+
+import os
+n_jobs = 64
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm.notebook import tqdm
+# !{sys.executable} -m pip install qcircuit
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+from qiskit_ibm_runtime import exceptions
+# from qiskit_machine_learning.optimizers import SPSA, Minimizer
+
+
+from joblib import dump, load
+from QiskitRegressor import QiskitRegressor
+
+
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-04-11 Pennylane_to_Qiskit/0.10_run/fake/ol3_rl0/fake.py

@@ -1,0 +1,217 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+
+import os
+n_jobs = 64
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm.notebook import tqdm
+# !{sys.executable} -m pip install qcircuit
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+from qiskit_ibm_runtime import exceptions
+# from qiskit_machine_learning.optimizers import SPSA, Minimizer
+
+
+from joblib import dump, load
+from QiskitRegressor import QiskitRegressor
+
+
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
[…]

### 2025-04-11 Pennylane_to_Qiskit/0.10_run/fake/ol3_rl1/fake.py

@@ -1,0 +1,217 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+
+import os
+n_jobs = 64
+os.environ["OMP_NUM_THREADS"] = str(n_jobs)
+import joblib
+import click
+import json
+import time
+
+import itertools
+import collections.abc
+import sys
+from tqdm.notebook import tqdm
+# !{sys.executable} -m pip install qcircuit
+
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import pennylane as qml
+from sklearn.metrics import mean_squared_error, r2_score, mean_absolute_error
+
+# Qiskit
+from qiskit import QuantumCircuit
+from qiskit.quantum_info import Pauli, SparsePauliOp, Operator
+from qiskit.primitives import StatevectorEstimator
+from qiskit.circuit import Parameter, ParameterVector
+from qiskit.transpiler.preset_passmanagers import generate_preset_pass_manager
+from qiskit.quantum_info import SparsePauliOp
+from qiskit_ibm_runtime import EstimatorV2 as Estimator
+from qiskit_ibm_runtime import QiskitRuntimeService
+from qiskit_aer import AerSimulator
+from qiskit_aer.noise import NoiseModel
+from qiskit_ibm_runtime.fake_provider import FakeQuebec
+from qiskit_ibm_runtime import Batch
+from qiskit_ibm_runtime import exceptions
+# from qiskit_machine_learning.optimizers import SPSA, Minimizer
+
+
+from joblib import dump, load
+from QiskitRegressor import QiskitRegressor
+
+
+
+
+def mitarai(quantumcircuit,num_wires,paramname='x'):
+    # encoding as proposed by Mitarai et al.
+    num_features = num_wires
+    features = ParameterVector(paramname,num_features*2)
+    for i in range(num_wires):
+        feature_idx = i % num_features  # Calculate the feature index using modulo
+        quantumcircuit.ry(np.arcsin(features[feature_idx * 2]), i)
+        quantumcircuit.rz(np.arccos(features[feature_idx * 2 + 1] ** 2), i)
+
+
+def double_angle(quantumcircuit, num_wires,paramname='x'):
+    #  creates a circuit that encodes features into wires via angle encoding with an RY then RZ gate
+    #  the features are encoded 1-1 onto the qubits
[…]
